### 2019-02-28 BayesianCubaturePaper2018 - Rev1.tex
Restore the original submitted tex file

% This is a general template file for the LaTeX package SVJour3
% for Springer journals. Original by Springer Heidelberg, 2010/09/16
%
% Use it as the basis for your article. Delete % signs as needed.
%
% This template includes a few options for different layouts and
% content for various journals. Please consult a previous issue of
% your journal as needed.
%
\RequirePackage{amsmath}
\RequirePackage{fix-cm}
%
%\documentclass{svjour3}                     % onecolumn (standard format)
%\documentclass[smallcondensed]{svjour3}     % onecolumn (ditto)
%\documentclass[smallextended]{svjour3}       % onecolumn (second format)
\documentclass[twocolumn]{svjour3}          % twocolumn
%
\smartqed  % flush right qed marks, e.g. at end of proof
%
\usepackage{graphicx}
\usepackage{amssymb}
%
% insert here the call for the packages your document requires
%\usepackage{mathptmx}      % use Times fonts if available on your TeX system
%\usepackage{latexsym}
% etc.
%
% Jag's 
\usepackage{tabu}
\usepackage{cancel}
\usepackage{algorithm}
\usepackage{algorithmicx}
\usepackage{algpseudocode}
%\usepackage[caption=false]{subfig}
\usepackage{subcaption}
\usepackage{booktabs, mathtools}
\usepackage[dvipsnames]{xcolor}
\usepackage{url}
%\usepackage{refcheck}  % points out unused labels, refs ...

\captionsetup{compatibility=false}

\algdef{SE}[DOWHILE]{Do}{doWhile}{\algorithmicdo}[1]{\algorithmicwhile\ #1}%

\DeclareMathOperator{\Order}{{\mathcal O}}

% please place your own definitions here and don't use \def but
% \newcommand{}{}
\newtheorem{prop}{Proposition}
\providecommand{\HickernellFJ}{Hickernell}
\newcommand{\bm}[1]{\boldsymbol{#1}}
\newcommand{\mSigma}{\mathsf{\Sigma}}
\newcommand{\mB}{\mathsf{B}}
\newcommand{\smallocite}[1]{{\small\ocite{#1}}}
% \newcommand{\bm}[1]{\boldsymbol{#1}}
\newcommand{\dif}[1]{\text{d}{#1}}
\newcommand{\D}[1]{\text{d}{#1}}
\newcommand{\trace}[1]{\textup{trace}{#1}}

\newcommand{\naturals}{\mathbb{N}}
\newcommand{\natzero}{\mathbb{N}_0}
\newcommand{\reals}{\mathbb{R}}
\newcommand{\integers}{\mathbb{Z}}
\newcommand{\posIntegers}{\mathbb{Z}_{> 0}}
\newcommand{\complex}{\mathbb{C}}
\newcommand{\hilbert}{\mathbb{H}}
\newcommand{\Ex}{\mathbb{E}}

\newcommand{\cf}{\mathcal{F}}
\newcommand{\cx}{\mathcal{X}}
\newcommand{\tcx}{\widetilde{\cx}}
\newcommand{\rC}{\mathring{C}}
\newcommand{\rlambda}{\mathring{\lambda}}

\newcommand{\valpha}{{\bm{\alpha}}}
\newcommand{\vbeta}{{\bm{\beta}}}
\newcommand{\vDelta}{{\boldsymbol{\Delta}}}
\newcommand{\vlambda}{{\bm{\lambda}}}
\newcommand{\vphi}{{\bm{\phi}}}
\newcommand{\vpsi}{{\bm{\psi}}}
\newcommand{\vtheta}{{\bm{\theta}}}
\newcommand{\vzeta}{{\bm{\zeta}}}
\newcommand{\vthetaMLE}{\bm{\theta}_{\text{MLE}}}
\newcommand{\hvtheta}{\hat{\vtheta}}
\newcommand{\va}{\bm{a}}
\newcommand{\vA}{\bm{A}}
\newcommand{\vb}{\bm{b}}
\newcommand{\vc}{\bm{c}}
\newcommand{\vC}{\bm{C}}
\newcommand{\tvc}{\tilde{\bm{c}}}
\newcommand{\vg}{\bm{g}}
\newcommand{\vh}{\bm{h}}
\newcommand{\vf}{\bm{f}}
\newcommand{\vk}{\bm{k}}
\newcommand{\vm}{\bm{m}}
\newcommand{\vs}{\bm{s}}
\newcommand{\vt}{\bm{t}}
\newcommand{\vv}{\bm{v}}
\newcommand{\vV}{\bm{V}}
\newcommand{\vw}{\bm{w}}
\newcommand{\vW}{\bm{W}}
\newcommand{\vx}{\bm{x}}
\newcommand{\dx}{\dif{{x}}}
\newcommand{\dt}{\dif{{t}}}
\newcommand{\dvx}{\dif{\bm{x}}}
\newcommand{\dvs}{\dif{\bm{s}}}
\newcommand{\dvt}{\dif{\bm{t}}}
\newcommand{\vrho}{\bm{\rho}}
\newcommand{\hy}{\hat{y}}
\newcommand{\vy}{\bm{y}}
\newcommand{\vY}{\bm{Y}}
\newcommand{\hvy}{\hat{\vy}}
\newcommand{\vz}{\bm{z}}
\newcommand{\vZ}{\bm{Z}}
\newcommand{\dvz}{\dif{\bm{z}}}
\newcommand{\tf}{\tilde{f}}
\newcommand{\vPsi}{\boldsymbol{\Psi}}

\newcommand{\tvv}{\tilde{\vv}}
\newcommand{\tvz}{\tilde{\vz}}

\newcommand{\vCvtheta}{{C_\vtheta}}
\newcommand{\hc}{\widehat{c}}

\newcommand{\hatvy}{\hat{\bm{y}}}
\newcommand{\haty}{\hat{y}}
\newcommand{\tvy}{\tilde{\bm{y}}}
\newcommand{\ty}{\tilde{y}}
\newcommand{\vzero}{\bm{0}}
\newcommand{\vone}{\bm{1}}
\newcommand{\tvone}{\tilde{\bm{1}}}
\newcommand{\mA}{\mathsf{A}}
\newcommand{\mC}{\mathsf{C}}
\newcommand{\rmC}{\mathring{\mathsf{C}}}
\newcommand{\mCtheta}{{\mathsf{C}_{\vtheta}}}
%\newcommand{\mCthetaInv}{{\mathsf{C}^{-1}_{\vtheta}}}
%\newcommand{\mCthetaMLE}{{\mathsf{C}_{\vthetaMLE}}}
%\newcommand{\mCthetaInvMLE}{{\mathsf{C}^{-1}_{\vthetaMLE}}}
\newcommand{\mCInv}{{\mathsf{C}^{-1}}}
\newcommand{\cov}{{\textup{cov}}}
\newcommand{\var}{{\textup{var}}}

\newcommand{\tmC}{\widetilde{\mathsf{C}}}
\newcommand{\tlambda}{\tilde{\lambda}}

\newcommand{\mL}{\mathsf{L}}

\newcommand{\mLambda}{\mathsf{\Lambda}}
\newcommand{\mLambdaInv}{\mathsf{\Lambda}^{-1}}

\newcommand{\mV}{\mathsf{V}}
\newcommand{\mW}{\mathsf{W}}

\newcommand{\calN}{\mathcal{N}}
\newcommand{\me}{\mathrm{e}}

\newcommand{\tvrho}{\widetilde{\vrho}}
\newcommand{\heta}{\hat{\eta}}
\newcommand{\hmu}{\widehat{\mu}}
\newcommand{\hsigma}{\widehat{\sigma}}
\newcommand{\hnu}{\hat{\nu}}
\newcommand{\rhoCond}{\mathring{\vrho}}

\newcommand{\MVN}{\textup{MVN}}
\newcommand{\MLE}{\textup{MLE}}
\newcommand{\full}{\textup{full}}
\newcommand{\GCV}{\textup{GCV}}
%\newcommand{\errtol}{\text{tol}}
\newcommand{\errtol}{\varepsilon}
\newcommand{\errn}{\text{err}_{n}}
\newcommand{\diag}{\text{diag}}
\newcommand{\err}{\textup{err}}
\newcommand{\code}[1]{\texttt{#1}}

\def\abs#1{\ensuremath{\left \lvert #1 \right \rvert}}
\newcommand{\norm}[2][{}]{\ensuremath{\left \lVert #2 \right \rVert}_{#1}}
\newcommand{\ip}[3][{}]{\ensuremath{\left \langle #2, #3 \right \rangle_{#1}}}

\newenvironment{nalign}{
    \begin{equation}
    \begin{aligned}
}{
    \end{aligned}
    \end{equation}
    \ignorespacesafterend
}

\providecommand{\argmin}{\operatorname*{argmin}}
\providecommand{\argmax}{\operatorname*{argmax}}
\newcommand\figref{Figure~\ref}
\newcommand\secref{Section~\ref}

\graphicspath{{.}{./figures/}{D:/Mega/MyWriteupBackup/Sep_2ndweek_1/}}
%\graphicspath{{./figures/}}

%
% Insert the name of "your journal" with
\journalname{Automatic Bayesian Cubature}
%

\newcommand{\FJHNote}[1]{{\textcolor{blue}{FJH: #1}}}
\newcommand{\JRNote}[1]{{\textcolor{green}{JR: #1}}}

%\allowdisplaybreaks[4]
\begin{document}
\setlength\abovedisplayskip{1pt}
\setlength{\belowdisplayskip}{1pt}

\title{Fast Automatic Bayesian Cubature Using Lattice Sampling
%\thanks{}
}
% Grants or other notes about the article that should go on the front
% page should be placed within the \thanks{} command in the title
% (and the %-sign in front of \thanks{} should be deleted)
%
% General acknowledgments should be placed at the end of the article.

%\subtitle{Do you have a subtitle?\\ If so, write it here}

%\titlerunning{Short form of title}        % if too long for running head

\author{R. Jagadeeswaran         \and
        Fred J. Hickernell %etc.
}

%\authorrunning{Short form of author list} % if too long for running head

\institute{R. Jagadeeswaran \at
              Department of Applied Mathematics, \\
              Illinois Institute of Technology \\
              10 W. 32nd St., Room 208\\
              Chicago IL 60616\\
              \email{jrathin1@iit.edu}           %  \\
%             \emph{Present address:} of F. Author  %  if needed
           \and
           Fred J. Hickernell \at
           Center for Computational Science and Department of Applied Mathematics, 
           Illinois Institute of Technology \\
           PS 106, 3105 S. Dearborn St., 
           Chicago IL 60616
           \\
           \email{hickernell@iit.edu} 
}

\date{Received: date / Accepted: date}
% The correct dates will be entered by the editor

\maketitle

\begin{abstract}
Automatic cubatures approximate multidimensional integrals to user-specified error tolerances.  For high dimensional problems, it makes sense to fix the sampling density but determine the 
sample size, $n$, automatically. Bayesian cubature postulates that the integrand is an instance of a stochastic process.  Here we assume a Gaussian process parameterized by a constant mean and a covariance function defined by a scale parameter times a parameterized function specifying how the integrand values at two different points in the domain are related.
These parameters are estimated from integrand values or are given non-informative priors.  The sample size, $n$, is chosen to make the half-width of the credible interval for the Bayesian posterior mean no greater than the error tolerance.

The process just outlined typically requires vector-matrix operations  with a computational cost of $O(n^3)$. Our innovation is to pair low discrepancy nodes with matching kernels that lower the  computational cost to $O(n \log n)$.   This approach is demonstrated using rank-1 lattice sequences and shift-invariant kernels.  Our algorithm is  implemented in the Guaranteed Automatic Integration Library (GAIL).

\keywords{Bayesian cubature \and Fast automatic cubature \and GAIL \and Probabilistic numeric methods }
% \PACS{PACS code1 \and PACS code2 \and more}
% \subclass{MSC code1 \and MSC code2 \and more}
\end{abstract}

\section{Introduction}
\label{intro}
Cubature is the problem of inferring a numerical value for an integral, 
$ \mu := \int_{\reals^d} g(\vx) \, \dif \vx$, where $\mu$ has no closed form analytic expression. Typically, $g$ is accessible as a black-box algorithm. 
Cubature is a key component of many problems in scientific computing, finance, statistical modeling, and machine learning.

The integral may often be expressed as
\begin{align}
\label{eqn:defn_mu}
\mu:= \Ex[f(\boldsymbol{X})] = \int_{[0,1]^d} f(\vx)\, \dif\vx, 
\end{align}
where $f:[0,1]^d \to \reals$ is the integrand, and $\boldsymbol{X} \sim \mathcal{U}[0,1]^d$.  The process of transforming the original integral into the form of \eqref{eqn:defn_mu} is not addressed here. See \cite[Section 2.11]{DicEtal14a} 
for a discussion of variable transformations. The cubature may be an affine function of integrand values:
\begin{align}
\label{eqn:defn_hmu}  % remove this
\hmu := w_0 + \sum_{i=1}^{n} f(\vx_i) w_i,
\end{align}
where the weights, $w_0$, and  $\vw = (w_i)_{i=1}^n \in \reals^n$, and the nodes, $\{\vx_i\}_{i=1}^n \subset [0,1]^d$, are chosen to make the error, $\abs{\mu - \hmu}$, small. The integration domain $[0,1]^d$ is convenient for the low discrepancy node sets \cite{DicEtal14a,SloJoe94} that we use.  The nodes are assumed to be deterministic.

We construct a reliable stopping criterion that determines the number of integrand values, $n$, required to ensure that the error is no greater than a user-defined error tolerance denoted by $\varepsilon$, i.e., 
\begin{align}
\label{eqn:err_crit} 
\abs{\mu - \hmu} \leq \errtol .
\end{align}
Rather than relying on strong assumptions about the integrand, such as an upper bound on its variance or total variation, we construct a stopping criterion that is based on a credible interval arising from a Bayesian approach to the problem.  We build upon the work of Briol et al.~\cite{BriEtal18a}, Diaconis~\cite{Dia88a}, O'Hagan~\cite{OHa91a}, Ritter~\cite{Rit00a}, Rasmussen and Ghahramani~\cite{RasGha03a}, and others.  Our algorithm is an example of \emph{probabilistic numerics}.

The primary contribution of this article is to demonstrate how the choice of a family of covariance kernels that match the low discrepancy sampling nodes facilitates fast computation of the cubature and the data-driven stopping criterion.  Our cubature requires $n$ function values---at a cost of $\$(f)$ each---plus $\Order(n \log(n))$ operations to check whether the error tolerance is satisfied.  The total cost of our algorithm is then $\Order(n [\$(f) + \log(n)])$.  This is significantly fewer operations than the $\Order(n^3)$ typically required for Bayesian cubature.  If function evaluation is expensive, then $\$(f)$ might be similar in magnitude to $\log(n)$.

Hickernell~\cite{Hic17a} compares different approaches to cubature error analysis depending on whether the rule is deterministic or random and whether the integrand is assumed to be deterministic or random.  Error analysis that assumes a deterministic integrand lying in a Banach space leads to an error bound that is typically impractical for deciding how large $n$ must be to satisfy \eqref{eqn:err_crit}.  The deterministic error bound includes a (semi-) norm of the integrand, often called the variation, which is often more complex to compute than the original integral.

Hickernell and Jim\'enez-Rugama~\cite{HicJim16a,JimHic16a} have developed stopping criteria for cubature rules based on low discrepancy nodes by tracking the decay of the discrete Fourier coefficients of the integrand.  The algorithm proposed here also relies on discrete Fourier coefficients, but in a different way.  Although we only explore automatic Bayesian cubature for absolute error tolerances, the recent work by Hickernell, Jim\'enez-Rugama, and Li~\cite{HicEtal17a} suggests how one might accommodate more general error criteria, such as relative error tolerances.

Section \ref{sec:BC} explains the Bayesian approach to estimate the posterior cubature error and defines our automatic Bayesian cubature. Although much of this material is known, it is included for completeness.  We end Section \ref{sec:BC}  by demonstrating why Bayesian cubature is typically computationally expensive.
Section \ref{sec:fast_BC}  introduces the concept of covariance kernels that match the nodes and expedite the computations required by our automatic Bayesian cubature. 
Section \ref{sec:shift_invariant_kernel} implements this concept for shift invariant kernels and rank-1 lattice nodes.  It also describes how to avoid cancellation error for kernels of product form.  Numerical examples are provided in Section \ref{sec:NumExp} to demonstrate our new algorithm.  We conclude with a brief discussion.

\section{Bayesian Cubature} \label{sec:BC}

\subsection{Bayesian posterior error}
\label{sec:BayesPostErr}

Suppose that the integrand, $f$, is drawn from a Gaussian process, i.e., $f \sim \mathcal{GP}(m,s^2 C_\vtheta)$.  Specifically, $f$ has real-valued constant mean $m$ and covariance function $s^2C_\vtheta$, where $s$ is a non-negative scale factor, and $C_\vtheta: [0,1]^d \times [0,1]^d \to \mathbb{R} $ is a symmetric, positive-definite function and parameterized by $\vtheta$:
\begin{multline} \label{FJH:eq:CondPosDef}
\mC^T = \mC,  \quad \va^T \mC \va > 0, \quad \text{where }  \mC = \left(  C_\vtheta(\vx_i,\vx_j)  \right)_{i,j=1}^n,\\
 \text{for all } \va \ne 0, \;
 n\in \mathbb{N}, \; \vx_1, \ldots, \vx_n \in [0,1]^d.
\end{multline}
The function, $C_{\vtheta}$, and the Gram matrix, $\mC$ depend implicitly on $\vtheta$, but the notation may omit this parameter for simplicity's sake.

For a Gaussian process, all vectors of linear functionals of $f$ have a multivariate Gaussian distribution. Defining  $\vf  := \left( f(\vx_i)\right)_{i=1}^n$ as the multivariate normal vector of function values, it follows that 
\begin{subequations} \label{eqn:fGaussDist}
\begin{align}
\vf  & \sim \calN(m \vone, s^2 \mC), \\
\nonumber & \qquad \qquad \text{where $\vone$ is a vector of all ones,}\\
\mu & \sim \calN(m, s^2 c_0), 
\\
\text{where }
c_0 &= \int_{[0,1]^{d}\times [0,1]^{d}} C_\vtheta(\vx,\vt) \, \dif{\vx} \, \dif{\vt}, \\
\cov(\vf, \mu) &= \left(  \int_{[0,1]^d} C(\vt,\vx_i) \, \D \vt \right)_{i=1}^n  =: \vc.
\end{align}
\end{subequations}
We need the following lemma on conditional normal distribution to derive the distribution of the posterior error of our cubature.

\begin{lemma} \cite[(A.6), (A.11--13)]{RasWil06a} \label{thrm:condDist} If $\vY = (\vY_1, \vY_2)^T \sim \calN (\vm,\mSigma)$, where $\vY_1$ and $\vY_2$ are random vectors of arbitrary length, and 
	\begin{gather*}
	\vm = \begin{pmatrix} \vm_1 \\ \vm_2 \end{pmatrix} = \begin{pmatrix} \Ex(\vY_1) \\ \Ex(\vY_2) \end{pmatrix}, \\
	\mSigma = \begin{pmatrix}
	\mSigma_{11} & \mSigma_{21}^T \\ 	\mSigma_{21} & \mSigma_{22}
	\end{pmatrix} =
	\begin{pmatrix}
	\var(\vY_{1}) & \cov(\vY_{1}, \vY_2) \\ 	\cov(\vY_2,\vY_{1}) & \var(\vY_{2})
	\end{pmatrix} 
	\end{gather*}
	then 
	\begin{multline*}
	\vY_1 \vert \vY_2 \; \sim \; \calN \bigl(\vm_1 + \mSigma_{21}^T \mSigma_{22}^{-1}(\vY_2 - \vm_2), \\ \mSigma_{11} - \mSigma_{21}^T \mSigma_{22}^{-1} \mSigma_{21} \bigr).
	\end{multline*}
Moreover, the inverse of the matrix $\mSigma$ may be partitioned as
\begin{gather*}
\mSigma^{-1} = \begin{pmatrix} \mA_{11} & \mA_{21}^T \\ \mA_{21} & \mA_{22} \end{pmatrix}, \\
\mA_{11} = (\mSigma_{11} - \mSigma_{12} \mSigma_{22}^{-1} \mSigma_{21})^{-1}, \qquad 
\mA_{21} = -  \mSigma_{22}^{-1} \mSigma_{21} \mA_{11}, \\ 
\mA_{22} = \mSigma_{22}^{-1} + \mSigma_{22}^{-1} \mSigma_{21} \mA_{11} \mSigma_{21}^T \mSigma_{22}^{-1}.
\end{gather*}

\end{lemma}

It follows from Lemma \ref{thrm:condDist} that the \emph{conditional} distribution of the integral given observed function values, $\vf = \vy$ is also Gaussian:
\begin{multline} \label{eqn:condInteg}
\mu | (\vf = \vy) \sim \calN \bigl(m (1 - \vc^T \mC^{-1} \vone)  + \vc^T \mC^{-1} \vy, 
\\
s^2(c_0  -\vc ^T \mC^{-1} \vc) \bigr).
\end{multline}
The natural choice for  the cubature is the posterior mean of the integral, namely, 
\begin{align}
\label{eqn:BayesCub}
\widehat{\mu}  \vert ( \vf = \vy)
= m(1 - \vc^T  \mC^{-1} \vone)
+ \vc^T \mC^{-1} \vy,
\end{align}
which takes the form of \eqref{eqn:defn_hmu}.
Under this definition, the cubature error has zero mean and a variance depending on the choice of nodes:
\begin{align*}
%\label{eqn_error_cond_prob}
(\mu-\hmu) | (\vf = \vy)
 \sim  \calN 
\left(
0, \;
s^2 (c_0 - \vc^T\mC^{-1}\vc) 
\right).
\end{align*}
A credible interval for the integral is given given by 
\begin{subequations} \label{eqn_prob_confidence_interval}
\begin{gather}
\mathbb{P}_f \left[
|\mu-\hmu| \leq \err_{\textup{CI}}
\right] = 99\%, \\
\err_{\textup{CI}} = 2.58 s \sqrt{c_0 - \vc^T\mC^{-1}\vc}
\end{gather}
\end{subequations}
Naturally, $2.58$ and $99\%$ can be replaced by other quantiles and credible levels.

\subsection{Parameter estimation}
The credible interval in \eqref{eqn_prob_confidence_interval} suggests how our automatic Bayesian cubature proceeds.  Integrand data is accumulated until the width of the credible interval, $\err_{\textup{CI}}$, is no greater than the error tolerance.  As $n$ increases, one expects $\sqrt{c_0 - \vc^T\mC^{-1}\vc}$ to decrease for well-chosen nodes, $\{\vx_i\}_{i=1}^n$.

Note that $\err_{\textup{CI}}$ has no explicit dependence on the integrand values, even though one would intuitively expect that larger integrand should imply a  larger $\err_{\textup{CI}}$.  This is because parameters, $m, s$, and $\vtheta$, have not yet been inferred from integrand data.  After inferring the parameters, $\err_{\textup{CI}}$ does reflect the size of the integrand values. This section describes three approaches to parameter estimation.

\subsubsection{Empirical Bayes}  \label{sec:MLE}
One approach is to estimate the parameters is via maximum likelihood estimation (MLE).  The log-likelihood function of the parameters given the function data $\vy$ is:
\begin{multline*}
l(s,m,\vtheta | \vy)
= -\frac{1}{2} s^{-2} (\vy-m\vone)^T\mCInv(\vy-m\vone) 
\\
 - \frac{1}{2} \log(\det\, \mC) - \frac{n}{2} \log(s^2) + \text{constants.}
\end{multline*}
Maximizing the log-likelihood first with respect to $m$, then with respect to $s$, and finally with respect to $\vtheta$ yields
\begin{align}
\label{eqn_m_MLE}
m_\MLE &= \frac{\vone^T \mCInv \vy }{ \vone^T \mCInv \vone}, \\
\nonumber
s^2_{\MLE}  
&= \frac{1}{n} (\vy-m_{\MLE}\vone)^T\mCInv(\vy-m_{\MLE}\vone) 
\\
\label{eqn_s2_MLE}
&= 
\frac{1}{n}
\vy^T 
\left[ 
\mCInv - 
\frac{ \mCInv \vone \vone^T \mCInv }{\vone^T\mCInv \vone}
\right] \vy, 
\end{align}
To obtain $\vtheta_\MLE$, substitute $m_\MLE$ and $s_\MLE$ into $l(s,m,\vtheta | \vy)$ and then numerically minimize
\begin{align}
\nonumber
\vtheta_\MLE
&= \argmin_{\vtheta} \biggl \{
\log\left(\vy^T 
\left[ \mCInv - 
\frac{ \mCInv \vone \vone^T \mCInv }{\vone^T\mCInv \vone}
\right] \vy 
\right)  \\
\label{eqn:thetaMLE}
 & \qquad +  \frac{1}{n} \log(\det(\mC))
\biggr \}.
\end{align}
The MLE estimate of $\vtheta$ balances minimizing the covariance scale factor, $s^2_{\MLE}$, against minimizing  $\det(\mC)$.

Under these estimates of the parameters, the cubature \eqref{eqn:BayesCub} and the credible interval \eqref{eqn_prob_confidence_interval} are explicitly written as
\begin{align} \label{eqn:cubMLE}
\hmu_\MLE  &= 
\left(
\frac{ (1 - \vone^T  \mCInv\vc )  \vone }{ \vone^T \mCInv \vone}   +  \vc 
\right)^T  \mCInv \vy, \\
\nonumber 
\err_\MLE^2 & : = \frac{2.58^2}{n}
 \vy^T \left[ \mCInv - 
\frac{ \mCInv \vone \vone^T \mCInv }{\vone^T\mCInv \vone}
\right] \vy \\
\label{eqn:errMLE}
&\qquad \qquad \times 
(c_0 - \vc^T\mC^{-1}\vc ),
\end{align}
\begin{align}
\label{eqn_prob_CI_MLE}
\mathbb{P}_f \left[
|\mu-\hmu_\MLE| \leq \err_\MLE \right]  = 99\%.
\end{align}
Here $c_0$, $\vc$, and $\mC$ are assumed implicitly to be based on $\vtheta = \vtheta_\MLE$.

\subsubsection{Full Bayes}

Rather than use maximum likelihood to determine $m$ and $s$ one can treat them as hyperparameters with a non-informative, conjugate prior, namely $\vrho_{m,s^2}(\xi, \lambda) \propto 1/\lambda$. Then the posterior density for the integral given the data using Bayes theorem is
\begin{align*}
\MoveEqLeft[1]{\rho_{\mu}(z | \vf = \vy)} \\
& \propto \int_{0}^\infty \int_{-\infty}^\infty \rho_{\mu}(z | \vf = \vy, m = \xi, s^2 = \lambda) \\
& \hspace{2.5cm} \times  \rho_{\vf}(\vy | \xi, \lambda ) \rho_{m, s^2}(\xi, \lambda) \, \D \xi \D \lambda \\
& \propto \displaystyle \int_{0}^\infty  \frac{1}{\lambda^{(n+3)/2}} \\
& \times \int_{-\infty}^\infty  \exp \biggl( -\frac{1}{2\lambda}\biggl\{
\frac{
[z - \xi (1 - \vc^T \mC^{-1} \vone)  -  \vc^T \mC^{-1} \vy]^2}
{c_0  -\vc ^T \mC^{-1} \vc}  \\
& \hspace{1.8cm} + (\vy - \xi \vone)^T \mC^{-1}(\vy - \xi \vone) \biggr \} \biggr) \, \D \xi \D \lambda \\
& \hspace{2.5cm}
\text{by \eqref{eqn:fGaussDist}, \eqref{eqn:condInteg}} \; \text{and} \; \rho_{m,s^2}(\xi,\lambda) \propto 1/\lambda \\
& \propto \displaystyle \int_{0}^\infty  \frac{1}{\lambda^{(n+3)/2}} \cdots \\ 
& \qquad \cdots \int_{-\infty}^\infty  \exp\left( -\frac{\alpha \xi^2 -2 \beta \xi + \gamma}{2\lambda(c_0  -\vc ^T \mC^{-1} \vc)} \right) \, \D \xi \D \lambda, \\
\intertext{where}
\alpha & = (1 - \vc^T \mC^{-1} \vone)^2 + \vone^T \mC^{-1} \vone (c_0  -\vc ^T \mC^{-1} \vc),\\
\beta & =(1 - \vc^T \mC^{-1} \vone)(z - \vc^T \mC^{-1} \vy ) \\
& \qquad \qquad  + \vone^T \mC^{-1} \vy (c_0  -\vc ^T \mC^{-1} \vc),\\
\gamma &  = (z - \vc^T \mC^{-1} \vy )^2  + \vy^T \mC^{-1} \vy (c_0  -\vc ^T \mC^{-1} \vc).
\end{align*}
In the derivation above and below, factors that are independent of $\xi$, $\lambda$, or $z$ can be discarded since we only need to preserve the proportion.  But, factors that depend on $\xi$, $\lambda$, or $z$ must be kept.  
%Completing the square allows us to compute the integral with respect to $\xi$:
Completing the square, $
\alpha \xi^2 -2 \beta \xi + \gamma 
= \alpha (\xi -\beta/\alpha)^2  - (\beta^2/\alpha) + \gamma,
$
allows us to evaluate the integrals with respect to $\xi$ and $\lambda$:
\begin{align*}
\MoveEqLeft{\rho_{\mu}(z | \vf = \vy)} \\
& \propto \displaystyle \int_{0}^\infty  \frac{1}{\lambda^{(n+3)/2}}  \exp\left( -\frac{  \gamma - \beta^2/\alpha}{2\lambda(c_0  -\vc ^T \mC^{-1} \vc)} \right)  \cdots \\
& \qquad \qquad \cdots \int_{-\infty}^\infty  \exp\left( -\frac{\alpha (\xi -\beta/\alpha)^2}{2\lambda(c_0  -\vc ^T \mC^{-1} \vc)} \right) \, \D \xi \D \lambda \\
& \propto \displaystyle \int_{0}^\infty  \frac{1}{\lambda^{(n+2)/2}}  \exp\left( -\frac{  \gamma - \beta^2/\alpha}{2\lambda(c_0  -\vc ^T \mC^{-1} \vc)} \right) \D \lambda \\
& \propto \left(\gamma - \frac{\beta^2}{\alpha}\right)^{-n/2} \propto \left(\alpha \gamma - \beta^2\right)^{-n/2}.
\end{align*}
Finally, we simplify the key term via straightforward calculations to the following:
\begin{align*}
\alpha \gamma - \beta^2 \propto 1 +  \frac{(z - \hmu_{\textup{MLE}})^2}{(n-1)\widehat{\sigma}_{\textup{full}}^2}, \\
\end{align*}
where 
\begin{multline*}
%\label{FJH:eq:signmaFull}
\hsigma^2_{\textup{full}} 
:= \frac{1}{n-1}
\vy^T\left[ \mC^{-1} 
- \frac{ \mC^{-1} \vone\vone^T \mC^{-1}}{\vone^T \mC^{-1} \vone}  \right]\vy
\\ 
\times  \left[\frac{(1 - \vc^T \mC^{-1} \vone)^2}{\vone^T \mC^{-1} \vone} + (c_0  -\vc ^T \mC^{-1} \vc) \right].
\end{multline*}

This means that $\mu \vert (\vf = \vy )$, properly centered and scaled, has a Student's $t$-distribution with $n-1$ degrees of freedom.   The estimated integral is the same as in the empirical Bayes case, $\hmu_{\textup{full}} = \hmu_{\MLE}$, but the confidence interval is wider:
\begin{align}
\label{eqn_prob_CI_full}
\mathbb{P}_f \left[
|\mu-\hmu_\full| \leq \err_{\full} \right]  = 99\%,
\end{align}
where
\begin{align}
\label{FJH:eq:errFull}
\err_{\textup{full}} 
:= t_{n_j-1,0.995} \hsigma_{\textup{full}} > \err_\MLE .
\end{align}
Here $t_{n-1,0.995}$ denotes the $99.5$ percentile of a standard Student's $t$-distribution with $n-1$ degrees of freedom.

Because the shape parameter, $\vtheta$, enters the definition of the covariance kernel in a non-trivial way, the only way to treat it as a hyperparameter and assign a tractable prior would be for the prior to be discrete.  We believe in practice that choosing such a prior involves more guesswork than using the empirical Bayes estimate of $\vtheta$ in \eqref{eqn:thetaMLE} or the cross-validation approach described next.

\subsubsection{Generalized Cross-Validation} \label{sec:GCV}
A third parameter optimization technique is \emph{leave-one-out cross-validation} (CV).  Let $\widetilde{y}_i = \Ex[f(\vx_i ) | \vf_{-i} = \vy_{-i}]$, where the subscript $-i$ denotes the vector excluding the $i^{\text{th}}$ component.  This is the conditional expectation of $f(\vx_i )$ given all data but the function value at $\vx_i$.  The cross-validation criterion, which is to be minimized, is the sum of squares of the difference between these conditional expectations and the observed values:
\begin{align} \label{FJH:eq:CVA}
\textup{CV} = \sum_{i=1}^n (y_i - \widetilde{y}_i)^2.
\end{align}

Let $\mA = \mC^{-1}$, let $\vzeta = \mA (\vy - m \vone)$, and partition $\mC$, $\mA$, and $\vzeta$ as
\begin{gather*}
\mC = \begin{pmatrix} c_{ii}  & \vC_{-i,i}^T \\  \vC_{-i,i} & \mC_{-i,-i}\end{pmatrix}, \qquad
\mA = \begin{pmatrix} a_{ii}  & \vA_{-i,i}^T \\  \vA_{-i,i} & \mA_{-i,-i}\end{pmatrix}, \\ \vzeta = \begin{pmatrix} \zeta_i   \\  \vzeta_{-i} \end{pmatrix},
\end{gather*}
where the subscript $i$ denotes the $i^{\text{th}}$ row or column, and the subscript $-i$ denotes all rows or columns except the $i^{\text{th}}$. Following this notation, Lemma \ref{thrm:condDist} implies that 
\begin{align*}
\widetilde{y}_i & = m + \vC^T_{-i,i} \mC_{-i,-i}^{-1} (\vy_{-i} -m \vone)  \\
\zeta_i  & = a_{ii}(y_i - m) + \vA_{-i,i}^T(\vy_{-i} - m \vone) \\
& = a_{ii}[(y_i - m) - \vC^T_{-i,i} \mC_{-i,-i}^{-1} (\vy_{-i} -m \vone)] \\
& = a_{ii}(y_i - \widetilde{y}_i).
\end{align*}
Thus, \eqref{FJH:eq:CVA} may be re-written as 
\begin{align*} %\label{FJH:eq:CVB}
\textup{CV} = \sum_{i=1}^n \left(\frac{\zeta_i}{a_{ii}} \right)^2, \qquad \vzeta = \mC^{-1}(\vy - m \vone).
\end{align*}
The \emph{generalized cross-validation} criterion (GCV) replaces the $i^{\text{th}}$ diagonal element of $\mA$ in the denominator by the average diagonal element of $\mA$ \cite{CraWah79a,GolHeaWah79a,Wah90}:
\begin{align*} 
\textup{GCV} &
= \frac{\sum_{i=1}^n\zeta_i^2}{\left(\frac 1n \sum_{i=1}^n a_{ii} \right)^2} \\
& = \frac{(\vy - m\vone)^T \mC^{-2} (\vy - m \vone)}{\left(\frac 1n \trace(\mC^{-1}) \right)^2}.
\end{align*}

The loss function $\textup{GCV}$ depends on $m$ and $\vtheta$, but not on $s$.  Minimizing the GCV  yields
\begin{align*}
m_{\textup{GCV}} = \frac{\vone^T \mC^{-2} \vy}{\vone^T \mC^{-2} \vone},\\ 
\end{align*}
\begin{multline}
\label{vthetaGCV}
\vtheta_{\textup{GCV}} = \argmin_\vtheta \biggl\{\log \left(  \vy^T \left[\mC^{-2} - \frac{\mC^{-2} \vone \vone^T \mC^{-2}}{\vone^T \mC^{-2} \vone}  \right] \vy \right)  \\
- 2 \log \left ( \trace(\mC^{-1}) \right ) \biggr\} .
\end{multline}
Plugging this value of $m$ into \eqref{eqn:BayesCub} yields
\begin{align}
\label{eqn:muCV}
\widehat{\mu}_{\textup{GCV}}
= \left(\frac{(1 - \vone^T  \mC^{-1}\vc) \mC^{-1} \vone}{\vone^T \mC^{-2} \vone} + \vc \right)^T \mC^{-1} \vy.
\end{align}

An estimate for $s$ may be obtained by noting that by Lemma \ref{thrm:condDist},
\begin{align*}
\var[f(\vx_i ) | \vf_{-i} = \vy_{-i}] = s^2 a_{ii}^{-1}.
\end{align*}
Thus, we may estimate $s$ using an argument similar to that used in deriving the GCV and then substituting $m_{\textup{GCV}}$ for $m$:
\begin{align*}
s^2 &= \var[f(\vx_i ) | \vf_{-i} = \vy_{-i}] a_{ii} \\ 
& \approx \frac 1n \sum_{i=1}^n (y_i - \widetilde{y}_i)^2a_{ii}
 = \frac 1n \sum_{i=1}^n \frac{\zeta_i^2}{a_{ii}} \\ 
 & \approx \frac{ \frac 1n \sum_{i=1}^n \zeta_i^2}{\frac 1n \sum_{i=1}^n a_{ii} } = \frac{(\vy - m\vone)^T \mC^{-2} (\vy - m \vone)}{ \trace(\mC^{-1}) } \\ 
 & \approx  s^2_{\textup{GCV}}, \\
 \intertext{where}
 s^2_{\textup{GCV}} & : = \vy^T \left[\mC^{-2} - \frac{\mC^{-2} \vone \vone^T \mC^{-2}}{\vone^T \mC^{-2} \vone}  \right] \vy  \left[ \trace(\mC^{-1}) \right]^{-1}. 
\end{align*}

The confidence interval based on GCV corresponds to \eqref{eqn_prob_confidence_interval} with the estimated $m$, $s$, and $\vtheta$:
\begin{gather}
\label{GCVerr}
\err_{\textup{GCV}} = 2.58 s_{\textup{GCV}}  \sqrt{c_0 - \vc^T\mC^{-1}\vc}, \\
\label{GCVCI}
\mathbb{P}_f \left[
|\mu-\hmu_{\textup{GCV}}| \leq \err_{\textup{GCV}} 
\right] = 99\%.
\end{gather}

Looking back over the results of Sections  \ref{sec:MLE}--\ref{sec:GCV}, it is noted that if the original covariance function, $C$, is replaced by $b C$ for some positive constant $b$, the cubature, $\hmu$, the estimates of $\vtheta$, and the credible interval widths, $\err_{\textup{CI}}$, all remain unchanged.  The estimates of $s^2$ are multiplied by $b^{-1}$, as would be expected.

\subsection{The automatic Bayesian cubature algorithm}
\label{sec:bayes_cubature_algo}
The previous section presents three credible intervals, \eqref{eqn_prob_CI_MLE}, \eqref{eqn_prob_CI_full}, and \eqref{GCVCI}, for the $\mu$, the desired integral.  Each credible interval is based on different assumptions about the hyperparameters $m$, $s$, and $\vtheta$.  We stress that one must estimate these hyperparameters or assume a prior distribution on them because the credible intervals are used as stopping criteria for our cubature rule.  Since a credible intervals makes a statement about a typical function---not an outlier---one must try to ensure that the integrand is a typical draw from the assumed Gaussian process.

Our  Bayesian cubature algorithm increases the sample size until the width of the credible interval is small enough.  This is accomplished through successively doubling the sample size.  The steps are detailed in Algorithm \ref{algorithm1}.

\algnewcommand{\IIf}[1]{\State\algorithmicif\ #1\ \algorithmicthen\ }
\algnewcommand{\IElse}{\unskip\ \algorithmicelse\ }
\algnewcommand{\EndIIf}{\unskip\ \algorithmicend\ \algorithmicif}

\begin{algorithm}
\caption{Automatic Bayesian Cubature}\label{algorithm1}
  \begin{algorithmic}[1]
  	\Require a generator for the sequence
  	$\vx_1, \vx_2, \ldots$; 
  	a black-box function, $f$; 
  	an absolute error tolerance,
  	$\varepsilon>0$; the positive initial sample size, $n_0$;
  	the maximum sample size $n_{\textup{max}}$

      \State $n \gets n_0, \; n' \gets 0, \; \err_{\textup{CI}} \gets \infty$

      \While{$\err_{\textup{CI}} > \varepsilon$ and $n \le n_{\textup{max}}$}

        \State\label{LoopStart}Generate $\{ \vx_i\}_{i=n' + 1}^{n}$ and sample $\{f(\vx_i)\}_{i=n'+1}^{n}$
        \State Compute $\vtheta$ by \eqref{eqn:thetaMLE} or \eqref{vthetaGCV}
        \State Compute $\err_{\textup{CI}}$  according to \eqref{eqn:errMLE}, \eqref{FJH:eq:errFull}, or \eqref{GCVerr}

       	\State	$n' \gets n, \; n \gets 2n'$

        \EndWhile

        \State Update sample size to compute $\hmu$, $n \gets n'$
        \State Compute $\hmu$, the approximate integral,   according to \eqref{eqn:cubMLE} or \eqref{eqn:muCV}
      \State \Return $\hmu, \; n$  and $\err_{\textup{CI}}$
  \end{algorithmic}
\end{algorithm}

\subsection{Example with the Mat\'ern kernel} \label{MVN_example}

To demonstrate automatic Bayesian cubature consider a Mat\'ern covariance kernel:
\begin{align*}
C_{\theta}(\vx, \vt) = \prod_{k=1}^d \exp(-\theta|\vx_k-\vt_k|)(1+\theta |\vx_k-\vt_k|),
\end{align*}
and Sobol points as the nodes.
Also, consider the integration problem of evaluating  \emph{multivariate normal probabilities}:
\begin{align}
\label{eqn:GaussDef}
\mu = \int_{(\va,\vb)} \frac{\exp\bigl(- \frac 12 \vt^T \mSigma^{-1} \vt \bigr)}{\sqrt{(2 \pi)^d \det(\mSigma)}} \, \dvt,
\end{align}
where $(\va,\vb)$ is a finite, semi-infinite or infinite box in $\reals^d$.  This integral does not have an analytic expression for general $\mSigma$, so cubatures are required.

Genz \cite{Gen93} introduced a variable transformation to transform \eqref{eqn:GaussDef} into an integral on the unit cube.  Let $\mSigma= \mL \mL^T$ be the Cholesky decomposition where $\mL = (l_{jk})_{j,k=1}^d$ is a lower triangular matrix.  Iteratively define
\begin{align*}
\alpha_1& = \Phi(a_1), \qquad \beta_1 = \Phi(b_1)
\\
\alpha_j&(x_1,...,x_{j-1}) = 
\\
&\; \Phi
\left(
\frac{1}{l_{jj}} 
\left(
a_j - \sum_{k=1}^{j-1} l_{jk} \Phi^{-1}(\alpha_k + x_k(\beta_k-\alpha_k))
\right)
\right), 
\\
&\hspace{5cm} j=2,...,d,
\\
\beta_j&(x_1,...,x_{j-1}) = 
\\
&\; \Phi
\left(
\frac{1}{l_{jj}} 
\left(
b_j - \sum_{k=1}^{j-1} l_{jk} \Phi^{-1}(\alpha_k + x_k(\beta_k-\alpha_k))
\right)
\right), 
\\
&\hspace{5cm} j=2,...,d,
\end{align*}
\begin{align}
\label{fGenzdef}
f_{\text{Genz}}(\vx) = \prod_{j=1}^d [\beta_j(\vx) - \alpha_j(\vx)].
\end{align}
where $\Phi$ is the cumulative standard normal distribution function.  Then, $\mu = \int_{[0,1]^{d-1}} f_{\text{Genz}}(\vx) \, \dvx$.

\begin{figure}
	\captionsetup[subfigure]{labelformat=empty}
	%\begin{subfigure}[h]{0.48\linewidth}
	%	\includegraphics[width=1.1\linewidth]{Plotting_gaussian}
	%\end{subfigure}
	\centering
	%\begin{subfigure}[h]{0.48\linewidth}
		\includegraphics[width=0.7\linewidth]{GenzFunc_varTx_none}
	%\end{subfigure}
	\caption{The $d=3$ multivariate normal probability transformed to an integral of $f_{\text{Genz}}$ with  $d=2$. This plot can be reproduced using \code{IntegrandPlots.m} in GAIL}
	\label{fig:MVN_Genz}
\end{figure}

We use the following parameter values in the simulation: 
\begin{align*}
d = 3, \quad \va = \begin{pmatrix}
-6 \\ -2 \\ -2
\end{pmatrix}, \quad 
\vb = \begin{pmatrix}
5 \\ 2 \\ 1
\end{pmatrix} , \quad 
\mL = \begin{pmatrix}
4 & 1 & 1 \\ 0 & 1 & 0.5 \\ 0 & 0 & 0.25
\end{pmatrix}.
\end{align*}
The node sets are randomly scrambled Sobol points \cite{DicEtal14a,DicPil10a}.  The results for  $\varepsilon = 10^{-2}, 10^{-3}, 10^{-4}$, and $10^{-5}$ and $100$ scrambles for each $\varepsilon$ are shown in \figref{fig:MVN_Metern_d2b2}.  We  observe the algorithm meets the error criterion 95\% of the time.
%with Intel i7 3630QM and 16GB RAM memory
%On our test computer, 
As shown in \figref{fig:MVN_Metern_d2b2}, computation time increases rapidly with $n$. 
The  maximum likelihood estimation of $\vtheta$, which requires repeated evaluation of the objective function, is the most time consuming of all. It takes tens of seconds to compute $\hmu_n$ once with $\varepsilon = 10^{-5}$.   In contrast, this example in Section \ref{sec:NumExp} take less than a hundredth of a second to compute $\hmu_n$ once with $\varepsilon = 10^{-5}$ using our new algorithm. Not only is the Bayesian cubature with the the Mat\'ern kernel slow, but also $\mC$ becomes highly ill-conditioned as $n$ increases.
So, Algorithm \ref{algorithm1}  in its current form is impractical. 
%\FJHNote{Jags, please check this re-write} %\JRNote{looks good}

\begin{figure}
	\centering
		\includegraphics[width=0.95\linewidth]{MVN_guaranteed_time_Matern_d2_2018-Aug-31}
	\centering
		\includegraphics[width=0.95\linewidth]{MVN_rapid_n_vs_time_Matern_d2_2018-Aug-31}
	\caption{Multivariate normal probability estimated using Mat\'ern kernel with $d=2$ using empirical stopping criterion. Top: Guaranteed integration within error tolerance $\varepsilon$. Bottom: Computation time rapidly increases with increase of $n$. These figures can be reproduced using \code{matern\_guaranteed\_plots.m} in GAIL.}
	\label{fig:MVN_Metern_d2b2}
\end{figure}

\section{Fast Automatic Bayesian Cubature}\label{sec:fast_BC}

The generic automatic Bayesian cubature algorithm described in the previous section requires $\Order(n^3)$ operations to estimate $\vtheta$, compute the credible interval width, and compute the cubature. Now we explain how to speed up the calculations. A key is to choose covariance kernels that match the nodes, $\{\vx_i\}_{i=1}^n$, so that the vector-matrix operations required by Bayesian cubature can be accomplished using fast transforms at a cost of $\Order(n \log(n))$.

\subsection{Fast Transform Kernel}
We make some assumptions about the relationship between the covariance kernel and the nodes, which will be shown to hold in Section \ref{sec:shift_invariant_kernel} for rank-1 lattices and shift-invariant kernels.  First we introduce the notation
\begin{align}
\nonumber
\mC &= \Big(C_\vtheta(\vx_i,\vx_j)\Big)_{i,j=1}^n  = (\vC_1,...,\vC_n) 
\\
\label{eqn:ftk_factor}
&= \frac 1n \mV \mLambda \mV^H , 
\quad \quad \mV^H = n \mV^{-1}, \\
\nonumber
\mV &= (\vv_1,...,\vv_n)^T = (\vV_1,...,\vV_n), \\
\nonumber
\mC^p  &= \frac 1n \mV \mLambda^{p} \mV^H, \qquad \forall p \in \integers,
\end{align}
where $\mV^H$ is the Hermitian of $\mV$.  The columns of matrix $\mV$ are eigenvectors of $\mC$, and $\mLambda$ is a diagonal matrix of eigenvalues of $\mC$.
For any $n \times n$ vector $\vb$, define the notation  $\widetilde{\vb} := \mV^H \vb$.

We make three assumptions that allow the fast computation:
\begin{subequations} \label{fastcompAssump}
	\begin{gather}
	\label{fastcompAssumpA}
	\mV \text{ may be identified analytically}, \\
	\label{fastcompAssumpB}
	\vv_1 = \vV_1 = \vone, \\
	\label{fastcompAssumpC}
	\mV^H \vb  \text{ requires only $\Order(n \log(n))$ operations } \forall \vb.
	\end{gather}
\end{subequations}
We call the transformation $\vb \mapsto \mV^H \vb$ a \emph{fast transform} and $C$ a \emph{fast transform kernel}.

Under assumptions \eqref{fastcompAssump} the eigenvalues may be identified as the fast transform of the first column of $\mC$:
\begin{align}
\nonumber
\vlambda 
& = \begin{pmatrix}
\lambda_1 \\ \vdots \\ \lambda_n
\end{pmatrix} = \mLambda \vone = \mLambda \vv_1^* 
= \underbrace{\left( \frac 1n \mV^H  \mV \right) }_{\mathsf{I}} \mLambda \vv_1^* \\
&= \mV^H \left( \frac 1n \mV \mLambda \vv_1^* \right)
= \mV^H \vC_1 =  \widetilde{\vC}_1,
\label{eqn:fast_transform_to_eigvalues}
\end{align}
Where $\mathsf{I}$ is the identity matrix.
Also note that the fast transform of $\vone$ has a simple form
\begin{align*} 
\widetilde{\vone}
& = \mV^H \vone = \mV^H \vV_1 = \begin{pmatrix}n  \\ 0 \\ \vdots \\ 0 \end{pmatrix}.
\label{eqn:fast_transform_one}
\end{align*}

Many of the terms that arise in the calculations in  Algorithm \ref{algorithm1} take the form $\va^T\mC^{p}\vb$ for real $\va$ and $\vb$ and integer $p$.  These can be calculated via the transforms $\widetilde{\va} = \mV^H \va$ and $\widetilde{\vb} = \mV^H \vb$ as 
\begin{equation*}
\va^T\mC^p\vb = \frac 1n \va^T \mV \mLambda^p \mV^H \vb
= \frac 1n \widetilde{\va}^H\mLambda^p \widetilde{\vb}
= \frac 1n \sum_{i=1}^n \lambda_i^p \widetilde{a}_i^* \widetilde{b}_i.
\end{equation*}
In particular,
\begin{align*}
\vone^T\mC^{-p}\vone & = \frac{n}{\lambda_1^p},
&
\vone^T\mC^{-p}\vy &= \frac{\widetilde{y}_1}{\lambda_1^p},
\\
\vy^T\mC^{-p} \vy &= \frac 1n \sum_{i=1}^n \frac{\abs{\widetilde{y}_i}^2}{\lambda_i^p},
&
\vc^T\mCInv \vone &= \frac{\widetilde{c}_1}{\lambda_1},\\
\vc^T\mCInv \vy &= \frac 1n \sum_{i=1}^n \frac{\widetilde{c}_i^* \widetilde{y}_i}{\lambda_i}, & 
\vc^T\mCInv \vc &= \frac 1n \sum_{i=1}^n \frac{\abs{\widetilde{c}_i}^2}{\lambda_i},
\end{align*}
where $\widetilde{\vy} = \mV^H \vy$ and 
$\widetilde{\vc} = \mV^H \vc$.  For any real $\vb$, with $\widetilde{\vb} = \mV^H\vb$, it follows that $\widetilde{b}_1$ is real since the first row of $\mV^H$ is $\vone$.

The covariance kernel used in practice also may satisfy an additional assumption:
\begin{align} \label{addAssump}
\int_{[0,1]^d} C_{\vtheta}(\vt,\vx) \, \D \vt = 1 \qquad \forall \vx \in [0,1]^d,
\end{align}
which implies that $c_0 = 1$ and $\vc = \vone$.  Under \eqref{addAssump}, the expressions above may be further simplified:
\begin{align*}
\vc^T\mCInv \vone =
\vc^T\mCInv \vc = \frac{n}{\lambda_1}.
\end{align*}

\subsection{Empirical Bayes}

Under assumptions \eqref{fastcompAssump}, the empirical Bayes parameters in \eqref{eqn_m_MLE}, \eqref{eqn_s2_MLE}, \eqref{eqn:thetaMLE} \eqref{eqn:cubMLE}, and \eqref{eqn:errMLE} can be expressed in terms of the fast transforms of the function data, the first column of the Gram matrix, and $\vc$ as follows:
\begin{align}
\nonumber
m_\MLE &=  \frac{\widetilde{y}_1}{n} = \frac 1n \sum_{i=1}^n y_i.
\\
\nonumber
s^2_\MLE 
& =
\frac{1}{n^2} 
\sum_{i=2}^n \frac{\abs{\widetilde{y}_i}^2}{\lambda_i}. \\
\nonumber
\vtheta_\MLE
&= 
\argmin_{\vtheta}
\left[
\log\left(
\sum_{i=2}^n \frac{\abs{\widetilde{y}_i}^2}{\lambda_i}
\right) \right .\\
\label{eqn_MLE_loss_func_optimized_2}
& \hspace{3cm} \left .
  + 
\frac{1}{n}\sum_{i=1}^n \log(\lambda_i)
\right].
\\
\nonumber
\hmu_\MLE  &= 
\frac{\widetilde{y}_1}{n} +
\frac 1n \sum_{i=2}^n \frac{ \widetilde{c}_i^* \widetilde{y}_i}{\lambda_i}. \\
\nonumber
\err_\MLE  &
=
\frac{2.58}{n}\sqrt{
	\sum_{i=2}^{n} \frac{\abs{\widetilde{y}_i}^2}{\lambda_i}  
	\,
	\left( c_0 - \frac 1n \sum_{i=1}^n \frac{\abs{\widetilde{c}_i}^2}{\lambda_i} \right) 
}.
\end{align}
Since all the quantities on the right hand sides can be obtained in $\Order(n \log(n))$ operations by fast transforms, the left hand sides are all computable using the asymptotic computational cost.

Under the further assumption \eqref{addAssump}, it follows that 
\begin{align}
\nonumber
\hmu_\MLE  &= 
\frac{\widetilde{y}_1}{n} = \frac 1n \sum_{i=1}^n y_i,\\
\label{eq:errMLEAllAsump}
\err_\MLE  &
=
\frac{2.58}{n}\sqrt{
	\sum_{i=2}^{n} \frac{\abs{\widetilde{y}_i}^2}{\lambda_i}  
	\,
	\left( 1 -  \frac{n}{\lambda_1} \right) 
}.
\end{align}
Thus, in this  case $\hmu$ is simply the sample mean.

\subsection{Full Bayes}
For the full Bayes approach the cubature is the same as for empirical Bayes.  We also defer to empirical Bayes to estimate the parameter $\vtheta$.  The width of the confidence interval is $\err_{\textup{full}} 
:= t_{n_j-1,0.995} \hsigma_{\textup{full}}$, where $\hsigma_{\textup{full}}^2$ can also be computed swiftly under assumptions \eqref{fastcompAssump}:
\begin{multline*} %\label{FJH:eq:signmaFull}
\widehat{\sigma}^2_{\textup{full}}
=
\frac{1}{n(n-1)} \sum_{i=2}^n \frac{\abs{\widetilde{y}_i}^2}{\lambda_i}
\\
\times
\left[\frac{\lambda_1}{n}{\left(1 - \frac{\widetilde{c}_1}{\lambda_1}\right)^2} + \left(c_0  - \frac 1n \sum_{i=1}^n \frac{\abs{\widetilde{c}_i}^2}{\lambda_i}\right) \right],
\end{multline*}
Under assumption \eqref{addAssump} further simplification can be made:
\begin{align*} %\label{FJH:eq:signmaFullSimple}
\widehat{\sigma}^2_{\textup{full}}
=
\frac{1}{n(n-1)} \sum_{i=2}^n \frac{\abs{\widetilde{y}_i}^2}{\lambda_i} \, \left(\frac{\lambda_1}{n}  - 1  \right),
\end{align*}
It follows that
\begin{align} \label{FJH:eq:errFullSimple}
\err_{\textup{full}}
=
t_{n_j-1,0.995}
\sqrt{\frac{1}{n(n-1)} \sum_{i=2}^n \frac{\abs{\widetilde{y}_i}^2}{\lambda_i}  \left(\frac{\lambda_1}{n}  - 1  \right)}.
\end{align}

\subsection{Generalized Cross-Validation}

GCV yields a different cubature, which nevertheless can also be computed quickly using the fast transform.  Under assumptions \eqref{fastcompAssump}:
\begin{align}
\nonumber
m_{\textup{GCV}} & = m_\MLE =  \frac{\widetilde{y}_1}{n} = \frac 1n \sum_{i=1}^n y_i,\\
\nonumber 
s^2_{\textup{GCV}} & : =  \frac 1{n} \sum_{i=2}^n \frac{\abs{\widetilde{y}_i}^2}{\lambda_i^2}  \left [ \sum_{i=1}^n \frac{1}{\lambda_i} \right]^{-1}, \\
\nonumber 
\vtheta_{\GCV} 
&= \argmin_\vtheta \left[ \log \left ( \sum_{i=2}^n \frac{\abs{\widetilde{y}_i}^2}{\lambda_i^2} 
\right) \right .\\
\label{thetaGCV}
& \qquad \qquad \qquad \qquad  \left . -2\log\left( \sum_{i=1}^n \frac{1}{\lambda_i} \right)
\right], \\
\nonumber
\hmu_{\GCV}
&= \hmu_\MLE  = \frac{\widetilde{y}_1}{n} +
\frac 1n \sum_{i=2}^n \frac{ \widetilde{c}_i^* \widetilde{y}_i}{\lambda_i}, \\
\nonumber
\err_{\textup{GCV}} & =
\frac{2.58}{n}\left\{\sum_{i=2}^n \frac{\abs{\widetilde{y}_i}^2}{\lambda_i^2}  \left [ \frac 1n \sum_{i=1}^n \frac{1}{\lambda_i} \right]^{-1} \right.
\\ 
\nonumber
&\qquad \qquad \left . \times
\left( c_0 - \frac 1n \sum_{i=1}^n \frac{\abs{\widetilde{c}_i}^2}{\lambda_i} \right) 
\right\}^{1/2}.
\end{align}
Moreover, under further assumption \eqref{addAssump}, it follows that 
\begin{align}
\label{muhatGCV-FB-MLE-Simple}
\hmu_{\textup{GCV}}
&= \hmu_\MLE = \hmu_{\textup{full}} =
\frac{\widetilde{y}_1}{n} = \frac 1n \sum_{i=1}^n y_i,\\
\nonumber
\err_{\textup{GCV}} & =
\frac{2.58}{n}\left\{\sum_{i=2}^n \frac{\abs{\widetilde{y}_i}^2}{\lambda_i^2}  \left [ \frac 1n \sum_{i=1}^n \frac{1}{\lambda_i} \right]^{-1} \right.
\\ 
&\qquad \qquad \left . \times
\left( 1 -  \frac{n}{\lambda_1} \right)  
\right\}^{1/2}. \label{errGCVSimple}
\end{align}
In this case too, $\hmu$ is simply the sample mean.

\section{Integration Lattices and Shift Invariant Kernels}
\label{sec:shift_invariant_kernel}

The preceding sections lay out an automatic Bayesian cubature algorithm whose computational cost is only $\Order(n \log(n))$ if $n$ function values are used.  However, this algorithm relies on covariance kernel functions, $C$ and node sets, $\{\vx_i\}_{i=1}^n$ that satisfy assumptions \eqref{fastcompAssump}.  We  also want to satisfy assumption \eqref{addAssump}.  
%To facilitate the fast transform, it is assumed in this section and the next that $n$ is power of $2$.  
To facilitate the fast transform, $n$ must be power of $2$.

\subsection{Extensible Integration Lattice Node Sets}

The set of nodes used is defined by a shifted extensible integration lattice node sequence, which takes the form
\begin{equation*}
\vx_{i} = \vh \phi(i-1) + \vDelta \mod \vone, \qquad i \in \naturals.
\end{equation*} 
Here, $\vh$ is a $d$-dimensional generating vector of positive integers, $\vDelta$ is some point in $[0,1)^d$, often chosen at random, and $\{\phi(i)\}_{i=0}^n$ is the van der Corput sequence, defined by reflecting the binary digits of the integer about the decimal point, i.e., 
\begin{align} \label{vdCDef}
\begin{array}{r|ccccccccccccc}
i & 0 & 1 & 2 & 3 & 4 &  5 & 6 & 7 & \cdots \\
i & 0_2 & 1_2 & 10_2 & 11_2 & 100_2 & 101_2 & 110_2 & 111_2  & \cdots\\
\toprule
\phi(i) & {}_2.0 &  {}_2.1 & {}_2.01 &  {}_2.11  & {}_2.001 &  {}_2.101 & {}_2.011 &  {}_2.111 & \cdots\\
\phi(i) & 0 &  0.5 &  0.25 & 0.75 &  0.125 & 0.625  &  0.375 & 0.875 & \cdots
\end{array}
\end{align}

An example of $64$ nodes is given in \figref{latticefig}.  The even coverage of the unit cube is ensured by a well chosen generating vector.  The choice of generating vector is typically done offline by computer search.  See \cite{DicEtal14a,HicNie03a} for more on extensible integration lattices.
\begin{figure}[htp]
	\centering
	\includegraphics[height=5cm]{ShiftedLatticePoints}
	\caption{Example of a shifted integration lattice node set  in $d=2$. 
	This figure can be reproduced using \code{PlotPoints.m} in GAIL} \label{latticefig}
\end{figure}

\subsection{Shift Invariant Kernels}
The covariance functions $C$ that match integration lattice node sets have the form
\begin{align} \label{eq:shInv}
C(\vt,\vx) = K(\vt - \vx \bmod \vone).
\end{align}
This is called a \emph{shift invariant kernel} because shifting both arguments of the covariance function by the same amount leaves the value unchanged.   By a proper scaling of the kernel $K$ it follows that assumption \eqref{addAssump} is satisfied. Of course, $K$ must also be of the form that ensures that $C$ is symmetric and positive definite, as assumed in \eqref{FJH:eq:CondPosDef}.

A family of shift invariant kernels is constructed via even degree Bernoulli polynomials:
\begin{multline}
\label{the_kernel_eqn_bernoulli}
C_\vtheta(\vt, \vx) =
\prod_{l=1}^d \biggl[
1 - (-1)^{r} \gamma B_{2r}( |{x_l-t_l}| ) \biggr], \\  
\forall \vt,\vx \in [0,1]^d, \  \vtheta = (r,\gamma), \ r \in \naturals, \ \gamma > 0.
\end{multline}
Symmetric, periodic, positive definite kernels of this form appear in  \cite{DicEtal14a,Hic96a}.  Bernoulli polynomials are described in \cite[Chapter 24]{OlvEtal10a}.

Larger $r$ implies a greater degree of smoothness of the kernel.  Larger $\gamma$ implies greater fluctuations of the output with respect to the input.  Plots of $C(\cdot, 0.3)$ are given in \figref{fig:fourierkernel-dim1} for various $r$ and $\gamma$ values.

\begin{figure}
	\centering
	\includegraphics[width=0.9\linewidth]{"fourier_kernel_dim_1"}
	\caption[Fourier kernel]{Shift invariant kernel in 1D shifted by 0.3 to show the discontinuity. This figure can be reproduced using \code{plot\_fourier\_kernel.m} in GAIL. }
	\label{fig:fourierkernel-dim1}
\end{figure}

\subsection{Eigenvectors}
For general shift-invariance covariance functions, the Gram matrix takes the form
\begin{align*}
%\label{shInvKernGramMatrix}
\mC &= \bigl ( C(\vx_i, \vx_j) \bigr)_{i, j = 1}^n \\
& = \Bigl ( K(\vh(\phi(i-1) - \phi(j-1)) \bmod \vone ) \Bigr)_{i, j = 1}^n.
\end{align*}

We now demonstrate that the eigenvector matrix for $\mC$ is 
\begin{align} \label{latticeVdef}
\mV = \Bigl ( \me^{2 \pi n \sqrt{-1} \phi(i-1)\phi(j-1)} \Bigr)_{i,j = 1}^n.
\end{align}
Assumption \eqref{fastcompAssumpB} follows automatically.
Now, note that the $k,j$ element of $\mV^H\mV$ is
\begin{equation*}
\sum_{i=1}^n \me^{2 \pi n \sqrt{-1} \phi(i-1)[\phi(j-1) - \phi(k-1)]} .
\end{equation*}
Noting that the sequence $\{\phi(i-1)\}_{i=1}^n$ is a re-ordering of $0, \ldots, 1-1/n$ for $n$ a power of $2$, this sum may be re-written by replacing $\phi(i-1)$ by $(i-1)/n$:
\begin{equation*}
\sum_{i=1}^n \me^{2 \pi \sqrt{-1} (i-1)[\phi(j-1) - \phi(k-1)]}.
\end{equation*}
Since $\phi(j-1) - \phi(k-1)$ is some integer multiple of $1/n$, it follows that this sum is $n \delta_{j,k}$, where $\delta$ is the Kronecker delta function.  This establishes that $\mV^H = n \mV^{-1}$ as in \eqref{eqn:ftk_factor}.

Next, let $\omega_{k, \ell}$ denote the $k,\ell$ element of $\mV^H \mC \mV$, which is given by the double sum
\begin{multline*}
\omega_{k, \ell} = \sum_{i,j=1}^n K(\vh(\phi(i-1) - \phi(j-1)) \bmod \vone ) \\
\times   \me^{-2 \pi n \sqrt{-1} \phi(k-1)\phi(i-1)}  \me^{2 \pi n \sqrt{-1} \phi(j-1)\phi(l-1)}
\end{multline*}
Noting that the sequence $\{\phi(i-1)\}_{i=1}^n$ is a re-ordering of $0, \ldots, 1-1/n$ for $n$ a power of $2$, this sum may be re-written by replacing $\phi(i-1)$ by $(i-1)/n$ and $\phi(j-1)$ by $(j-1)/n$:
\begin{multline*}
\omega_{k, \ell} = \sum_{i,j=1}^n K\left (\vh \left(\frac{i-j}{n} \right) \bmod \vone \right) \\
\times   \me^{-2 \pi \sqrt{-1} \phi(k-1)(i-1)}  \me^{2 \pi \sqrt{-1} (j-1)\phi(\ell-1)}.
\end{multline*}
This sum also remains unchanged if $i$ is replaced by $i+m$ and $j$ is replaced by $j+m$ for any integer $m$:
\begin{multline*}
\omega_{k, \ell} = \sum_{i,j=1}^n K\left (\vh \left(\frac{i-j}{n} \right) \bmod \vone \right) \\
\times   \me^{-2 \pi \sqrt{-1} \phi(k-1)(i+m-1)}  \me^{2 \pi \sqrt{-1} (j+m-1)\phi(\ell-1)} \\
=   \omega_{k, \ell}  \me^{2 \pi \sqrt{-1} m(\phi(\ell-1) - \phi(k-1))}.
\end{multline*}
For this last equality to hold for all integers $m$, we must have $k = \ell$ or $\omega_{k,\ell} = 0$.  Thus, 
\begin{align*}
\omega_{k, \ell} &= \delta_{k,\ell} \sum_{i,j=1}^n K\left (\vh \left(\frac{i-j}{n} \right) \bmod \vone \right) \\
& \qquad \qquad \qquad \qquad \times   \me^{-2 \pi \sqrt{-1} (i - j) \phi(k-1)} \\
& = n \delta_{k,\ell}  \sum_{i=1}^n K\left ( \left(\frac{i\vh}{n} \right) \bmod \vone \right)  \me^{-2 \pi \sqrt{-1} i \phi(k-1) }.
\end{align*}
This establishes $\mV^H \mC \mV$ as a diagonal matrix whose diagonal elements are $n$ times the eigenvalues, i.e., $\lambda_k = \omega_{k,k}/n$.  Furthermore, $\mV$ is the matrix of eigenvectors, which satisfies assumption \eqref{fastcompAssumpA}.

\subsection{Iterative Computation of the Fast Transform}
Assumption \eqref{fastcompAssumpA} is that computing $\mV^H \vb$ requires only $\Order(n \log(n)) $ operations.  Recall that we assume that $n$ is a power of $2$.  This can be accomplished by an iterative algorithm.  Let $\mV^{(n)}$ denote the $n \times n$ matrix $\mV$ defined in  \eqref{latticeVdef}.  We show how to compute $\mV^{(2n)H}\vb$ quickly for all $\vb \in \reals^{2n}$ assuming that $\mV^{(n)H}\vb$ can be computed quickly for all $\vb \in \reals^n$.

From the definition of the van der Corput sequence in \eqref{vdCDef}, it follows that
\begin{gather} 
\label{vdCProp}
\phi(2i) = \phi(i)/2, \;  \phi(2i+1) = [\phi(i)+1]/2, \ \ \ i \in \natzero\\
\label{vdCPropB}
\phi(i+n) = \phi(i) + 1/(2n), \qquad i = 0, \ldots, n-1,
\\
\label{vdCPropC}
n \phi(i) \in \natzero, \qquad i = 0, \ldots, n-1,
\end{gather}
still assuming that $n$ is an integer power of two.
Let $\widetilde{\vb} = \mV^{(2n)H}\vb$ for some arbitrary $\vb \in \reals^{2n}$, and define
\begin{gather*}
\vb = \begin{pmatrix} b_1 \\ \vdots \\ b_{2n} \end{pmatrix}, \quad 
\vb^{(1)} = \begin{pmatrix} b_1 \\ \vdots \\ b_{n} \end{pmatrix}, \quad 
\vb^{(2)}  = \begin{pmatrix} b_{n+1} \\ \vdots \\ b_{2n} \end{pmatrix}, \\ 
\widetilde{\vb} = \begin{pmatrix} \widetilde{b}_1 \\ \vdots \\ \widetilde{b}_{2n} \end{pmatrix}, \quad 
\widetilde{\vb}^{(1)} = \begin{pmatrix} b_1 \\ b_3 \\ \vdots \\ b_{2n-1} \end{pmatrix}, \quad 
\widetilde{\vb}^{(2)}  = \begin{pmatrix} b_{2} \\  b_{4} \\ \vdots \\ b_{2n} \end{pmatrix}. 
\end{gather*}
It follows from these definitions and the definition of $\mV$ in  \eqref{latticeVdef} that
\begin{align*}
\widetilde{\vb}^{(1)} &= \left( \sum_{j=1}^{2n}  \me^{-4 \pi n \sqrt{-1} \phi(2i-2)\phi(j-1)} b_{j} \right)_{i=1}^n \\
&= \left( \sum_{j=1}^{2n}  \me^{-2 \pi n \sqrt{-1} \phi(i-1)\phi(j-1)} b_{j} \right)_{i=1}^n \quad \text{by \eqref{vdCProp}}\\
&= \left( \sum_{j=1}^{n}  \me^{-2 \pi n \sqrt{-1} \phi(i-1)\phi(j-1)} b_{j} \right)_{i=1}^n \quad \\
&\qquad \qquad +  \left( \sum_{j=1}^{n}  \me^{-2 \pi n \sqrt{-1} \phi(i-1)\phi(n+j-1)} b_{n+j} \right)_{i=1}^n \\
&= \mV^{(n)H}\vb^{(1)}  +  \biggl(  \me^{-\pi \sqrt{-1} \phi(i-1)}  \\
& \quad \times \sum_{j=1}^{n}  \me^{-2 \pi n \sqrt{-1} \phi(i-1)\phi(j-1)} b_{n+j} \biggr)_{i=1}^n \quad  \text{by \eqref{vdCPropB}}\\
&= \mV^{(n)H}\vb^{(1)} +  \left(  \me^{-\pi \sqrt{-1} \phi(i-1)} \right)_{i=1}^n \odot \bigl(\mV^{(n)H}\vb^{(2)} \bigr),
\end{align*}
where $\odot$ denotes the Hadamard (term-by-term) product.  By a similar argument, 
\begin{align*}
\widetilde{\vb}^{(2)} &= \left( \sum_{j=1}^{2n}  \me^{-4 \pi n \sqrt{-1} \phi(2i-1)\phi(j-1)} b_{j} \right)_{i=1}^n \\
&= \left( \sum_{j=1}^{2n}  \me^{-2 \pi n \sqrt{-1} [\phi(i-1)+1]\phi(j-1)} b_{j} \right)_{i=1}^n \quad \text{by \eqref{vdCProp}}\\
&= \left( \sum_{j=1}^{n}  \me^{-2 \pi n \sqrt{-1} [\phi(i-1)+1]\phi(j-1)} b_{j} \right)_{i=1}^n \quad \\
&\qquad  +  \left( \sum_{j=1}^{n}  \me^{-2 \pi n \sqrt{-1} [\phi(i-1)+1]\phi(n+j-1)} b_{n+j} \right)_{i=1}^n \\
&= \mV^{(n)H}\vb^{(1)} 
+  \left(  \me^{ -\pi \sqrt{-1} [\phi(i-1) + 1]} \right. 
\\
& \qquad \qquad \left . \times \sum_{j=1}^{n}  \me^{-2 \pi n \sqrt{-1} \phi(i-1)\phi(j-1)} b_{n+j} \right)_{i=1}^n \\
& \hspace{4cm}  \text{by \eqref{vdCPropB} and \eqref{vdCPropC}}\\
&= \mV^{(n)H}\vb^{(1)} -  \left(  \me^{-\pi \sqrt{-1} \phi(i-1)} \right)_{i=1}^n \odot \bigl(\mV^{(n)H}\vb^{(2)} \bigr).
\end{align*}

The computational cost to compute $\mV^{(2n)H}\vb$ is then twice the cost of computing $\mV^{(n)H}\vb^{(1)}$ plus $2n$ multiplications plus $2n$ additions.  An inductive argument shows that $\mV^{(n)H}\vb$ requires only $\Order(n \log(n))$ operations.

\subsection{Overcoming Cancellation Error}
For the kernels used in our computation, it may happen that $n/\lambda_1$ is close to $1$.  Thus, the term $1-n/\lambda_1$, which appears in the credible interval widths, $\err_{\MLE}$, $\err_{\textup{full}}$, and $\err_{\textup{GCV}}$, may suffer from cancellation error.  We can avoid this cancellation error by modifying how we compute the Gram matrix and its eigenvalues.

Define a new function $\rC : = C -1$, and its associated Gram matrix $\rmC = \mC - \vone \vone^T$.   Note that $\rC$ inherits the shift-invariant properties of $C$.  Since $\vone$ is the first eigenvector of $\mC$, it follows that the eigenvalues of $\rmC$ are $\rlambda_1 = \lambda_1 - n, \lambda_2, \ldots, \lambda_n$.  Moreover,
\begin{equation*}
1 - \frac{n}{\lambda_1}  = \frac{\lambda_1 - n}{\lambda_1} = \frac{\rlambda_1}{\rlambda_1 +n},
\end{equation*}
where now the right hand side is free of cancellation error.

We show how to compute $\rC$ without introducing round-off error.  The covariance functions that we use are of product form, namely,
\begin{equation*}
C(\vt, \vx) = \prod_{\ell=1}^d \left[1 + \rC_\ell(t_\ell,x_\ell) \right], \qquad  \rC_\ell:[0,1]^2 \to \reals.
\end{equation*}
Direct computation of $\rC (\vt,\vx) = C(\vt,\vx) -1$ introduces cancellation error if the $ \rC_\ell$ are small.  So, we employ the iteration
\begin{align*}
\rC^{(1)} &= \rC_1(t_1,x_1),  \\
\rC^{(\ell)} &  = \rC^{(\ell-1)}[1 + \rC_\ell(t_\ell,x_\ell)] + \rC_\ell(t_\ell,x_\ell), \\
& \hspace{5cm} \ell = 2, \ldots, d, \\
\rC(\vt,\vx)  & = \rC^{(d)}.
\end{align*}
In this way, the Gram matrix $\rmC$, whose $i,j$-element is $\rC(\vx_i,\vx_j)$ can be constructed with minimal round-off error.

Computing the eigenvalues of $\rmC$ via the procedure given in \eqref{eqn:fast_transform_to_eigvalues} yields $\rlambda_1 = \lambda_1 - n, \lambda_2, \ldots, \lambda_n$. The estimates of $\vtheta$ are computed in terms of the eigenvalues of $\rmC$, so \eqref{eqn_MLE_loss_func_optimized_2} and \eqref{thetaGCV} become
\begin{subequations}
\label{thetaSimple}
\begin{align}
\label{thetaSimpleMLE}
\vtheta_\MLE
&= 
\argmin_{\vtheta}
\left[
\log\left(
\sum_{i=2}^n \frac{\abs{\widetilde{y}_i}^2}{\lambda_i}
\right) 
%\label{thetaMLEsimple}
 + 
 \frac{1}{n}\sum_{i=1}^n \log(\lambda_i)
\right], \\
\label{thetaSimpleGCV}
\vtheta_{\GCV} 
&= \argmin_\vtheta \left[ \log \left ( \sum_{i=2}^n \frac{\abs{\widetilde{y}_i}^2}{\lambda_i^2} 
\right)  -2\log\left( \sum_{i=1}^n \frac{1}{\lambda_i} \right)
\right],
\end{align}
\end{subequations}
where $\lambda_1 = n + \rlambda_1$.  The widths of the credible intervals in \eqref{eq:errMLEAllAsump}, \eqref{FJH:eq:errFullSimple}, and   \eqref{errGCVSimple} become
\begin{subequations}
\label{fastStoppingCriterions}
	\begin{align}
\label{fastStoppingCriterionMLE}
\err_\MLE  &
=
\frac{2.58}{n}\sqrt{
	\frac{\rlambda_1}{\lambda_1}
	\sum_{i=2}^{n} \frac{\abs{\widetilde{y}_i}^2}{\lambda_i}  
}, 
\\
\label{fastStoppingCriterionFull}
\err_{\textup{full}} 
& = \frac{t_{n_j-1,0.995}}{n} \sqrt{
	\frac{\rlambda_1}{n-1} \sum_{i=2}^n \frac{\abs{\widetilde{y}_i}^2}{\lambda_i}
}, \\
\label{fastStoppingCriterionGCV}
\err_{\textup{GCV}} & =
\frac{2.58}{n}\sqrt{	\frac{\rlambda_1}{\lambda_1} \sum_{i=2}^n \frac{\abs{\widetilde{y}_i}^2}{\lambda_i^2}  \left [ \frac 1n \sum_{i=1}^n \frac{1}{\lambda_i} \right]^{-1}} .
	\end{align}
\end{subequations}
Since $\rlambda_1 = \lambda_1 - n$ and $\lambda_1 \sim n$ it follows $\rlambda_1/\lambda_1 \approx \rlambda_1/(n-1)$ and is small for  large $n$.  Moreover, the credible intervals via empirical Bayes and full Bayes are similar, since $t_{n_j-1,0.995}$ is approximately $2.58$. 
The computational steps for the improved, faster, automatic Bayesian cubature are detailed in Algorithm \ref{algorithm2}.

\begin{algorithm}
	\caption{Fast Automatic Bayesian Cubature}\label{algorithm2}
	\begin{algorithmic}[1]
		\Require a generator for the rank-1 Lattice sequence
		$\vx_1, \vx_2, \ldots$; 
		a shift-invariant periodic kernel, $C$;
		a black-box function, $f$; 
		an absolute error tolerance,
		$\varepsilon>0$; the positive initial sample size, $n_0$;
		the maximum sample size $n_{\textup{max}}$

		\State $n \gets n_0, \; n' \gets 0, \; \err_{\textup{CI}} \gets \infty$

		\While{$\err_{\textup{CI}} > \varepsilon$ and $n \le n_{\textup{max}}$}

		\State\label{LoopStart}Generate $\{ \vx_i\}_{i=n' + 1}^{n}$ and sample $\{f(\vx_i)\}_{i=n'+1}^{n}$
		\State Compute $\vtheta$ by \eqref{thetaSimpleMLE} or \eqref{thetaSimpleGCV}
		\State Compute $\err_{\textup{CI}}$  according to \eqref{fastStoppingCriterionMLE}, \eqref{fastStoppingCriterionFull}, or \eqref{fastStoppingCriterionGCV}

		\State	$n' \gets n, \; n \gets 2n'$

		\EndWhile

		\State Update sample size to compute $\hmu$, $n \gets n'$
		\State Compute $\hmu$, the approximate integral,   according to \eqref{muhatGCV-FB-MLE-Simple}
		\State \Return $\hmu, \; n$  and $\err_{\textup{CI}}$
	\end{algorithmic}
\end{algorithm}

We summarize the results of this section and the previous one as follows:
\begin{prop}
Any periodic, symmetric, positive definite, shift-invariant covariance kernel of the form \eqref{eq:shInv} scaled to satisfy \eqref{addAssump}, when matched with rank-1 lattice data-sites, must satisfy assumptions \eqref{fastcompAssump}.  The \emph{fast Fourier transform} (FFT) can be used to expedite the estimates of $\vtheta$ in \eqref{thetaSimple} and the credible interval widths \eqref{fastStoppingCriterions} in $\Order(n \log(n))$ operations. The cubature, $\hmu$, is just the sample mean.
\end{prop}

We have implemented the fast adaptive Bayesian cubature algorithm in MATLAB as part of the Guaranteed Adaptive Integration Library (GAIL) \cite{ChoEtal17b} as \allowbreak \code{cubBayesLattice\_g}. This algorithm uses the kernel defined in  \eqref{the_kernel_eqn_bernoulli} with  $r=1,2$ and the periodizing variable transforms in  \secref{period_var_tx}.  The rank-1 lattice node generator is taken from \cite{Nuy17a} (\code{exod2\_base2\_m20}).

\section{Numerical Experiments} \label{sec:NumExp}

\subsection{Periodizing Variable Transformations}
\label{period_var_tx}
The shift-invariant covariance kernels underlying our Bayesian cubature  assume that the integrand has a degree of periodicity, with the smoothness assumed depending on the smoothness of the kernel.  While integrands arising in practice may be smooth, they might not be periodic.  Variable transformations can be used to ensure periodicity.

Suppose that the original integral has been expressed as 
\begin{equation*}
\mu := \int_{[0,1]^d} g(\vt) \, \dif \vt
\end{equation*}
where $g$ has sufficient smoothness, but lacks periodicity.  The Baker's transform,
\begin{multline} \label{eq:bakerTrans}
\vPsi: \vx \mapsto (\Psi(x_1),  \ldots, \Psi(x_d)), \\ \Psi(x)  =1 - 2 \abs{x - 1/2},
\end{multline}
allows us to write $\mu$ in the form of \eqref{eqn:defn_mu}, where $f(\vx) = g(\vPsi(\vx))$.

A family of variable transforms take the form
\begin{subequations} %\label{eq:varTrans}
\begin{equation*}
\vPsi: \vx \mapsto (\Psi(x_1),  \ldots, \Psi(x_d)), \quad \Psi:[0,1] \mapsto [0,1],
\end{equation*}
which allows us to write $\mu$ in the form of \eqref{eqn:defn_mu} with
\begin{equation*}
f(\vx) = g(\vPsi(\vx)) \prod_{\ell = 1}^d \Psi'(x_l).
\end{equation*}
\end{subequations}
If $\Psi$ is sufficiently smooth, $\lim_{x \downarrow 0}x^{-r}\Psi'(x) = \lim_{x \uparrow 1} (x-1)^{-r}\Psi'(x) = 0$ for $ r \in \natzero$, and $g \in C^{(r, \ldots, r)}[0,1]^d$, then $f$ has continuous, periodic derivatives up to order $r$ in each direction.  
Examples of this kind of transform include \cite{Sid08a}:
\begin{align*}
%C^0 &: \Psi(x) =  3 x^2 - 2 x^3, \quad   \Psi'(x) = 6x(1-x), \\
%C^1 & : \Psi(x) = x^3(10-15x+6x^2),  \\
%&\qquad \qquad \qquad   \Psi'(x) = 30x^2(1-x)^2 \\
\text{Sidi's } C^1 & : \Psi(x) = x - \frac{\sin(2\pi x)}{2 \pi}, \\
&\qquad \qquad \qquad   \Psi'(x) = 1 - \cos(2\pi x), \\
\text{Sidi's } C^2 & : \Psi(x) = \frac {8 - 9 \cos(\pi x) + \cos(3 \pi x)}{16} ,  \\
&\qquad \qquad \Psi'(x) = \frac {3 \pi[3 \sin(\pi x) - \sin(3 \pi x)]}{16}.
\end{align*}

Periodizing variable transforms are used for the numerical examples below. In some cases, they can speed the convergence of the Bayesian cubature.

\subsection{Test Results and Observations}
%\label{sec:numerical_experiments}

Three integrals were evaluated using the GAIL algorithm \code{cubBayesLattice\_g}:  a multivariate normal probability, the Keister's example, and an option pricing example.  Four different error tolerances, $\varepsilon$,  were set for each example, with the tolerances chosen depending on the difficulty of the problem.  The sequences $\{\vx_i\}_{i=1}^\infty$ were the randomly shifted lattice node sequences supplied by GAIL. The accuracy of the algorithm differs based on the shift. For each integral,  each tolerance, and each of our stopping criteria---empirical Bayes, full Bayes, and generalized cross-validation---our algorithm was run for $100$ different random shifts.  For each test, the execution times were plotted against $\abs{\mu - \hmu}/\varepsilon$.  We expect $\abs{\mu - \hmu}/\varepsilon$ to be no greater than one, but hope that it is not too much smaller than one, which would indicate a stopping criterion that is too conservative.

Figures \ref{fig:mvn-guaranteed-MLE} to \ref{fig:optprice-guaranteed-GCV} can be reproduced using the script \code{cubBayesLattice\_guaranteed\_plots.m} in GAIL.

\paragraph{Multivariate Normal Probability.}

This example was already introduced in Section \ref{MVN_example}, where we used the Mat\'ern covariance kernel.  Here we apply Sidi's $C^2$  periodization to $ f_{\textup{Genz}}$ \eqref{fGenzdef}, choose $d=3$ and $r=2$. The simulation results for this example function are summarized in Figures \ref{fig:mvn-guaranteed-MLE}, \ref{fig:mvn-guaranteed-FB}, and \ref{fig:mvn-guaranteed-GCV}.  In all cases, the Bayesian cubature returns an approximation within the prescribed error tolerance. We used the same setting as before with generic slow Bayesian cubature in \secref{MVN_example} for comparison. For error threshold $\varepsilon=10^{-5}$ with the empirical Bayes stopping criterion, our fast algorithm takes just under 0.01 second as shown in \figref{fig:mvn-guaranteed-MLE} whereas the basic algorithm takes over 20 seconds as shown in \figref{fig:MVN_Metern_d2b2}.

% breaking it a paragraph here, otherwise it looks big
Amongst the three stopping criteria, GCV achieves the desired tolerance faster than the others. 
One can also observe from the figures, the credible intervals are in general much wider than the true error.
This could be due to the periodized integrand being smoother than the $r=2$ kernel assumes. Perhaps one should consider smoother covariance kernels.

\begin{figure}
	\centering
	%d=3 problem transformed into d=2
	\includegraphics[width=0.98\linewidth]{"MVN_guaranteed_time_MLE_C2sin_d2_r2_2018-Sep-6"}
	\caption[Guaranteed:]{Multivariate normal probability example using the empirical Bayes stopping criterion.}
	\label{fig:mvn-guaranteed-MLE}
	\centering
	\includegraphics[width=0.98\linewidth]{"MVN_guaranteed_time_full_C2sin_d2_r2_2018-Sep-6"}
	\caption[MVN guaranteed : FB]{Multivariate normal probability example using the full Bayes stopping criterion.}
	\label{fig:mvn-guaranteed-FB}
	\centering
	\includegraphics[width=0.98\linewidth]{"MVN_guaranteed_time_GCV_C2sin_d2_r2_2018-Sep-6"}
	\caption[MVN guaranteed : GCV]{Multivariate normal probability example using the GCV stopping criterion.}
	\label{fig:mvn-guaranteed-GCV}
\end{figure}

\paragraph{Keister's Example.}

This multidimensional integral function comes from \cite{Kei96} and is inspired by a physics application:
\begin{align*}
\mu & =  \int_{\reals^d} \cos(\norm{ \vt}) \exp(-\norm{ \vt }^2) \, \dvt \\
\nonumber
%&  = 
%\int_{\reals^d} \cos(a\norm{ \vt}) \exp(-a^2\norm{ \vt }^2)  a^d \, \dvt \\
& = \int_{[0,1]^d} f_{\textup{Keister}}(\vx) \, \dvx,\\
\intertext{where }
f_\textup{Keister}(\vx) &= \pi^{d/2} \cos\left(\norm{ \Phi^{-1}(\vx)/2}\right)  ,
\end{align*}
and again $\Phi$ is the standard normal distribution.
The true value of $\mu$ can be calculated iteratively in terms of a quadrature as follows:  
\begin{equation*}
\mu = \frac{2 \pi^{d/2} I_c(d)}{\Gamma(d/2)}, \quad d=1,2, \ldots
\end{equation*}
where $\Gamma$ denotes the gamma function, and
\begin{align*}
I_c(1) &= \frac{\sqrt{\pi}}{2 \exp(1/4)}, 
\\
I_s(1) &= \int_{x=0}^\infty \exp(-\vx^T\vx)\sin(\vx) \, \dvx 
\\
& =  0.4244363835020225,
\\
I_c(2) &= \frac{1-I_s(1)}{2}, \qquad
I_s(2) = \frac{I_c(1)}{2}
\\
I_c(j) &= \frac{(j-2)I_c(j-2)-I_s(j-1)}{2},
\qquad j =3,4,\ldots
\\
I_s(j) &= \frac{(j-2)I_s(j-2)-I_c(j-1)}{2},
\qquad j =3,4,\ldots.
% ref: https://www.mathworks.com/help/matlab/ref/gamma.html
\end{align*}
\begin{figure}
	\centering
	\includegraphics[width=0.95\linewidth]{"Keister_guaranteed_time_MLE_C1sin_d4_r2_2018-Sep-6"}
	\caption[Keister guaranteed:MLE]{Keister example using the empirical Bayes stopping criterion.}
	\label{fig:keister-guaranteed-MLE}
%\end{figure}
%\begin{figure}
	\centering
	\includegraphics[width=0.95\linewidth]{"Keister_guaranteed_time_full_C1sin_d4_r2_2018-Sep-6"}
	\caption[Keister guaranteed:FB]{Keister example using the full Bayes stopping criterion.}
	\label{fig:keister-guaranteed-FB}
%\end{figure}
%\begin{figure}
	\centering
	\includegraphics[width=0.95\linewidth]{"Keister_guaranteed_time_GCV_C1sin_d4_r2_2018-Sep-6"}
	\caption[Keister guaranteed:GCV]{Keister example using the GCV stopping criterion.}
	\label{fig:keister-guaranteed-GCV}
\end{figure}

Figures \ref{fig:keister-guaranteed-MLE}, \ref{fig:keister-guaranteed-FB} and \ref{fig:keister-guaranteed-GCV} summarize the numerical tests for this integral.  We used the Sidi's $C^1$ periodization, dimension $d=4$, and $r=2$. 
As we can see, the GCV stopping criterion achieves faster results than the other stopping criteria, similarly to the multivariate normal case.

\paragraph{Option Pricing.}

The price of financial derivatives can often be modeled by high dimensional integrals. If the underlying asset is described in terms of a discretized geometric Brownian motion, then the fair price of the option is:
\begin{equation*}
\mu = \int_{\reals^d} \text{payoff}(\vz) \frac{\exp(\frac 12 \vz^T\mSigma^{-1}\vz)}{\sqrt{(2\pi)^d \det(\mSigma)}} \, \dvz = \int_{[0,1]^d} f(\vx) \, \dvx,
\end{equation*} 
where {payoff($\cdot$)} defines the discounted payoff of the option,
\begin{align*}
\mSigma &= (T/d) \bigl(\min(j,k) \bigr)_{j,k=1}^d = \mL \mL^T,\\
f(\vx) &= \text{payoff} \left(\mL 
\begin{pmatrix}
\Phi^{-1}(x_1) \\ \vdots \\ \Phi^{-1}(x_d)
\end{pmatrix} \right).
\end{align*}
The Asian arithmetic mean call option has a payoff of the form
\begin{align*}
\text{payoff}(\vz) &= \max\left( \frac 1d  \sum_{j=1}^d S_j(\vz) - K, 0 \right) \me^{-\upsilon T}, \\
\text{where}\;
S_j(\vz) &= S_0 \exp\bigl((\upsilon-\sigma^2/2)jT/d + \sigma \sqrt{T/d} z_j \bigr).
\end{align*}
Here, $T$ denotes the time to maturity of the option, $d$ the number of time steps, $S_0$ the initial price of the stock, $\upsilon$ the interest rate, $\sigma$ the volatility, and $K$ the strike price.

Figures \ref{fig:optprice-guaranteed-MLE}, \ref{fig:optprice-guaranteed-FB} and 
\ref{fig:optprice-guaranteed-GCV} summarize the numerical results for this example using
$
T = 1/4, \ \ d = 13, \ \ S_0 = 100, \ \ \upsilon =  0.05, \ \ \sigma = 0.5, \ \ K = 100.
$
Moreover, $\mL$ is chosen to be the matrix of eigenvectors of $\mSigma$ times the square root of the diagonal matrix of eigenvalues of $\mSigma$.
Because the integrand has a kink caused by the $\max$ function, it does not help to use a periodizing transform that is very smooth.  We choose the Baker's transform \eqref{eq:bakerTrans} and $r = 1$.

\begin{figure}
	\centering
	\includegraphics[width=0.95\linewidth]{"optPrice_guaranteed_time_MLE_Baker_d12_r1_2018-Sep-6"}
	\caption[Option pricing Guaranteed: MLE]{Option pricing using the empirical Bayes stopping criterion.}
	\label{fig:optprice-guaranteed-MLE}
%\end{figure}
%\begin{figure}
	\centering
	\includegraphics[width=0.95\linewidth]{"optPrice_guaranteed_time_full_Baker_d12_r1_2018-Sep-6"}
	\caption[OptPrice guaranteed : FB]{Option pricing using the full Bayes stopping criterion.}
	\label{fig:optprice-guaranteed-FB}
%\end{figure}
%\begin{figure}
	\centering
	\includegraphics[width=0.95\linewidth]{"optPrice_guaranteed_time_GCV_Baker_d12_r1_2018-Sep-6"}
	\caption[OptPrice guaranteed : GCV]{Option pricing using the  GCV stopping criterion.}
	\label{fig:optprice-guaranteed-GCV}
\end{figure}

In summary, the Bayesian cubature algorithm computes the integral within the user-specified threshold in nearly all of the test cases.  The rare exceptions occurred in the option pricing example for $\varepsilon=10^{-4}$. Our algorithm used the maximum allowed sample size and still did not reach the stopping criterion $\err_{\textup{CI}} \leq \varepsilon$, due to the complexity and high dimension of the integrand. 
%Also notice, our algorithm finished within 10 seconds for Keister and multivariate Normal examples while the option pricing took closer to 70 seconds, again due to the complexity of the integrand.
%FH it is difficult to compare apples to orances, and the timing depends on the error tolerances as well

A noticeable aspect from the plots is how much the error bounds differ from the true error. For option pricing example, the error bound is not as conservative as it is for the multivariate normal and Keister examples. A possible reason is that the latter integrands are significantly smoother than the covariance kernel assumed.  This is a matter for further investigation.

\iffalse
\subsection{Diagnostics for the Gaussian Process Assumption}

The starting point for our Bayesian cubature is the assumption that the integrand arises from a Gaussian process. This means that the function data, $\vf$ satisfy a multivariate Gaussian distribution, as in \eqref{eqn:fGaussDist}.  The transformed data, $\vZ = ( n\mLambda)^{-\frac 12} \mV^H(\vf - m \vone)$ has zero mean and is also uncorrelated because
\begin{align*}
\cov (\vZ) 
&= \frac 1n \Ex\left[  
\mLambda^{-\frac 12} \mV^H (\vf - m \vone)
(\vf - m \vone)^T \mV \mLambda^{-\frac 12}
\right]
\\
&=
 \mLambda^{-\frac 12} \mV^H 
\Ex\left[ (\vf - m \vone)
(\vf - m \vone)^T \right] \mV \mLambda^{-\frac 12}
\\
&=
\frac{1}{n} \mLambda^{-\frac 12} \mV^H 
\frac 1n \mV \mLambda \mV^H \mV \mLambda^{-\frac 12}
 = \mathsf{I}
\end{align*}
Thus, the elements of $\vZ$ are IID standard Gaussian random variables.

\figref{fig:mvn-normplot} and \figref{fig:keister-normplot} are normal probability plots of the $Z_i$ using empirical Bayes estimates of $m$ and $\vtheta$. \textbf{more goes here}.

\begin{figure}
	\centering
	\includegraphics[width=0.9\linewidth]{"figures/arbMean/Keister/C1sin/Keister Normplot d_2 bernoulli_2 Period_C1sin n_32768"}
	\caption{Normal plot : Keister function with arbMean assumption}
	\label{fig:keister-normplot}
\end{figure}

\begin{figure}
	\centering
	\includegraphics[width=0.9\linewidth]{"figures/arbMean/MVN/C1sin/MVN Normplot d_2 bernoulli_2 Period_C1sin n_32768"}
	\caption{Normal plot : MVN with arbMean assumption}
	\label{fig:mvn-normplot}
\end{figure}

\fi

\section{Discussion and Further Work}

We have developed a fast, automatic Bayesian cubature that estimates a multidimensional definite integral within a user defined error tolerance.  The stopping criteria arise from assuming the integrand to be a Gaussian process.  There are three approaches:  empirical Bayes, full Bayes, and generalized cross-validation.  The computational cost of the automatic Bayesian cubature can be dramatically reduced if the covariance kernel matches the nodes.  One such match in practice is rank-1 lattice nodes and shift-invariant kernels.  The matrix-vector multiplications can be accomplished using the fast Fourier Transform.  The performance of our automatic Bayesian cubature are illustrated using three integration problems.

Digital sequences and digital shift and/or scramble invariant kernels have the potential of being another match that satisfies the conditions in Section \ref{sec:fast_BC}.  The fast transform would correspond to a fast Walsh transform.

%For such kernels, periodicity is not assumed; however, special structure of both the sequences and the kernels are required to take advantage of integrand smoothness.

One should be able to adapt our Bayesian cubature to control variates, i.e., assuming  
\begin{equation*}
f = \mathcal{GP} \left( \beta_0 + \beta_1 g_1 + \cdots + \beta_p g_p, s^2 C \right),
\end{equation*}
for some choice of $g_1, \ldots, g_p$ whose integrals are known, and some parameters $\beta_0, \ldots, \beta_p$ in addition to $s$ and $C$.  The efficacy of this approach has not yet been explored.

%\section{Appendix}

%\iffalse
%\subsection{Properties of Multivariate Normal Distributions}

%\fi

\iffalse

% For one-column wide figures use
\begin{figure}
% Use the relevant command to insert your figure file.
% For example, with the graphicx package use
  \includegraphics{example.eps}
% figure caption is below the figure
\caption{Please write your figure caption here}
\label{fig:1}       % Give a unique label
\end{figure}
%
% For two-column wide figures use
\begin{figure*}
% Use the relevant command to insert your figure file.
% For example, with the graphicx package use
  \includegraphics[width=0.75\textwidth]{example.eps}
% figure caption is below the figure
\caption{Please write your figure caption here}
\label{fig:2}       % Give a unique label
\end{figure*}
%
% For tables use
\begin{table}
% table caption is above the table
\caption{Please write your table caption here}
\label{tab:1}       % Give a unique label
% For LaTeX tables use
\begin{tabular}{lll}
\hline\noalign{\smallskip}
first & second & third  \\
\noalign{\smallskip}\hline\noalign{\smallskip}
number & number & number \\
number & number & number \\
\noalign{\smallskip}\hline
\end{tabular}
\end{table}

\fi

\begin{acknowledgements}
This research was supported in part by the National Science Foundation grants DMS-1522687 and DMS-1638521 (SAMSI).
The authors would like to thank the organizers of the SAMSI-Lloyds-Turing Workshop on Probabilistic Numerical Methods, where a preliminary version of this work was discussed.  The authors also thank Chris Oates and Sou-Cheng Choi for valuable comments.
\end{acknowledgements}

% BibTeX users please use one of
%\bibliographystyle{spbasic}      % basic style, author-year citations
%\bibliographystyle{spmpsci}      % mathematics and physical sciences
%\bibliographystyle{spphys}       % APS-like style for physics
%\bibliography{}   % name your BibTeX data base
\bibliography{FJHown23,FJH23}
\bibliographystyle{spmpsci}

\iffalse
% Non-BibTeX users please use
\begin{thebibliography}{}
%
% and use \bibitem to create references. Consult the Instructions
% for authors for reference list style.
%
\bibitem{RefJ}
% Format for Journal Reference
Author, Article title, Journal, Volume, page numbers (year)
% Format for books
\bibitem{RefB}
Author, Book title, page numbers. Publisher, place (year)
% etc
\end{thebibliography}
\fi

\end{document}
% end of file template.tex

### 2019-03-01 BayesianCubaturePaper2018 - Rev1.tex
Fixed some more minor issues reported in editorial review

@@
  \text{for all } \va \ne 0, \;
- n\in \mathbb{N}, \; \vx_1, \ldots, \vx_n \in [0,1]^d.
+ n\in \mathbb{N}, \\
+ \vx_1, \ldots, \vx_n \in [0,1]^d, \; \text{s.t} \; \vx_i \neq \vx_j \forall i\neq j, \; 1 \leq i, j \leq n.
 \end{multline}
@@
 Rather than use maximum likelihood to determine $m$ and $s$ one can treat them as hyperparameters with a non-informative, conjugate prior, namely $\vrho_{m,s^2}(\xi, \lambda) \propto 1/\lambda$.
-Then the posterior density for the integral given the data using Bayes theorem is
+Let us assume integral $\mu$, a random variable, taking typical values $z$, then the posterior density for the $\mu$ given data $\vy$ using Bayes theorem is
 \begin{align*}
@@
 \err_{\textup{full}} 
-:= t_{n_j-1,0.995} \hsigma_{\textup{full}} > \err_\MLE .
+:= t_{n-1,0.995} \hsigma_{\textup{full}} > \err_\MLE .
 \end{align}
@@
 \label{sec:bayes_cubature_algo}
-The previous section presents three credible intervals, \eqref{eqn_prob_CI_MLE}, \eqref{eqn_prob_CI_full}, and \eqref{GCVCI}, for the $\mu$, the desired integral.
+The previous section presents three credible intervals, \eqref{eqn_prob_CI_MLE}, \eqref{eqn_prob_CI_full}, and \eqref{GCVCI}, for $\mu$, the desired integral.
 Each credible interval is based on different assumptions about the hyperparameters $m$, $s$, and $\vtheta$.
 We stress that one must estimate these hyperparameters or assume a prior distribution on them because the credible intervals are used as stopping criteria for our cubature rule.
-Since a credible intervals makes a statement about a typical function---not an outlier---one must try to ensure that the integrand is a typical draw from the assumed Gaussian process.
+Since a credible interval makes a statement about a typical function---not an outlier---one must try to ensure that the integrand is a typical draw from the assumed Gaussian process.
 
@@
 In contrast, this example in Section \ref{sec:NumExp} take less than a hundredth of a second to compute $\hmu_n$ once with $\varepsilon = 10^{-5}$ using our new algorithm.
-Not only is the Bayesian cubature with the the Mat\'ern kernel slow, but also $\mC$ becomes highly ill-conditioned as $n$ increases.
+Not only is the Bayesian cubature with the Mat\'ern kernel slow, but also $\mC$ becomes highly ill-conditioned as $n$ increases.
 So, Algorithm \ref{algorithm1}  in its current form is impractical. 
@@
 The width of the confidence interval is $\err_{\textup{full}}
-:= t_{n_j-1,0.995} \hsigma_{\textup{full}}$, where $\hsigma_{\textup{full}}^2$ can also be computed swiftly under assumptions \eqref{fastcompAssump}:
+:= t_{n-1,0.995} \hsigma_{\textup{full}}$, where $\hsigma_{\textup{full}}^2$ can also be computed swiftly under assumptions \eqref{fastcompAssump}:
 \begin{multline*} %\label{FJH:eq:signmaFull}
@@
 =
-t_{n_j-1,0.995}
+t_{n-1,0.995}
 \sqrt{\frac{1}{n(n-1)} \sum_{i=2}^n \frac{\abs{\widetilde{y}_i}^2}{\lambda_i}  \left(\frac{\lambda_1}{n}  - 1  \right)}.
@@
 \subsection{Eigenvectors}
-For general shift-invariance covariance functions, the Gram matrix takes the form
+For general shift-invariant covariance functions, the Gram matrix takes the form
 \begin{align*}
@@
 \err_{\textup{full}} 
-& = \frac{t_{n_j-1,0.995}}{n} \sqrt{
+& = \frac{t_{n-1,0.995}}{n} \sqrt{
 	\frac{\rlambda_1}{n-1} \sum_{i=2}^n \frac{\abs{\widetilde{y}_i}^2}{\lambda_i}
@@
 Since $\rlambda_1 = \lambda_1 - n$ and $\lambda_1 \sim n$ it follows $\rlambda_1/\lambda_1 \approx \rlambda_1/(n-1)$ and is small for  large $n$.
-Moreover, the credible intervals via empirical Bayes and full Bayes are similar, since $t_{n_j-1,0.995}$ is approximately $2.58$.
+Moreover, the credible intervals via empirical Bayes and full Bayes are similar, since $t_{n-1,0.995}$ is approximately $2.58$.
 The computational steps for the improved, faster, automatic Bayesian cubature are detailed in Algorithm \ref{algorithm2}.

### 2019-03-04 BayesianCubaturePaper2018 - Rev1.tex
Moved out full bayes derivations to Appendix and few other corrections

@@
 \usepackage{url}
+\usepackage[titletoc,title]{appendix}
 %\usepackage{refcheck}  % points out unused labels, refs ...
@@
 
-Suppose that the integrand, $f$, is drawn from a Gaussian process, i.e., $f \sim \mathcal{GP}(m,s^2 C_\vtheta)$.
+Suppose that the integrand, $f$, is drawn from a Gaussian process (\cite{BriEtal18a}, \cite{Dia88a}, \cite{OHa91a}, \cite{Rit00a}, \cite{RasGha03a}), i.e., $f \sim \mathcal{GP}(m,s^2 C_\vtheta)$.
 Specifically, $f$ has real-valued constant mean $m$ and covariance function $s^2C_\vtheta$, where $s$ is a non-negative scale factor, and $C_\vtheta: [0,1]^d \times [0,1]^d \to \mathbb{R} $ is a symmetric, positive-definite function and parameterized by $\vtheta$:
@@
  \text{for all } \va \ne 0, \;
- n\in \mathbb{N}, \\
- \vx_1, \ldots, \vx_n \in [0,1]^d, \; \text{s.t} \; \vx_i \neq \vx_j \forall i\neq j, \; 1 \leq i, j \leq n.
+ n\in \mathbb{N}, \qquad
+ \vx_1, \ldots, \vx_n \in [0,1]^d, \; \text{s.t} \; \\\vx_i \neq \vx_j \forall i\neq j, \; 1 \leq i, j \leq n.
 \end{multline}
@@
 \label{eqn_m_MLE}
-m_\MLE &= \frac{\vone^T \mCInv \vy }{ \vone^T \mCInv \vone}, \\
+m_\MLE &= \frac{\vone^T \mCInv \vy }{ \vone^T \mCInv \vone}, 
+\end{align}
+\begin{align}
 \nonumber
@@
 \frac{ (1 - \vone^T  \mCInv\vc )  \vone }{ \vone^T \mCInv \vone}   +  \vc 
-\right)^T  \mCInv \vy, \\
+\right)^T  \mCInv \vy,
+\end{align}
+\begin{align}
 \nonumber 
@@
 Here $c_0$, $\vc$, and $\mC$ are assumed implicitly to be based on $\vtheta = \vtheta_\MLE$.   
-
 \subsubsection{Full Bayes}
-
 Rather than use maximum likelihood to determine $m$ and $s$ one can treat them as hyperparameters with a non-informative, conjugate prior, namely $\vrho_{m,s^2}(\xi, \lambda) \propto 1/\lambda$.
@@
 & \hspace{2.5cm} \times  \rho_{\vf}(\vy | \xi, \lambda ) \rho_{m, s^2}(\xi, \lambda) \, \D \xi \D \lambda \\
-& \propto \displaystyle \int_{0}^\infty  \frac{1}{\lambda^{(n+3)/2}} \\
-& \times \int_{-\infty}^\infty  \exp \biggl( -\frac{1}{2\lambda}\biggl\{
-\frac{
-[z - \xi (1 - \vc^T \mC^{-1} \vone)  -  \vc^T \mC^{-1} \vy]^2}
-{c_0  -\vc ^T \mC^{-1} \vc}  \\
-& \hspace{1.8cm} + (\vy - \xi \vone)^T \mC^{-1}(\vy - \xi \vone) \biggr \} \biggr) \, \D \xi \D \lambda \\
-& \hspace{2.5cm}
-\text{by \eqref{eqn:fGaussDist}, \eqref{eqn:condInteg}} \; \text{and} \; \rho_{m,s^2}(\xi,\lambda) \propto 1/\lambda \\
-& \propto \displaystyle \int_{0}^\infty  \frac{1}{\lambda^{(n+3)/2}} \cdots \\ 
-& \qquad \cdots \int_{-\infty}^\infty  \exp\left( -\frac{\alpha \xi^2 -2 \beta \xi + \gamma}{2\lambda(c_0  -\vc ^T \mC^{-1} \vc)} \right) \, \D \xi \D \lambda, \\
-\intertext{where}
-\alpha & = (1 - \vc^T \mC^{-1} \vone)^2 + \vone^T \mC^{-1} \vone (c_0  -\vc ^T \mC^{-1} \vc),\\
-\beta & =(1 - \vc^T \mC^{-1} \vone)(z - \vc^T \mC^{-1} \vy ) \\
-& \qquad \qquad  + \vone^T \mC^{-1} \vy (c_0  -\vc ^T \mC^{-1} \vc),\\
-\gamma &  = (z - \vc^T \mC^{-1} \vy )^2  + \vy^T \mC^{-1} \vy (c_0  -\vc ^T \mC^{-1} \vc).
-\end{align*}
-In the derivation above and below, factors that are independent of $\xi$, $\lambda$, or $z$ can be discarded since we only need to preserve the proportion.
-But, factors that depend on $\xi$, $\lambda$, or $z$ must be kept.
-%Completing the square allows us to compute the integral with respect to $\xi$:
-Completing the square, $
-\alpha \xi^2 -2 \beta \xi + \gamma 
-= \alpha (\xi -\beta/\alpha)^2  - (\beta^2/\alpha) + \gamma,
-$
-allows us to evaluate the integrals with respect to $\xi$ and $\lambda$:
-\begin{align*}
-\MoveEqLeft{\rho_{\mu}(z | \vf = \vy)} \\
-& \propto \displaystyle \int_{0}^\infty  \frac{1}{\lambda^{(n+3)/2}}  \exp\left( -\frac{  \gamma - \beta^2/\alpha}{2\lambda(c_0  -\vc ^T \mC^{-1} \vc)} \right)  \cdots \\
-& \qquad \qquad \cdots \int_{-\infty}^\infty  \exp\left( -\frac{\alpha (\xi -\beta/\alpha)^2}{2\lambda(c_0  -\vc ^T \mC^{-1} \vc)} \right) \, \D \xi \D \lambda \\
-& \propto \displaystyle \int_{0}^\infty  \frac{1}{\lambda^{(n+2)/2}}  \exp\left( -\frac{  \gamma - \beta^2/\alpha}{2\lambda(c_0  -\vc ^T \mC^{-1} \vc)} \right) \D \lambda \\
-& \propto \left(\gamma - \frac{\beta^2}{\alpha}\right)^{-n/2} \propto \left(\alpha \gamma - \beta^2\right)^{-n/2}.
-\end{align*}
-Finally, we simplify the key term via straightforward calculations to the following:
-\begin{align*}
-\alpha \gamma - \beta^2 \propto 1 +  \frac{(z - \hmu_{\textup{MLE}})^2}{(n-1)\widehat{\sigma}_{\textup{full}}^2}, \\
+& \propto \left( 1 +  \frac{(z - \hmu_{\textup{MLE}})^2}{(n-1)\widehat{\sigma}_{\textup{full}}^2} \right)^{-n/2}, \text{  (by Appendix \ref{appendix:full_bayes})}
 \end{align*}
@@
 Because the shape parameter, $\vtheta$, enters the definition of the covariance kernel in a non-trivial way, the only way to treat it as a hyperparameter and assign a tractable prior would be for the prior to be discrete.
-We believe in practice that choosing such a prior involves more guesswork than using the empirical Bayes estimate of $\vtheta$ in \eqref{eqn:thetaMLE} or the cross-validation approach described next.
+We believe in practice that choosing such a prior involves more guesswork, so we choose to use either empirical Bayes estimate of $\vtheta$ in \eqref{eqn:thetaMLE} or cross-validation approach described next.
 
@@
 \begin{align*}
-m_{\textup{GCV}} = \frac{\vone^T \mC^{-2} \vy}{\vone^T \mC^{-2} \vone},\\ 
+m_{\textup{GCV}} = \frac{\vone^T \mC^{-2} \vy}{\vone^T \mC^{-2} \vone},
 \end{align*}
@@
 \vtheta_{\textup{GCV}} = \argmin_\vtheta \biggl\{\log \left(  \vy^T \left[\mC^{-2} - \frac{\mC^{-2} \vone \vone^T \mC^{-2}}{\vone^T \mC^{-2} \vone}  \right] \vy \right)  \\
-- 2 \log \left ( \trace(\mC^{-1}) \right ) \biggr\} .
+- 2 \log \left ( \trace(\mC^{-1}) \right ) \biggr\}.
 \end{multline}
-Plugging this value of $m$ into \eqref{eqn:BayesCub} yields
+Plugging the value of $m_\GCV$ into \eqref{eqn:BayesCub} yields
 \begin{align}
@@
 \label{eqn:GaussDef}
-\mu = \int_{(\va,\vb)} \frac{\exp\bigl(- \frac 12 \vt^T \mSigma^{-1} \vt \bigr)}{\sqrt{(2 \pi)^d \det(\mSigma)}} \, \dvt,
-\end{align}
-where $(\va,\vb)$ is a finite, semi-infinite or infinite box in $\reals^d$.  This integral does not have an analytic expression for general $\mSigma$, so cubatures are required.
+\mu = \int_{(\va,\vb)} \frac{\exp\bigl(- \frac 12 \vt^T \mSigma^{-1} \vt \bigr)}{\sqrt{(2 \pi)^{d'} \det(\mSigma)}} \, \dvt,
+\end{align}
+where $(\va,\vb)$ is a finite, semi-infinite or infinite box in $\reals^{d'}$.  This integral does not have an analytic expression for general $\mSigma$, so cubatures are required.
 
@@
 \end{align}
-where $\Phi$ is the cumulative standard normal distribution function.  Then, $\mu = \int_{[0,1]^{d-1}} f_{\text{Genz}}(\vx) \, \dvx$.
+where $\Phi$ is the cumulative standard normal distribution function.  Then, $\mu = \int_{[0,1]^{d'-1}} f_{\text{Genz}}(\vx) \, \dvx$.
 
@@
 	%\end{subfigure}
-	\caption{The $d=3$ multivariate normal probability transformed to an integral of $f_{\text{Genz}}$ with  $d=2$. This plot can be reproduced using \code{IntegrandPlots.m} in GAIL}
+	\caption{The $d'=3$ multivariate normal probability transformed to an integral of $f_{\text{Genz}}$ with  $d=2$. This plot can be reproduced using \code{IntegrandPlots.m} in GAIL}
 	\label{fig:MVN_Genz}
@@
 \begin{align*}
-d = 3, \quad \va = \begin{pmatrix}
+d' = 3, \quad \va = \begin{pmatrix}
 -6 \\ -2 \\ -2
@@
 \end{align}
-where $\mV^H$ is the Hermitian of $\mV$.  The columns of matrix $\mV$ are eigenvectors of $\mC$, and $\mLambda$ is a diagonal matrix of eigenvalues of $\mC$.
+where $\mV^H$ is the Hermitian of $\mV$, $\vC_1,...,\vC_n$ are columns of $\mC$.
+$\vV_1,...,\vV_n$ are columns of $\mV$ and $\vv_1,...,\vv_n$ are rows of $\mV$.
+The columns of matrix $\mV$ are eigenvectors of $\mC$, and $\mLambda$ is a diagonal matrix of eigenvalues of $\mC$.
 For any $n \times n$ vector $\vb$, define the notation  $\widetilde{\vb} := \mV^H \vb$.
@@
 \widetilde{\vone}
-& = \mV^H \vone = \mV^H \vV_1 = \begin{pmatrix}n  \\ 0 \\ \vdots \\ 0 \end{pmatrix}.
+& = \mV^H \vone = \mV^H \vV_1 = 
+\left(n, 0, \dots, 0 \right)^T.
+% \begin{pmatrix}n  \\ 0 \\ \vdots \\ 0 \end{pmatrix}.
 \label{eqn:fast_transform_one}
@@
 \nonumber
-m_\MLE &=  \frac{\widetilde{y}_1}{n} = \frac 1n \sum_{i=1}^n y_i.
+m_\MLE &=  \frac{\widetilde{y}_1}{n} = \frac 1n \sum_{i=1}^n y_i,
 \\
@@
 \frac{1}{n^2} 
-\sum_{i=2}^n \frac{\abs{\widetilde{y}_i}^2}{\lambda_i}. \\
-\nonumber
+\sum_{i=2}^n \frac{\abs{\widetilde{y}_i}^2}{\lambda_i},
+\end{align}
+\begin{align}
+\label{eqn_MLE_loss_func_optimized_2} %\nonumber
 \vtheta_\MLE
@@
 \sum_{i=2}^n \frac{\abs{\widetilde{y}_i}^2}{\lambda_i}
-\right) \right .\\
-\label{eqn_MLE_loss_func_optimized_2}
-& \hspace{3cm} \left .
-  + 
-\frac{1}{n}\sum_{i=1}^n \log(\lambda_i)
-\right].
-\\
+\right) %\right .\\ \hspace{3cm} \left .
+ + \frac{1}{n}\sum_{i=1}^n \log(\lambda_i)
+\right],
+\end{align}
+\begin{align}
 \nonumber
@@
 \frac{\widetilde{y}_1}{n} +
-\frac 1n \sum_{i=2}^n \frac{ \widetilde{c}_i^* \widetilde{y}_i}{\lambda_i}. \\
+\frac 1n \sum_{i=2}^n \frac{ \widetilde{c}_i^* \widetilde{y}_i}{\lambda_i}, \\
 \nonumber
@@
 \nonumber 
-s^2_{\textup{GCV}} & : =  \frac 1{n} \sum_{i=2}^n \frac{\abs{\widetilde{y}_i}^2}{\lambda_i^2}  \left [ \sum_{i=1}^n \frac{1}{\lambda_i} \right]^{-1}, \\
+s^2_{\textup{GCV}} & : =  \frac 1{n} \sum_{i=2}^n \frac{\abs{\widetilde{y}_i}^2}{\lambda_i^2}  \left [ \sum_{i=1}^n \frac{1}{\lambda_i} \right]^{-1}, 
+\end{align}
+\begin{align}
 \nonumber 
@@
 \prod_{l=1}^d \biggl[
-1 - (-1)^{r} \gamma B_{2r}( |{x_l-t_l}| ) \biggr], \\  
-\forall \vt,\vx \in [0,1]^d, \  \vtheta = (r,\gamma), \ r \in \naturals, \ \gamma > 0.
+1 - (-1)^{r} \eta B_{2r}( |{x_l-t_l}| ) \biggr], \\  
+\forall \vt,\vx \in [0,1]^d, \  \vtheta = (r,\eta), \ r \in \naturals, \ \eta > 0.
 \end{multline}
@@
 Larger $r$ implies a greater degree of smoothness of the kernel.
-Larger $\gamma$ implies greater fluctuations of the output with respect to the input.
-Plots of $C(\cdot, 0.3)$ are given in \figref{fig:fourierkernel-dim1} for various $r$ and $\gamma$ values.
+Larger $\eta$ implies greater fluctuations of the output with respect to the input.
+Plots of $C(\cdot, 0.3)$ are given in \figref{fig:fourierkernel-dim1} for various $r$ and $\eta$ values.
 
@@
 \begin{prop}
-Any periodic, symmetric, positive definite, shift-invariant covariance kernel of the form \eqref{eq:shInv} scaled to satisfy \eqref{addAssump}, when matched with rank-1 lattice data-sites, must satisfy assumptions \eqref{fastcompAssump}.
+Any symmetric, positive definite, shift-invariant covariance kernel of the form \eqref{eq:shInv} scaled to satisfy \eqref{addAssump}, when matched with rank-1 lattice data-sites, must satisfy assumptions \eqref{fastcompAssump}.
 The \emph{fast Fourier transform} (FFT) can be used to expedite the estimates of $\vtheta$ in \eqref{thetaSimple} and the credible interval widths \eqref{fastStoppingCriterions} in $\Order(n \log(n))$ operations.
@@
 
+\begin{appendices}
+\section{Details of full Bayes posterior} \label{appendix:full_bayes}
+Let us start with given integral $\mu$, a random variable, taking typical values $z$, then the posterior density for the $\mu$ given data $\vy$ using Bayes theorem is
+\begin{align*}
+\MoveEqLeft[1]{\rho_{\mu}(z | \vf = \vy)} \\
+& \propto \int_{0}^\infty \int_{-\infty}^\infty \rho_{\mu}(z | \vf = \vy, m = \xi, s^2 = \lambda) \\
+& \hspace{2.5cm} \times  \rho_{\vf}(\vy | \xi, \lambda ) \rho_{m, s^2}(\xi, \lambda) \, \D \xi \D \lambda \\
+& \propto \displaystyle \int_{0}^\infty  \frac{1}{\lambda^{(n+3)/2}} \\
+& \times \int_{-\infty}^\infty  \exp \biggl( -\frac{1}{2\lambda}\biggl\{
+\frac{
+	[z - \xi (1 - \vc^T \mC^{-1} \vone)  -  \vc^T \mC^{-1} \vy]^2}
+{c_0  -\vc ^T \mC^{-1} \vc}  \\
+& \hspace{1.8cm} + (\vy - \xi \vone)^T \mC^{-1}(\vy - \xi \vone) \biggr \} \biggr) \, \D \xi \D \lambda \\
+& \hspace{2.5cm}
+\text{by \eqref{eqn:fGaussDist}, \eqref{eqn:condInteg}} \; \text{and} \; \rho_{m,s^2}(\xi,\lambda) \propto 1/\lambda \\
+& \propto \displaystyle \int_{0}^\infty  \frac{1}{\lambda^{(n+3)/2}} \cdots \\ 
+& \qquad \cdots \int_{-\infty}^\infty  \exp\left( -\frac{\alpha \xi^2 -2 \beta \xi + \gamma}{2\lambda(c_0  -\vc ^T \mC^{-1} \vc)} \right) \, \D \xi \D \lambda,
+\end{align*}
+where
+\begin{align*}
+\alpha & = (1 - \vc^T \mC^{-1} \vone)^2 + \vone^T \mC^{-1} \vone (c_0  -\vc ^T \mC^{-1} \vc),\\
+\beta & =(1 - \vc^T \mC^{-1} \vone)(z - \vc^T \mC^{-1} \vy ) \\
+& \qquad \qquad  + \vone^T \mC^{-1} \vy (c_0  -\vc ^T \mC^{-1} \vc),\\
+\gamma &  = (z - \vc^T \mC^{-1} \vy )^2  + \vy^T \mC^{-1} \vy (c_0  -\vc ^T \mC^{-1} \vc).
+\end{align*}
+In the derivation above and below, factors that are independent of $\xi$, $\lambda$, or $z$ can be discarded since we only need to preserve the proportion.
+But, factors that depend on $\xi$, $\lambda$, or $z$ must be kept.
+%Completing the square allows us to compute the integral with respect to $\xi$:
+Completing the square, $
+\alpha \xi^2 -2 \beta \xi + \gamma 
+= \alpha (\xi -\beta/\alpha)^2  - (\beta^2/\alpha) + \gamma,
+$
+allows us to evaluate the integrals with respect to $\xi$ and $\lambda$:
+\begin{align*}
+\MoveEqLeft{\rho_{\mu}(z | \vf = \vy)} \\
+& \propto \displaystyle \int_{0}^\infty  \frac{1}{\lambda^{(n+3)/2}}  \exp\left( -\frac{  \gamma - \beta^2/\alpha}{2\lambda(c_0  -\vc ^T \mC^{-1} \vc)} \right)  \cdots \\
+& \qquad \qquad \cdots \int_{-\infty}^\infty  \exp\left( -\frac{\alpha (\xi -\beta/\alpha)^2}{2\lambda(c_0  -\vc ^T \mC^{-1} \vc)} \right) \, \D \xi \D \lambda \\
+& \propto \displaystyle \int_{0}^\infty  \frac{1}{\lambda^{(n+2)/2}}  \exp\left( -\frac{  \gamma - \beta^2/\alpha}{2\lambda(c_0  -\vc ^T \mC^{-1} \vc)} \right) \D \lambda \\
+& \propto \left(\gamma - \frac{\beta^2}{\alpha}\right)^{-n/2} \propto \left(\alpha \gamma - \beta^2\right)^{-n/2}.
+\end{align*}
+Finally, we simplify the key term via straightforward calculations to the following:
+\begin{align*}
+\alpha \gamma - \beta^2 \propto 1 +  \frac{(z - \hmu_{\textup{MLE}})^2}{(n-1)\widehat{\sigma}_{\textup{full}}^2}, \\
+\end{align*}
+where 
+\begin{multline*}
+\hsigma^2_{\textup{full}} 
+:= \frac{1}{n-1}
+\vy^T\left[ \mC^{-1} 
+- \frac{ \mC^{-1} \vone\vone^T \mC^{-1}}{\vone^T \mC^{-1} \vone}  \right]\vy
+\\ 
+\times  \left[\frac{(1 - \vc^T \mC^{-1} \vone)^2}{\vone^T \mC^{-1} \vone} + (c_0  -\vc ^T \mC^{-1} \vc) \right].
+\end{multline*}
+\end{appendices}
+
 \iffalse

### 2019-04-23 BayesianCubaturePaper2018 - Rev1.tex
Minor updates based on Reviewer2 comments

@@
 \end{align}
-where $\Phi$ is the cumulative standard normal distribution function.  Then, $\mu = \int_{[0,1]^{d'-1}} f_{\text{Genz}}(\vx) \, \dvx$.
+where $\Phi$ is the cumulative standard normal distribution function.
+Then, $\mu = \int_{[0,1]^{d'-1}} f_{\text{Genz}}(\vx) \, \dvx$.
+As we can see, this approach transforms $d'$ integral into a $d=d'-1$ integral.
 
@@
 	%\end{subfigure}
-	\caption{The $d'=3$ multivariate normal probability transformed to an integral of $f_{\text{Genz}}$ with  $d=2$. This plot can be reproduced using \code{IntegrandPlots.m} in GAIL}
+	\caption{The $d'=3$ multivariate normal probability transformed to an integral of $f_{\text{Genz}}$ of $d=2$. This plot can be reproduced using \code{IntegrandPlots.m} in GAIL}
 	\label{fig:MVN_Genz}
@@
 \end{align*}
+Here we show the resulting matrix $\mC$ is circulant.
+Then using the well known fact, circulant matrices are diagonalized by discrete Fourier transform (DFT), one can obtain the eigenvectors analytically and the eigenvalues using DFT.
+% The speedup of their algorithm is in the linear algebra part of the calculations. 
+% But the derivation in Sections 4.3 and 4.4 can be obtained much faster by realising that their definition of the covariance matrix,
+By the definition of $\mC$, $i,j$th element
+\begin{align*}
+\mC_{i,j} & = K( x_i - x_j \bmod 1 ) \\
+&= K\bigl( \bigl(\vh \phi(i-1) - \vh \phi(j-1)\bigr) \bmod 1 \bigr) 
+\end{align*}
+Noting that the sequence $\{\phi(i-1)\}_{i=1}^n$ is a re-ordering of $0, \ldots, 1-1/n$ for $n$ a power of $2$, and $\vh$ is a vector integers, one can rewrite
+\begin{align*}
+\mC_{i,j} &= K_{\vh}\bigl( \bigl(\pi_{2^m}(i-1) - \pi_{2^m}(j-1)\bigr) \bmod 2^m \bigr)
+\end{align*}
+where $\pi_{2^m}(i-1) = 2^m\phi(i-1)$ is the ''integer version'' of the radical inverse function for the full initial sequence of $2^m$ points and $K_{\vh}(\vt) = K(\vh^T \vt)$. By similar approach
+\begin{align*}
+\mC_{i,j} &= K_{\vh,\pi_{2^m}}( (i-1) - (j-1) \bmod 2^m ) , 
+\\
+& \hspace{4cm} \text{for}\; i,j=1,...,2^m ,
+\end{align*}
+is a permutation of a circulant matrix.
+
+The function $\pi_{2^m}$ is a permutation on $\{0, 1, ..., 2^m-1\}$, undoing this
+permutation on the rows and columns of the matrix $\mC$ one obtains a circulant
+matrix:
+$P_{2^m}^T \mC P_{2^m}$.
+%The current Sections 4.3 and 4.4 are therefore not needed. See further.
+Eigenvectors of the circulant matrices are 
+\begin{align} \label{latticeVdef}
+\mV = \Bigl ( \me^{2 \pi n \sqrt{-1} \phi(i-1)\phi(j-1)} \Bigr)_{i,j = 1}^n.
+\end{align}
+and the eigenvalues are
+\begin{align*}
+\vlambda = \mV \vC_1
+\end{align*}
+which automatically follow from the properties of circulant matrices.
+This proves the assumption $\eqref{fastcompAssumpB}$.
+
+\iftrue
+\JRNote{Original content of Section 4.3 begins from here:}
 
@@
 Furthermore, $\mV$ is the matrix of eigenvectors, which satisfies assumption \eqref{fastcompAssumpA}.
+\fi
 
@@
 Let $\mV^{(n)}$ denote the $n \times n$ matrix $\mV$ defined in  \eqref{latticeVdef}.
-We show how to compute $\mV^{(2n)H}\vb$ quickly for all $\vb \in \reals^{2n}$ assuming that $\mV^{(n)H}\vb$ can be computed quickly for all $\vb \in \reals^n$.
+One can compute $\mV^{(2n)H}\vb$ quickly for all $\vb \in \reals^{2n}$ assuming that $\mV^{(n)H}\vb$ can be computed quickly for all $\vb \in \reals^n$, using the butterfly structure of the Fast Fourier Transform (FFT).
+For the brevity, we only provide the results.
 
@@
 \widetilde{\vb}^{(1)} &= \left( \sum_{j=1}^{2n}  \me^{-4 \pi n \sqrt{-1} \phi(2i-2)\phi(j-1)} b_{j} \right)_{i=1}^n \\
-&= \left( \sum_{j=1}^{2n}  \me^{-2 \pi n \sqrt{-1} \phi(i-1)\phi(j-1)} b_{j} \right)_{i=1}^n \quad \text{by \eqref{vdCProp}}\\
-&= \left( \sum_{j=1}^{n}  \me^{-2 \pi n \sqrt{-1} \phi(i-1)\phi(j-1)} b_{j} \right)_{i=1}^n \quad \\
-&\qquad \qquad +  \left( \sum_{j=1}^{n}  \me^{-2 \pi n \sqrt{-1} \phi(i-1)\phi(n+j-1)} b_{n+j} \right)_{i=1}^n \\
-&= \mV^{(n)H}\vb^{(1)}  +  \biggl(  \me^{-\pi \sqrt{-1} \phi(i-1)}  \\
-& \quad \times \sum_{j=1}^{n}  \me^{-2 \pi n \sqrt{-1} \phi(i-1)\phi(j-1)} b_{n+j} \biggr)_{i=1}^n \quad  \text{by \eqref{vdCPropB}}\\
+% &= \left( \sum_{j=1}^{2n}  \me^{-2 \pi n \sqrt{-1} \phi(i-1)\phi(j-1)} b_{j} \right)_{i=1}^n \quad \text{by \eqref{vdCProp}}\\
+% &= \left( \sum_{j=1}^{n}  \me^{-2 \pi n \sqrt{-1} \phi(i-1)\phi(j-1)} b_{j} \right)_{i=1}^n \quad \\
+% &\qquad \qquad +  \left( \sum_{j=1}^{n}  \me^{-2 \pi n \sqrt{-1} \phi(i-1)\phi(n+j-1)} b_{n+j} \right)_{i=1}^n \\
+% &= \mV^{(n)H}\vb^{(1)}  +  \biggl(  \me^{-\pi \sqrt{-1} \phi(i-1)}  \\
+% & \quad \times \sum_{j=1}^{n}  \me^{-2 \pi n \sqrt{-1} \phi(i-1)\phi(j-1)} b_{n+j} \biggr)_{i=1}^n \quad  \text{by \eqref{vdCPropB}}\\
 &= \mV^{(n)H}\vb^{(1)} +  \left(  \me^{-\pi \sqrt{-1} \phi(i-1)} \right)_{i=1}^n \odot \bigl(\mV^{(n)H}\vb^{(2)} \bigr),
@@
 \widetilde{\vb}^{(2)} &= \left( \sum_{j=1}^{2n}  \me^{-4 \pi n \sqrt{-1} \phi(2i-1)\phi(j-1)} b_{j} \right)_{i=1}^n \\
-&= \left( \sum_{j=1}^{2n}  \me^{-2 \pi n \sqrt{-1} [\phi(i-1)+1]\phi(j-1)} b_{j} \right)_{i=1}^n \quad \text{by \eqref{vdCProp}}\\
-&= \left( \sum_{j=1}^{n}  \me^{-2 \pi n \sqrt{-1} [\phi(i-1)+1]\phi(j-1)} b_{j} \right)_{i=1}^n \quad \\
-&\qquad  +  \left( \sum_{j=1}^{n}  \me^{-2 \pi n \sqrt{-1} [\phi(i-1)+1]\phi(n+j-1)} b_{n+j} \right)_{i=1}^n \\
-&= \mV^{(n)H}\vb^{(1)} 
-+  \left(  \me^{ -\pi \sqrt{-1} [\phi(i-1) + 1]} \right. 
-\\
-& \qquad \qquad \left . \times \sum_{j=1}^{n}  \me^{-2 \pi n \sqrt{-1} \phi(i-1)\phi(j-1)} b_{n+j} \right)_{i=1}^n \\
-& \hspace{4cm}  \text{by \eqref{vdCPropB} and \eqref{vdCPropC}}\\
+% &= \left( \sum_{j=1}^{2n}  \me^{-2 \pi n \sqrt{-1} [\phi(i-1)+1]\phi(j-1)} b_{j} \right)_{i=1}^n \quad \text{by \eqref{vdCProp}}\\
+% &= \left( \sum_{j=1}^{n}  \me^{-2 \pi n \sqrt{-1} [\phi(i-1)+1]\phi(j-1)} b_{j} \right)_{i=1}^n \quad \\
+% &\qquad  +  \left( \sum_{j=1}^{n}  \me^{-2 \pi n \sqrt{-1} [\phi(i-1)+1]\phi(n+j-1)} b_{n+j} \right)_{i=1}^n \\
+% &= \mV^{(n)H}\vb^{(1)} +  \left(  \me^{ -\pi \sqrt{-1} [\phi(i-1) + 1]} \right. \\
+% & \qquad \qquad \left . \times \sum_{j=1}^{n}  \me^{-2 \pi n \sqrt{-1} \phi(i-1)\phi(j-1)} b_{n+j} \right)_{i=1}^n \\
+% & \hspace{4cm}  \text{by \eqref{vdCPropB} and \eqref{vdCPropC}}\\
 &= \mV^{(n)H}\vb^{(1)} -  \left(  \me^{-\pi \sqrt{-1} \phi(i-1)} \right)_{i=1}^n \odot \bigl(\mV^{(n)H}\vb^{(2)} \bigr).
@@
 
-Define a new function $\rC : = C -1$, and its associated Gram matrix $\rmC = \mC - \vone \vone^T$.
+The shift-invariant kernel of our interest \eqref{the_kernel_eqn_bernoulli} has the form $C = 1 + \rC$. 
+One could take advantage of it to avoid the subtraction in $1-n/\lambda_1$. 
+Define the new function $\rC : = C -1$, and its associated Gram matrix $\rmC = \mC - \vone \vone^T$, where $\rmC$ is simply the original kernel after discarding ``$1$", there is no actual subtraction involved in the computation.
+So we are not really shifting the cancellation error to another place.
 Note that $\rC$ inherits the shift-invariant properties of $C$.  
-Since $\vone$ is the first eigenvector of $\mC$, it follows that the eigenvalues of $\rmC$ are $\rlambda_1 = \lambda_1 - n, \lambda_2, \ldots, \lambda_n$.
-Moreover,
+Since $\vone$ is the first eigenvector of $\mC$, it follows that the eigenvalues of $\rmC$ are $\rlambda_1 = \lambda_1 - n, \lambda_2, \ldots, \lambda_n$.  Moreover,
 \begin{equation*}
@@
 allows us to write $\mu$ in the form of \eqref{eqn:defn_mu}, where $f(\vx) = g(\vPsi(\vx))$.
-
-A family of variable transforms take the form
+Also called tent transform, $\Psi'(x)$ is not defined, not suitable when the $f$ is required to have also smooth derivatives.
+
+A family of variable transforms that also provide some derivatives take the form
 \begin{subequations} %\label{eq:varTrans}

### 2019-06-17 ResponseToReferees.tex
Updates from Overleaf

\documentclass{amsart}

\usepackage{xcolor}

\voffset -1in
\hoffset -0.75in
\textheight 9in
\textwidth 6.5in

\newcommand{\vV}{\boldsymbol{V}}
\newcommand{\vone}{\boldsymbol{1}}

\begin{document}
\title[Response for Fast Automatic Bayesian Cubature]{Response to Referees of the manuscript \\
\emph{Fast Automatic Bayesian Cubature Using Lattice Sampling}}
\maketitle

\newcommand{\Response}[1]{{\color{blue}#1}}
\renewcommand{\vec}[1]{\boldsymbol{#1}}

Thanks to the the referees and the editors for their helpful comments.  We have revised our manuscript in light of these comments, which we address point-by-point below.

\section*{Reviewer 1: The paper is an interesting read on Bayesian cubature \ldots}

The speedup of their algorithm is in the linear algebra part of the
calculations. But the derivation in Sections 4.3 and 4.4 can be obtained much
faster by realising that their definition of the covariance matrix, \ldots 
is a permutation of a circulant matrix from which all required properties follow. \ldots The current Sections 4.3 and 4.4 are therefore not
needed. \Response{We have altered these sections.}

A second contribution is made in section 4.5 titled 'Overcoming cancellation
error', but here it is not so clear to me if what is proposed will really help.
See further.

\begin{itemize}
\item Abstract
\begin{itemize}
\item The second sentence doesn't make sense to me.
\item In the third sentence I would replace 'postulates' with 'considers'.
\end{itemize}

\item Section 1
\begin{itemize}
\item The authors write 'We construct a reliable stopping criterion' but it is
unclear what they mean with 'reliable'.
\item On page 2 they write 'If function evaluation is expensive, then $\$(f)$ might
be similar in magnitude to $\log(n)$.': this makes no sense as evaluating $f$
depends on the dimension $d$. So this depends on how big $n$ is and if we want more
accuracy then $n$ becomes bigger.
\end{itemize}

\item Section 2
\begin{itemize}
\item '$f$ is drawn from a Guaussian process': it should be explained what this
means, e.g., does it mean $f$ is the Gaussian function with unknown mean and
covariance, or does it behave like this in expectation, or \ldots This sounds like
a very strong assumption.
\item It should maybe be mentioned here that there are hyper distributions for the
hyper parameters.
\item It is never said how the $x_i$ are sampled. Does (5a) hold for any
distribution of samples $x_i$?
\item In this section there are different quantities being defined: the matrix
$C_{\vec{\theta}}$ which involves evaluating the covariance function, $c_0$ which
involves integrating the covariance function and $\vec{c}$ which involves
calculating integrals of the covariance function with one leg fixed to a sample
point. Only at the end the authors say that they assume these things to be
cheap. I think this should be spelled out immediately.
\item  It think is not a good idea to leave out the dependence on $\vec{\theta}$ for
$C$. E.g. in (11) the $\vec{\theta}$ is not visible at all in the expression to be
minimized for it. The $C$ without subscript also clashes that of lemma 1.
\item  The lead in to lemma 1 makes it feel like this is a field specific lemma but
in fact it is just the well known conditional gaussian. Please write something
like 'We need the following lemma on conditional normal distribution ...'.
\item  Do not use $C$ in this lemma.
\item  The other derivations in the paper are all made in prose. It would be better
to formally state some of them. E.g., the results on the top of page 3.
\item  From (6) to (7) the notation is different: $c^T C^{-1} 1$ vs $1^T C^{-1} c$,
this might be corrected.
\end{itemize}

\item Section 2.2.1
\begin{itemize}
\item It would help to see the dependence on $\vec{\theta}$ in (9), (10) and (11).
\item It looks like (11) is independent of $m_{\text{MLE}}$ and $s^2_{\text{MLE}}$, how does it pop up?
Otherwise we could just first optimize for $\vec{\theta}$, then for m and then
for $s^2$.
\end{itemize}

\item Section 2.2.2
\begin{itemize}
\item I cannot follow the derivation.
\item At the end of the section the authors say that this is not a good method.
Why then list it? Maybe the final paragraph needs to be rewritten.
\end{itemize}

\item Section 2.3. The authors stress here that the integrand must be a 'typical' draw from the assumed Gaussian process and not an outlier. That sounds scary.

\item Section 2.4. Please use $d'$ for the dimension of the original integral in (22) and
immediately say that the dimension for the computation is $d = d' - 1$, 'as will
now be explained \ldots'. So put $d'$ after the display (22) and in the display (23)
and update the formula for $\mu$ at the bottom of the page and the display on the
next page. After these changes you can keep the '$d=2$' in the caption of Fig 2.

\item Section 3
\begin{itemize}
\item Maybe write 'previous section' instead of 'last section'.
-- Maybe write 'covariance kernel' instead of just 'kernel'. I think the word
kernel hasn't been used up till this point.
\end{itemize}

\item Section 3.1. Use $C_{\vec{\theta}}$ in (27) for clarity.

\item Section 3.3. Elaborate on what is meant with the second sentence.

\item Sections 4.2, 4.3 and 4.4. 
The definition (35) makes it that the covariance matrix $C$ is a permutation
of a circulant matrix. \ldots

\item  Section 4.5. 
\begin{itemize}
    \item The authors present an alternative form of calculating the matrix $C$ for
covariance functions of the particular product form in Section 4.2 \ldots I think they are right that this is a good
way of calculating Ccirc without doing the -1 at the end.
However, it is not clear whether this will actually help. \ldots It is not clear to me if operating
the FFT on the first (permuted) column of $\mathring{C}$ in this form is not going to
increase the error on $\mathring{\lambda}_1$, so putting the numerical error elsewhere.

\item Please delete the word 'periodic' in proposition 1, this is covered by the
shift-invariantness.
\end{itemize}

\item Section 5.1. The Baker's transform is introduced first and then the authors talk about
more general transforms without saying so. For the Baker's transform the
substitution written with $\Psi'$ is undefined. This paragraph should be
restructured.

\end{itemize}

\section*{Reviewer 2: The authors study a stopping criterion \ldots}

\begin{itemize}
\item p.\ 3, Sec.\ 2.2 The application of Lemma 1 to automatic Bayesian cubature is not clear to me, since integrand data is accumulated sequentially, which does not correspond to applying a single linear mapping to all integrands (realizations) $f$.

\item Sec.\ 2.2.1, 2.2.2 I suggest to include some references for the results that are presented in Sections 2.2.1 and 2.2.2.

\item p.\ 5, Sec.\ 2.4 Why are Sobol points chosen for the Matern kernel? Is there some theoretical link?

In the example the integral (22) is considered over a compact set. What is the benefit of Genz’s transformation, compared to a simple affine linear transformation, in this case?

\item p.\ 6 Why Hermitian? Are you considering complex-valued kernels? \Response{It is convenient since we are working with FFT's of real vectors, which are complex vectors.  Some explanation is provided at the beginning of Section 3.1.}

\item p.\ 7, top left Definition of v1∗?
...where ...(lower case)

\item Sec.\ 3.2--3.4 Does the operation count also include the computational cost for the minimization problem to estimate $\theta$? I suspect that this is not the case, since there is no assumption concerning the dependence of $C_\theta$ on $\theta$. The same question arises in the setting of Section 4.

\item Sec.\ 4.1 and 4.2 As the authors state, larger $r$ implies a greater degree of smoothness of the kernel. This should lead to a greater amount of smoothness of the integrands, and thus to a fast convergence of suitable cubature formulas. It might be that this is not exploited by the integration lattices (plus periodization), as studied in the present paper. Please comment.

\item p.\ 9, eqn. (37) $i, j = 1$

\item p.\ 9, bottom, right Assumption (25c) \ldots

\item p.\ 12, center left  \ldots differs depends \ldots ?

\item Sec.\ 5.1 Is there some kind of a universal periodization that ‘works’ for every value of $r$?

\item Sec. 5.2 You take $r = 2$ or $r = 1$ for the periodization in these examples. Does this mean that $\theta = (2,\gamma)$ is considered for the shift-invariant kernel, or do you still consider $\theta = (r,\gamma)$ with $r \in \mathbb{N}$ as the unknown parameter?
I suggest not to use $r$ also in the drift term in the option pricing example.

\end{itemize}

\section*{Reviewer 3}

\begin{itemize}
    \item Section 2.1, line 9: I think ``The function $C$" should be "The function $C_\theta$," since there is no function $C$.

\item Right before (12):  Not sure if ``simplify to" is the right expression, since it does not look like a simplification of those formulas.

\item Section 2.2.3, line 5: This is conditional on the data, but also a function of the parameters, I suppose?  I think this should be clarified.  On line 7, read "is the sum".

\item Two lines before Equation (20): ``confidence interval" and not ``credibility interval" like the other ones?

\item Five lines after (21): err$_{\rm CI}$ refers to what exactly? The value in (20)?  Clarify.

\item In (24), are $C_1,\dots,C_n$ the columns of C?

\item It took me a while to figure out what the four different colors of the points in Figures 5 to 13 mean.  There is a continuum of colors on the right, but only four specific colors for the points are used, so I think it would be useful to say explicitly what each of these four colors  represent.  In the text on page 12, it would be useful to say for example that $\epsilon = 10^{-5}$ corresponds to the green points.   By the way, are there 100 green points, for the 100 independent shifts?

\item Section 5.2, line 8: correct ``differs depends".

\item Page 14: The three figures look all the same!  Any comment on that?

\item In this example, does it really make sense to assume that the integrand comes from a Gaussian process?

\item Four lines below Figure 13:  "A noticeable aspect from the plots is how much ....":  It may be good to explain exactly how we see that in the plots.

\item Reference [1]:  "Griolami"?   Mark may not recognize himself!

\end{itemize}

\section*{Editor: We have received two very careful reviews of this paper \ldots}

The revision should at a minimum point out the connection to the FFT.

Because the goal is to reach people outside of PN some additional explanations are in order.

\begin{enumerate}
\renewcommand{\labelenumi}{\arabic{enumi}.}
    \item The results in Section 2.2.2 were confusing. \ldots

    \item It is weird to use complex numbers for the eigenvectors of a real symmetric matrix \ldots \Response{While it may be strange, it is convenient since we are working with FFT's of real vectors, which are complex vectors.  Some explanation is provided at the beginning of Section 3.1.}

\item In(24), why is $V^H =nV^{-1}$ and not just $V^{-1}$? \ldots \Response{This normalization allows $\vV_1 = \vone$.}

\item The argument at the end of section 4.3 involving is very slippery. \ldots

\end{enumerate}

Some minor points

\begin{enumerate}
\renewcommand{\labelenumi}{\arabic{enumi}.}

\item The $x_i$ in (4) would have to be distinct to force a strictly positive quadratic form. \Response{Clarified.}

\item The notation for the full Bayes treatment is not consistent. \ldots 
\item  First paragraph of 2.3: for the $\mu$ $\rightarrow$ for $\mu$. Also intervals $\rightarrow$ interval. \Response{Fixed.}
\item  End of Section 2: the the Mat\'ern $\rightarrow$ the Mat\'ern
\item  In the big display near the middle of the left column on page 7 should $c^T$
be $c^H$ ? Otherwise how do we get $\tilde{c}^*_i$?
\item  In equation (30), I think t should have $n-1$ df, not $n_{j-1}$ df. Otherwise
what is $n_j$?
\item  1st sentence of 4.3: shift-invariance $\rightarrow$ shift-invariant

\end{enumerate}

\end{document}

### 2019-06-17 BayesianCubaturePaper2018 - Rev1b.tex
Updates from Overleaf

--- 2019-04-23 BayesianCubaturePaper2018 - Rev1.tex
@@
 \begin{abstract}
-Automatic cubatures approximate multidimensional integrals to user-specified error tolerances.  For high dimensional problems, it makes sense to fix the sampling density but determine the 
-sample size, $n$, automatically.
-Bayesian cubature postulates that the integrand is an instance of a stochastic process.
-Here we assume a Gaussian process parameterized by a constant mean and a covariance function defined by a scale parameter times a parameterized function specifying how the integrand values at two different points in the domain are related.
-These parameters are estimated from integrand values or are given non-informative priors.
+Automatic cubatures approximate multidimensional integrals to user-specified error tolerances.
+For high dimensional problems it is difficult to adaptively change the sampling pattern, but one can automatically determine the
+sample size, $n$, give a fixed and reasonable sampling pattern.
+We take this approach here using a Bayesian perspective.
+We postulate that the integrand is an instance of a Gaussian stochastic process parameterized by a constant mean and a covariance function defined by a scale parameter times a parameterized function specifying how the integrand values at two different points in the domain are related.
+These hyperparameters are handled using integrand values via empirical Bayes, full Bayes, and generalized cross-validation.
 The sample size, $n$, is chosen to make the half-width of the credible interval for the Bayesian posterior mean no greater than the error tolerance.
 
-The process just outlined typically requires vector-matrix operations  with a computational cost of $O(n^3)$.
+The process just outlined typically requires vector-matrix operations  with a computational cost of $O(n^3)$ to .
 Our innovation is to pair low discrepancy nodes with matching kernels that lower the  computational cost to $O(n \log n)$.
@@
 \mC^T = \mC,  \quad \va^T \mC \va > 0, \quad \text{where }  \mC = \left(  C_\vtheta(\vx_i,\vx_j)  \right)_{i,j=1}^n,\\
- \text{for all } \va \ne 0, \;
- n\in \mathbb{N}, \qquad
- \vx_1, \ldots, \vx_n \in [0,1]^d, \; \text{s.t} \; \\\vx_i \neq \vx_j \forall i\neq j, \; 1 \leq i, j \leq n.
+ \forall \va \ne 0, \;
+ n\in \mathbb{N}, \; \text{ distinct }\vx_1, \ldots, \vx_n \in [0,1]^d.
 \end{multline}
@@
 We make some assumptions about the relationship between the covariance kernel and the nodes, which will be shown to hold in Section \ref{sec:shift_invariant_kernel} for rank-1 lattices and shift-invariant kernels.
-First we introduce the notation
+Although the integrands and covariance kernels are real, it is convenient to allow related vectors and matrices to be complex.
+A relevant example is the fast Fourier transform (FFT) of a real-valued vector, which is a complex-valued vector.
+
+We introduce some notation:
 \begin{align}
@@
 $\vV_1,...,\vV_n$ are columns of $\mV$ and $\vv_1,...,\vv_n$ are rows of $\mV$.
+The normalization of $\mV$ assumed in \eqref{eqn:ftk_factor} conveniently allows the first eigenvector, $\vV_1$, to be the vector of ones in \eqref{fastcompAssumpB} below.
 The columns of matrix $\mV$ are eigenvectors of $\mC$, and $\mLambda$ is a diagonal matrix of eigenvalues of $\mC$.

### 2019-06-25 ResponseToReferees.tex
Updates from Overleaf

@@
 \renewcommand{\vec}[1]{\boldsymbol{#1}}
+\newcommand{\vtheta}{\vec{\theta}}
 
-Thanks to the the referees and the editors for their helpful comments.  We have revised our manuscript in light of these comments, which we address point-by-point below.
+Thanks to the the referees and the editors for their helpful comments.  We have revised our manuscript in light of these comments, \Response{which we address point-by-point below in blue.}
 
@@
 \begin{itemize}
-\item The second sentence doesn't make sense to me.
-\item In the third sentence I would replace 'postulates' with 'considers'.
+\item The second sentence doesn't make sense to me. \Response{Re-written.}
+\item In the third sentence I would replace 'postulates' with 'considers'.  \Response{Done.}
 \end{itemize}
@@
 \item The authors write 'We construct a reliable stopping criterion' but it is
-unclear what they mean with 'reliable'.
-\item On page 2 they write 'If function evaluation is expensive, then $\$(f)$ might
-be similar in magnitude to $\log(n)$.': this makes no sense as evaluating $f$
+unclear what they mean with 'reliable'. \Response{This paragraph has been rewritten for clarity.}
+\item On page 2 they write 'If function evaluation is expensive, then $\$(f)$ might be similar in magnitude to $\log(n)$.': this makes no sense as evaluating $f$
 depends on the dimension $d$. So this depends on how big $n$ is and if we want more
 accuracy then $n$ becomes bigger.
+\Response{We have added some clarification.
+If function evaluation from an expensive simulation takes an 5 minutes for one value, then performing the FFT calculations is going to take less time for practical $n$, say up to a million.}
 \end{itemize}
@@
 \begin{itemize}
-\item '$f$ is drawn from a Guaussian process': it should be explained what this
+\item '$f$ is drawn from a Gaussian process': it should be explained what this
 means, e.g., does it mean $f$ is the Gaussian function with unknown mean and
@@
 a very strong assumption.
+\Response{Some further explanation has been provided.
+The assumption may be strong, but it is common in this literature.
+The fact that we require some parameters to be inferred from data should make that assumption more palatable.}
 \item It should maybe be mentioned here that there are hyper distributions for the
-hyper parameters.
+hyper parameters. \Response{Done.}
 \item It is never said how the $x_i$ are sampled. Does (5a) hold for any
-distribution of samples $x_i$?
+distribution of samples $x_i$? \Response{Yes, any distinct nodes.}
 \item In this section there are different quantities being defined: the matrix
@@
 point. Only at the end the authors say that they assume these things to be
-cheap. I think this should be spelled out immediately.
+cheap. I think this should be spelled out immediately. \Response{Done.}
 \item  It think is not a good idea to leave out the dependence on $\vec{\theta}$ for
 $C$. E.g. in (11) the $\vec{\theta}$ is not visible at all in the expression to be
-minimized for it. The $C$ without subscript also clashes that of lemma 1.
+minimized for it. The $C$ without subscript also clashes that of lemma 1. \Response{$\vec{\theta}$ has been added into the equations where there is optimization.}
 \item  The lead in to lemma 1 makes it feel like this is a field specific lemma but
-in fact it is just the well known conditional gaussian. Please write something
-like 'We need the following lemma on conditional normal distribution ...'.
-\item  Do not use $C$ in this lemma.
+in fact it is just the well known conditional Gaussian. Please write something
+like 'We need the following lemma on conditional normal distribution ...'.  \Response{Done.}
+\item  Do not use $C$ in this lemma. \Response{Notation has been changed.}
 \item  The other derivations in the paper are all made in prose. It would be better
-to formally state some of them. E.g., the results on the top of page 3.
+to formally state some of them. E.g., the results on the top of page 3. \Response{The key results from Sections 2.2.1--2.2.3 have been collected in a theorem just before Section 2.2.1.}
 \item  From (6) to (7) the notation is different: $c^T C^{-1} 1$ vs $1^T C^{-1} c$,
-this might be corrected.
+this might be corrected. \Response{Done.}
 \end{itemize}
@@
 \item It would help to see the dependence on $\vec{\theta}$ in (9), (10) and (11).
+\Response{We have added the dependence on $\vec{\theta}$ through the end of Section 2.
+However, we have omitted it later where it would make the derivations hard to follow.}
 \item It looks like (11) is independent of $m_{\text{MLE}}$ and $s^2_{\text{MLE}}$, how does it pop up?
 Otherwise we could just first optimize for $\vec{\theta}$, then for m and then
-for $s^2$.
+for $s^2$. \Response{No, the optimization problem for $\vec{\theta}$ already has  $m_{\text{MLE}}$ and $s^2_{\text{MLE}}$ inserted into the log-likelihood.}
 \end{itemize}
@@
 \begin{itemize}
-\item I cannot follow the derivation.
+\item I cannot follow the derivation.  \Response{The notation has been clarified.  This is a tedious derivation and has been moved to the Appendix.}
 \item At the end of the section the authors say that this is not a good method.
-Why then list it? Maybe the final paragraph needs to be rewritten.
+Why then list it? Maybe the final paragraph needs to be rewritten.  \Response{We only cast doubt on the full Bayes approach for estimating $\vec{\theta}$.}
 \end{itemize}
 
-\item Section 2.3. The authors stress here that the integrand must be a 'typical' draw from the assumed Gaussian process and not an outlier. That sounds scary.
+\item Section 2.3.
+The authors stress here that the integrand must be a 'typical' draw from the assumed Gaussian process and not an outlier.
+That sounds scary.
+\Response{It may sound scary, but that is the common implicit assumption of probabilistic approaches, such as this one.
+Other traditional methods for estimating the error of a cubature rule either assume that the integrand lies in the ball of some function space (how do you know the radius of that ball?) or estimate the error heuristically.}
 
@@
 and update the formula for $\mu$ at the bottom of the page and the display on the
-next page. After these changes you can keep the '$d=2$' in the caption of Fig 2.
+next page. After these changes you can keep the '$d=2$' in the caption of Fig 2.  \Response{Excellent suggestion.  Done.}
 
@@
 \item Maybe write 'previous section' instead of 'last section'.
--- Maybe write 'covariance kernel' instead of just 'kernel'. I think the word
+\item Maybe write 'covariance kernel' instead of just 'kernel'. I think the word
 kernel hasn't been used up till this point.
@@
 \item  First paragraph of 2.3: for the $\mu$ $\rightarrow$ for $\mu$. Also intervals $\rightarrow$ interval. \Response{Fixed.}
-\item  End of Section 2: the the Mat\'ern $\rightarrow$ the Mat\'ern
+\item  End of Section 2: the the Mat\'ern $\rightarrow$ the Mat\'ern \Response{Fixed.}
 \item  In the big display near the middle of the left column on page 7 should $c^T$
-be $c^H$ ? Otherwise how do we get $\tilde{c}^*_i$?
+be $c^H$ ? Otherwise how do we get $\tilde{c}^*_i$? \Response{It is correct as stands.  A sentence of explanation has been added just before those equations.}
 \item  In equation (30), I think t should have $n-1$ df, not $n_{j-1}$ df. Otherwise
-what is $n_j$?
-\item  1st sentence of 4.3: shift-invariance $\rightarrow$ shift-invariant
+what is $n_j$?  \Response{Corrected.}
+\item  1st sentence of 4.3: shift-invariance $\rightarrow$ shift-invariant \Response{Corrected.}
 

### 2019-06-25 BayesianCubaturePaper2018 - Rev1b.tex
Updates from Overleaf

@@
 \newcommand{\rC}{\mathring{C}}
+\newcommand{\ry}{\mathring{y}}
 \newcommand{\rlambda}{\mathring{\lambda}}
@@
 %\newcommand{\mCthetaInvMLE}{{\mathsf{C}^{-1}_{\vthetaMLE}}}
-\newcommand{\mCInv}{{\mathsf{C}^{-1}}}
+\newcommand{\mCInv}{\mathsf{C}^{-1}}
 \newcommand{\cov}{{\textup{cov}}}
@@
 \newcommand{\MVN}{\textup{MVN}}
-\newcommand{\MLE}{\textup{MLE}}
+\newcommand{\MLE}{\textup{EB}}
 \newcommand{\full}{\textup{full}}
@@
 
-We construct a reliable stopping criterion that determines the number of integrand values, $n$, required to ensure that the error is no greater than a user-defined error tolerance denoted by $\varepsilon$, i.e.,
+The users of cubature algorithms typically want the error to be no greater than their error tolerance denoted by $\varepsilon$, i.e., 
 \begin{align}
@@
 \end{align}
-Rather than relying on strong assumptions about the integrand, such as an upper bound on its variance or total variation, we construct a stopping criterion that is based on a credible interval arising from a Bayesian approach to the problem.
+Some stopping criteria used in practice are heuristic.
+Other rigorous algorithms require rather strong assumptions about the integrand, such as an upper bound on its variance (for simple Monte Carlo) or total variation (for quasi-Monte Carlo).
+We take a Bayesian approach by constructing a stopping criterion that is based on a credible interval.
 We build upon the work of Briol et al.~\cite{BriEtal18a}, Diaconis~\cite{Dia88a}, O'Hagan~\cite{OHa91a}, Ritter~\cite{Rit00a}, Rasmussen and Ghahramani~\cite{RasGha03a}, and others.
@@
 The primary contribution of this article is to demonstrate how the choice of a family of covariance kernels that match the low discrepancy sampling nodes facilitates fast computation of the cubature and the data-driven stopping criterion.
-Our cubature requires $n$ function values---at a cost of $\$(f)$ each---plus $\Order(n \log(n))$ operations to check whether the error tolerance is satisfied.
-The total cost of our algorithm is then $\Order(n [\$(f) + \log(n)])$.
-This is significantly fewer operations than the $\Order(n^3)$ typically required for Bayesian cubature.
-If function evaluation is expensive, then $\$(f)$ might be similar in magnitude to $\log(n)$.
+Our Bayesian cubature requires a computational cost of
+\begin{equation} \label{eqn:OuralgoCost}
+    \Order\bigl(K_{\textup{opt}}[n \$(f) + n\$(C) + n \log(n)] \bigr),
+\end{equation} 
+where $\$(f)$ is the cost of one integrand value, $\$(C)$ is the cost of a single covariance kernel value,  $\Order(n \log(n))$ is the cost of a fast Fourier transform, and $K_{\textup{opt}$ is an upper bound on the number of optimization steps required to choose the hyperparameters.
+If function evaluation is expensive, such as coming from computationally intensive simulation, or $\$(f) = \Order(d)$ for large $d$, then $\$(f)$ might be similar in magnitude to $\log(n)$ in practice.
+Note that the $\Order(n \log(n))$ contribution is $d$ independent.
+
+By contrast to our fast algorithm, the typical computational cost for Bayesian cubature is
+\begin{equation} \label{eqn:TheiralgoCost}
+    \Order\bigl(K_{\textup{opt}}[n \$(f) + n^2\$(C)) + n^3] \bigr),
+\end{equation} 
+which is explained in Section \ref{sec:bayes_cubature_algo}. Note that the work beyond evaluating the integrand in \label{eqn:TheiralgoCost} is much larger than that in \eqref{eqn:TheiralgoCost}.
 
@@
 
-Suppose that the integrand, $f$, is drawn from a Gaussian process (\cite{BriEtal18a}, \cite{Dia88a}, \cite{OHa91a}, \cite{Rit00a}, \cite{RasGha03a}), i.e., $f \sim \mathcal{GP}(m,s^2 C_\vtheta)$.
-Specifically, $f$ has real-valued constant mean $m$ and covariance function $s^2C_\vtheta$, where $s$ is a non-negative scale factor, and $C_\vtheta: [0,1]^d \times [0,1]^d \to \mathbb{R} $ is a symmetric, positive-definite function and parameterized by $\vtheta$:
+Suppose that the integrand, $f$, is assumed to be an instance of a Gaussian stochastic process \cite{BriEtal18a}, \cite{Dia88a}, \cite{OHa91a}, \cite{Rit00a}, \cite{RasGha03a}, i.e., $f \sim \mathcal{GP}(m,s^2 C_\vtheta)$.
+Specifically, $f$ is a random function with real-valued constant mean $m$ and covariance function $s^2C_\vtheta$:
+\begin{gather*}
+        m = \Ex[f(\vx)] \qquad \forall \vx \in \reals^d, \\
+        \Ex\{[f(\vt) - m][f(\vx) -m]\} = s^2 C_\vtheta(\vt,\vx) \qquad \forall \vt, \vx \in \reals^d.
+\end{gather*}
+Here $s$ is a non-negative scale factor, and $C_\vtheta: [0,1]^d \times [0,1]^d \to \mathbb{R} $ is a symmetric, positive-definite function and parameterized by $\vtheta$:
 \begin{multline} \label{FJH:eq:CondPosDef}
-\mC^T = \mC,  \quad \va^T \mC \va > 0, \quad \text{where }  \mC = \left(  C_\vtheta(\vx_i,\vx_j)  \right)_{i,j=1}^n,\\
+\mC_\vtheta^T = \mC_\vtheta,  \; \va^T \mC_\vtheta \va > 0, \; \text{where }  \mC_\vtheta = \left(  C_\vtheta(\vx_i,\vx_j)  \right)_{i,j=1}^n,\\
  \forall \va \ne 0, \;
@@
 \end{multline}
-The function, $C_{\vtheta}$, and the Gram matrix, $\mC$ depend implicitly on $\vtheta$, but the notation may omit this parameter for simplicity's sake.
-
-For a Gaussian process, all vectors of linear functionals of $f$ have a multivariate Gaussian distribution.
-Defining  $\vf  := \left( f(\vx_i)\right)_{i=1}^n$ as the multivariate normal vector of function values, it follows that
+Procedures for estimating or integrating out the hyperparameters $m$, $s$, and $\vtheta$ are explained later in this section.
+
+Furthermore, for a Gaussian process, all vectors of linear functionals of $f$ have a multivariate Gaussian distribution.
+For any deterministic sampling scheme with distinct nodes, $\{\vx_i\}_{i=1}^n$, and defining  $\vf  := \left( f(\vx_i)\right)_{i=1}^n$ as the multivariate normal vector of function values, it follows from the definition of a Gaussian process that
 \begin{subequations} \label{eqn:fGaussDist}
 \begin{align}
-\vf  & \sim \calN(m \vone, s^2 \mC), \\
+\vf  & \sim \calN(m \vone, s^2 \mCtheta), \\
 \nonumber & \qquad \qquad \text{where $\vone$ is a vector of all ones,}\\
-\mu & \sim \calN(m, s^2 c_0), 
+\mu & \sim \calN(m, s^2 c_{0\vtheta}), 
 \\
 \text{where }
-c_0 &= \int_{[0,1]^{d}\times [0,1]^{d}} C_\vtheta(\vx,\vt) \, \dif{\vx} \, \dif{\vt}, \\
-\cov(\vf, \mu) &= \left(  \int_{[0,1]^d} C(\vt,\vx_i) \, \D \vt \right)_{i=1}^n  =: \vc.
+c_{0\vtheta} &:= \int_{[0,1]^{d}\times [0,1]^{d}} C_\vtheta(\vt,\vx) \, \dif{\vt} \, \dif{\vx}, \\
+\cov(\vf, \mu) &= \left(  \int_{[0,1]^d} C_\vtheta(\vt,\vx_i) \, \D \vt \right)_{i=1}^n  =: \vc_\vtheta.
 \end{align}
 \end{subequations}
-We need the following lemma on conditional normal distribution to derive the distribution of the posterior error of our cubature.
+Again, $c_{0\vtheta}$ and $\vc_\vtheta$ depend explicitly on $\vtheta$.
+We assume that the integrals in these definitions can be computed analytically.
+We need the following lemma pertaining to a conditional normal distribution to derive the distribution of the posterior error of our cubature.
 
@@
 \begin{multline} \label{eqn:condInteg}
-\mu | (\vf = \vy) \sim \calN \bigl(m (1 - \vc^T \mC^{-1} \vone)  + \vc^T \mC^{-1} \vy, 
-\\
-s^2(c_0  -\vc ^T \mC^{-1} \vc) \bigr).
+\mu | (\vf = \vy) \sim \calN \bigl(m (1 - \vc_\vtheta^T \mCtheta^{-1} \vone)  + \vc_\vtheta^T \mCtheta^{-1} \vy, 
+\\
+s^2(c_{0\vtheta}  -\vc_\vtheta ^T \mCtheta^{-1} \vc_\vtheta) \bigr).
 \end{multline}
@@
 \widehat{\mu}  \vert ( \vf = \vy)
-= m(1 - \vc^T  \mC^{-1} \vone)
-+ \vc^T \mC^{-1} \vy,
+= m(1 - \vc_\vtheta^T  \mCtheta^{-1} \vone)
++ \vc_\vtheta^T \mCtheta^{-1} \vy,
 \end{align}
@@
 0, \;
-s^2 (c_0 - \vc^T\mC^{-1}\vc) 
+s^2 (c_{0\vtheta} - \vc_\vtheta^T\mCtheta^{-1}\vc_\vtheta) 
 \right).
@@
 \right] = 99\%, \\
-\err_{\textup{CI}} = 2.58 s \sqrt{c_0 - \vc^T\mC^{-1}\vc}
+\err_{\textup{CI}} = 2.58 s \sqrt{c_{0\vtheta} - \vc_\vtheta^T\mCtheta^{-1}\vc_\vtheta}
 \end{gather}
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsection{Parameter estimation}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 The credible interval in \eqref{eqn_prob_confidence_interval} suggests how our automatic Bayesian cubature proceeds.
 Integrand data is accumulated until the width of the credible interval, $\err_{\textup{CI}}$, is no greater than the error tolerance.
-As $n$ increases, one expects $\sqrt{c_0 - \vc^T\mC^{-1}\vc}$ to decrease for well-chosen nodes, $\{\vx_i\}_{i=1}^n$.
+As $n$ increases, one expects $\sqrt{c_{0\vtheta} - \vc_\vtheta^T\mCtheta^{-1}\vc_\vtheta}$ to decrease for well-chosen nodes, $\{\vx_i\}_{i=1}^n$.
 
@@
 
-\subsubsection{Empirical Bayes}  \label{sec:MLE}
-One approach is to estimate the parameters is via maximum likelihood estimation (MLE).  The log-likelihood function of the parameters given the function data $\vy$ is:
-\begin{multline*}
-l(s,m,\vtheta | \vy)
-= -\frac{1}{2} s^{-2} (\vy-m\vone)^T\mCInv(\vy-m\vone) 
-\\
- - \frac{1}{2} \log(\det\, \mC) - \frac{n}{2} \log(s^2) + \text{constants.}
-\end{multline*}
-Maximizing the log-likelihood first with respect to $m$, then with respect to $s$, and finally with respect to $\vtheta$ yields
+\begin{theorem} \label{thm:param} There are at least three approaches to estimating or integrating out the hyperparameters defining the Gaussian process from which the integrand is drawn: empirical Bayes, full Bayes, and generalized cross validation.
+Under these three approaches we have the following:
+\begin{allowdisplaybreaks}
 \begin{align}
     \label{eqn_m_MLE}
-m_\MLE &= \frac{\vone^T \mCInv \vy }{ \vone^T \mCInv \vone}, 
-\end{align}
-\begin{align}
-\nonumber
+m_\MLE &= \frac{\vone^T \mCInv_\vtheta \vy }{ \vone^T \mCInv_\vtheta \vone}, \qquad
+m_{\textup{GCV}} = \frac{\vone^T \mC_\vtheta^{-2} \vy}{\vone^T \mC_\vtheta^{-2} \vone}, \\
+\label{eqn_s2_MLE}
 s^2_{\MLE} 
-&= \frac{1}{n} (\vy-m_{\MLE}\vone)^T\mCInv(\vy-m_{\MLE}\vone) 
-\\
-\label{eqn_s2_MLE}
 &= 
@@
 \vy^T 
-\left[ 
-\mCInv - 
-\frac{ \mCInv \vone \vone^T \mCInv }{\vone^T\mCInv \vone}
-\right] \vy, 
-\end{align}
-To obtain $\vtheta_\MLE$, substitute $m_\MLE$ and $s_\MLE$ into $l(s,m,\vtheta | \vy)$ and then numerically minimize
-\begin{align}
+\left[ \mCInv_\vtheta - 
+\frac{ \mCInv_\vtheta \vone \vone^T \mCInv_\vtheta }{\vone^T\mCInv_\vtheta \vone}
+\right] \vy, \\
+\nonumber
+\hsigma_{\textup{full}}^2 
+& = \frac{1}{n-1}
+\vy^T\left[ \mC_\vtheta^{-1} 
+- \frac{ \mC_\vtheta^{-1} \vone\vone^T \mC_\vtheta^{-1}}{\vone^T \mC_\vtheta^{-1} \vone}  \right]\vy
+\\ 
+& \times  \left[\frac{(1 - \vc_{\vtheta}^T \mC_\vtheta^{-1} \vone)^2}{\vone^T \mC_\vtheta^{-1} \vone} + (c_{0\vtheta}  -\vc_{\vtheta} ^T \mC_\vtheta^{-1} \vc_{\vtheta}) \right], \\
+\nonumber
+ s^2_{\textup{GCV}} & = \vy^T \left[\mC_\vtheta^{-2} - \frac{\mC_\vtheta^{-2} \vone \vone^T \mC_\vtheta^{-2}}{\vone^T \mC_\vtheta^{-2} \vone}  \right] \vy  \left[ \trace(\mC_\vtheta^{-1}) \right]^{-1}, \\
 \nonumber
@@
 \log\left(\vy^T 
-\left[ \mCInv - 
-\frac{ \mCInv \vone \vone^T \mCInv }{\vone^T\mCInv \vone}
+\left[ \mC_\vtheta^{-1} - 
+\frac{ \mCInv_\vtheta \vone \vone^T \mCInv_\vtheta }{\vone^T\mCInv_\vtheta \vone}
+\right] \vy 
+\right)  \\
+\label{eqn:thetaMLE}
+ & \qquad +  \frac{1}{n} \log(\det(\mC_\vtheta))
+\biggr \}, \\
+\nonumber
+\vtheta_{\textup{GCV}} &= \argmin_\vtheta \biggl\{\log \left(  \vy^T \left[\mC^{-2}_\vtheta - \frac{\mC^{-2}_\vtheta \vone \vone^T \mC^{-2}_\vtheta}{\vone^T \mC^{-2}_\vtheta \vone}  \right] \vy \right)  \\
+\label{vthetaGCV}
+& - \log \left ( \trace(\mC^{-2}_\vtheta) \right ) \biggr\}, \\
+\hmu_\MLE  &= \hmu_\full =
+\left(
+\frac{ (1 - \vone^T  \mCInv_\vtheta\vc_{\vtheta} )  \vone }{ \vone^T \mCInv_\vtheta \vone}   +  \vc_{\vtheta} 
+\right)^T  \mCInv_\vtheta \vy, \\
+\label{eqn:muCV}
+\widehat{\mu}_{\textup{GCV}}
+& = \left(\frac{(1 - \vone^T  \mC_\vtheta^{-1}\vc_{\vtheta}) \mC_\vtheta^{-1} \vone}{\vone^T \mC_\vtheta^{-2} \vone} + \vc_{\vtheta} \right)^T \mC_\vtheta^{-1} \vy, \\
+\nonumber 
+\err_{\mathsf{x}} & = 2.58 s_{\mathsf{x}} \sqrt{c_{0\vtheta} - \vc_{\vtheta}^T\mC_\vtheta^{-1}\vc_{\vtheta} }, \quad \mathsf{x} \in \{\MLE, \GCV\}, \\
+\nonumber 
+\err_{\textup{full}} 
+& = t_{n-1,0.995} \hsigma_{\textup{full}} > \err_\MLE,
+\end{align}
+\end{allowdisplaybreaks}
+\begin{multline}
+\label{eqn_prob_CI}
+\mathbb{P}_f \left[
+|\mu-\hmu_{\mathsf{x}}| \leq \err_{\mathsf{x}} \right]  = 99\%, \\ \mathsf{x} \in \{\MLE, \full, \GCV\}.
+\end{multline}
+Here $t_{n-1,0.995}$ denotes the $99.5$ percentile of a standard Student's $t$-distribution with $n-1$ degrees of freedom.
+\end{theorem}
+
+For the results summarized in the theorem above, note that if the original covariance function, $C$, is replaced by $b C$ for some positive constant $b$, the cubature, $\hmu$, the estimates of $\vtheta$, and the credible interval widths, $\err_{\textup{CI}}$, all remain unchanged.
+The estimates of $s^2$ are multiplied by $b^{-1}$, as would be expected.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsubsection{Proof for Empirical Bayes}  \label{sec:MLE}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+The empirical Bayes approach estimates the parameters, $m$, $s$, and $\vtheta$ via maximum likelihood estimation (MLE).  The log-likelihood function of the parameters given the function data $\vy$ is:
+\begin{multline*}
+l(s,m,\vtheta | \vy)
+= -\frac{1}{2} s^{-2} (\vy-m\vone)^T\mCInv_\vtheta(\vy-m\vone) 
+\\
+ - \frac{1}{2} \log(\det\, \mC_\vtheta) - \frac{n}{2} \log(s^2) + \text{constants.}
+\end{multline*}
+Maximizing the log-likelihood first with respect to $m$ and then with respect to $s$ yields the values given in Theorem \ref{thm:param}.
+To obtain $\vtheta_\MLE$, we substitute $m_\MLE$ and $s_\MLE$ into $l(s,m,\vtheta | \vy)$ and then numerically optimize:
+\begin{align}
+\nonumber
+\vtheta_\MLE
+&= \argmin_{\vtheta} \biggl \{
+\log\left(\vy^T 
+\left[ \mCInv_\vtheta - 
+\frac{ \mCInv_\vtheta \vone \vone^T \mCInv_\vtheta }{\vone^T\mCInv_\vtheta \vone}
 \right] \vy 
@@
 \end{align}
-The MLE estimate of $\vtheta$ balances minimizing the covariance scale factor, $s^2_{\MLE}$, against minimizing  $\det(\mC)$.
-
-Under these estimates of the parameters, the cubature \eqref{eqn:BayesCub} and the credible interval \eqref{eqn_prob_confidence_interval} are explicitly written as
-\begin{align} \label{eqn:cubMLE}
-\hmu_\MLE  &= 
-\left(
-\frac{ (1 - \vone^T  \mCInv\vc )  \vone }{ \vone^T \mCInv \vone}   +  \vc 
-\right)^T  \mCInv \vy,
-\end{align}
-\begin{align}
-\nonumber 
-\err_\MLE^2 & : = \frac{2.58^2}{n}
- \vy^T \left[ \mCInv - 
-\frac{ \mCInv \vone \vone^T \mCInv }{\vone^T\mCInv \vone}
-\right] \vy \\
-\label{eqn:errMLE}
-&\qquad \qquad \times 
-(c_0 - \vc^T\mC^{-1}\vc ),
-\end{align}
-\begin{align}
-\label{eqn_prob_CI_MLE}
-\mathbb{P}_f \left[
-|\mu-\hmu_\MLE| \leq \err_\MLE \right]  = 99\%.
-\end{align}
-Here $c_0$, $\vc$, and $\mC$ are assumed implicitly to be based on $\vtheta = \vtheta_\MLE$.   
-\subsubsection{Full Bayes}
+The empirical Bayes estimate of $\vtheta$ balances minimizing the covariance scale factor, $s^2_{\MLE}$, against minimizing  $\det(\mC)$. 
+Under these estimates of the parameters, the cubature \eqref{eqn:BayesCub} and the credible interval \eqref{eqn_prob_confidence_interval} are explicitly written as in Theorem \ref{thm:param}.
+The quantities $c_{0\vtheta}$, $\vc_\vtheta$, and $\mC$ are assumed implicitly to be based on $\vtheta = \vtheta_\MLE$.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsubsection{Proof for Full Bayes} \label{sec:fullBayes}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 Rather than use maximum likelihood to determine $m$ and $s$ one can treat them as hyperparameters with a non-informative, conjugate prior, namely $\vrho_{m,s^2}(\xi, \lambda) \propto 1/\lambda$.
-Let us assume integral $\mu$, a random variable, taking typical values $z$, then the posterior density for the $\mu$ given data $\vy$ using Bayes theorem is
-\begin{align*}
-\MoveEqLeft[1]{\rho_{\mu}(z | \vf = \vy)} \\
-& \propto \int_{0}^\infty \int_{-\infty}^\infty \rho_{\mu}(z | \vf = \vy, m = \xi, s^2 = \lambda) \\
-& \hspace{2.5cm} \times  \rho_{\vf}(\vy | \xi, \lambda ) \rho_{m, s^2}(\xi, \lambda) \, \D \xi \D \lambda \\
-& \propto \left( 1 +  \frac{(z - \hmu_{\textup{MLE}})^2}{(n-1)\widehat{\sigma}_{\textup{full}}^2} \right)^{-n/2}, \text{  (by Appendix \ref{appendix:full_bayes})}
-\end{align*}
-where 
+We want to compute $\rho_{\mu|\vf}(z | \vy)$, the conditional posterior density of $\mu$ given the data $\vf = \vy$.
+This may be expressed as
 \begin{multline*}
-%\label{FJH:eq:signmaFull}
-\hsigma^2_{\textup{full}} 
-:= \frac{1}{n-1}
-\vy^T\left[ \mC^{-1} 
-- \frac{ \mC^{-1} \vone\vone^T \mC^{-1}}{\vone^T \mC^{-1} \vone}  \right]\vy
-\\ 
-\times  \left[\frac{(1 - \vc^T \mC^{-1} \vone)^2}{\vone^T \mC^{-1} \vone} + (c_0  -\vc ^T \mC^{-1} \vc) \right].
+    \rho_{\mu|\vf}(z | \vy) 
+= \int_{0}^\infty \int_{-\infty}^\infty 
+\rho_{\mu | m, s^2, \vf}(z | \xi, \lambda , \vy) \\
+\times  \rho_{m, s^2 | \vf}(\xi, \lambda | \vy)  \, \D \xi \D \lambda, 
 \end{multline*}
+where $\rho_{m, s^2 | \vf}$ is the posterior density of the hyperparameters given the function data. Bayes Theorem, $\rho_{m, s^2 | \vf} \propto \rho_{\vf | m, s^2} \, \vrho_{m,s^2}$, so 
+\begin{align}
+\nonumber 
+    \rho_{\mu|\vf}(z | \vy) 
+& = \int_{0}^\infty \int_{-\infty}^\infty 
+\rho_{\mu | m, s^2, \vf}(z | \xi, \lambda , \vy) \\
+\nonumber
+& \qquad \times  \rho_{\vf | m, s^2} (\vy | \xi, \lambda) \, \vrho_{m,s^2}(\xi,\lambda)  \, \D \xi \D \lambda \\
+\nonumber
+& \propto \left( 1 +  \frac{(z - \hmu_{\MLE})^2}{(n-1) \hsigma_{\textup{full}}^2} \right)^{-n/2},
+\end{align}
+where $\hsigma_{\textup{full}}^2$ is given in Theorem \ref{thm:param}, and the result above is derived Appendix \ref{appendix:full_bayes}.
 
 This means that $\mu \vert (\vf = \vy )$, properly centered and scaled, has a Student's $t$-distribution with $n-1$ degrees of freedom.
-The estimated integral is the same as in the empirical Bayes case, $\hmu_{\textup{full}} = \hmu_{\MLE}$, but the confidence interval is wider:
-\begin{align}
-\label{eqn_prob_CI_full}
-\mathbb{P}_f \left[
-|\mu-\hmu_\full| \leq \err_{\full} \right]  = 99\%,
-\end{align}
-where
-\begin{align}
-\label{FJH:eq:errFull}
-\err_{\textup{full}} 
-:= t_{n-1,0.995} \hsigma_{\textup{full}} > \err_\MLE .
-\end{align}
-Here $t_{n-1,0.995}$ denotes the $99.5$ percentile of a standard Student's $t$-distribution with $n-1$ degrees of freedom.
+The estimated integral is the same as in the empirical Bayes case, $\hmu_{\textup{full}} = \hmu_{\MLE}$, but the confidence interval is wider, as stated in the Theorem \ref{thm:param}.
 
 Because the shape parameter, $\vtheta$, enters the definition of the covariance kernel in a non-trivial way, the only way to treat it as a hyperparameter and assign a tractable prior would be for the prior to be discrete.
-We believe in practice that choosing such a prior involves more guesswork, so we choose to use either empirical Bayes estimate of $\vtheta$ in \eqref{eqn:thetaMLE} or cross-validation approach described next.
-
-\subsubsection{Generalized Cross-Validation} \label{sec:GCV}
+We believe that choosing such a prior in practice involves too much guesswork, so we choose to use either $\vtheta_\MLE$ or $\vtheta_\GCV$.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsubsection{Proof for Generalized Cross-Validation} \label{sec:GCV}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 A third parameter optimization technique is \emph{leave-one-out cross-validation} (CV).
-Let $\widetilde{y}_i = \Ex[f(\vx_i ) | \vf_{-i} = \vy_{-i}]$, where the subscript $-i$ denotes the vector excluding the $i^{\text{th}}$ component.
+Let $\mathring{y}_i = \Ex[f(\vx_i ) | \vf_{-i} = \vy_{-i}]$, where the subscript $-i$ denotes the vector excluding the $i^{\text{th}}$ component.
 This is the conditional expectation of $f(\vx_i )$ given all data but the function value at $\vx_i$.
@@
 \begin{align} \label{FJH:eq:CVA}
-\textup{CV} = \sum_{i=1}^n (y_i - \widetilde{y}_i)^2.
-\end{align}
-
-Let $\mA = \mC^{-1}$, let $\vzeta = \mA (\vy - m \vone)$, and partition $\mC$, $\mA$, and $\vzeta$ as
+\textup{CV} = \sum_{i=1}^n (y_i - \mathring{y}_i)^2.
+\end{align}
+
+Let $\mA = \mC^{-1}_\vtheta$, let $\vzeta = \mA (\vy - m \vone)$, and partition $\mC_\vtheta$, $\mA$, and $\vzeta$ as
 \begin{gather*}
-\mC = \begin{pmatrix} c_{ii}  & \vC_{-i,i}^T \\  \vC_{-i,i} & \mC_{-i,-i}\end{pmatrix}, \qquad
+\mC_\vtheta = \begin{pmatrix} c_{ii}  & \vC_{-i,i}^T \\  \vC_{-i,i} & \mC_{-i,-i}\end{pmatrix}, \qquad
 \mA = \begin{pmatrix} a_{ii}  & \vA_{-i,i}^T \\  \vA_{-i,i} & \mA_{-i,-i}\end{pmatrix}, \\ \vzeta = \begin{pmatrix} \zeta_i   \\  \vzeta_{-i} \end{pmatrix},
@@
 \begin{align*}
-\widetilde{y}_i & = m + \vC^T_{-i,i} \mC_{-i,-i}^{-1} (\vy_{-i} -m \vone)  \\
+\mathring{y}_i & = m + \vC^T_{-i,i} \mC_{-i,-i}^{-1} (\vy_{-i} -m \vone)  \\
 \zeta_i  & = a_{ii}(y_i - m) + \vA_{-i,i}^T(\vy_{-i} - m \vone) \\
 & = a_{ii}[(y_i - m) - \vC^T_{-i,i} \mC_{-i,-i}^{-1} (\vy_{-i} -m \vone)] \\
-& = a_{ii}(y_i - \widetilde{y}_i).
+& = a_{ii}(y_i - \mathring{y}_i).
 \end{align*}
@@
 \begin{align*} %\label{FJH:eq:CVB}
-\textup{CV} = \sum_{i=1}^n \left(\frac{\zeta_i}{a_{ii}} \right)^2, \qquad \vzeta = \mC^{-1}(\vy - m \vone).
+\textup{CV} = \sum_{i=1}^n \left(\frac{\zeta_i}{a_{ii}} \right)^2, \qquad \vzeta = \mC^{-1}_\vtheta(\vy - m \vone).
 \end{align*}
@@
 = \frac{\sum_{i=1}^n\zeta_i^2}{\left(\frac 1n \sum_{i=1}^n a_{ii} \right)^2} \\
-& = \frac{(\vy - m\vone)^T \mC^{-2} (\vy - m \vone)}{\left(\frac 1n \trace(\mC^{-1}) \right)^2}.
-\end{align*}
-
-The loss function $\textup{GCV}$ depends on $m$ and $\vtheta$, but not on $s$.  Minimizing the GCV  yields
-\begin{align*}
-m_{\textup{GCV}} = \frac{\vone^T \mC^{-2} \vy}{\vone^T \mC^{-2} \vone},
-\end{align*}
-\begin{multline}
-\label{vthetaGCV}
-\vtheta_{\textup{GCV}} = \argmin_\vtheta \biggl\{\log \left(  \vy^T \left[\mC^{-2} - \frac{\mC^{-2} \vone \vone^T \mC^{-2}}{\vone^T \mC^{-2} \vone}  \right] \vy \right)  \\
-- 2 \log \left ( \trace(\mC^{-1}) \right ) \biggr\}.
-\end{multline}
-Plugging the value of $m_\GCV$ into \eqref{eqn:BayesCub} yields
-\begin{align}
-\label{eqn:muCV}
-\widehat{\mu}_{\textup{GCV}}
-= \left(\frac{(1 - \vone^T  \mC^{-1}\vc) \mC^{-1} \vone}{\vone^T \mC^{-2} \vone} + \vc \right)^T \mC^{-1} \vy.
-\end{align}
+& = \frac{(\vy - m\vone)^T \mC^{-2}_\vtheta (\vy - m \vone)}{\left(\frac 1n \trace(\mC^{-1}) \right)^2}.
+\end{align*}
+
+The loss function $\textup{GCV}$ depends on $m$ and $\vtheta$, but not on $s$.
+Minimizing the GCV  yields the formulae in Theorem \ref{thm:param} for $\widehat{\mu}_{\textup{GCV}}$ and $\vtheta_{\textup{GCV}}$.
+Plugging the value of $m_\GCV$ into \eqref{eqn:BayesCub} yields the formulae in Theorem \ref{thm:param} for $\widehat{\mu}_{\textup{GCV}}$.
 
@@
 s^2 &= \var[f(\vx_i ) | \vf_{-i} = \vy_{-i}] a_{ii} \\ 
-& \approx \frac 1n \sum_{i=1}^n (y_i - \widetilde{y}_i)^2a_{ii}
+& \approx \frac 1n \sum_{i=1}^n (y_i - \mathring{y}_i)^2a_{ii}
  = \frac 1n \sum_{i=1}^n \frac{\zeta_i^2}{a_{ii}} \\ 
- & \approx \frac{ \frac 1n \sum_{i=1}^n \zeta_i^2}{\frac 1n \sum_{i=1}^n a_{ii} } = \frac{(\vy - m\vone)^T \mC^{-2} (\vy - m \vone)}{ \trace(\mC^{-1}) } \\ 
- & \approx  s^2_{\textup{GCV}}, \\
- \intertext{where}
- s^2_{\textup{GCV}} & : = \vy^T \left[\mC^{-2} - \frac{\mC^{-2} \vone \vone^T \mC^{-2}}{\vone^T \mC^{-2} \vone}  \right] \vy  \left[ \trace(\mC^{-1}) \right]^{-1}. 
-\end{align*}
-
-The confidence interval based on GCV corresponds to \eqref{eqn_prob_confidence_interval} with the estimated $m$, $s$, and $\vtheta$:
-\begin{gather}
-\label{GCVerr}
-\err_{\textup{GCV}} = 2.58 s_{\textup{GCV}}  \sqrt{c_0 - \vc^T\mC^{-1}\vc}, \\
-\label{GCVCI}
-\mathbb{P}_f \left[
-|\mu-\hmu_{\textup{GCV}}| \leq \err_{\textup{GCV}} 
-\right] = 99\%.
-\end{gather}
-
-Looking back over the results of Sections  \ref{sec:MLE}--\ref{sec:GCV}, it is noted that if the original covariance function, $C$, is replaced by $b C$ for some positive constant $b$, the cubature, $\hmu$, the estimates of $\vtheta$, and the credible interval widths, $\err_{\textup{CI}}$, all remain unchanged.
-The estimates of $s^2$ are multiplied by $b^{-1}$, as would be expected.
-
+ & \approx \frac{ \frac 1n \sum_{i=1}^n \zeta_i^2}{\frac 1n \sum_{i=1}^n a_{ii} } = \frac{(\vy - m\vone)^T \mC_\vtheta^{-2} (\vy - m \vone)}{ \trace(\mC_\vtheta^{-1}) } \\ 
+ & \approx  s^2_{\textup{GCV}}.
+\end{align*}
+where $s^2_{\textup{GCV}}$ is given by the formula in Theorem \ref{thm:param}.
+
+The confidence interval based on GCV corresponds to \eqref{eqn_prob_confidence_interval} with the estimated $m$, $s$, and $\vtheta$.  This completes the proof of Theorem \ref{thm:param}.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsection{The automatic Bayesian cubature algorithm}
 \label{sec:bayes_cubature_algo}
-The previous section presents three credible intervals, \eqref{eqn_prob_CI_MLE}, \eqref{eqn_prob_CI_full}, and \eqref{GCVCI}, for $\mu$, the desired integral.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+The previous section presents three credible intervals, \eqref{eqn_prob_CI}, for $\mu$, the desired integral.
 Each credible interval is based on different assumptions about the hyperparameters $m$, $s$, and $\vtheta$.
 We stress that one must estimate these hyperparameters or assume a prior distribution on them because the credible intervals are used as stopping criteria for our cubature rule.
-Since a credible interval makes a statement about a typical function---not an outlier---one must try to ensure that the integrand is a typical draw from the assumed Gaussian process.
+Since a credible interval makes a statement about a typical function---not an outlier---one must try to ensure that the integrand is a typical draw from the assumed Gaussian stochastic process.
 
@@
 
+\FJHNote{Add something about the cost.}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsection{Example with the Mat\'ern kernel} \label{MVN_example}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 In contrast, this example in Section \ref{sec:NumExp} take less than a hundredth of a second to compute $\hmu_n$ once with $\varepsilon = 10^{-5}$ using our new algorithm.
-Not only is the Bayesian cubature with the Mat\'ern kernel slow, but also $\mC$ becomes highly ill-conditioned as $n$ increases.
+Not only is the Bayesian cubature with the Mat\'ern kernel slow, but also $\mC_\vtheta$ becomes highly ill-conditioned as $n$ increases.
 So, Algorithm \ref{algorithm1}  in its current form is impractical. 
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Fast Automatic Bayesian Cubature}\label{sec:fast_BC}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsection{Fast Transform Kernel}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 We make some assumptions about the relationship between the covariance kernel and the nodes, which will be shown to hold in Section \ref{sec:shift_invariant_kernel} for rank-1 lattices and shift-invariant kernels.
@@
 \nonumber
-\mC &= \Big(C_\vtheta(\vx_i,\vx_j)\Big)_{i,j=1}^n  = (\vC_1,...,\vC_n) 
+\mC = \mC_\vtheta &= \Big(C_\vtheta(\vx_i,\vx_j)\Big)_{i,j=1}^n  = (\vC_1,...,\vC_n) 
 \\
@@
 \nonumber
-\mC^p  &= \frac 1n \mV \mLambda^{p} \mV^H, \qquad \forall p \in \integers,
-\end{align}
-where $\mV^H$ is the Hermitian of $\mV$, $\vC_1,...,\vC_n$ are columns of $\mC$.
+\mC^p  &= \frac 1n \mV \mLambda^{p} \mV^H, \qquad \forall p \in \integers.
+\end{align}
+Going forward we often drop the $\vtheta$ dependence of various quantities for simplicty of notation.
+Here, $\mV^H$ is the Hermitian of $\mV$, $\vC_1,...,\vC_n$ are columns of $\mC$.
 $\vV_1,...,\vV_n$ are columns of $\mV$ and $\vv_1,...,\vv_n$ are rows of $\mV$.
@@
 \end{equation*}
-In particular,
+Note that $\widetilde{\va}^*$ appears on the right side of this equation because $\va^T \mV = (\mV^H \va)^* = \widetilde{\va}^*$.  In particular,
 \begin{align*}
@@
 \begin{appendices}
-\section{Details of full Bayes posterior} \label{appendix:full_bayes}
-Let us start with given integral $\mu$, a random variable, taking typical values $z$, then the posterior density for the $\mu$ given data $\vy$ using Bayes theorem is
-\begin{align*}
-\MoveEqLeft[1]{\rho_{\mu}(z | \vf = \vy)} \\
-& \propto \int_{0}^\infty \int_{-\infty}^\infty \rho_{\mu}(z | \vf = \vy, m = \xi, s^2 = \lambda) \\
-& \hspace{2.5cm} \times  \rho_{\vf}(\vy | \xi, \lambda ) \rho_{m, s^2}(\xi, \lambda) \, \D \xi \D \lambda \\
-& \propto \displaystyle \int_{0}^\infty  \frac{1}{\lambda^{(n+3)/2}} \\
-& \times \int_{-\infty}^\infty  \exp \biggl( -\frac{1}{2\lambda}\biggl\{
+\section{Details of the Full Bayes Posterior Density for $\mu$} \label{appendix:full_bayes}
+Starting from the Bayesian formula for the posterior density for $\mu$ at the beginning of Section \ref{sec:fullBayes} with the non-informative prior, it follows that 
+\begin{align*}
+\MoveEqLeft[1]{\rho_{\mu|\vf}(z | \vy)}\\
+& \propto \int_{0}^\infty \int_{-\infty}^\infty 
+\rho_{\mu | m, s^2, \vf}(z | \xi, \lambda , \vy) \\
+& \qquad \times  \rho_{\vf | m, s^2} (\vy | \xi, \lambda) \, \vrho_{m,s^2}(\xi,\lambda)  \, \D \xi \D \lambda \\
+& \propto \displaystyle \int_{0}^\infty  \frac{1}{\lambda^{(n+3)/2}} \cdots \\
+& \cdots \int_{-\infty}^\infty  \exp \biggl( -\frac{1}{2\lambda}\biggl\{
 \frac{
@@
 {c_0  -\vc ^T \mC^{-1} \vc}  \\
-& \hspace{1.8cm} + (\vy - \xi \vone)^T \mC^{-1}(\vy - \xi \vone) \biggr \} \biggr) \, \D \xi \D \lambda \\
-& \hspace{2.5cm}
+& \qquad + (\vy - \xi \vone)^T \mC^{-1}(\vy - \xi \vone) \biggr \} \biggr) \, \D \xi \D \lambda \\
+& \qquad \qquad
 \text{by \eqref{eqn:fGaussDist}, \eqref{eqn:condInteg}} \; \text{and} \; \rho_{m,s^2}(\xi,\lambda) \propto 1/\lambda \\
@@
 \begin{align*}
-\MoveEqLeft{\rho_{\mu}(z | \vf = \vy)} \\
+\MoveEqLeft{\rho_{\mu|\vf}(z | \vy)} \\
 & \propto \displaystyle \int_{0}^\infty  \frac{1}{\lambda^{(n+3)/2}}  \exp\left( -\frac{  \gamma - \beta^2/\alpha}{2\lambda(c_0  -\vc ^T \mC^{-1} \vc)} \right)  \cdots \\
@@
 \begin{align*}
-\alpha \gamma - \beta^2 \propto 1 +  \frac{(z - \hmu_{\textup{MLE}})^2}{(n-1)\widehat{\sigma}_{\textup{full}}^2}, \\
+\alpha \gamma - \beta^2 \propto 1 +  \frac{(z - \hmu_{\textup{MLE}})^2}{(n-1)s_{\textup{full}}^2},
 \end{align*}
@@
 \begin{multline*}
-\hsigma^2_{\textup{full}} 
+\hsigma_{\textup{full}}^2
 := \frac{1}{n-1}
@@
 \end{multline*}
+This completes the derivation of \eqref{eqn:fullBayesrho}.
 \end{appendices}

### 2019-06-29 BayesianCubaturePaper2018 - Rev1b.tex
Plots revised with randomly chosen error tols instead of 4 fixed values

@@
 \end{equation} 
-where $\$(f)$ is the cost of one integrand value, $\$(C)$ is the cost of a single covariance kernel value,  $\Order(n \log(n))$ is the cost of a fast Fourier transform, and $K_{\textup{opt}$ is an upper bound on the number of optimization steps required to choose the hyperparameters.
+where $\$(f)$ is the cost of one integrand value, $\$(C)$ is the cost of a single covariance kernel value,  $\Order(n \log(n))$ is the cost of a fast Fourier transform, and $K_{\textup{opt}}$ is an upper bound on the number of optimization steps required to choose the hyperparameters.
 If function evaluation is expensive, such as coming from computationally intensive simulation, or $\$(f) = \Order(d)$ for large $d$, then $\$(f)$ might be similar in magnitude to $\log(n)$ in practice.
@@
 	\centering
-		\includegraphics[width=0.95\linewidth]{MVN_guaranteed_time_Matern_d2_2018-Aug-31}
+		\includegraphics[width=0.95\linewidth]{MVN_guaranteed_time_Matern_d2_2019-Jun-29}
 	\centering
-		\includegraphics[width=0.95\linewidth]{MVN_rapid_n_vs_time_Matern_d2_2018-Aug-31}
+		\includegraphics[width=0.95\linewidth]{MVN_rapid_n_vs_time_Matern_d2_2019-Jun-29}
 	\caption{Multivariate normal probability estimated using Mat\'ern kernel with $d=2$ using empirical stopping criterion.
@@
 	%d=3 problem transformed into d=2
-	\includegraphics[width=0.98\linewidth]{"MVN_guaranteed_time_MLE_C2sin_d2_r2_2018-Sep-6"}
+	\includegraphics[width=0.98\linewidth]{"Lattice_MVN_guaranteed_time_MLE_C2sin_d2_r2_2019-Jun-27"}
 	\caption[Guaranteed:]{Multivariate normal probability example using the empirical Bayes stopping criterion.}
@@
 	\centering
-	\includegraphics[width=0.98\linewidth]{"MVN_guaranteed_time_full_C2sin_d2_r2_2018-Sep-6"}
+	\includegraphics[width=0.98\linewidth]{"Lattice_MVN_guaranteed_time_full_C2sin_d2_r2_2019-Jun-27"}
 	\caption[MVN guaranteed : FB]{Multivariate normal probability example using the full Bayes stopping criterion.}
@@
 	\centering
-	\includegraphics[width=0.98\linewidth]{"MVN_guaranteed_time_GCV_C2sin_d2_r2_2018-Sep-6"}
+	\includegraphics[width=0.98\linewidth]{"Lattice_MVN_guaranteed_time_GCV_C2sin_d2_r2_2019-Jun-27"}
 	\caption[MVN guaranteed : GCV]{Multivariate normal probability example using the GCV stopping criterion.}
@@
 	\centering
-	\includegraphics[width=0.95\linewidth]{"Keister_guaranteed_time_MLE_C1sin_d4_r2_2018-Sep-6"}
+	\includegraphics[width=0.95\linewidth]{"Lattice_Keister_guaranteed_time_MLE_C1sin_d4_r2_2019-Jun-27"}
 	\caption[Keister guaranteed:MLE]{Keister example using the empirical Bayes stopping criterion.}
@@
 	\centering
-	\includegraphics[width=0.95\linewidth]{"Keister_guaranteed_time_full_C1sin_d4_r2_2018-Sep-6"}
+	\includegraphics[width=0.95\linewidth]{"Lattice_Keister_guaranteed_time_full_C1sin_d4_r2_2019-Jun-27"}
 	\caption[Keister guaranteed:FB]{Keister example using the full Bayes stopping criterion.}
@@
 	\centering
-	\includegraphics[width=0.95\linewidth]{"Keister_guaranteed_time_GCV_C1sin_d4_r2_2018-Sep-6"}
+	\includegraphics[width=0.95\linewidth]{"Lattice_Keister_guaranteed_time_GCV_C1sin_d4_r2_2019-Jun-27"}
 	\caption[Keister guaranteed:GCV]{Keister example using the GCV stopping criterion.}
@@
 	\centering
-	\includegraphics[width=0.95\linewidth]{"optPrice_guaranteed_time_MLE_Baker_d12_r1_2018-Sep-6"}
+	\includegraphics[width=0.95\linewidth]{"Lattice_optPrice_guaranteed_time_MLE_Baker_d12_r1_2019-Jun-29"}
 	\caption[Option pricing Guaranteed: MLE]{Option pricing using the empirical Bayes stopping criterion.}
@@
 	\centering
-	\includegraphics[width=0.95\linewidth]{"optPrice_guaranteed_time_full_Baker_d12_r1_2018-Sep-6"}
+	\includegraphics[width=0.95\linewidth]{"Lattice_optPrice_guaranteed_time_full_Baker_d12_r1_2019-Jun-29"}
 	\caption[OptPrice guaranteed : FB]{Option pricing using the full Bayes stopping criterion.}
@@
 	\centering
-	\includegraphics[width=0.95\linewidth]{"optPrice_guaranteed_time_GCV_Baker_d12_r1_2018-Sep-6"}
+	\includegraphics[width=0.95\linewidth]{"Lattice_optPrice_guaranteed_time_GCV_Baker_d12_r1_2019-Jun-28"}
 	\caption[OptPrice guaranteed : GCV]{Option pricing using the  GCV stopping criterion.}

### 2019-06-29 BayesianCubaturePaper2018 - Rev1b.tex
Text revised to reflect the randomly chosen error tolerance.

@@
 The node sets are randomly scrambled Sobol points \cite{DicEtal14a,DicPil10a}.
-The results for  $\varepsilon = 10^{-2}, 10^{-3}, 10^{-4}$, and $10^{-5}$ and $100$ scrambles for each $\varepsilon$ are shown in \figref{fig:MVN_Metern_d2b2}.
+The results are for 400 randomly chosen $\varepsilon$ in the interval $[10^{-5}, 10^{-2}]$ as shown in \figref{fig:MVN_Metern_d2b2}.
+In each run, the nodes are randomly scrambled.
 We  observe the algorithm meets the error criterion 95\% of the time.
@@
 Three integrals were evaluated using the GAIL algorithm \code{cubBayesLattice\_g}:  a multivariate normal probability, the Keister's example, and an option pricing example.  
-Four different error tolerances, $\varepsilon$,  were set for each example, with the tolerances chosen depending on the difficulty of the problem.
 The sequences $\{\vx_i\}_{i=1}^\infty$ were the randomly shifted lattice node sequences supplied by GAIL. 
+For each integral,  each of our stopping criteria---empirical Bayes, full Bayes, and generalized cross-validation---our algorithm was run for $400$ different randomly chosen error tolerance.
+The error tolerances were chosen randomly in an interval depending on the difficulty of the problem.
+In each run, the nodes were also randomly shifted.
 The accuracy of the algorithm differs based on the shift.
-For each integral,  each tolerance, and each of our stopping criteria---empirical Bayes, full Bayes, and generalized cross-validation---our algorithm was run for $100$ different random shifts.
 For each test, the execution times were plotted against $\abs{\mu - \hmu}/\varepsilon$.

### 2019-07-09 BayesianCubaturePaper2018 - Rev1b.tex
Option pricing plots corrected

@@
 	\centering
-	\includegraphics[width=0.95\linewidth]{"Lattice_optPrice_guaranteed_time_MLE_Baker_d12_r1_2019-Jun-29"}
+	\includegraphics[width=0.95\linewidth]{"Lattice_optPrice_guaranteed_time_MLE_Baker_d12_r1_2019-Jul-9"}
 	\caption[Option pricing Guaranteed: MLE]{Option pricing using the empirical Bayes stopping criterion.}
@@
 	\centering
-	\includegraphics[width=0.95\linewidth]{"Lattice_optPrice_guaranteed_time_full_Baker_d12_r1_2019-Jun-29"}
+	\includegraphics[width=0.95\linewidth]{"Lattice_optPrice_guaranteed_time_full_Baker_d12_r1_2019-Jul-9"}
 	\caption[OptPrice guaranteed : FB]{Option pricing using the full Bayes stopping criterion.}
@@
 	\centering
-	\includegraphics[width=0.95\linewidth]{"Lattice_optPrice_guaranteed_time_GCV_Baker_d12_r1_2019-Jun-28"}
+	\includegraphics[width=0.95\linewidth]{"Lattice_optPrice_guaranteed_time_GCV_Baker_d12_r1_2019-Jul-8"}
 	\caption[OptPrice guaranteed : GCV]{Option pricing using the  GCV stopping criterion.}

### 2019-07-13 BayesianCubaturePaper2018 - Rev1b.tex
Fixing a typo in Sec 4.4 Iterative Computation of the Fast Transform
Updates from Overleaf

--- 2019-06-29 BayesianCubaturePaper2018 - Rev1b.tex
@@
 	\centering
-		\includegraphics[width=0.95\linewidth]{MVN_guaranteed_time_Matern_d2_2019-Jun-29}
+		\includegraphics[width=0.95\linewidth]{MVN_guaranteed_time_Matern_d2_2018-Aug-31}
 	\centering
-		\includegraphics[width=0.95\linewidth]{MVN_rapid_n_vs_time_Matern_d2_2019-Jun-29}
+		\includegraphics[width=0.95\linewidth]{MVN_rapid_n_vs_time_Matern_d2_2018-Aug-31}
 	\caption{Multivariate normal probability estimated using Mat\'ern kernel with $d=2$ using empirical stopping criterion.
@@
 	%d=3 problem transformed into d=2
-	\includegraphics[width=0.98\linewidth]{"Lattice_MVN_guaranteed_time_MLE_C2sin_d2_r2_2019-Jun-27"}
+	\includegraphics[width=0.98\linewidth]{"MVN_guaranteed_time_MLE_C2sin_d2_r2_2018-Sep-6"}
 	\caption[Guaranteed:]{Multivariate normal probability example using the empirical Bayes stopping criterion.}
@@
 	\centering
-	\includegraphics[width=0.98\linewidth]{"Lattice_MVN_guaranteed_time_full_C2sin_d2_r2_2019-Jun-27"}
+	\includegraphics[width=0.98\linewidth]{"MVN_guaranteed_time_full_C2sin_d2_r2_2018-Sep-6"}
 	\caption[MVN guaranteed : FB]{Multivariate normal probability example using the full Bayes stopping criterion.}
@@
 	\centering
-	\includegraphics[width=0.98\linewidth]{"Lattice_MVN_guaranteed_time_GCV_C2sin_d2_r2_2019-Jun-27"}
+	\includegraphics[width=0.98\linewidth]{"MVN_guaranteed_time_GCV_C2sin_d2_r2_2018-Sep-6"}
 	\caption[MVN guaranteed : GCV]{Multivariate normal probability example using the GCV stopping criterion.}
@@
 	\centering
-	\includegraphics[width=0.95\linewidth]{"Lattice_Keister_guaranteed_time_MLE_C1sin_d4_r2_2019-Jun-27"}
+	\includegraphics[width=0.95\linewidth]{"Keister_guaranteed_time_MLE_C1sin_d4_r2_2018-Sep-6"}
 	\caption[Keister guaranteed:MLE]{Keister example using the empirical Bayes stopping criterion.}
@@
 	\centering
-	\includegraphics[width=0.95\linewidth]{"Lattice_Keister_guaranteed_time_full_C1sin_d4_r2_2019-Jun-27"}
+	\includegraphics[width=0.95\linewidth]{"Keister_guaranteed_time_full_C1sin_d4_r2_2018-Sep-6"}
 	\caption[Keister guaranteed:FB]{Keister example using the full Bayes stopping criterion.}
@@
 	\centering
-	\includegraphics[width=0.95\linewidth]{"Lattice_Keister_guaranteed_time_GCV_C1sin_d4_r2_2019-Jun-27"}
+	\includegraphics[width=0.95\linewidth]{"Keister_guaranteed_time_GCV_C1sin_d4_r2_2018-Sep-6"}
 	\caption[Keister guaranteed:GCV]{Keister example using the GCV stopping criterion.}
@@
 	\centering
-	\includegraphics[width=0.95\linewidth]{"Lattice_optPrice_guaranteed_time_MLE_Baker_d12_r1_2019-Jun-29"}
+	\includegraphics[width=0.95\linewidth]{"optPrice_guaranteed_time_MLE_Baker_d12_r1_2018-Sep-6"}
 	\caption[Option pricing Guaranteed: MLE]{Option pricing using the empirical Bayes stopping criterion.}
@@
 	\centering
-	\includegraphics[width=0.95\linewidth]{"Lattice_optPrice_guaranteed_time_full_Baker_d12_r1_2019-Jun-29"}
+	\includegraphics[width=0.95\linewidth]{"optPrice_guaranteed_time_full_Baker_d12_r1_2018-Sep-6"}
 	\caption[OptPrice guaranteed : FB]{Option pricing using the full Bayes stopping criterion.}
@@
 	\centering
-	\includegraphics[width=0.95\linewidth]{"Lattice_optPrice_guaranteed_time_GCV_Baker_d12_r1_2019-Jun-28"}
+	\includegraphics[width=0.95\linewidth]{"optPrice_guaranteed_time_GCV_Baker_d12_r1_2018-Sep-6"}
 	\caption[OptPrice guaranteed : GCV]{Option pricing using the  GCV stopping criterion.}

### 2019-07-15 ResponseToReferees.tex
Updates from Overleaf

@@
 \item  The other derivations in the paper are all made in prose. It would be better
-to formally state some of them. E.g., the results on the top of page 3. \Response{The key results from Sections 2.2.1--2.2.3 have been collected in a theorem just before Section 2.2.1.}
+to formally state some of them.
+E.g., the results on the top of page 3.
+\Response{The key results from Sections 2.2.1--2.2.3 have been collected in a theorem just before Section 2.2.1.
+The key results of Section 3 are also collected into a theorem.}
 \item  From (6) to (7) the notation is different: $c^T C^{-1} 1$ vs $1^T C^{-1} c$,
@@
 \begin{itemize}
-\item Maybe write 'previous section' instead of 'last section'.
+\item Maybe write 'previous section' instead of 'last section'.  \Response{Done.}
 \item Maybe write 'covariance kernel' instead of just 'kernel'. I think the word
-kernel hasn't been used up till this point.
+kernel hasn't been used up till this point.  \Response{Done.}
 \end{itemize}
 
-\item Section 3.1. Use $C_{\vec{\theta}}$ in (27) for clarity.
+\item Section 3.1. Use $C_{\vec{\theta}}$ in (27) for clarity. \Response{Done.}
 
@@
 
-\item p.\ 5, Sec.\ 2.4 Why are Sobol points chosen for the Matern kernel? Is there some theoretical link?
+\item p.\ 5, Sec.\ 2.4 Why are Sobol points chosen for the Matern kernel? Is there some theoretical link?  \Response{Added ``Sobol' points are a typical space-filling design.''}
 
@@
 
-\item p.\ 9, eqn. (37) $i, j = 1$
+\item p.\ 9, eqn. (37) $i, j = 1$. \Response{Done.}
 
@@
 \begin{itemize}
-    \item Section 2.1, line 9: I think ``The function $C$" should be "The function $C_\theta$," since there is no function $C$.
+    \item Section 2.1, line 9: I think ``The function $C$" should be "The function $C_\theta$," since there is no function $C$.  \Response{Yes, corrected.}
 
-\item Right before (12):  Not sure if ``simplify to" is the right expression, since it does not look like a simplification of those formulas.
+\item Right before (12):  Not sure if ``simplify to" is the right expression, since it does not look like a simplification of those formulas.  \Response{This part has been re-written.}
 
-\item Section 2.2.3, line 5: This is conditional on the data, but also a function of the parameters, I suppose?  I think this should be clarified.  On line 7, read "is the sum".
+\item Section 2.2.3, line 5: This is conditional on the data, but also a function of the parameters, I suppose?  I think this should be clarified.  \Response{Done.}
 
-\item Two lines before Equation (20): ``confidence interval" and not ``credibility interval" like the other ones?
+\item On line 7, read ``is the sum". \Response{Fixed.}
 
-\item Five lines after (21): err$_{\rm CI}$ refers to what exactly? The value in (20)?  Clarify.
+\item Two lines before Equation (20): ``confidence interval" and not ``credibility interval" like the other ones?  \Response{Fixed.}
 
-\item In (24), are $C_1,\dots,C_n$ the columns of C?
+\item Five lines after (21): err$_{\rm CI}$ refers to what exactly? The value in (20)?  Clarify.  \Response{Re-written to clarify.}
+
+\item In (24), are $C_1,\dots,C_n$ the columns of C?  \Response{Yes.}
 
@@
 
-\item Section 5.2, line 8: correct ``differs depends".
+\item Section 5.2, line 8: correct ``differs depends". \Response{Fixed.}
 
@@
 
-\item Reference [1]:  "Griolami"?   Mark may not recognize himself!
+\item Reference [1]:  "Griolami"?   Mark may not recognize himself!  \Response{Sorry.  Fixed.}
 

### 2019-07-15 BayesianCubaturePaper2018 - Rev1b.tex
Updates from Overleaf

--- 2019-07-09 BayesianCubaturePaper2018 - Rev1b.tex
@@
 
-The process just outlined typically requires vector-matrix operations  with a computational cost of $O(n^3)$ to .
-Our innovation is to pair low discrepancy nodes with matching kernels that lower the  computational cost to $O(n \log n)$.
+The process outlined above typically requires a computational cost of $O(N_{\text{opt}}n^3)$, where $N_{\text{opt}}$ is the number of optimizations required to identify the hyperparameters.
+Our innovation is to pair low discrepancy nodes with matching kernels that lower the  computational cost to $O(N_{\text{opt}} n \log n)$.
 This approach is demonstrated using rank-1 lattice sequences and shift-invariant kernels.
@@
 \begin{equation} \label{eqn:OuralgoCost}
-    \Order\bigl(K_{\textup{opt}}[n \$(f) + n\$(C) + n \log(n)] \bigr),
+    \Order\bigl(N_{\textup{opt}}[n \$(f) + n\$(C) + n \log(n)] \bigr),
 \end{equation} 
-where $\$(f)$ is the cost of one integrand value, $\$(C)$ is the cost of a single covariance kernel value,  $\Order(n \log(n))$ is the cost of a fast Fourier transform, and $K_{\textup{opt}}$ is an upper bound on the number of optimization steps required to choose the hyperparameters.
+where $\$(f)$ is the cost of one integrand value, $\$(C)$ is the cost of a single covariance kernel value,  $\Order(n \log(n))$ is the cost of a fast Fourier transform, and $N_{\textup{opt}}$ is an upper bound on the number of optimization steps required to choose the hyperparameters.
 If function evaluation is expensive, such as coming from computationally intensive simulation, or $\$(f) = \Order(d)$ for large $d$, then $\$(f)$ might be similar in magnitude to $\log(n)$ in practice.
+Typically, $\$(C) = \Order(d)$.
 Note that the $\Order(n \log(n))$ contribution is $d$ independent.
@@
 \begin{equation} \label{eqn:TheiralgoCost}
-    \Order\bigl(K_{\textup{opt}}[n \$(f) + n^2\$(C)) + n^3] \bigr),
+    \Order\bigl(N_{\textup{opt}}[n \$(f) + n^2\$(C) + n^3] \bigr),
 \end{equation} 
-which is explained in Section \ref{sec:bayes_cubature_algo}. Note that the work beyond evaluating the integrand in \label{eqn:TheiralgoCost} is much larger than that in \eqref{eqn:TheiralgoCost}.
+which is explained in Section \ref{sec:bayes_cubature_algo}. Note that the work beyond evaluating the integrand in \eqref{eqn:TheiralgoCost} is much larger than that in \eqref{eqn:OuralgoCost}.
 
@@
 
-For the results summarized in the theorem above, note that if the original covariance function, $C$, is replaced by $b C$ for some positive constant $b$, the cubature, $\hmu$, the estimates of $\vtheta$, and the credible interval widths, $\err_{\textup{CI}}$, all remain unchanged.
+For the results summarized in the theorem above, note that if the original covariance function, $C_\vtheta$, is replaced by $b C_\vtheta$ for some positive constant $b$, the cubature, $\hmu$, the estimates of $\vtheta$, and the credible interval widths, $\err_{\mathsf{x}}$ for $\mathsf{x} \in \{\MLE, \full, \GCV\}$, all remain unchanged.
 The estimates of $s^2$ are multiplied by $b^{-1}$, as would be expected.
@@
 \label{eqn:thetaMLE}
- & \qquad +  \frac{1}{n} \log(\det(\mC))
+ & \qquad +  \frac{1}{n} \log(\det(\mC_\vtheta))
 \biggr \}.
 \end{align}
-The empirical Bayes estimate of $\vtheta$ balances minimizing the covariance scale factor, $s^2_{\MLE}$, against minimizing  $\det(\mC)$. 
+The empirical Bayes estimate of $\vtheta$ balances minimizing the covariance scale factor, $s^2_{\MLE}$, against minimizing  $\det(\mC_\vtheta)$. 
 Under these estimates of the parameters, the cubature \eqref{eqn:BayesCub} and the credible interval \eqref{eqn_prob_confidence_interval} are explicitly written as in Theorem \ref{thm:param}.
-The quantities $c_{0\vtheta}$, $\vc_\vtheta$, and $\mC$ are assumed implicitly to be based on $\vtheta = \vtheta_\MLE$.
+The quantities $c_{0\vtheta}$, $\vc_\vtheta$, and $\mC_\vtheta$ are assumed implicitly to be based on $\vtheta = \vtheta_\MLE$.
 
@@
 This means that $\mu \vert (\vf = \vy )$, properly centered and scaled, has a Student's $t$-distribution with $n-1$ degrees of freedom.
-The estimated integral is the same as in the empirical Bayes case, $\hmu_{\textup{full}} = \hmu_{\MLE}$, but the confidence interval is wider, as stated in the Theorem \ref{thm:param}.
+The estimated integral is the same as in the empirical Bayes case, $\hmu_{\textup{full}} = \hmu_{\MLE}$, but the credible interval is wider, as stated in the Theorem \ref{thm:param}.
 
@@
 Let $\mathring{y}_i = \Ex[f(\vx_i ) | \vf_{-i} = \vy_{-i}]$, where the subscript $-i$ denotes the vector excluding the $i^{\text{th}}$ component.
-This is the conditional expectation of $f(\vx_i )$ given all data but the function value at $\vx_i$.
+This is the conditional expectation of $f(\vx_i )$ given the parameters $m$, $s$, and $\vtheta$, and all data but the function value at $\vx_i$.
 The cross-validation criterion, which is to be minimized, is the sum of squares of the difference between these conditional expectations and the observed values:
@@
 = \frac{\sum_{i=1}^n\zeta_i^2}{\left(\frac 1n \sum_{i=1}^n a_{ii} \right)^2} \\
-& = \frac{(\vy - m\vone)^T \mC^{-2}_\vtheta (\vy - m \vone)}{\left(\frac 1n \trace(\mC^{-1}) \right)^2}.
+& = \frac{(\vy - m\vone)^T \mC^{-2}_\vtheta (\vy - m \vone)}{\left(\frac 1n \trace(\mC_\vtheta^{-1}) \right)^2}.
 \end{align*}
@@
 
-The confidence interval based on GCV corresponds to \eqref{eqn_prob_confidence_interval} with the estimated $m$, $s$, and $\vtheta$.  This completes the proof of Theorem \ref{thm:param}.
+The credible interval based on GCV corresponds to \eqref{eqn_prob_confidence_interval} with the estimated $m$, $s$, and $\vtheta$.  This completes the proof of Theorem \ref{thm:param}.
 
@@
 \end{align*}
-and Sobol points as the nodes.
+and Sobol' points as the nodes.  (Sobol' points are a typical space-filling design.)
 Also, consider the integration problem of evaluating  \emph{multivariate normal probabilities}:
@@
 \end{align*}
-The node sets are randomly scrambled Sobol points \cite{DicEtal14a,DicPil10a}.
+The node sets are randomly scrambled Sobol' points \cite{DicEtal14a,DicPil10a}.
 The results are for 400 randomly chosen $\varepsilon$ in the interval $[10^{-5}, 10^{-2}]$ as shown in \figref{fig:MVN_Metern_d2b2}.
@@
 \end{align}
-Going forward we often drop the $\vtheta$ dependence of various quantities for simplicty of notation.
+Here the $\vC_j$ are the columns of $\mC$.
+In this and later sections, we drop the $\vtheta$ dependence of various quantities for simplicty of notation.
 Here, $\mV^H$ is the Hermitian of $\mV$, $\vC_1,...,\vC_n$ are columns of $\mC$.
@@
 \end{align}
-which implies that $c_0 = 1$ and $\vc = \vone$.  Under \eqref{addAssump}, the expressions above may be further simplified:
+which implies that $c_{0\vtheta} = 1$ and $\vc_\vtheta = \vone$.  Under \eqref{addAssump}, the expressions above may be further simplified:
 \begin{align*}
@@
 \end{align*}
-
-\subsection{Empirical Bayes}
-
-Under assumptions \eqref{fastcompAssump}, the empirical Bayes parameters in \eqref{eqn_m_MLE}, \eqref{eqn_s2_MLE}, \eqref{eqn:thetaMLE} \eqref{eqn:cubMLE}, and \eqref{eqn:errMLE} can be expressed in terms of the fast transforms of the function data, the first column of the Gram matrix, and $\vc$ as follows:
+The assumptions and derivations above lead to the following theorem.
+
+\begin{theorem} \label{thm:fastparam}
+Under assumptions \eqref{fastcompAssump}, the parameters and credible interval widths in Theorem \ref{thm:param} may be expressed in terms of the fast transforms of the function data, the first column of the Gram matrix, and $\vc_\vtheta$ as follows:
+\allowdisplaybreaks
 \begin{align}
 \nonumber
-m_\MLE &=  \frac{\widetilde{y}_1}{n} = \frac 1n \sum_{i=1}^n y_i,
+m_\MLE &=  m_{\full} = m_{\GCV} =  \frac{\widetilde{y}_1}{n} = \frac 1n \sum_{i=1}^n y_i,
 \\
@@
 \frac{1}{n^2} 
-\sum_{i=2}^n \frac{\abs{\widetilde{y}_i}^2}{\lambda_i},
-\end{align}
-\begin{align}
+\sum_{i=2}^n \frac{\abs{\widetilde{y}_i}^2}{\lambda_i}, \\
+\nonumber
+\widehat{\sigma}^2_{\textup{full}}
+& =
+\frac{1}{n(n-1)} \sum_{i=2}^n \frac{\abs{\widetilde{y}_i}^2}{\lambda_i}
+\\
+\nonumber
+& \qquad \times
+\left[\frac{\lambda_1}{n}{\left(1 - \frac{\widetilde{c}_1}{\lambda_1}\right)^2} + \left(c_0  - \frac 1n \sum_{i=1}^n \frac{\abs{\widetilde{c}_i}^2}{\lambda_i}\right) \right], \\
+\nonumber 
+s^2_{\textup{GCV}} & : =  \frac 1{n} \sum_{i=2}^n \frac{\abs{\widetilde{y}_i}^2}{\lambda_i^2}  \left [ \sum_{i=1}^n \frac{1}{\lambda_i} \right]^{-1},\\
 \label{eqn_MLE_loss_func_optimized_2} %\nonumber
@@
 \log\left(
-\sum_{i=2}^n \frac{\abs{\widetilde{y}_i}^2}{\lambda_i}
+\sum_{i=2}^n \frac{\abs{\widetilde{y}_i}^2}{\lambda_{\vtheta i}}
 \right) %\right .\\ \hspace{3cm} \left .
- + \frac{1}{n}\sum_{i=1}^n \log(\lambda_i)
-\right],
-\end{align}
-\begin{align}
-\nonumber
-\hmu_\MLE  &= 
+ + \frac{1}{n}\sum_{i=1}^n \log(\lambda_{\vtheta i})
+\right],\\
+\nonumber 
+\vtheta_{\GCV} 
+&= \argmin_\vtheta \left[ \log \left ( \sum_{i=2}^n \frac{\abs{\widetilde{y}_i}^2}{\lambda_{\vtheta i}^2} 
+\right) \right .\\
+\label{thetaGCV}
+& \qquad \qquad \qquad \qquad  \left . -2\log\left( \sum_{i=1}^n \frac{1}{\lambda_{\vtheta i}} \right)
+\right], \\
+\nonumber
+\hmu_\MLE  &= \hmu_{\full} = \hmu_{\GCV} =
 \frac{\widetilde{y}_1}{n} +
@@
 	\left( c_0 - \frac 1n \sum_{i=1}^n \frac{\abs{\widetilde{c}_i}^2}{\lambda_i} \right) 
-}.
-\end{align}
-Since all the quantities on the right hand sides can be obtained in $\Order(n \log(n))$ operations by fast transforms, the left hand sides are all computable using the asymptotic computational cost.
-
+}, \\
+\nonumber
+\err_{\full} & = t_{n-1,0.995} \hsigma_{\textup{full}}, \\
+\nonumber
+\err_{\textup{GCV}} & =
+\frac{2.58}{n}\left\{\sum_{i=2}^n \frac{\abs{\widetilde{y}_i}^2}{\lambda_i^2}  \left [ \frac 1n \sum_{i=1}^n \frac{1}{\lambda_i} \right]^{-1} \right.
+\\ 
+\nonumber
+&\qquad \qquad \left . \times
+\left( c_0 - \frac 1n \sum_{i=1}^n \frac{\abs{\widetilde{c}_i}^2}{\lambda_i} \right) 
+\right\}^{1/2}.
+\end{align}
 Under the further assumption \eqref{addAssump}, it follows that 
@@
 \nonumber
-\hmu_\MLE  &= 
-\frac{\widetilde{y}_1}{n} = \frac 1n \sum_{i=1}^n y_i,\\
+\hmu_\MLE  &= \hmu_{\full} = \hmu_{\GCV} =
+\frac{\widetilde{y}_1}{n} = \frac 1n \sum_{i=1}^n y_i,
+\end{align}
+and so $\hmu$ is simply the sample mean.  Also, under assumption \eqref{addAssump}, the credible interval widths simplify to
+\begin{align}
 \label{eq:errMLEAllAsump}
@@
 	\left( 1 -  \frac{n}{\lambda_1} \right) 
-}.
-\end{align}
-Thus, in this  case $\hmu$ is simply the sample mean.
-
-\subsection{Full Bayes}
-For the full Bayes approach the cubature is the same as for empirical Bayes.
-We also defer to empirical Bayes to estimate the parameter $\vtheta$.
-The width of the confidence interval is $\err_{\textup{full}}
-:= t_{n-1,0.995} \hsigma_{\textup{full}}$, where $\hsigma_{\textup{full}}^2$ can also be computed swiftly under assumptions \eqref{fastcompAssump}:
-\begin{multline*} %\label{FJH:eq:signmaFull}
-\widehat{\sigma}^2_{\textup{full}}
-=
-\frac{1}{n(n-1)} \sum_{i=2}^n \frac{\abs{\widetilde{y}_i}^2}{\lambda_i}
-\\
-\times
-\left[\frac{\lambda_1}{n}{\left(1 - \frac{\widetilde{c}_1}{\lambda_1}\right)^2} + \left(c_0  - \frac 1n \sum_{i=1}^n \frac{\abs{\widetilde{c}_i}^2}{\lambda_i}\right) \right],
-\end{multline*}
-Under assumption \eqref{addAssump} further simplification can be made:
-\begin{align*} %\label{FJH:eq:signmaFullSimple}
-\widehat{\sigma}^2_{\textup{full}}
-=
-\frac{1}{n(n-1)} \sum_{i=2}^n \frac{\abs{\widetilde{y}_i}^2}{\lambda_i} \, \left(\frac{\lambda_1}{n}  - 1  \right),
-\end{align*}
-It follows that
-\begin{align} \label{FJH:eq:errFullSimple}
+}, \\
+\label{FJH:eq:errFullSimple}
 \err_{\textup{full}}
-=
+&=
 t_{n-1,0.995}
-\sqrt{\frac{1}{n(n-1)} \sum_{i=2}^n \frac{\abs{\widetilde{y}_i}^2}{\lambda_i}  \left(\frac{\lambda_1}{n}  - 1  \right)}.
-\end{align}
-
-\subsection{Generalized Cross-Validation}
-
-GCV yields a different cubature, which nevertheless can also be computed quickly using the fast transform.  Under assumptions \eqref{fastcompAssump}:
-\begin{align}
-\nonumber
-m_{\textup{GCV}} & = m_\MLE =  \frac{\widetilde{y}_1}{n} = \frac 1n \sum_{i=1}^n y_i,\\
-\nonumber 
-s^2_{\textup{GCV}} & : =  \frac 1{n} \sum_{i=2}^n \frac{\abs{\widetilde{y}_i}^2}{\lambda_i^2}  \left [ \sum_{i=1}^n \frac{1}{\lambda_i} \right]^{-1}, 
-\end{align}
-\begin{align}
-\nonumber 
-\vtheta_{\GCV} 
-&= \argmin_\vtheta \left[ \log \left ( \sum_{i=2}^n \frac{\abs{\widetilde{y}_i}^2}{\lambda_i^2} 
-\right) \right .\\
-\label{thetaGCV}
-& \qquad \qquad \qquad \qquad  \left . -2\log\left( \sum_{i=1}^n \frac{1}{\lambda_i} \right)
-\right], \\
-\nonumber
-\hmu_{\GCV}
-&= \hmu_\MLE  = \frac{\widetilde{y}_1}{n} +
-\frac 1n \sum_{i=2}^n \frac{ \widetilde{c}_i^* \widetilde{y}_i}{\lambda_i}, \\
+\sqrt{\frac{1}{n(n-1)} \sum_{i=2}^n \frac{\abs{\widetilde{y}_i}^2}{\lambda_i}  \left(\frac{\lambda_1}{n}  - 1  \right)}, \\
 \nonumber
 \err_{\textup{GCV}} & =
-\frac{2.58}{n}\left\{\sum_{i=2}^n \frac{\abs{\widetilde{y}_i}^2}{\lambda_i^2}  \left [ \frac 1n \sum_{i=1}^n \frac{1}{\lambda_i} \right]^{-1} \right.
-\\ 
-\nonumber
-&\qquad \qquad \left . \times
-\left( c_0 - \frac 1n \sum_{i=1}^n \frac{\abs{\widetilde{c}_i}^2}{\lambda_i} \right) 
-\right\}^{1/2}.
-\end{align}
-Moreover, under further assumption \eqref{addAssump}, it follows that 
-\begin{align}
-\label{muhatGCV-FB-MLE-Simple}
-\hmu_{\textup{GCV}}
-&= \hmu_\MLE = \hmu_{\textup{full}} =
-\frac{\widetilde{y}_1}{n} = \frac 1n \sum_{i=1}^n y_i,\\
-\nonumber
-\err_{\textup{GCV}} & =
-\frac{2.58}{n}\left\{\sum_{i=2}^n \frac{\abs{\widetilde{y}_i}^2}{\lambda_i^2}  \left [ \frac 1n \sum_{i=1}^n \frac{1}{\lambda_i} \right]^{-1} \right.
-\\ 
-&\qquad \qquad \left . \times
+\frac{2.58}{n}\left\{\sum_{i=2}^n \frac{\abs{\widetilde{y}_i}^2}{\lambda_i^2}  \left [ \frac 1n \sum_{i=1}^n \frac{1}{\lambda_i} \right]^{-1} 
+\right. \\ &\qquad \qquad \left . \times
 \left( 1 -  \frac{n}{\lambda_1} \right)  
@@
 \end{align}
-In this case too, $\hmu$ is simply the sample mean.
+\end{theorem}
 
@@
 \widetilde{\vb} = \begin{pmatrix} \widetilde{b}_1 \\ \vdots \\ \widetilde{b}_{2n} \end{pmatrix}, \quad 
-\widetilde{\vb}^{(1)} = \begin{pmatrix} b_1 \\ b_3 \\ \vdots \\ b_{2n-1} \end{pmatrix}, \quad 
-\widetilde{\vb}^{(2)}  = \begin{pmatrix} b_{2} \\  b_{4} \\ \vdots \\ b_{2n} \end{pmatrix}. 
+\widetilde{\vb}^{(1)} = \begin{pmatrix} \widetilde{b}_1 \\ \widetilde{b}_3 \\ \vdots \\ \widetilde{b}_{2n-1} \end{pmatrix}, \quad 
+\widetilde{\vb}^{(2)}  = \begin{pmatrix} \widetilde{b}_{2} \\  \widetilde{b}_{4} \\ \vdots \\ \widetilde{b}_{2n} \end{pmatrix}. 
 \end{gather*}
@@
 The sequences $\{\vx_i\}_{i=1}^\infty$ were the randomly shifted lattice node sequences supplied by GAIL. 
-For each integral,  each of our stopping criteria---empirical Bayes, full Bayes, and generalized cross-validation---our algorithm was run for $400$ different randomly chosen error tolerance.
+For each integral,  each of our stopping criteria---empirical Bayes, full Bayes, and generalized cross-validation---our algorithm was run for $400$ different randomly chosen error tolerances.
 The error tolerances were chosen randomly in an interval depending on the difficulty of the problem.

### 2019-07-18 BayesianCubaturePaper2018 - Rev1b.tex
Updates from Overleaf
revising

@@
 \newcommand{\mC}{\mathsf{C}}
+\newcommand{\mP}{\mathsf{P}}
+\newcommand{\mK}{\mathsf{K}}
 \newcommand{\rmC}{\mathring{\mathsf{C}}}
@@
 \newcommand{\var}{{\textup{var}}}
+\newcommand{\opt}{{\textup{opt}}}
 
@@
 
-%\allowdisplaybreaks[4]
+\allowdisplaybreaks
 \begin{document}
@@
 \begin{equation} \label{eqn:OuralgoCost}
-    \Order\bigl(N_{\textup{opt}}[n \$(f) + n\$(C) + n \log(n)] \bigr),
+    \Order\bigl(n \$(f) + N_{\textup{opt}}[n\$(C) + n \log(n)] \bigr),
 \end{equation} 
 where $\$(f)$ is the cost of one integrand value, $\$(C)$ is the cost of a single covariance kernel value,  $\Order(n \log(n))$ is the cost of a fast Fourier transform, and $N_{\textup{opt}}$ is an upper bound on the number of optimization steps required to choose the hyperparameters.
-If function evaluation is expensive, such as coming from computationally intensive simulation, or $\$(f) = \Order(d)$ for large $d$, then $\$(f)$ might be similar in magnitude to $\log(n)$ in practice.
+If function evaluation is expensive, such as coming from computationally intensive simulation, or $\$(f) = \Order(d)$ for large $d$, then $\$(f)$ might be similar in magnitude to $N_{\textup{opt}} \log(n)$ in practice.
 Typically, $\$(C) = \Order(d)$.
@@
 \begin{equation} \label{eqn:TheiralgoCost}
-    \Order\bigl(N_{\textup{opt}}[n \$(f) + n^2\$(C) + n^3] \bigr),
+    \Order\bigl(n \$(f) + N_{\textup{opt}}[n^2\$(C) + n^3] \bigr),
 \end{equation} 
@@
 Section \ref{sec:fast_BC}  introduces the concept of covariance kernels that match the nodes and expedite the computations required by our automatic Bayesian cubature. 
-Section \ref{sec:shift_invariant_kernel} implements this concept for shift invariant kernels and rank-1 lattice nodes.
+Section \ref{sec:shift_invariant_kernel} implements this concept for shift-invariant kernels and rank-1 lattice nodes.
 It also describes how to avoid cancellation error for kernels of product form.
@@
 Under these three approaches we have the following:
-\begin{allowdisplaybreaks}
+%\begin{allowdisplaybreaks}
 \begin{align}
@@
 \nonumber
-\err_{\mathsf{x}} & = 2.58 s_{\mathsf{x}} \sqrt{c_{0\vtheta} - \vc_{\vtheta}^T\mC_\vtheta^{-1}\vc_{\vtheta} }, \quad \mathsf{x} \in \{\MLE, \GCV\}, \\
-\nonumber 
+\err_{\mathsf{x}} & = 2.58 s_{\mathsf{x}} \sqrt{c_{0\vtheta} - \vc_{\vtheta}^T\mC_\vtheta^{-1}\vc_{\vtheta} }, \\
+& \hspace{3.5cm} \mathsf{x} \in \{\MLE, \GCV\},  \label{eqn:err_MLEGCV}\\ 
 \err_{\textup{full}} 
-& = t_{n-1,0.995} \hsigma_{\textup{full}} > \err_\MLE,
-\end{align}
-\end{allowdisplaybreaks}
+& = t_{n-1,0.995} \hsigma_{\textup{full}} > \err_\MLE, \label{FJH:eq:errFull}
+\end{align}
+%\end{allowdisplaybreaks}
 \begin{multline}
@@
 Maximizing the log-likelihood first with respect to $m$ and then with respect to $s$ yields the values given in Theorem \ref{thm:param}.
-To obtain $\vtheta_\MLE$, we substitute $m_\MLE$ and $s_\MLE$ into $l(s,m,\vtheta | \vy)$ and then numerically optimize:
-\begin{align}
-\nonumber
-\vtheta_\MLE
-&= \argmin_{\vtheta} \biggl \{
-\log\left(\vy^T 
-\left[ \mCInv_\vtheta - 
-\frac{ \mCInv_\vtheta \vone \vone^T \mCInv_\vtheta }{\vone^T\mCInv_\vtheta \vone}
-\right] \vy 
-\right)  \\
-\label{eqn:thetaMLE}
- & \qquad +  \frac{1}{n} \log(\det(\mC_\vtheta))
-\biggr \}.
-\end{align}
+To obtain $\vtheta_\MLE$, we substitute $m_\MLE$ and $s_\MLE$ into $l(s,m,\vtheta | \vy)$, which leads directly to the optimization problem in \eqref{eqn:thetaMLE}.
+
 The empirical Bayes estimate of $\vtheta$ balances minimizing the covariance scale factor, $s^2_{\MLE}$, against minimizing  $\det(\mC_\vtheta)$. 
@@
         \State Compute $\vtheta$ by \eqref{eqn:thetaMLE} or \eqref{vthetaGCV}
-        \State Compute $\err_{\textup{CI}}$  according to \eqref{eqn:errMLE}, \eqref{FJH:eq:errFull}, or \eqref{GCVerr}
+        \State Compute $\err_{\textup{CI}}$  according to \eqref{eqn:err_MLEGCV} or \eqref{FJH:eq:errFull}
 
@@
         \State Compute $\hmu$, the approximate integral,   according to \eqref{eqn:cubMLE} or \eqref{eqn:muCV}
-      \State \Return $\hmu, \; n$  and $\err_{\textup{CI}}$
+      \State \Return $\hmu$, $n$,  and $\err_{\textup{CI}}$
   \end{algorithmic}
@@
 
-\FJHNote{Add something about the cost.}
+As described above, the computational cost of Algorithm \ref{algorithm1} is the sum of the following:
+\begin{itemize}
+	\item $\Order\bigl(n\$(f) \bigr)$ for the function data, where $\$(f)$ is the computational cost of a single $f(\vx)$; $\$(f)$ may be large if it is the result of an expensive simulation; $\$(f)$ is typically proportional to $d$;
+
+	\item $\Order\bigl(N_{\opt} n^2 \$(C_\vtheta) \bigr)$ for the evaluation of the matrix $\mC_{\vtheta}$, $N_\opt$ is the number of optimization steps required, and  $\$(C_\vtheta)$ is the computational cost of a single $C_\vtheta(\vt,\vx)$; $\$(C)$ is typically proportional to $d$; and
+
+	\item $\Order\bigl(N_{\opt} n^3 \bigr)$ for the matrix inversions and determinant calculations.
+
+\end{itemize}
+As we see in the example in the next section, this cost increases quickly as the $n$ required to meet the error tolerance increases.
+This motivates the fast Bayesian cubature algorithm presented in Section \ref{sec:fast_BC}.
 
@@
 Iteratively define
+\allowdisplaybreaks
 \begin{align*}
@@
 Not only is the Bayesian cubature with the Mat\'ern kernel slow, but also $\mC_\vtheta$ becomes highly ill-conditioned as $n$ increases.
-So, Algorithm \ref{algorithm1}  in its current form is impractical. 
+So, Algorithm \ref{algorithm1}  in its current form is impractical when $n$ must be large. 
 %\FJHNote{Jags, please check this re-write} %\JRNote{looks good}
@@
 
-The generic automatic Bayesian cubature algorithm described in the previous section requires $\Order(n^3)$ operations to estimate $\vtheta$, compute the credible interval width, and compute the cubature.
+The generic automatic Bayesian cubature algorithm described in the previous section requires $\Order\bigl(n \$(f) + \break N_{\opt} [n^2 \$(C_\vtheta)  + n^3]\bigr)$ operations to estimate $\vtheta$, compute the credible interval width, and compute the cubature.
 Now we explain how to speed up the calculations.
-A key is to choose covariance kernels that match the nodes, $\{\vx_i\}_{i=1}^n$, so that the vector-matrix operations required by Bayesian cubature can be accomplished using fast transforms at a cost of $\Order(n \log(n))$.
+A key is to choose covariance kernels that match the nodes, $\{\vx_i\}_{i=1}^n$, so that the vector-matrix operations required by Bayesian cubature can be accomplished using fast transforms at a cost of $\Order\bigl(n \$(f) + N_{\opt} [n \$(C_\vtheta)  + n \log(n)] \bigr)$.
 
@@
 \end{align}
-Where $\mathsf{I}$ is the identity matrix.
+where $\mathsf{I}$ is the identity matrix and $\vv_1^*$ is the complex conjugate of the first row of $\mV$.
 Also note that the fast transform of $\vone$ has a simple form
@@
 Under assumptions \eqref{fastcompAssump}, the parameters and credible interval widths in Theorem \ref{thm:param} may be expressed in terms of the fast transforms of the function data, the first column of the Gram matrix, and $\vc_\vtheta$ as follows:
-\allowdisplaybreaks
 \begin{align}
@@
 
-The preceding sections lay out an automatic Bayesian cubature algorithm whose computational cost is only $\Order(n \log(n))$ if $n$ function values are used.
-However, this algorithm relies on covariance kernel functions, $C$ and node sets, $\{\vx_i\}_{i=1}^n$ that satisfy assumptions \eqref{fastcompAssump}.
+The preceding sections lay out an automatic Bayesian cubature algorithm whose computational cost is drastically reduced.
+However, this algorithm relies on covariance kernel functions, $C_\vtheta$ and node sets, $\{\vx_i\}_{i=1}^n$ that satisfy assumptions \eqref{fastcompAssump}.
 We  also want to satisfy assumption \eqref{addAssump}.
@@
 The set of nodes used is defined by a shifted extensible integration lattice node sequence, which takes the form
-\begin{equation*}
+\begin{equation} \label{eqn:lattice_def}
 \vx_{i} = \vh \phi(i-1) + \vDelta \mod \vone, \qquad i \in \naturals.
-\end{equation*} 
+\end{equation} 
 Here, $\vh$ is a $d$-dimensional generating vector of positive integers, $\vDelta$ is some point in $[0,1)^d$, often chosen at random, and $\{\phi(i)\}_{i=0}^n$ is the van der Corput sequence, defined by reflecting the binary digits of the integer about the decimal point, i.e.,
@@
 \end{align}
+Note that $\phi$ is one-to-one, and 
+\begin{equation} \label{phiprop}
+\phi:\{0, \ldots, n-1 \} \to \{0, 1/n, \ldots, (n-1)/n\},
+\end{equation}
+when $n$ is a power of $2$.
 
@@
 \subsection{Shift Invariant Kernels}
-The covariance functions $C$ that match integration lattice node sets have the form
+The covariance functions $C_\vtheta$ that match integration lattice node sets have the form
 \begin{align} \label{eq:shInv}
-C(\vt,\vx) = K(\vt - \vx \bmod \vone).
-\end{align}
-This is called a \emph{shift invariant kernel} because shifting both arguments of the covariance function by the same amount leaves the value unchanged.
+C_\vtheta(\vt,\vx) = K_\vtheta(\vt - \vx \bmod \vone).
+\end{align}
+This is called a \emph{shift-invariant kernel} because shifting both arguments of the covariance function by the same amount leaves the value unchanged.
 By a proper scaling of the kernel $K$ it follows that assumption \eqref{addAssump} is satisfied.
-Of course, $K$ must also be of the form that ensures that $C$ is symmetric and positive definite, as assumed in \eqref{FJH:eq:CondPosDef}.
-
-A family of shift invariant kernels is constructed via even degree Bernoulli polynomials:
+Of course, $K_\vtheta$ must also be of the form that ensures that $C_\vtheta$ is symmetric and positive definite, as assumed in \eqref{FJH:eq:CondPosDef}.
+
+A family of shift-invariant kernels is constructed via even degree Bernoulli polynomials:
 \begin{multline}
@@
 \subsection{Eigenvectors}
-For general shift-invariant covariance functions, the Gram matrix takes the form
+For general shift-invariant covariance functions, the Gram matrix takes the form of a permutation of the rows and columns of a circulant matrix:
 \begin{align*}
 %\label{shInvKernGramMatrix}
-\mC &= \bigl ( C(\vx_i, \vx_j) \bigr)_{i, j = 1}^n \\
-& = \Bigl ( K(\vh(\phi(i-1) - \phi(j-1)) \bmod \vone ) \Bigr)_{i, j = 1}^n.
-\end{align*}
+\mC &= \mC_\vtheta = \bigl ( C_\vtheta(\vx_i, \vx_j) \bigr)_{i, j = 1}^n \\
+& = \Bigl ( K_\vtheta \bigl(\vh(\phi(i-1) - \phi(j-1) \bigr) \bmod \vone ) \Bigr)_{i, j = 1}^n \\
+& \qquad \qquad  \text{by \eqref{eqn:lattice_def} and \eqref{eq:shInv}}  \\
+& = \mP^T \Bigl ( K_\vtheta \bigl (\vh (i-j)/n \bmod \vone \bigr ) \Bigr)_{i, j = 1}^n \mP\\
+& = \mP^T \mK \mP
+\end{align*}
+where $\mP = \bigl( \delta_{\phi(i-1), (j-1)/n}  \bigr)_{i,j=1}^n$, $\delta$ is the Kronecker delta function, and $\mK = \bigl ( K_\vtheta \bigl (\vh (i-j)/n \bmod \vone \bigr ) \bigr)_{i, j = 1}^n$.
+\FJHNote{Check this.}
+
+Because $\mK$ is circulant,
+
 Here we show the resulting matrix $\mC$ is circulant.
@@
 
-We summarize the results of this section and the previous one as follows:
-\begin{prop}
-Any symmetric, positive definite, shift-invariant covariance kernel of the form \eqref{eq:shInv} scaled to satisfy \eqref{addAssump}, when matched with rank-1 lattice data-sites, must satisfy assumptions \eqref{fastcompAssump}.
-The \emph{fast Fourier transform} (FFT) can be used to expedite the estimates of $\vtheta$ in \eqref{thetaSimple} and the credible interval widths \eqref{fastStoppingCriterions} in $\Order(n \log(n))$ operations.
+We summarize the results of this section and the previous one in the theorem below.
+In comparison to Algorithm \ref{algorithm1}, the cost second and third components of the computational cost of Algorithm  \ref{algorithm2} are substantially reduced.
+\begin{theorem}
+Any symmetric, positive definite,  shift-\break invariant covariance kernel of the form \eqref{eq:shInv} scaled to satisfy \eqref{addAssump}, when matched with rank-1 lattice data-sites, must satisfy assumptions \eqref{fastcompAssump}.
 The cubature, $\hmu$, is just the sample mean.
-\end{prop}
+The \emph{fast Fourier transform} (FFT) can be used to expedite the estimates of $\vtheta$ in \eqref{thetaSimple} and the credible interval widths \eqref{fastStoppingCriterions} so that Algorithm \ref{algorithm2} has a computational cost which is the sum of the following:
+\begin{itemize}
+	\item $\Order\bigl(n\$(f) \bigr)$ for the function data, where $\$(f)$ is the computational cost of a single $f(\vx)$;
+
+	\item $\Order\bigl(N_{\opt} n \$(C_\vtheta) \bigr)$ for the evaluations of the vector $\vC_{1}$, where $N_\opt$ is the number of optimization steps required, and  $\$(C_\vtheta)$ is the computational cost of a single $C_\vtheta(\vt,\vx)$; and
+
+	\item $\Order\bigl(N_{\opt} n \log(n) \bigr)$ for the FFT calculations.
+
+\end{itemize}
+
+\end{theorem}
 

### 2019-07-20 BayesianCubaturePaper2018 - Rev1b.tex
Updates from Overleaf

@@
 \end{multline*}
-where $\rho_{m, s^2 | \vf}$ is the posterior density of the hyperparameters given the function data. Bayes Theorem, $\rho_{m, s^2 | \vf} \propto \rho_{\vf | m, s^2} \, \vrho_{m,s^2}$, so 
+where $\rho_{m, s^2 | \vf}$ is the posterior density of the hyperparameters given the function data. Bayes Theorem tells us that $\rho_{m, s^2 | \vf} \propto \rho_{\vf | m, s^2} \, \vrho_{m,s^2}$, so 
 \begin{align}
@@
 \end{align}
-Note that $\phi$ is one-to-one, and 
-\begin{equation} \label{phiprop}
-\phi:\{0, \ldots, n-1 \} \to \{0, 1/n, \ldots, (n-1)/n\},
+Note that 
+\begin{multline} \label{phiprop}
+\phi:\{0, \ldots, n-1 \} \to \{0, 1/n, \ldots, (n-1)/n\} \\
+\text{is one-to-one},
 \end{equation}
-when $n$ is a power of $2$.
+assuming $n$ is a power of $2$.
 
@@
 This is called a \emph{shift-invariant kernel} because shifting both arguments of the covariance function by the same amount leaves the value unchanged.
-By a proper scaling of the kernel $K$ it follows that assumption \eqref{addAssump} is satisfied.
 Of course, $K_\vtheta$ must also be of the form that ensures that $C_\vtheta$ is symmetric and positive definite, as assumed in \eqref{FJH:eq:CondPosDef}.
@@
 
-\subsection{Eigenvectors}
-For general shift-invariant covariance functions, the Gram matrix takes the form of a permutation of the rows and columns of a circulant matrix:
-\begin{align*}
-%\label{shInvKernGramMatrix}
-\mC &= \mC_\vtheta = \bigl ( C_\vtheta(\vx_i, \vx_j) \bigr)_{i, j = 1}^n \\
+\subsection{The Gram Matrix as the Permutation of a Circulant Matrix}
+For general shift-invariant covariance functions, the Gram matrix takes the form of a permutation of the rows and columns of a circulant matrix.
+By the properties of $\phi$ in \eqref{phiprop}, it follows tht
+\begin{equation} \label{PermMat}
+    \mP = \bigl( \delta_{\phi(i-1), (j-1)/n}  \bigr)_{i,j=1}^n
+\end{equation}
+is a permuation matrix, where $\delta$ is the Kronecker delta function.  Then,
+\begin{align}
+\nonumber
+\mC_\vtheta &= \bigl ( C_\vtheta(\vx_i, \vx_j) \bigr)_{i, j = 1}^n \\
+\nonumber
 & = \Bigl ( K_\vtheta \bigl(\vh(\phi(i-1) - \phi(j-1) \bigr) \bmod \vone ) \Bigr)_{i, j = 1}^n \\
+\nonumber
 & \qquad \qquad  \text{by \eqref{eqn:lattice_def} and \eqref{eq:shInv}}  \\
-& = \mP^T \Bigl ( K_\vtheta \bigl (\vh (i-j)/n \bmod \vone \bigr ) \Bigr)_{i, j = 1}^n \mP\\
-& = \mP^T \mK \mP
-\end{align*}
-where $\mP = \bigl( \delta_{\phi(i-1), (j-1)/n}  \bigr)_{i,j=1}^n$, $\delta$ is the Kronecker delta function, and $\mK = \bigl ( K_\vtheta \bigl (\vh (i-j)/n \bmod \vone \bigr ) \bigr)_{i, j = 1}^n$.
+& = \mP \mK_{\vtheta}  \mP^T,  \label{shInvKernGramMatrix} \\
+\nonumber 
+\text{where } \mK_{\vtheta} &= \bigl ( K_\vtheta \bigl (\vh (i-j)/n \bmod \vone \bigr ) \bigr)_{i, j = 1}^n.
+\end{align}
 \FJHNote{Check this.}
 
-Because $\mK$ is circulant,
-
-Here we show the resulting matrix $\mC$ is circulant.
-Then using the well known fact, circulant matrices are diagonalized by discrete Fourier transform (DFT), one can obtain the eigenvectors analytically and the eigenvalues using DFT.
-% The speedup of their algorithm is in the linear algebra part of the calculations. 
-% But the derivation in Sections 4.3 and 4.4 can be obtained much faster by realising that their definition of the covariance matrix,
-By the definition of $\mC$, $i,j$th element
-\begin{align*}
-\mC_{i,j} & = K( x_i - x_j \bmod 1 ) \\
-&= K\bigl( \bigl(\vh \phi(i-1) - \vh \phi(j-1)\bigr) \bmod 1 \bigr) 
-\end{align*}
-Noting that the sequence $\{\phi(i-1)\}_{i=1}^n$ is a re-ordering of $0, \ldots, 1-1/n$ for $n$ a power of $2$, and $\vh$ is a vector integers, one can rewrite
-\begin{align*}
-\mC_{i,j} &= K_{\vh}\bigl( \bigl(\pi_{2^m}(i-1) - \pi_{2^m}(j-1)\bigr) \bmod 2^m \bigr)
-\end{align*}
-where $\pi_{2^m}(i-1) = 2^m\phi(i-1)$ is the ''integer version'' of the radical inverse function for the full initial sequence of $2^m$ points and $K_{\vh}(\vt) = K(\vh^T \vt)$. By similar approach
-\begin{align*}
-\mC_{i,j} &= K_{\vh,\pi_{2^m}}( (i-1) - (j-1) \bmod 2^m ) , 
-\\
-& \hspace{4cm} \text{for}\; i,j=1,...,2^m ,
-\end{align*}
-is a permutation of a circulant matrix.
-
-The function $\pi_{2^m}$ is a permutation on $\{0, 1, ..., 2^m-1\}$, undoing this
-permutation on the rows and columns of the matrix $\mC$ one obtains a circulant
-matrix:
-$P_{2^m}^T \mC P_{2^m}$.
-%The current Sections 4.3 and 4.4 are therefore not needed. See further.
-Eigenvectors of the circulant matrices are 
-\begin{align} \label{latticeVdef}
-\mV = \Bigl ( \me^{2 \pi n \sqrt{-1} \phi(i-1)\phi(j-1)} \Bigr)_{i,j = 1}^n.
-\end{align}
-and the eigenvalues are
-\begin{align*}
-\vlambda = \mV \vC_1
-\end{align*}
-which automatically follow from the properties of circulant matrices.
-This proves the assumption $\eqref{fastcompAssumpB}$.
-
-\iftrue
-\JRNote{Original content of Section 4.3 begins from here:}
-
-We now demonstrate that the eigenvector matrix for $\mC$ is 
-\begin{align} \label{latticeVdef}
-\mV = \Bigl ( \me^{2 \pi n \sqrt{-1} \phi(i-1)\phi(j-1)} \Bigr)_{i,j = 1}^n.
-\end{align}
-Assumption \eqref{fastcompAssumpB} follows automatically.
-Now, note that the $k,j$ element of $\mV^H\mV$ is
-\begin{equation*}
-\sum_{i=1}^n \me^{2 \pi n \sqrt{-1} \phi(i-1)[\phi(j-1) - \phi(k-1)]} .
-\end{equation*}
-Noting that the sequence $\{\phi(i-1)\}_{i=1}^n$ is a re-ordering of $0, \ldots, 1-1/n$ for $n$ a power of $2$, this sum may be re-written by replacing $\phi(i-1)$ by $(i-1)/n$:
-\begin{equation*}
-\sum_{i=1}^n \me^{2 \pi \sqrt{-1} (i-1)[\phi(j-1) - \phi(k-1)]}.
-\end{equation*}
-Since $\phi(j-1) - \phi(k-1)$ is some integer multiple of $1/n$, it follows that this sum is $n \delta_{j,k}$, where $\delta$ is the Kronecker delta function.
-This establishes that $\mV^H = n \mV^{-1}$ as in \eqref{eqn:ftk_factor}.
-
-Next, let $\omega_{k, \ell}$ denote the $k,\ell$ element of $\mV^H \mC \mV$, which is given by the double sum
-\begin{multline*}
-\omega_{k, \ell} = \sum_{i,j=1}^n K(\vh(\phi(i-1) - \phi(j-1)) \bmod \vone ) \\
-\times   \me^{-2 \pi n \sqrt{-1} \phi(k-1)\phi(i-1)}  \me^{2 \pi n \sqrt{-1} \phi(j-1)\phi(l-1)}
-\end{multline*}
-Noting that the sequence $\{\phi(i-1)\}_{i=1}^n$ is a re-ordering of $0, \ldots, 1-1/n$ for $n$ a power of $2$, this sum may be re-written by replacing $\phi(i-1)$ by $(i-1)/n$ and $\phi(j-1)$ by $(j-1)/n$:
-\begin{multline*}
-\omega_{k, \ell} = \sum_{i,j=1}^n K\left (\vh \left(\frac{i-j}{n} \right) \bmod \vone \right) \\
-\times   \me^{-2 \pi \sqrt{-1} \phi(k-1)(i-1)}  \me^{2 \pi \sqrt{-1} (j-1)\phi(\ell-1)}.
-\end{multline*}
-This sum also remains unchanged if $i$ is replaced by $i+m$ and $j$ is replaced by $j+m$ for any integer $m$:
-\begin{multline*}
-\omega_{k, \ell} = \sum_{i,j=1}^n K\left (\vh \left(\frac{i-j}{n} \right) \bmod \vone \right) \\
-\times   \me^{-2 \pi \sqrt{-1} \phi(k-1)(i+m-1)}  \me^{2 \pi \sqrt{-1} (j+m-1)\phi(\ell-1)} \\
-=   \omega_{k, \ell}  \me^{2 \pi \sqrt{-1} m(\phi(\ell-1) - \phi(k-1))}.
-\end{multline*}
-For this last equality to hold for all integers $m$, we must have $k = \ell$ or $\omega_{k,\ell} = 0$.  Thus, 
-\begin{align*}
-\omega_{k, \ell} &= \delta_{k,\ell} \sum_{i,j=1}^n K\left (\vh \left(\frac{i-j}{n} \right) \bmod \vone \right) \\
-& \qquad \qquad \qquad \qquad \times   \me^{-2 \pi \sqrt{-1} (i - j) \phi(k-1)} \\
-& = n \delta_{k,\ell}  \sum_{i=1}^n K\left ( \left(\frac{i\vh}{n} \right) \bmod \vone \right)  \me^{-2 \pi \sqrt{-1} i \phi(k-1) }.
-\end{align*}
-This establishes $\mV^H \mC \mV$ as a diagonal matrix whose diagonal elements are $n$ times the eigenvalues, i.e., $\lambda_k = \omega_{k,k}/n$.
-Furthermore, $\mV$ is the matrix of eigenvectors, which satisfies assumption \eqref{fastcompAssumpA}.
-\fi
-
-\subsection{Iterative Computation of the Fast Transform}
-Assumption \eqref{fastcompAssumpA} is that computing $\mV^H \vb$ requires only $\Order(n \log(n)) $ operations.
-Recall that we assume that $n$ is a power of $2$.
-This can be accomplished by an iterative algorithm.
-Let $\mV^{(n)}$ denote the $n \times n$ matrix $\mV$ defined in  \eqref{latticeVdef}.
-One can compute $\mV^{(2n)H}\vb$ quickly for all $\vb \in \reals^{2n}$ assuming that $\mV^{(n)H}\vb$ can be computed quickly for all $\vb \in \reals^n$, using the butterfly structure of the Fast Fourier Transform (FFT).
-For the brevity, we only provide the results.
-
-From the definition of the van der Corput sequence in \eqref{vdCDef}, it follows that
-\begin{gather} 
-\label{vdCProp}
-\phi(2i) = \phi(i)/2, \;  \phi(2i+1) = [\phi(i)+1]/2, \ \ \ i \in \natzero\\
-\label{vdCPropB}
-\phi(i+n) = \phi(i) + 1/(2n), \qquad i = 0, \ldots, n-1,
-\\
-\label{vdCPropC}
-n \phi(i) \in \natzero, \qquad i = 0, \ldots, n-1,
-\end{gather}
-still assuming that $n$ is an integer power of two.
-Let $\widetilde{\vb} = \mV^{(2n)H}\vb$ for some arbitrary $\vb \in \reals^{2n}$, and define
-\begin{gather*}
-\vb = \begin{pmatrix} b_1 \\ \vdots \\ b_{2n} \end{pmatrix}, \quad 
-\vb^{(1)} = \begin{pmatrix} b_1 \\ \vdots \\ b_{n} \end{pmatrix}, \quad 
-\vb^{(2)}  = \begin{pmatrix} b_{n+1} \\ \vdots \\ b_{2n} \end{pmatrix}, \\ 
-\widetilde{\vb} = \begin{pmatrix} \widetilde{b}_1 \\ \vdots \\ \widetilde{b}_{2n} \end{pmatrix}, \quad 
-\widetilde{\vb}^{(1)} = \begin{pmatrix} \widetilde{b}_1 \\ \widetilde{b}_3 \\ \vdots \\ \widetilde{b}_{2n-1} \end{pmatrix}, \quad 
-\widetilde{\vb}^{(2)}  = \begin{pmatrix} \widetilde{b}_{2} \\  \widetilde{b}_{4} \\ \vdots \\ \widetilde{b}_{2n} \end{pmatrix}. 
-\end{gather*}
-It follows from these definitions and the definition of $\mV$ in  \eqref{latticeVdef} that
-\begin{align*}
-\widetilde{\vb}^{(1)} &= \left( \sum_{j=1}^{2n}  \me^{-4 \pi n \sqrt{-1} \phi(2i-2)\phi(j-1)} b_{j} \right)_{i=1}^n \\
-% &= \left( \sum_{j=1}^{2n}  \me^{-2 \pi n \sqrt{-1} \phi(i-1)\phi(j-1)} b_{j} \right)_{i=1}^n \quad \text{by \eqref{vdCProp}}\\
-% &= \left( \sum_{j=1}^{n}  \me^{-2 \pi n \sqrt{-1} \phi(i-1)\phi(j-1)} b_{j} \right)_{i=1}^n \quad \\
-% &\qquad \qquad +  \left( \sum_{j=1}^{n}  \me^{-2 \pi n \sqrt{-1} \phi(i-1)\phi(n+j-1)} b_{n+j} \right)_{i=1}^n \\
-% &= \mV^{(n)H}\vb^{(1)}  +  \biggl(  \me^{-\pi \sqrt{-1} \phi(i-1)}  \\
-% & \quad \times \sum_{j=1}^{n}  \me^{-2 \pi n \sqrt{-1} \phi(i-1)\phi(j-1)} b_{n+j} \biggr)_{i=1}^n \quad  \text{by \eqref{vdCPropB}}\\
-&= \mV^{(n)H}\vb^{(1)} +  \left(  \me^{-\pi \sqrt{-1} \phi(i-1)} \right)_{i=1}^n \odot \bigl(\mV^{(n)H}\vb^{(2)} \bigr),
-\end{align*}
-where $\odot$ denotes the Hadamard (term-by-term) product.  By a similar argument, 
-\begin{align*}
-\widetilde{\vb}^{(2)} &= \left( \sum_{j=1}^{2n}  \me^{-4 \pi n \sqrt{-1} \phi(2i-1)\phi(j-1)} b_{j} \right)_{i=1}^n \\
-% &= \left( \sum_{j=1}^{2n}  \me^{-2 \pi n \sqrt{-1} [\phi(i-1)+1]\phi(j-1)} b_{j} \right)_{i=1}^n \quad \text{by \eqref{vdCProp}}\\
-% &= \left( \sum_{j=1}^{n}  \me^{-2 \pi n \sqrt{-1} [\phi(i-1)+1]\phi(j-1)} b_{j} \right)_{i=1}^n \quad \\
-% &\qquad  +  \left( \sum_{j=1}^{n}  \me^{-2 \pi n \sqrt{-1} [\phi(i-1)+1]\phi(n+j-1)} b_{n+j} \right)_{i=1}^n \\
-% &= \mV^{(n)H}\vb^{(1)} +  \left(  \me^{ -\pi \sqrt{-1} [\phi(i-1) + 1]} \right. \\
-% & \qquad \qquad \left . \times \sum_{j=1}^{n}  \me^{-2 \pi n \sqrt{-1} \phi(i-1)\phi(j-1)} b_{n+j} \right)_{i=1}^n \\
-% & \hspace{4cm}  \text{by \eqref{vdCPropB} and \eqref{vdCPropC}}\\
-&= \mV^{(n)H}\vb^{(1)} -  \left(  \me^{-\pi \sqrt{-1} \phi(i-1)} \right)_{i=1}^n \odot \bigl(\mV^{(n)H}\vb^{(2)} \bigr).
-\end{align*}
-
-The computational cost to compute $\mV^{(2n)H}\vb$ is then twice the cost of computing $\mV^{(n)H}\vb^{(1)}$ plus $2n$ multiplications plus $2n$ additions.
-An inductive argument shows that $\mV^{(n)H}\vb$ requires only $\Order(n \log(n))$ operations.
+Because $\mK_\vtheta$ is circulant, we know the form of it's eigevector-eigenvalue decomposition:
+\begin{equation} \label{Keig}
+    \mK_{\vtheta} = \frac 1n \mW \mLambda_\vtheta \mW^H, \; \ \mW =  \Bigl ( \me^{2 \pi \sqrt{-1} (i-1)(j-1)/n} \Bigr)_{i,j = 1}^n.
+\end{equation}
+By \eqref{shInvKernGramMatrix} we then have the eigevector-eigenvalue decomposition for $\mC_{\vtheta}$ assumed in \eqref{eqn:ftk_factor}, namely
+\begin{equation} \label{Clateig}
+    \mC_{\vtheta} = \frac 1n \mV \mLambda_\vtheta \mV^H , \qquad \mV = \mP \mW,
+\end{equation}
+where the eigenvalues of $\mK_{\vtheta}$ and $\mC_{\vtheta}$ are identical.
+
+Assumptions \eqref{fastcompAssumpA} and \eqref{fastcompAssumpB} can be verified by \eqref{PermMat}, \eqref{Keig}, and \eqref{Clateig}.
+Assumption \eqref{fastcompAssumpC} is satisfied because $\mV^H \vb = \mW^H \mP^T \vb$ is just the permutation of the rows of the discrete Fourier transform of a vector.
+This can be performed in $\Order(n \log(n))$ operations by the FFT algorithm.
+By a proper scaling of the kernel $K_\vtheta$ ensures that assumption \eqref{addAssump} is satisfied.
 
@@
 For the kernels used in our computation, it may happen that $n/\lambda_1$ is close to $1$.
-Thus, the term $1-n/\lambda_1$, which appears in the credible interval widths, $\err_{\MLE}$, $\err_{\textup{full}}$, and $\err_{\textup{GCV}}$, may suffer from cancellation error.
+Thus, the term $1-n/\lambda_1$, which appears in the credible interval widths, $\err_{\MLE}$, $\err_{\textup{full}}$, and $\err_{\textup{GCV}}$, may suffer from cancellation error and even become negative.
+We have observed this phenomenon.
 We can avoid this cancellation error by modifying how we compute the Gram matrix and its eigenvalues.
 
-The shift-invariant kernel of our interest \eqref{the_kernel_eqn_bernoulli} has the form $C = 1 + \rC$. 
-One could take advantage of it to avoid the subtraction in $1-n/\lambda_1$. 
-Define the new function $\rC : = C -1$, and its associated Gram matrix $\rmC = \mC - \vone \vone^T$, where $\rmC$ is simply the original kernel after discarding ``$1$", there is no actual subtraction involved in the computation.
-So we are not really shifting the cancellation error to another place.
-Note that $\rC$ inherits the shift-invariant properties of $C$.  
-Since $\vone$ is the first eigenvector of $\mC$, it follows that the eigenvalues of $\rmC$ are $\rlambda_1 = \lambda_1 - n, \lambda_2, \ldots, \lambda_n$.  Moreover,
+Any shift-invariant covariance kernel can be written as $C_\vtheta = 1 + \rC_\vtheta$.
+The associated Gram matrix for $\rC_\vtheta$ is then $\rmC_\vtheta = \mC_\vtheta - \vone \vone^T$, and the eigenvalues of $\rmC_\vtheta$ are $\rlambda_1 = \lambda_1 - n, \lambda_2, \ldots, \lambda_n$, which follows because $\vone$ is the first eigenvector of both $\mC_\vtheta$ and $\rmC_\vtheta$.
+Then,
 \begin{equation*}
@@
 \begin{equation*}
-C(\vt, \vx) = \prod_{\ell=1}^d \left[1 + \rC_\ell(t_\ell,x_\ell) \right], \qquad  \rC_\ell:[0,1]^2 \to \reals.
+C_\vtheta(\vt, \vx) = \prod_{\ell=1}^d \left[1 + \rC_{_\vtheta\ell}(t_\ell,x_\ell) \right], \qquad  \rC_\ell:[0,1]^2 \to \reals.
 \end{equation*}
-Direct computation of $\rC (\vt,\vx) = C(\vt,\vx) -1$ introduces cancellation error if the $ \rC_\ell$ are small.  So, we employ the iteration
-\begin{align*}
-\rC^{(1)} &= \rC_1(t_1,x_1),  \\
-\rC^{(\ell)} &  = \rC^{(\ell-1)}[1 + \rC_\ell(t_\ell,x_\ell)] + \rC_\ell(t_\ell,x_\ell), \\
+Direct computation of $\rC_\vtheta(\vt,\vx) = C_\vtheta(\vt,\vx) -1$ introduces cancellation error if the $ \rC_{_\vtheta \ell}$ are small.  So, we employ the iteration
+\begin{align*}
+\rC^{(1)}_\vtheta(\vt,\vx) &= \rC_{\vtheta 1}(t_1,x_1),  \\
+\rC^{(\ell)}_\vtheta(\vt,\vx) &  = \rC^{(\ell-1)}_\vtheta[1 + \rC_{_\vtheta\ell}(t_\ell,x_\ell)] + \rC_\ell(t_\ell,x_\ell), \\
 & \hspace{5cm} \ell = 2, \ldots, d, \\
-\rC(\vt,\vx)  & = \rC^{(d)}.
-\end{align*}
-In this way, the Gram matrix $\rmC$, whose $i,j$-element is $\rC(\vx_i,\vx_j)$ can be constructed with minimal round-off error.
+\rC_\vtheta(\vt,\vx)  & = \rC^{(d)}_\vtheta(\vt,\vx).
+\end{align*}
+In this way, the Gram matrix $\rmC_\vtheta$, whose $i,j$-element is $\rC_\vtheta(\vx_i,\vx_j)$ can be constructed with minimal round-off error.
 
 Computing the eigenvalues of $\rmC$ via the procedure given in \eqref{eqn:fast_transform_to_eigvalues} yields $\rlambda_1 = \lambda_1 - n, \lambda_2, \ldots, \lambda_n$.
-The estimates of $\vtheta$ are computed in terms of the eigenvalues of $\rmC$, so \eqref{eqn_MLE_loss_func_optimized_2} and \eqref{thetaGCV} become
-\begin{subequations}
-\label{thetaSimple}
-\begin{align}
-\label{thetaSimpleMLE}
-\vtheta_\MLE
-&= 
-\argmin_{\vtheta}
-\left[
-\log\left(
-\sum_{i=2}^n \frac{\abs{\widetilde{y}_i}^2}{\lambda_i}
-\right) 
-%\label{thetaMLEsimple}
- + 
- \frac{1}{n}\sum_{i=1}^n \log(\lambda_i)
-\right], \\
-\label{thetaSimpleGCV}
-\vtheta_{\GCV} 
-&= \argmin_\vtheta \left[ \log \left ( \sum_{i=2}^n \frac{\abs{\widetilde{y}_i}^2}{\lambda_i^2} 
-\right)  -2\log\left( \sum_{i=1}^n \frac{1}{\lambda_i} \right)
-\right],
-\end{align}
-\end{subequations}
-where $\lambda_1 = n + \rlambda_1$.  The widths of the credible intervals in \eqref{eq:errMLEAllAsump}, \eqref{FJH:eq:errFullSimple}, and   \eqref{errGCVSimple} become
+The widths of the credible intervals in \eqref{eq:errMLEAllAsump}, \eqref{FJH:eq:errFullSimple}, and   \eqref{errGCVSimple} become
 \begin{subequations}
@@
 \end{subequations}
-Since $\rlambda_1 = \lambda_1 - n$ and $\lambda_1 \sim n$ it follows $\rlambda_1/\lambda_1 \approx \rlambda_1/(n-1)$ and is small for  large $n$.
-Moreover, the credible intervals via empirical Bayes and full Bayes are similar, since $t_{n-1,0.995}$ is approximately $2.58$.
+For large $n$, $\lambda_1 \sim n$ and it follows that $\rlambda_1/\lambda_1 \approx \rlambda_1/(n-1)$  is small.
+Moreover, for large $n$, the credible intervals via empirical Bayes and full Bayes are similar, since $t_{n-1,0.995} \approx 2.58$.
 The computational steps for the improved, faster, automatic Bayesian cubature are detailed in Algorithm \ref{algorithm2}.

### 2019-07-20 BayesianCubaturePaper2018 - Rev1b.tex
revising

@@
 \nonumber 
-s^2_{\textup{GCV}} & : =  \frac 1{n} \sum_{i=2}^n \frac{\abs{\widetilde{y}_i}^2}{\lambda_i^2}  \left [ \sum_{i=1}^n \frac{1}{\lambda_i} \right]^{-1},\\
-\label{eqn_MLE_loss_func_optimized_2} %\nonumber
+s^2_{\textup{GCV}} & : =  \frac 1{n} \sum_{i=2}^n \frac{\abs{\widetilde{y}_i}^2}{\lambda_i^2}  \left [ \sum_{i=1}^n \frac{1}{\lambda_i} \right]^{-1},
+\end{align}
+\begin{subequations}
+	\label{fastTheta}
+	\begin{align}
+\nonumber
 \vtheta_\MLE
@@
 \sum_{i=2}^n \frac{\abs{\widetilde{y}_i}^2}{\lambda_{\vtheta i}}
-\right) %\right .\\ \hspace{3cm} \left .
+\right) \right .\\ 
+\label{eqn_MLE_loss_func_optimized_2} %
+& \hspace{3cm} \left .
  + \frac{1}{n}\sum_{i=1}^n \log(\lambda_{\vtheta i})
@@
 & \qquad \qquad \qquad \qquad  \left . -2\log\left( \sum_{i=1}^n \frac{1}{\lambda_{\vtheta i}} \right)
-\right], \\
+\right], 
+\end{align}
+\end{subequations}
+\begin{align}
 \nonumber
@@
 Under the further assumption \eqref{addAssump}, it follows that 
-\begin{align}
-\nonumber
-\hmu_\MLE  &= \hmu_{\full} = \hmu_{\GCV} =
+\begin{equation}
+\label{muhatGCV-FB-MLE-Simple}
+\hmu_\MLE  = \hmu_{\full} = \hmu_{\GCV} =
 \frac{\widetilde{y}_1}{n} = \frac 1n \sum_{i=1}^n y_i,
-\end{align}
+\end{equation}
 and so $\hmu$ is simply the sample mean.  Also, under assumption \eqref{addAssump}, the credible interval widths simplify to
@@
 \text{is one-to-one},
-\end{equation}
+\end{multline}
 assuming $n$ is a power of $2$.
@@
 
-Larger $r$ implies a greater degree of smoothness of the kernel.
+Larger $r$ implies a greater degree of smoothness of the covariance kernel.
 Larger $\eta$ implies greater fluctuations of the output with respect to the input.
@@
 This can be performed in $\Order(n \log(n))$ operations by the FFT algorithm.
-By a proper scaling of the kernel $K_\vtheta$ ensures that assumption \eqref{addAssump} is satisfied.
+A proper scaling of the kernel $K_\vtheta$ ensures that assumption \eqref{addAssump} is satisfied.
 
 \subsection{Overcoming Cancellation Error}
-For the kernels used in our computation, it may happen that $n/\lambda_1$ is close to $1$.
+For the covariance kernels used in our computation, it may happen that $n/\lambda_1$ is close to $1$.
 Thus, the term $1-n/\lambda_1$, which appears in the credible interval widths, $\err_{\MLE}$, $\err_{\textup{full}}$, and $\err_{\textup{GCV}}$, may suffer from cancellation error and even become negative.
@@
 		$\vx_1, \vx_2, \ldots$; 
-		a shift-invariant periodic kernel, $C$;
+		a shift-invariant periodic kernel, $C_\vtheta$;
 		a black-box function, $f$; 
@@
 		\State\label{LoopStart}Generate $\{ \vx_i\}_{i=n' + 1}^{n}$ and sample $\{f(\vx_i)\}_{i=n'+1}^{n}$
-		\State Compute $\vtheta$ by \eqref{thetaSimpleMLE} or \eqref{thetaSimpleGCV}
+		\State Compute $\vtheta$ by \eqref{eqn_MLE_loss_func_optimized_2} or \eqref{thetaGCV}
 		\State Compute $\err_{\textup{CI}}$  according to \eqref{fastStoppingCriterionMLE}, \eqref{fastStoppingCriterionFull}, or \eqref{fastStoppingCriterionGCV}
@@
 The cubature, $\hmu$, is just the sample mean.
-The \emph{fast Fourier transform} (FFT) can be used to expedite the estimates of $\vtheta$ in \eqref{thetaSimple} and the credible interval widths \eqref{fastStoppingCriterions} so that Algorithm \ref{algorithm2} has a computational cost which is the sum of the following:
+The \emph{fast Fourier transform} (FFT) can be used to expedite the estimates of $\vtheta$ in \eqref{fastTheta} and the credible interval widths \eqref{fastStoppingCriterions} so that Algorithm \ref{algorithm2} has a computational cost which is the sum of the following:
 \begin{itemize}
@@
 
-	\item $\Order\bigl(N_{\opt} n \log(n) \bigr)$ for the FFT calculations.
+	\item $\Order\bigl(N_{\opt} n \log(n) \bigr)$ for the FFT calculations; there is no $d$ dependence in these calculations.
 
@@
 
+Although the third part of the computational cost has the largest dependence on $n$, in practice it need not be the largest contributor to the computational cost.
+If function values are the result of an expensive simulation, then the first part may consume most of the computation time.
+
 We have implemented the fast adaptive Bayesian cubature algorithm in MATLAB as part of the Guaranteed Adaptive Integration Library (GAIL) \cite{ChoEtal17b} as \allowbreak \code{cubBayesLattice\_g}.
-This algorithm uses the kernel defined in  \eqref{the_kernel_eqn_bernoulli} with  $r=1,2$ and the periodizing variable transforms in  \secref{period_var_tx}.
+This algorithm uses the covariance kernel defined in  \eqref{the_kernel_eqn_bernoulli} with  $r=1,2$ and the periodizing variable transforms in  \secref{period_var_tx}.
 The rank-1 lattice node generator is taken from \cite{Nuy17a} (\code{exod2\_base2\_m20}).
@@
 \label{period_var_tx}
-The shift-invariant covariance kernels underlying our Bayesian cubature  assume that the integrand has a degree of periodicity, with the smoothness assumed depending on the smoothness of the kernel.
+The shift-invariant covariance kernels underlying our Bayesian cubature  assume that the integrand has a degree of periodicity, with the smoothness assumed depending on the smoothness of the covariance kernel.
 While integrands arising in practice may be smooth, they might not be periodic.

### 2019-07-20 ResponseToReferees.tex
revising
Updates from Overleaf

@@
 is a permutation of a circulant matrix from which all required properties follow. \ldots The current Sections 4.3 and 4.4 are therefore not
-needed. \Response{We have altered these sections.}
+needed. \Response{We have altered these sections substantially.}
 
@@
 error', but here it is not so clear to me if what is proposed will really help.
-See further.
+See further. \Response{We believe that it does help, both experientially and theoretically.}
 
@@
 \item The second sentence doesn't make sense to me. \Response{Re-written.}
-\item In the third sentence I would replace 'postulates' with 'considers'.  \Response{Done.}
+\item In the third sentence I would replace `postulates' with `considers'.  \Response{Done.}
 \end{itemize}
@@
 \item It is never said how the $x_i$ are sampled. Does (5a) hold for any
-distribution of samples $x_i$? \Response{Yes, any distinct nodes.}
+distribution of samples $x_i$? \Response{Yes, any distinct nodes. This has been mentioned explicitly}
 \item In this section there are different quantities being defined: the matrix
@@
 $C$. E.g. in (11) the $\vec{\theta}$ is not visible at all in the expression to be
-minimized for it. The $C$ without subscript also clashes that of lemma 1. \Response{$\vec{\theta}$ has been added into the equations where there is optimization.}
+minimized for it. The $C$ without subscript also clashes that of lemma 1. \Response{$\vec{\theta}$ has been added as much as possible, and particularly into the equations where there is optimization.}
 \item  The lead in to lemma 1 makes it feel like this is a field specific lemma but
@@
 \Response{The key results from Sections 2.2.1--2.2.3 have been collected in a theorem just before Section 2.2.1.
-The key results of Section 3 are also collected into a theorem.}
+The key results of Section 3 are also collected into a theorem.
+Theorem 3 now summarizes the results of Section 4.}
 \item  From (6) to (7) the notation is different: $c^T C^{-1} 1$ vs $1^T C^{-1} c$,
@@
 \item At the end of the section the authors say that this is not a good method.
-Why then list it? Maybe the final paragraph needs to be rewritten.  \Response{We only cast doubt on the full Bayes approach for estimating $\vec{\theta}$.}
+Why then list it?
+Maybe the final paragraph needs to be rewritten.
+\Response{We only cast doubt on the full Bayes approach for estimating $\vec{\theta}$, not for dealing with the other hyperparameters.}
 \end{itemize}
@@
 
-\item Section 3.3. Elaborate on what is meant with the second sentence.
+\item Section 3.3. Elaborate on what is meant with the second sentence.  \Response{This section re-written and eliminaets this sentence.}
 
@@
 The definition (35) makes it that the covariance matrix $C$ is a permutation
-of a circulant matrix. \ldots
+of a circulant matrix. \ldots. \Response{These subsections have been substantially re-written in response to the referee's suggestion.}
 
@@
 
-\item p.\ 7, top left Definition of v1∗?
-...where ...(lower case)
+\item p.\ 7, top left Definition of $v_1^*$? \ldots where \ldots (lower case) \Response{Clarified.  Fixed.}
 
@@
 The same question arises in the setting of Section 4.
+\Response{You are correct.
+This has been clarified.}
 
@@
 
-\item p.\ 12, center left  \ldots differs depends \ldots ?
+\item p.\ 12, center left  \ldots differs depends \ldots ?  \Response{Fixed.}
 

### 2019-07-20 ResponseToReferees.tex
Updates from Overleaf

@@
 increase the error on $\mathring{\lambda}_1$, so putting the numerical error elsewhere.
+\Response{A key quantity can lose accuracy due to catastrophic cancellation.
+This has been observed by us in practice.
+The proposed method avoids this.
+We do not see how we are introducing significantly more numerical error elsewhere.
+We are basically pulling a large constant matrix one out of the Gram matrix.
+Then the FFT of the first column is not essentially $n$.
+We want the difference from $n$.}
 
 \item Please delete the word 'periodic' in proposition 1, this is covered by the
-shift-invariantness.
+shift-invariantness. \Response{Done.}
 \end{itemize}
@@
 substitution written with $\Psi'$ is undefined. This paragraph should be
-restructured.
+restructured. \Response{Done.}
 
@@
 \item p.\ 3, Sec.\ 2.2 The application of Lemma 1 to automatic Bayesian cubature is not clear to me, since integrand data is accumulated sequentially, which does not correspond to applying a single linear mapping to all integrands (realizations) $f$.
+\Response{This is a valid criticism, which we address in Section 2.3.}
 
 \item Sec.\ 2.2.1, 2.2.2 I suggest to include some references for the results that are presented in Sections 2.2.1 and 2.2.2.
+\Response{Our knowledge of the literature is limited, but much of what we read assumes a zero mean for the Gaussian process.
+We would welcome sources to cite that consider our setting.}
 
@@
 Please comment.
+\Response{Greater smoothness of the covariance kernel implies an \emph{assumption} of greater smoothness of the integrands, which may or may not be justified.
+Lattice rules work well for all degrees of smoothness.
+}
 

### 2019-07-20 BayesianCubaturePaper2018 - Rev1b.tex
revising paper.

@@
 
+We recognize that multiple applications of our credible intervals in one run of our algorithm is not strictly justified.
+However, if our integrand comes from the middle of the sample space and not the extremes, we expect our automatic Bayesian cubature approximate  the integral within the desired error tolerance with high probability.
+The example in the next subsection and the examples in Section \ref{sec:NumExp} support that expectation.
+We also believe that an important factor contributing to the failure of our algorithm is unreasonable parameterizations of the stochastic process from which the integrand is hypothesized to be drawn.
+Overcoming this latter challenge is a topic for future research.
+
 \algnewcommand{\IIf}[1]{\State\algorithmicif\ #1\ \algorithmicthen\ }
@@
 
-	\item $\Order\bigl(N_{\opt} n^2 \$(C_\vtheta) \bigr)$ for the evaluation of the matrix $\mC_{\vtheta}$, $N_\opt$ is the number of optimization steps required, and  $\$(C_\vtheta)$ is the computational cost of a single $C_\vtheta(\vt,\vx)$; $\$(C)$ is typically proportional to $d$; and
+	\item $\Order\bigl(N_{\opt} n^2 \$(C_\vtheta) \bigr)$ for the evaluation of the Gram matrix $\mC_{\vtheta}$, $N_\opt$ is the number of optimization steps required, and  $\$(C_\vtheta)$ is the computational cost of a single $C_\vtheta(\vt,\vx)$; $\$(C_\vtheta)$ is typically proportional to $d$; and
 
@@
 \end{equation*}
-where $g$ has sufficient smoothness, but lacks periodicity.  The Baker's transform,
+where $g$ has sufficient smoothness, but lacks periodicity.  
+The goal is to transform the integral above to the form of \eqref{eqn:defn_mu}, where the integrand $f$---and perhaps its derivatives---are  periodic.
+
+The Baker's transform, also called tent transform,
 \begin{multline} \label{eq:bakerTrans}
@@
 \end{multline}
-allows us to write $\mu$ in the form of \eqref{eqn:defn_mu}, where $f(\vx) = g(\vPsi(\vx))$.
-Also called tent transform, $\Psi'(x)$ is not defined, not suitable when the $f$ is required to have also smooth derivatives.
-
-A family of variable transforms that also provide some derivatives take the form
+allows us to write $\mu$ in the form of \eqref{eqn:defn_mu}, where $f(\vx) = g(\vPsi(\vx))$.  Since  $\Psi'(x)$ is not continuous, $f$ does not have continuous derivatives.
+
+A family of variable transforms that can also preserve continuity of the derivatives that exists in the original integrand $g$ takes the form
 \begin{subequations} %\label{eq:varTrans}
 \begin{equation*}
-\vPsi: \vx \mapsto (\Psi(x_1),  \ldots, \Psi(x_d)), \quad \Psi:[0,1] \mapsto [0,1],
+\vPsi: \vx \mapsto (\Psi(x_1),  \ldots, \Psi(x_d)), \quad \Psi:[0,1] \mapsto [0,1].
 \end{equation*}
-which allows us to write $\mu$ in the form of \eqref{eqn:defn_mu} with
+This allows us to write $\mu$ in the form of \eqref{eqn:defn_mu} with
 \begin{equation*}
@@
 
-Periodizing variable transforms are used for the numerical examples below. In some cases, they can speed the convergence of the Bayesian cubature.
+Periodizing variable transforms are used in the numerical examples below.
+In some cases, they can speed the convergence of the Bayesian cubature because they allow one to take advantage of smoother kernels.
 

### 2019-07-20 ResponseToReferees.tex
Updates from Overleaf

@@
 
-Thanks to the the referees and the editors for their helpful comments.  We have revised our manuscript in light of these comments, \Response{which we address point-by-point below in blue.}
+Thanks to the the referees and the editors for their very helpful comments.
+We have revised our manuscript substantially in response.
+\Response{Specific concerns are addressed point-by-point below in blue.}.
+We hope that all will find the revision satisfactory.
 
@@
 
+There is no theory available that covers the whole process (estimation and cubature with credible interval); instead, the authors present numerical experiments to demonstrate the performance of three variants of their new algorithm.
+\Response{We would disagree with the sweeping nature of the claim that ``there is no theory''.
+Our method is taking the established theory of Bayesian numerical analysis and using it to develop adaptive stopping criteria.
+In our revised manuscript we summarize our results in three theorems.
+We recognize some gaps in the theory.}
+
 \begin{itemize}
@@
 Lattice rules work well for all degrees of smoothness.
-}
+This point is mentioned at the end of Section 4.2.}
 
@@
 
-\item p.\ 9, bottom, right Assumption (25c) \ldots
+\item p.\ 9, bottom, right Assumption (25c) \ldots \Response{The rewriting of this section has eliminated that sentence.}
 
@@
 \item Sec.\ 5.1 Is there some kind of a universal periodization that ‘works’ for every value of $r$?
+\Response{One could choose an infinitely smooth periodization, but this would change the integrand to potentially make its covariance $s$ large.
+This is mentioned at the end of Section 5.1.}
 
@@
 Does this mean that $\theta = (2,\gamma)$ is considered for the shift-invariant kernel, or do you still consider $\theta = (r,\gamma)$ with $r \in \mathbb{N}$ as the unknown parameter?
-I suggest not to use $r$ also in the drift term in the option pricing example.
+\Response{For technical simplicity we fix $r$.
+We mention that in Section 5.2.}
+
+\item I suggest not to use $r$ also in the drift term in the option pricing example. \Response{Excellent suggestion.  Replaced by $R$.}
 
@@
 By the way, are there 100 green points, for the 100 independent shifts?
+\Response{We have modified our experiments to randomly choose from a continuum of error tolerances.
+We have also explained that each experiment correspondes to a different random shift.}
 
@@
 
-\item Page 14: The three figures look all the same!  Any comment on that?
+\item Page 14: The three figures look all the same!  Any comment on that?  \Response{They are similar, but not the same.}
 
 \item In this example, does it really make sense to assume that the integrand comes from a Gaussian process?
+\Response{Theoretically, perhaps not, but with a nonzero mean, maybe this is not too much of a stretch.
+Bayesian cubature assuming non-Gaussian processes is much more challenging.
+We have addressed this at the end of Section 5.2}
 
-\item Four lines below Figure 13:  "A noticeable aspect from the plots is how much ....":  It may be good to explain exactly how we see that in the plots.
+\item Four lines below Figure 13:  "A noticeable aspect from the plots is how much ....":  It may be good to explain exactly how we see that in the plots. \Response{We have elaborated more.}
 
@@
 
-The revision should at a minimum point out the connection to the FFT.
+The revision should at a minimum point out the connection to the FFT. \Response{Done.}
 
-Because the goal is to reach people outside of PN some additional explanations are in order.
+Because the goal is to reach people outside of PN some additional explanations are in order. \Response{We have tried.}
 
@@
 \renewcommand{\labelenumi}{\arabic{enumi}.}
-    \item The results in Section 2.2.2 were confusing. \ldots
+    \item The results in Section 2.2.2 were confusing. \ldots \Response{This has been re-written}
 
@@
 
-\item The argument at the end of section 4.3 involving is very slippery. \ldots
+\item The argument at the end of section 4.3 involving is very slippery. \ldots \Response{Section 4 has been substantially re-written.}
 
@@
 
-\item The notation for the full Bayes treatment is not consistent. \ldots 
+\item The notation for the full Bayes treatment is not consistent. \ldots \Response{We have tried to fix this.}
 \item  First paragraph of 2.3: for the $\mu$ $\rightarrow$ for $\mu$. Also intervals $\rightarrow$ interval. \Response{Fixed.}

### 2019-07-20 BayesianCubaturePaper2018 - Rev1b.tex
revising paper

@@
 
+Integration lattice cubature rules are known to have convergence rates that depend on the smoothness of the integrands \cite{DicEtal14a}.
+Thus, we expect integration lattice node sets to perform well regardless of the smoothness of the covariance kernel.
+The bigger concern is whether the derivatives of the integrand are as smooth as the covariance kernel implies.
+This topic is touched upon again in Section  \ref{period_var_tx}.
+
 \begin{figure}
@@
 Assumptions \eqref{fastcompAssumpA} and \eqref{fastcompAssumpB} can be verified by \eqref{PermMat}, \eqref{Keig}, and \eqref{Clateig}.
-Assumption \eqref{fastcompAssumpC} is satisfied because $\mV^H \vb = \mW^H \mP^T \vb$ is just the permutation of the rows of the discrete Fourier transform of a vector.
+Assumption \eqref{fastcompAssumpC} is satisfied because $\mV^H \vb = \mW^H \mP^T \vb$ is just the discrete Fourier transform of a vectors whose rows have been permuted.
 This can be performed in $\Order(n \log(n))$ operations by the FFT algorithm.
@@
 In some cases, they can speed the convergence of the Bayesian cubature because they allow one to take advantage of smoother kernels.
+However, there is a trade-off.  Smoother periodizing transformations tend to give integrands $f$ with larger inferred $s$ values and thus wider credible intervals.
 
@@
 Three integrals were evaluated using the GAIL algorithm \code{cubBayesLattice\_g}:  a multivariate normal probability, the Keister's example, and an option pricing example.  
-The sequences $\{\vx_i\}_{i=1}^\infty$ were the randomly shifted lattice node sequences supplied by GAIL. 
+The sequences $\{\vx_i\}_{i=1}^\infty$ are the randomly shifted lattice node sequences supplied by GAIL. 
 For each integral,  each of our stopping criteria---empirical Bayes, full Bayes, and generalized cross-validation---our algorithm was run for $400$ different randomly chosen error tolerances.
@@
 In each run, the nodes were also randomly shifted.
-The accuracy of the algorithm differs based on the shift.
-For each test, the execution times were plotted against $\abs{\mu - \hmu}/\varepsilon$.
-We expect $\abs{\mu - \hmu}/\varepsilon$ to be no greater than one, but hope that it is not too much smaller than one, which would indicate a stopping criterion that is too conservative.
+The accuracy of the algorithm depends mildly on the shift; there is no universally optimal shift.
+For each test, the execution times are plotted against $\abs{\mu - \hmu}/\varepsilon$.
+We expect $\abs{\mu - \hmu}/\varepsilon$ to be no greater than one, but hopefully not too much smaller than one, which would indicate a stopping criterion that is too conservative.
+
+Ideally, we would optimize both $r$ and $\eta$ simultaneously in the definition of our $C_\vtheta$ in \eqref{the_kernel_eqn_bernoulli}.
+However, in these examples we fix $r$ and optimize $\eta$ only.
+This is a technical challenge, not a limitation of our theory.
 
@@
 \begin{align*}
-\text{payoff}(\vz) &= \max\left( \frac 1d  \sum_{j=1}^d S_j(\vz) - K, 0 \right) \me^{-\upsilon T}, \\
+\text{payoff}(\vz) &= \max\left( \frac 1d  \sum_{j=1}^d S_j(\vz) - K, 0 \right) \me^{-R T}, \\
 \text{where}\;
-S_j(\vz) &= S_0 \exp\bigl((\upsilon-\sigma^2/2)jT/d + \sigma \sqrt{T/d} z_j \bigr).
-\end{align*}
-Here, $T$ denotes the time to maturity of the option, $d$ the number of time steps, $S_0$ the initial price of the stock, $\upsilon$ the interest rate, $\sigma$ the volatility, and $K$ the strike price.
+S_j(\vz) &= S_0 \exp\bigl((R-\sigma^2/2)jT/d + \sigma \sqrt{T/d} z_j \bigr).
+\end{align*}
+Here, $T$ denotes the time to maturity of the option, $d$ the number of time steps, $S_0$ the initial price of the stock, $R$ the interest rate, $\sigma$ the volatility, and $K$ the strike price.
 
@@
 $
-T = 1/4, \ \ d = 13, \ \ S_0 = 100, \ \ \upsilon =  0.05, \ \ \sigma = 0.5, \ \ K = 100.
+T = 1/4, \ \ d = 13, \ \ S_0 = 100, \ \ R =  0.05, \ \ \sigma = 0.5, \ \ K = 100.
 $
@@
 
-A noticeable aspect from the plots is how much the error bounds differ from the true error.
-For option pricing example, the error bound is not as conservative as it is for the multivariate normal and Keister examples.
+One may question whether an integrand with non-negative values is well represented by a Gaussian process.
+Since we allow a nonzero mean, this assumption is somewhat more palatable.
+Bayesian algorithms assuming non-Gaussian processes are more difficult, but this is an ares for further research.
+
+A noticeable observation from the plots in all three examples is how much the credible interval widths differ from the true error.
+The credible interval widths are not much smaller than $\varepsilon$.
+The ratio of the true error to $\varepsilon$ ranges from around one to as small as $10^{-7}$.
+In the latter case, the credible interval widths are quite conservative.
+For option pricing example, this less serious of an issue than for the multivariate normal and Keister examples.
 A possible reason is that the latter integrands are significantly smoother than the covariance kernel assumed.
 This is a matter for further investigation.
-
-\iffalse
-\subsection{Diagnostics for the Gaussian Process Assumption}
-
-The starting point for our Bayesian cubature is the assumption that the integrand arises from a Gaussian process.
-This means that the function data, $\vf$ satisfy a multivariate Gaussian distribution, as in \eqref{eqn:fGaussDist}.
-The transformed data, $\vZ = ( n\mLambda)^{-\frac 12} \mV^H(\vf - m \vone)$ has zero mean and is also uncorrelated because
-\begin{align*}
-\cov (\vZ) 
-&= \frac 1n \Ex\left[  
-\mLambda^{-\frac 12} \mV^H (\vf - m \vone)
-(\vf - m \vone)^T \mV \mLambda^{-\frac 12}
-\right]
-\\
-&=
- \mLambda^{-\frac 12} \mV^H 
-\Ex\left[ (\vf - m \vone)
-(\vf - m \vone)^T \right] \mV \mLambda^{-\frac 12}
-\\
-&=
-\frac{1}{n} \mLambda^{-\frac 12} \mV^H 
-\frac 1n \mV \mLambda \mV^H \mV \mLambda^{-\frac 12}
- = \mathsf{I}
-\end{align*}
-Thus, the elements of $\vZ$ are IID standard Gaussian random variables.
-
-\figref{fig:mvn-normplot} and \figref{fig:keister-normplot} are normal probability plots of the $Z_i$ using empirical Bayes estimates of $m$ and $\vtheta$. \textbf{more goes here}.
-
-\begin{figure}
-	\centering
-	\includegraphics[width=0.9\linewidth]{"figures/arbMean/Keister/C1sin/Keister Normplot d_2 bernoulli_2 Period_C1sin n_32768"}
-	\caption{Normal plot : Keister function with arbMean assumption}
-	\label{fig:keister-normplot}
-\end{figure}
-
-\begin{figure}
-	\centering
-	\includegraphics[width=0.9\linewidth]{"figures/arbMean/MVN/C1sin/MVN Normplot d_2 bernoulli_2 Period_C1sin n_32768"}
-	\caption{Normal plot : MVN with arbMean assumption}
-	\label{fig:mvn-normplot}
-\end{figure}
-
-\fi
 

### 2019-07-21 BayesianCubaturePaper2018 - Rev1b.tex
few minor corrections

@@
 Automatic cubatures approximate multidimensional integrals to user-specified error tolerances.
-For high dimensional problems it is difficult to adaptively change the sampling pattern, but one can automatically determine the
-sample size, $n$, give a fixed and reasonable sampling pattern.
+For high dimensional problems, it is difficult to adaptively change the sampling pattern, but one can automatically determine the
+sample size, $n$, given a fixed and reasonable sampling pattern.
 We take this approach here using a Bayesian perspective.
@@
 
-The process outlined above typically requires a computational cost of $O(N_{\text{opt}}n^3)$, where $N_{\text{opt}}$ is the number of optimizations required to identify the hyperparameters.
+The process outlined above typically requires a computational cost of $O(N_{\text{opt}}n^3)$, where $N_{\text{opt}}$ is the number of optimization steps required to identify the hyperparameters.
 Our innovation is to pair low discrepancy nodes with matching kernels that lower the  computational cost to $O(N_{\text{opt}} n \log n)$.
@@
 Here the $\vC_j$ are the columns of $\mC$.
-In this and later sections, we drop the $\vtheta$ dependence of various quantities for simplicty of notation.
+In this and later sections, we drop the $\vtheta$ dependence of various quantities for simplicity of notation.
 Here, $\mV^H$ is the Hermitian of $\mV$, $\vC_1,...,\vC_n$ are columns of $\mC$.
@@
 The columns of matrix $\mV$ are eigenvectors of $\mC$, and $\mLambda$ is a diagonal matrix of eigenvalues of $\mC$.
-For any $n \times n$ vector $\vb$, define the notation  $\widetilde{\vb} := \mV^H \vb$.
+For any $n \times 1$ vector $\vb$, define the notation  $\widetilde{\vb} := \mV^H \vb$.
 
@@
 \nonumber 
-s^2_{\textup{GCV}} & : =  \frac 1{n} \sum_{i=2}^n \frac{\abs{\widetilde{y}_i}^2}{\lambda_i^2}  \left [ \sum_{i=1}^n \frac{1}{\lambda_i} \right]^{-1},
+s^2_{\textup{GCV}} & =  \frac 1{n} \sum_{i=2}^n \frac{\abs{\widetilde{y}_i}^2}{\lambda_i^2}  \left [ \sum_{i=1}^n \frac{1}{\lambda_i} \right]^{-1},
 \end{align}
@@
 For general shift-invariant covariance functions, the Gram matrix takes the form of a permutation of the rows and columns of a circulant matrix.
-By the properties of $\phi$ in \eqref{phiprop}, it follows tht
+By the properties of $\phi$ in \eqref{phiprop}, it follows that
 \begin{equation} \label{PermMat}
@@
 \end{equation}
-is a permuation matrix, where $\delta$ is the Kronecker delta function.  Then,
+is a permutation matrix, where $\delta$ is the Kronecker delta function.  Then,
 \begin{align}
@@
 We summarize the results of this section and the previous one in the theorem below.
-In comparison to Algorithm \ref{algorithm1}, the cost second and third components of the computational cost of Algorithm  \ref{algorithm2} are substantially reduced.
+In comparison to Algorithm \ref{algorithm1}, the second and third components of the computational cost of Algorithm  \ref{algorithm2} are substantially reduced.
 \begin{theorem}
@@
 This algorithm uses the covariance kernel defined in  \eqref{the_kernel_eqn_bernoulli} with  $r=1,2$ and the periodizing variable transforms in  \secref{period_var_tx}.
-The rank-1 lattice node generator is taken from \cite{Nuy17a} (\code{exod2\_base2\_m20}).
+The rank-1 lattice node generator is taken from \cite{Nuy17a} \break (\code{exod2\_base2\_m20}).
 
@@
 This example was already introduced in Section \ref{MVN_example}, where we used the Mat\'ern covariance kernel.
-Here we apply Sidi's $C^2$  periodization to $ f_{\textup{Genz}}$ \eqref{fGenzdef}, choose $d=3$ and $r=2$.
+Here we apply Sidi's $C^2$  periodization to $ f_{\textup{Genz}}$ \eqref{fGenzdef}, choose $d=2$ and $r=2$.
 The simulation results for this example function are summarized in Figures \ref{fig:mvn-guaranteed-MLE}, \ref{fig:mvn-guaranteed-FB}, and \ref{fig:mvn-guaranteed-GCV}.
@@
 We used the same setting as before with generic slow Bayesian cubature in \secref{MVN_example} for comparison.
-For error threshold $\varepsilon=10^{-5}$ with the empirical Bayes stopping criterion, our fast algorithm takes just under 0.01 second as shown in \figref{fig:mvn-guaranteed-MLE} whereas the basic algorithm takes over 20 seconds as shown in \figref{fig:MVN_Metern_d2b2}.
+For error threshold $\varepsilon=10^{-5}$ with the empirical Bayes stopping criterion, our fast algorithm takes just under 0.01 second as shown in \figref{fig:mvn-guaranteed-MLE} whereas the generic algorithm takes over 20 seconds as shown in \figref{fig:MVN_Metern_d2b2}.
 
@@
 
-Figures \ref{fig:keister-guaranteed-MLE}, \ref{fig:keister-guaranteed-FB} and \ref{fig:keister-guaranteed-GCV} summarize the numerical tests for this integral.
+Figures \ref{fig:keister-guaranteed-MLE}, \ref{fig:keister-guaranteed-FB}, and \ref{fig:keister-guaranteed-GCV} summarize the numerical tests for this integral.
 We used the Sidi's $C^1$ periodization, dimension $d=4$, and $r=2$.
 As we can see, the GCV stopping criterion achieves faster results than the other stopping criteria, similarly to the multivariate normal case.
+The credible intervals are narrower than the multi variate normal case since the kernel is smoother than the periodization transform used.
 
@@
 \mSigma &= (T/d) \bigl(\min(j,k) \bigr)_{j,k=1}^d = \mL \mL^T,\\
-f(\vx) &= \text{payoff} \left(\mL 
+f(\vx) &= \code{payoff} \left(\mL 
 \begin{pmatrix}
@@
 \begin{align*}
-\text{payoff}(\vz) &= \max\left( \frac 1d  \sum_{j=1}^d S_j(\vz) - K, 0 \right) \me^{-R T}, \\
+\code{payoff}(\vz) &= \max\left( \frac 1d  \sum_{j=1}^d S_j(\vz) - K, 0 \right) \me^{-R T}, \\
 \text{where}\;
-S_j(\vz) &= S_0 \exp\bigl((R-\sigma^2/2)jT/d + \sigma \sqrt{T/d} z_j \bigr).
+S_j(\vz) &= S_0 \exp\bigl((R-\sigma^2/2)j(T/d) + \sigma \sqrt{(T/d)} z_j \bigr).
 \end{align*}
@@
 
-Figures \ref{fig:optprice-guaranteed-MLE}, \ref{fig:optprice-guaranteed-FB} and 
+Figures \ref{fig:optprice-guaranteed-MLE}, \ref{fig:optprice-guaranteed-FB}, and 
 \ref{fig:optprice-guaranteed-GCV} summarize the numerical results for this example using
@@
 In summary, the Bayesian cubature algorithm computes the integral within the user-specified threshold in nearly all of the test cases.
-The rare exceptions occurred in the option pricing example for $\varepsilon=10^{-4}$.
+The rare exceptions occurred in the option pricing example for $\varepsilon \le 10^{-4}$.
 Our algorithm used the maximum allowed sample size and still did not reach the stopping criterion $\err_{\textup{CI}} \leq \varepsilon$, due to the complexity and high dimension of the integrand.
+Those cases are shown as hollow stars in Figures \ref{fig:optprice-guaranteed-MLE}, \ref{fig:optprice-guaranteed-FB}, and
+\ref{fig:optprice-guaranteed-GCV}.
 %Also notice, our algorithm finished within 10 seconds for Keister and multivariate Normal examples while the option pricing took closer to 70 seconds, again due to the complexity of the integrand.
@@
 Since we allow a nonzero mean, this assumption is somewhat more palatable.
-Bayesian algorithms assuming non-Gaussian processes are more difficult, but this is an ares for further research.
+Bayesian algorithms assuming non-Gaussian processes are more difficult, but this is an area for further research.
 
@@
 In the latter case, the credible interval widths are quite conservative.
-For option pricing example, this less serious of an issue than for the multivariate normal and Keister examples.
+For option pricing example, this is less serious of an issue than for the multivariate normal and Keister examples.
 A possible reason is that the latter integrands are significantly smoother than the covariance kernel assumed.
@@
 We have developed a fast, automatic Bayesian cubature that estimates a multidimensional definite integral within a user defined error tolerance.
-The stopping criteria arise from assuming the integrand to be a Gaussian process.
+The stopping criteria arise from assuming the integrand to be an instance of a Gaussian process.
 There are three approaches:  empirical Bayes, full Bayes, and generalized cross-validation.
@@
 The matrix-vector multiplications can be accomplished using the fast Fourier Transform.
-The performance of our automatic Bayesian cubature are illustrated using three integration problems.
+The performance of our automatic Bayesian cubature is illustrated using three integration problems.
 

### 2019-07-21 BayesianCubaturePaper2018 - Rev1b.tex
few minor corrections

@@
 
-\begin{theorem} \label{thm:param} There are at least three approaches to estimating or integrating out the hyperparameters defining the Gaussian process from which the integrand is drawn: empirical Bayes, full Bayes, and generalized cross validation.
-Under these three approaches we have the following:
+\begin{theorem} \label{thm:param} There are at least three approaches to estimating or integrating out the hyperparameters defining the Gaussian process from which the integrand is drawn: empirical Bayes, full Bayes, and generalized cross-validation.
+Under these three approaches, we have the following:
 %\begin{allowdisplaybreaks}
@@
 \nonumber
-\hsigma_{\textup{full}}^2 
+\hsigma_{\full}^2 
 & = \frac{1}{n-1}
@@
 \\ 
+\label{eqn:sigma2_full}
 & \times  \left[\frac{(1 - \vc_{\vtheta}^T \mC_\vtheta^{-1} \vone)^2}{\vone^T \mC_\vtheta^{-1} \vone} + (c_{0\vtheta}  -\vc_{\vtheta} ^T \mC_\vtheta^{-1} \vc_{\vtheta}) \right], \\
@@
 \nonumber
-\vtheta_{\textup{GCV}} &= \argmin_\vtheta \biggl\{\log \left(  \vy^T \left[\mC^{-2}_\vtheta - \frac{\mC^{-2}_\vtheta \vone \vone^T \mC^{-2}_\vtheta}{\vone^T \mC^{-2}_\vtheta \vone}  \right] \vy \right)  \\
+\vtheta_{\GCV} &= \argmin_\vtheta \biggl\{\log \left(  \vy^T \left[\mC^{-2}_\vtheta - \frac{\mC^{-2}_\vtheta \vone \vone^T \mC^{-2}_\vtheta}{\vone^T \mC^{-2}_\vtheta \vone}  \right] \vy \right)  \\
 \label{vthetaGCV}
 & - \log \left ( \trace(\mC^{-2}_\vtheta) \right ) \biggr\}, \\
+\label{eqn:cubMLE}
 \hmu_\MLE  &= \hmu_\full =
@@
 \label{eqn:muCV}
-\widehat{\mu}_{\textup{GCV}}
+\hmu_{\GCV}
 & = \left(\frac{(1 - \vone^T  \mC_\vtheta^{-1}\vc_{\vtheta}) \mC_\vtheta^{-1} \vone}{\vone^T \mC_\vtheta^{-2} \vone} + \vc_{\vtheta} \right)^T \mC_\vtheta^{-1} \vy, \\ 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-Rather than use maximum likelihood to determine $m$ and $s$ one can treat them as hyperparameters with a non-informative, conjugate prior, namely $\vrho_{m,s^2}(\xi, \lambda) \propto 1/\lambda$.
+Rather than use maximum likelihood to determine $m$ and $s$,  one can treat them as hyperparameters with a non-informative, conjugate prior, namely $\vrho_{m,s^2}(\xi, \lambda) \propto 1/\lambda$.
 We want to compute $\rho_{\mu|\vf}(z | \vy)$, the conditional posterior density of $\mu$ given the data $\vf = \vy$.
@@
 \end{align}
-where $\hsigma_{\textup{full}}^2$ is given in Theorem \ref{thm:param}, and the result above is derived Appendix \ref{appendix:full_bayes}.
+where $\hsigma_{\textup{full}}^2$ is given in Theorem \ref{thm:param}, and the result above is derived in Appendix \ref{appendix:full_bayes}.
 
@@
 We recognize that multiple applications of our credible intervals in one run of our algorithm is not strictly justified.
-However, if our integrand comes from the middle of the sample space and not the extremes, we expect our automatic Bayesian cubature approximate  the integral within the desired error tolerance with high probability.
+However, if our integrand comes from the middle of the sample space and not the extremes, we expect our automatic Bayesian cubature to approximate the integral within the desired error tolerance with high probability.
 The example in the next subsection and the examples in Section \ref{sec:NumExp} support that expectation.
@@
 
-To demonstrate automatic Bayesian cubature consider a Mat\'ern covariance kernel:
+To demonstrate the automatic Bayesian cubature Algorithm \ref{algorithm1}, consider a Mat\'ern covariance kernel:
 \begin{align*}
@@
 \\
-\alpha_j&(x_1,...,x_{j-1}) = 
+\alpha_j&(x_1,\dots,x_{j-1}) = 
 \\
@@
 \\
-&\hspace{5cm} j=2,...,d,
-\\
-\beta_j&(x_1,...,x_{j-1}) = 
+&\hspace{5cm} j=2,\dots,d,
+\\
+\beta_j&(x_1,\dots,x_{j-1}) = 
 \\
@@
 \\
-&\hspace{5cm} j=2,...,d,
+&\hspace{5cm} j=2,\dots,d,
 \end{align*}
@@
 In each run, the nodes are randomly scrambled.
-We  observe the algorithm meets the error criterion 95\% of the time.
+We  observe the algorithm meets the error criterion 95\% of the time even though we used 99\% credible interval.
+One possible explanation is, the matrix inversions in the algorithm are ill-conditioned leading to numerical inaccuracies.
 %with Intel i7 3630QM and 16GB RAM memory
@@
 \nonumber
-\mC = \mC_\vtheta &= \Big(C_\vtheta(\vx_i,\vx_j)\Big)_{i,j=1}^n  = (\vC_1,...,\vC_n) 
+\mC = \mC_\vtheta &= \Big(C_\vtheta(\vx_i,\vx_j)\Big)_{i,j=1}^n  = (\vC_1,\dots,\vC_n) 
 \\
@@
 \nonumber
-\mV &= (\vv_1,...,\vv_n)^T = (\vV_1,...,\vV_n), \\
+\mV &= (\vv_1,\ldots,\vv_n)^T = (\vV_1,\ldots,\vV_n), \\
 \nonumber
@@
 \end{align}
-Here the $\vC_j$ are the columns of $\mC$.
 In this and later sections, we drop the $\vtheta$ dependence of various quantities for simplicity of notation.
-Here, $\mV^H$ is the Hermitian of $\mV$, $\vC_1,...,\vC_n$ are columns of $\mC$.
-$\vV_1,...,\vV_n$ are columns of $\mV$ and $\vv_1,...,\vv_n$ are rows of $\mV$.
+Here, $\mV^H$ is the Hermitian of $\mV$, $\vC_1,\dots,\vC_n$ are columns of $\mC$.
+$\vV_1,\dots,\vV_n$ are columns of $\mV$ and $\vv_1,\dots,\vv_n$ are rows of $\mV$.
 The normalization of $\mV$ assumed in \eqref{eqn:ftk_factor} conveniently allows the first eigenvector, $\vV_1$, to be the vector of ones in \eqref{fastcompAssumpB} below.
@@
 
-Many of the terms that arise in the calculations in  Algorithm \ref{algorithm1} take the form $\va^T\mC^{p}\vb$ for real $\va$ and $\vb$ and integer $p$.
+Many of the terms that arise in the calculations in  Algorithm \ref{algorithm1} take the form $\va^T\mC^{p}\vb$ for real $\va$ and $\vb$, and integer $p$.
 These can be calculated via the transforms $\widetilde{\va} = \mV^H \va$ and $\widetilde{\vb} = \mV^H \vb$ as
@@
 \end{multline*}
-This completes the derivation of \eqref{eqn:fullBayesrho}.
+This completes the derivation of \eqref{eqn:sigma2_full}.
 \end{appendices}

### 2019-07-22 ResponseToReferees.tex
Polishing

@@
 That sounds scary.
-\Response{It may sound scary, but that is the common implicit assumption of probabilistic approaches, such as this one.
+\Response{It may sound scary, but that is the common implicit assumption of probabilistic numerics approaches, such as this one.
 Other traditional methods for estimating the error of a cubature rule either assume that the integrand lies in the ball of some function space (how do you know the radius of that ball?) or estimate the error heuristically.}
@@
 
-In the example the integral (22) is considered over a compact set. What is the benefit of Genz’s transformation, compared to a simple affine linear transformation, in this case?
+\item In the example the integral (22) is considered over a compact set.
+What is the benefit of Genz's transformation, compared to a simple affine linear transformation, in this case?
+\Response{A sentence has been added.
+Genz's transformation is state-of-the-art.}
 

### 2019-07-22 BayesianCubaturePaper2018 - Rev1b.tex
polishing

@@
 \newcommand{\vzeta}{{\bm{\zeta}}}
-\newcommand{\vthetaMLE}{\bm{\theta}_{\text{MLE}}}
+\newcommand{\vthetaMLE}{\bm{\theta}_{\MLE}}
 \newcommand{\hvtheta}{\hat{\vtheta}}
@@
 We postulate that the integrand is an instance of a Gaussian stochastic process parameterized by a constant mean and a covariance function defined by a scale parameter times a parameterized function specifying how the integrand values at two different points in the domain are related.
-These hyperparameters are handled using integrand values via empirical Bayes, full Bayes, and generalized cross-validation.
+These hyperparameters are inferred integrated out using integrand values via one of three techniques:  empirical Bayes, full Bayes, or generalized cross-validation.
 The sample size, $n$, is chosen to make the half-width of the credible interval for the Bayesian posterior mean no greater than the error tolerance.
@@
 
-The users of cubature algorithms typically want the error to be no greater than their error tolerance denoted by $\varepsilon$, i.e., 
+Users of cubature algorithms typically want the error to be no greater than their error tolerance, denoted by $\varepsilon$, i.e., 
 \begin{align}
@@
 \begin{equation} \label{eqn:OuralgoCost}
-    \Order\bigl(n \$(f) + N_{\textup{opt}}[n\$(C) + n \log(n)] \bigr),
+    \Order\bigl(n \$(f) + N_{\opt}[n\$(C) + n \log(n)] \bigr),
 \end{equation} 
-where $\$(f)$ is the cost of one integrand value, $\$(C)$ is the cost of a single covariance kernel value,  $\Order(n \log(n))$ is the cost of a fast Fourier transform, and $N_{\textup{opt}}$ is an upper bound on the number of optimization steps required to choose the hyperparameters.
-If function evaluation is expensive, such as coming from computationally intensive simulation, or $\$(f) = \Order(d)$ for large $d$, then $\$(f)$ might be similar in magnitude to $N_{\textup{opt}} \log(n)$ in practice.
+where $\$(f)$ is the cost of one integrand value, $\$(C)$ is the cost of a single covariance kernel value,  $\Order(n \log(n))$ is the cost of a fast Fourier transform, and $N_{\opt}$ is an upper bound on the number of optimization steps required to choose the hyperparameters.
+If function evaluation is expensive, such as the output of a computationally intensive simulation, or $\$(f) = \Order(d)$ for large $d$, then $\$(f)$ might be similar in magnitude to $N_{\opt} \log(n)$ in practice.
 Typically, $\$(C) = \Order(d)$.
@@
 \begin{equation} \label{eqn:TheiralgoCost}
-    \Order\bigl(n \$(f) + N_{\textup{opt}}[n^2\$(C) + n^3] \bigr),
+    \Order\bigl(n \$(f) + N_{\opt}[n^2\$(C) + n^3] \bigr),
 \end{equation} 
-which is explained in Section \ref{sec:bayes_cubature_algo}. Note that the work beyond evaluating the integrand in \eqref{eqn:TheiralgoCost} is much larger than that in \eqref{eqn:OuralgoCost}.
+which is explained in Section \ref{sec:bayes_cubature_algo}.
+Note that beyond evaluating the integrand, the computational cost in \eqref{eqn:TheiralgoCost} is much larger than that in \eqref{eqn:OuralgoCost}.
 
@@
 
-Section \ref{sec:BC} explains the Bayesian approach to estimate the posterior cubature error and defines our automatic Bayesian cubature.
+Section \ref{sec:BC} explains the Bayesian approach to estimating the posterior cubature error and defines our automatic Bayesian cubature.
 Although much of this material is known, it is included for completeness.
 We end Section \ref{sec:BC}  by demonstrating why Bayesian cubature is typically computationally expensive.
-Section \ref{sec:fast_BC}  introduces the concept of covariance kernels that match the nodes and expedite the computations required by our automatic Bayesian cubature. 
+Section \ref{sec:fast_BC}  introduces the concept of covariance kernels that match the nodes, which expedites the computations required by our automatic Bayesian cubature. 
 Section \ref{sec:shift_invariant_kernel} implements this concept for shift-invariant kernels and rank-1 lattice nodes.
-It also describes how to avoid cancellation error for kernels of product form.
+This section also describes how to avoid cancellation error for kernels of product form.
 Numerical examples are provided in Section \ref{sec:NumExp} to demonstrate our new algorithm.
@@
 
-\subsection{Bayesian posterior error}
+\subsection{Bayesian posterior cubature error}
 \label{sec:BayesPostErr}
 
-Suppose that the integrand, $f$, is assumed to be an instance of a Gaussian stochastic process \cite{BriEtal18a}, \cite{Dia88a}, \cite{OHa91a}, \cite{Rit00a}, \cite{RasGha03a}, i.e., $f \sim \mathcal{GP}(m,s^2 C_\vtheta)$.
-Specifically, $f$ is a random function with real-valued constant mean $m$ and covariance function $s^2C_\vtheta$:
+We assume that the integrand, $f$, is an instance of a Gaussian stochastic process \cite{BriEtal18a}, \cite{Dia88a}, \cite{OHa91a}, \cite{Rit00a}, \cite{RasGha03a}, i.e., $f \sim \mathcal{GP}(m,s^2 C_\vtheta)$.
+Specifically, $f$ is a real-valued random function with constant mean $m$ and covariance function $s^2C_\vtheta$:
 \begin{gather*}
@@
 \end{gather*}
-Here $s$ is a non-negative scale factor, and $C_\vtheta: [0,1]^d \times [0,1]^d \to \mathbb{R} $ is a symmetric, positive-definite function and parameterized by $\vtheta$:
+Here $s$ is a positive scale factor, and $C_\vtheta: [0,1]^d \times [0,1]^d \to \mathbb{R} $ is a symmetric, positive-definite function and parameterized by the vector $\vtheta$:
 \begin{multline} \label{FJH:eq:CondPosDef}
-\mC_\vtheta^T = \mC_\vtheta,  \; \va^T \mC_\vtheta \va > 0, \; \text{where }  \mC_\vtheta = \left(  C_\vtheta(\vx_i,\vx_j)  \right)_{i,j=1}^n,\\
+\mC_\vtheta^T = \mC_\vtheta,  \; \va^T \mC_\vtheta \va > 0,  \text{ where }  \mC_\vtheta = \left(  C_\vtheta(\vx_i,\vx_j)  \right)_{i,j=1}^n,\\
  \forall \va \ne 0, \;
@@
 Furthermore, for a Gaussian process, all vectors of linear functionals of $f$ have a multivariate Gaussian distribution.
-For any deterministic sampling scheme with distinct nodes, $\{\vx_i\}_{i=1}^n$, and defining  $\vf  := \left( f(\vx_i)\right)_{i=1}^n$ as the multivariate normal vector of function values, it follows from the definition of a Gaussian process that
+For any deterministic sampling scheme with distinct nodes, $\{\vx_i\}_{i=1}^n$, and defining  $\vf  := \left( f(\vx_i)\right)_{i=1}^n$ as the multivariate Gaussian vector of function values, it follows from the definition of a Gaussian process that
 \begin{subequations} \label{eqn:fGaussDist}
@@
 \text{where }
-c_{0\vtheta} &:= \int_{[0,1]^{d}\times [0,1]^{d}} C_\vtheta(\vt,\vx) \, \dif{\vt} \, \dif{\vx}, \\
+c_{0\vtheta} &:= \int_{[0,1]^{d}\times [0,1]^{d}} C_\vtheta(\vt,\vx) \, \dif{\vt} \, \dif{\vx}, \text{ and}\\
 \cov(\vf, \mu) &= \left(  \int_{[0,1]^d} C_\vtheta(\vt,\vx_i) \, \D \vt \right)_{i=1}^n  =: \vc_\vtheta.
@@
 \end{subequations}
-Again, $c_{0\vtheta}$ and $\vc_\vtheta$ depend explicitly on $\vtheta$.
+Here, $c_{0\vtheta}$ and $\vc_\vtheta$ depend explicitly on $\vtheta$.
 We assume that the integrals in these definitions can be computed analytically.
-We need the following lemma pertaining to a conditional normal distribution to derive the distribution of the posterior error of our cubature.
+We need the following lemma pertaining to a conditional Gaussian distribution to derive the distribution of the posterior error of our cubature.
 
@@
 \hmu_{\GCV}
-& = \left(\frac{(1 - \vone^T  \mC_\vtheta^{-1}\vc_{\vtheta}) \mC_\vtheta^{-1} \vone}{\vone^T \mC_\vtheta^{-2} \vone} + \vc_{\vtheta} \right)^T \mC_\vtheta^{-1} \vy, \\ 
+& = \left(\frac{(1 - \vone^T  \mC_\vtheta^{-1}\vc_{\vtheta}) \mC_\vtheta^{-1} \vone}{\vone^T \mC_\vtheta^{-2} \vone} + \vc_{\vtheta} \right)^T \mC_\vtheta^{-1} \vy.
+\intertext{The credible intervals widths, $\err_{\textup{CI}}$, are given by}
 \nonumber
@@
 Here $t_{n-1,0.995}$ denotes the $99.5$ percentile of a standard Student's $t$-distribution with $n-1$ degrees of freedom.
+In the formulas above, $\vtheta$ is assumed to take on the values $\vtheta_{\MLE}$ or $\vtheta_{\GCV}$ as appropriate.
 \end{theorem}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-The empirical Bayes approach estimates the parameters, $m$, $s$, and $\vtheta$ via maximum likelihood estimation (MLE).  The log-likelihood function of the parameters given the function data $\vy$ is:
+The empirical Bayes approach estimates the parameters, $m$, $s$, and $\vtheta$ via maximum likelihood estimation.  The log-likelihood function of the parameters given the function data $\vy$ is:
 \begin{multline*}
@@
 \\
- - \frac{1}{2} \log(\det\, \mC_\vtheta) - \frac{n}{2} \log(s^2) + \text{constants.}
+ - \frac{1}{2} \log(\det(\mC_\vtheta)) - \frac{n}{2} \log(s^2) + \text{constants.}
 \end{multline*}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-A third parameter optimization technique is \emph{leave-one-out cross-validation} (CV).
+A third parameter selection technique is \emph{leave-one-out cross-validation} (CV).
 Let $\mathring{y}_i = \Ex[f(\vx_i ) | \vf_{-i} = \vy_{-i}]$, where the subscript $-i$ denotes the vector excluding the $i^{\text{th}}$ component.
@@
  & \approx \frac{ \frac 1n \sum_{i=1}^n \zeta_i^2}{\frac 1n \sum_{i=1}^n a_{ii} } = \frac{(\vy - m\vone)^T \mC_\vtheta^{-2} (\vy - m \vone)}{ \trace(\mC_\vtheta^{-1}) } \\ 
- & \approx  s^2_{\textup{GCV}}.
-\end{align*}
-where $s^2_{\textup{GCV}}$ is given by the formula in Theorem \ref{thm:param}.
+ & \approx  \frac{(\vy - m_\GCV\vone)^T \mC_{\vtheta_\GCV}^{-2} (\vy - m_\GCV \vone)}{ \trace(\mC_{\vtheta_\GCV}^{-1}) } =: s^2_{\textup{GCV}}.
+\end{align*}
+Here, $s^2_{\textup{GCV}}$ is given by the formula in Theorem \ref{thm:param}.
 
@@
 The example in the next subsection and the examples in Section \ref{sec:NumExp} support that expectation.
-We also believe that an important factor contributing to the failure of our algorithm is unreasonable parameterizations of the stochastic process from which the integrand is hypothesized to be drawn.
+We also believe that an important factor contributing to the occasional failure of our algorithm is unreasonable parameterizations of the stochastic process from which the integrand is hypothesized to be drawn.
 Overcoming this latter challenge is a topic for future research.
@@
 and Sobol' points as the nodes.  (Sobol' points are a typical space-filling design.)
-Also, consider the integration problem of evaluating  \emph{multivariate normal probabilities}:
+Also, consider the integration problem of evaluating  \emph{multivariate Gaussian probabilities}:
 \begin{align}
@@
 Genz \cite{Gen93} introduced a variable transformation to transform \eqref{eqn:GaussDef} into an integral on the unit cube.
+Not only does this variable transformation accommodate domains that are (semi-)infinite, it also tends to smooth out the integrand better than an affine transformation, which expedites the cubature.
 Let $\mSigma= \mL \mL^T$ be the Cholesky decomposition where $\mL = (l_{jk})_{j,k=1}^d$ is a lower triangular matrix.
@@
 \begin{align*}
-\alpha_1& = \Phi(a_1), \qquad \beta_1 = \Phi(b_1)
+\alpha_1& = \Phi(a_1), \qquad \beta_1 = \Phi(b_1),
 \\
@@
 \end{align}
-where $\Phi$ is the cumulative standard normal distribution function.
+where $\Phi$ is the univariate cumulative standard Gaussian distribution function.
 Then, $\mu = \int_{[0,1]^{d'-1}} f_{\text{Genz}}(\vx) \, \dvx$.
-As we can see, this approach transforms $d'$ integral into a $d=d'-1$ integral.
+As we can see, this approach transforms a $d'$ dimensional integral into a $d=d'-1$ dimensional integral.
 
@@
 	%\end{subfigure}
-	\caption{The $d'=3$ multivariate normal probability transformed to an integral of $f_{\text{Genz}}$ of $d=2$. This plot can be reproduced using \code{IntegrandPlots.m} in GAIL}
+	\caption{The $d'=3$ multivariate Gaussian probability transformed to an integral of $f_{\text{Genz}}$ of $d=2$. This plot can be reproduced using \code{IntegrandPlots.m} in GAIL}
 	\label{fig:MVN_Genz}
@@
 		\includegraphics[width=0.95\linewidth]{MVN_rapid_n_vs_time_Matern_d2_2019-Jun-29}
-	\caption{Multivariate normal probability estimated using Mat\'ern kernel with $d=2$ using empirical stopping criterion.
+	\caption{Multivariate Gaussian probability estimated using Mat\'ern kernel with $d=2$ using empirical stopping criterion.
 Top: Guaranteed integration within error tolerance $\varepsilon$.
@@
 \end{align}
+In the formulas for the credible interval widths, $\vlambda$ depends on $\vtheta$, and  $\vtheta$ is assumed to take on the values $\vtheta_{\MLE}$ or $\vtheta_{\GCV}$ as appropriate.
 \end{theorem}
@@
 
-Three integrals were evaluated using the GAIL algorithm \code{cubBayesLattice\_g}:  a multivariate normal probability, the Keister's example, and an option pricing example.  
+Three integrals were evaluated using the GAIL algorithm \code{cubBayesLattice\_g}:  a multivariate Gaussian probability, the Keister's example, and an option pricing example.  
 The sequences $\{\vx_i\}_{i=1}^\infty$ are the randomly shifted lattice node sequences supplied by GAIL. 
@@
 	\includegraphics[width=0.98\linewidth]{"Lattice_MVN_guaranteed_time_MLE_C2sin_d2_r2_2019-Jun-27"}
-	\caption[Guaranteed:]{Multivariate normal probability example using the empirical Bayes stopping criterion.}
+	\caption[Guaranteed:]{Multivariate Gaussian probability example using the empirical Bayes stopping criterion.}
 	\label{fig:mvn-guaranteed-MLE}
@@
 	\includegraphics[width=0.98\linewidth]{"Lattice_MVN_guaranteed_time_full_C2sin_d2_r2_2019-Jun-27"}
-	\caption[MVN guaranteed : FB]{Multivariate normal probability example using the full Bayes stopping criterion.}
+	\caption[MVN guaranteed : FB]{Multivariate Gaussian probability example using the full Bayes stopping criterion.}
 	\label{fig:mvn-guaranteed-FB}
@@
 	\includegraphics[width=0.98\linewidth]{"Lattice_MVN_guaranteed_time_GCV_C2sin_d2_r2_2019-Jun-27"}
-	\caption[MVN guaranteed : GCV]{Multivariate normal probability example using the GCV stopping criterion.}
+	\caption[MVN guaranteed : GCV]{Multivariate Gaussian probability example using the GCV stopping criterion.}
 	\label{fig:mvn-guaranteed-GCV}
@@
 \end{align*}
-and again $\Phi$ is the standard normal distribution.
+and again $\Phi$ is the standard Gaussian distribution.
 The true value of $\mu$ can be calculated iteratively in terms of a quadrature as follows:  
@@
 We used the Sidi's $C^1$ periodization, dimension $d=4$, and $r=2$.
-As we can see, the GCV stopping criterion achieves faster results than the other stopping criteria, similarly to the multivariate normal case.
-The credible intervals are narrower than the multi variate normal case since the kernel is smoother than the periodization transform used.
+As we can see, the GCV stopping criterion achieves faster results than the other stopping criteria, similarly to the multivariate Gaussian case.
+The credible intervals are narrower than the multivariate Gaussian case since the kernel is smoother than the periodization transform used.
 
@@
 In the latter case, the credible interval widths are quite conservative.
-For option pricing example, this is less serious of an issue than for the multivariate normal and Keister examples.
+For option pricing example, this is less serious of an issue than for the multivariate Gaussian and Keister examples.
 A possible reason is that the latter integrands are significantly smoother than the covariance kernel assumed.
@@
 
-\iffalse
-
-% For one-column wide figures use
-\begin{figure}
-% Use the relevant command to insert your figure file.
-% For example, with the graphicx package use
-  \includegraphics{example.eps}
-% figure caption is below the figure
-\caption{Please write your figure caption here}
-\label{fig:1}       % Give a unique label
-\end{figure}
-%
-% For two-column wide figures use
-\begin{figure*}
-% Use the relevant command to insert your figure file.
-% For example, with the graphicx package use
-  \includegraphics[width=0.75\textwidth]{example.eps}
-% figure caption is below the figure
-\caption{Please write your figure caption here}
-\label{fig:2}       % Give a unique label
-\end{figure*}
-%
-% For tables use
-\begin{table}
-% table caption is above the table
-\caption{Please write your table caption here}
-\label{tab:1}       % Give a unique label
-% For LaTeX tables use
-\begin{tabular}{lll}
-\hline\noalign{\smallskip}
-first & second & third  \\
-\noalign{\smallskip}\hline\noalign{\smallskip}
-number & number & number \\
-number & number & number \\
-\noalign{\smallskip}\hline
-\end{tabular}
-\end{table}
-
-\fi
-
 \begin{acknowledgements}
@@
 \section{Details of the Full Bayes Posterior Density for $\mu$} \label{appendix:full_bayes}
+To simplify, we drop the dependence of $c_{0\vtheta}$, $\vc_\vtheta$, and $\mC_\vtheta$ on $\vtheta$ in the notation below.
 Starting from the Bayesian formula for the posterior density for $\mu$ at the beginning of Section \ref{sec:fullBayes} with the non-informative prior, it follows that 
@@
 \end{align*}
-In the derivation above and below, factors that are independent of $\xi$, $\lambda$, or $z$ can be discarded since we only need to preserve the proportion.
+In the derivation above and below, factors that are \emph{independent} of $\xi$, $\lambda$, or $z$ can be discarded since we only need to preserve the proportion.
 But, factors that depend on $\xi$, $\lambda$, or $z$ must be kept.
@@
 \begin{align*}
-\alpha \gamma - \beta^2 \propto 1 +  \frac{(z - \hmu_{\textup{MLE}})^2}{(n-1)s_{\textup{full}}^2},
+\alpha \gamma - \beta^2 \propto 1 +  \frac{(z - \hmu_{\MLE})^2}{(n-1)s_{\textup{full}}^2},
 \end{align*}

### 2019-07-22 BayesianCubaturePaper2018 - Rev1b.tex
polished

@@
 The process outlined above typically requires a computational cost of $O(N_{\text{opt}}n^3)$, where $N_{\text{opt}}$ is the number of optimization steps required to identify the hyperparameters.
-Our innovation is to pair low discrepancy nodes with matching kernels that lower the  computational cost to $O(N_{\text{opt}} n \log n)$.
+Our innovation is to pair low discrepancy nodes with matching covariance kernels that lower the  computational cost to $O(N_{\text{opt}} n \log n)$.
 This approach is demonstrated using rank-1 lattice sequences and shift-invariant kernels.
@@
 Section \ref{sec:shift_invariant_kernel} implements this concept for shift-invariant kernels and rank-1 lattice nodes.
-This section also describes how to avoid cancellation error for kernels of product form.
+This section also describes how to avoid cancellation error for covariance kernels of product form.
 Numerical examples are provided in Section \ref{sec:NumExp} to demonstrate our new algorithm.
@@
 In each run, the nodes are randomly scrambled.
-We  observe the algorithm meets the error criterion 95\% of the time even though we used 99\% credible interval.
-One possible explanation is, the matrix inversions in the algorithm are ill-conditioned leading to numerical inaccuracies.
+The empirical Bayes credible intervals are used for stopping criteria.
+We  observe that the algorithm meets the error criterion 95\% of the time even though we used 99\% credible intervals.
+One possible explanation is that the matrix inversions in the algorithm are ill-conditioned leading to numerical inaccuracies.
+Another possible explanation is that this Mat\'ern covariance kernel is not a good match for the integrand.
 %with Intel i7 3630QM and 16GB RAM memory
 %On our test computer,
-As shown in \figref{fig:MVN_Metern_d2b2}, computation time increases rapidly with $n$. 
-The  maximum likelihood estimation of $\vtheta$, which requires repeated evaluation of the objective function, is the most time consuming of all.
-It takes tens of seconds to compute $\hmu_n$ once with $\varepsilon = 10^{-5}$.
-In contrast, this example in Section \ref{sec:NumExp} take less than a hundredth of a second to compute $\hmu_n$ once with $\varepsilon = 10^{-5}$ using our new algorithm.
+
+As shown in \figref{fig:MVN_Metern_d2b2}, the computation time increases rapidly with $n$. 
+The  empirical Bayes estimation of $\vtheta$, which requires repeated evaluation of the objective function, is the most time consuming of all.
+It takes tens of seconds to compute $\hmu_n$ with $\varepsilon = 10^{-5}$.
+In contrast, this example in Section \ref{sec:NumExp} take less than a hundredth of a second to compute $\hmu_n$ with the same $\varepsilon$ using our new algorithm.
 Not only is the Bayesian cubature with the Mat\'ern kernel slow, but also $\mC_\vtheta$ becomes highly ill-conditioned as $n$ increases.
@@
 		\includegraphics[width=0.95\linewidth]{MVN_rapid_n_vs_time_Matern_d2_2019-Jun-29}
-	\caption{Multivariate Gaussian probability estimated using Mat\'ern kernel with $d=2$ using empirical stopping criterion.
-Top: Guaranteed integration within error tolerance $\varepsilon$.
-Bottom: Computation time rapidly increases with increase of $n$.
+	\caption{Multivariate Gaussian probability estimated using Mat\'ern kernel with $d=2$ using the empirical Bayes stopping criterion.
+Top: Ratio of the integration error to the error tolerance versus execution time.
+Bottom: Execution time rapidly increases with increasing $n$.
 These figures can be reproduced using \code{matern\_guaranteed\_plots.m} in GAIL.}
@@
 
-The generic automatic Bayesian cubature algorithm described in the previous section requires $\Order\bigl(n \$(f) + \break N_{\opt} [n^2 \$(C_\vtheta)  + n^3]\bigr)$ operations to estimate $\vtheta$, compute the credible interval width, and compute the cubature.
+The generic automatic Bayesian cubature algorithm described in the previous section requires $\Order\bigl(n \$(f) + \linebreak[4] N_{\opt} [n^2 \$(C_\vtheta)  + n^3]\bigr)$ operations to compute the cubature.
 Now we explain how to speed up the calculations.
-A key is to choose covariance kernels that match the nodes, $\{\vx_i\}_{i=1}^n$, so that the vector-matrix operations required by Bayesian cubature can be accomplished using fast transforms at a cost of $\Order\bigl(n \$(f) + N_{\opt} [n \$(C_\vtheta)  + n \log(n)] \bigr)$.
+A key is to choose covariance kernels that match the nodes, $\{\vx_i\}_{i=1}^n$, so that the vector-matrix operations required by Bayesian cubature can be accomplished using fast transforms at a computational cost of $\Order\bigl(n \$(f) + N_{\opt} [n \$(C_\vtheta)  + n \log(n)] \bigr)$.
 
@@
 
-We make three assumptions that allow the fast computation:
+We make three assumptions that facilitate  fast computation:
 \begin{subequations} \label{fastcompAssump}
@@
 \log\left(
-\sum_{i=2}^n \frac{\abs{\widetilde{y}_i}^2}{\lambda_{\vtheta i}}
+\sum_{i=2}^n \frac{\abs{\widetilde{y}_i}^2}{\lambda_{\vtheta, i}}
 \right) \right .\\ 
@@
 & \hspace{3cm} \left .
- + \frac{1}{n}\sum_{i=1}^n \log(\lambda_{\vtheta i})
+ + \frac{1}{n}\sum_{i=1}^n \log(\lambda_{\vtheta,i})
 \right],\\
@@
 \vtheta_{\GCV} 
-&= \argmin_\vtheta \left[ \log \left ( \sum_{i=2}^n \frac{\abs{\widetilde{y}_i}^2}{\lambda_{\vtheta i}^2} 
+&= \argmin_\vtheta \left[ \log \left ( \sum_{i=2}^n \frac{\abs{\widetilde{y}_i}^2}{\lambda_{\vtheta, i}^2} 
 \right) \right .\\
 \label{thetaGCV}
-& \qquad \qquad \qquad \qquad  \left . -2\log\left( \sum_{i=1}^n \frac{1}{\lambda_{\vtheta i}} \right)
+& \qquad \qquad \qquad \qquad  \left . -2\log\left( \sum_{i=1}^n \frac{1}{\lambda_{\vtheta, i}} \right)
 \right], 
@@
 We  also want to satisfy assumption \eqref{addAssump}.
-%To facilitate the fast transform, it is assumed in this section and the next that $n$ is power of $2$.  
-To facilitate the fast transform, $n$ must be power of $2$.
+To conveniently facilitate the fast transform, it is assumed in this section and the next that $n$ is power of $2$.  
+%To facilitate the fast transform, $n$ must be power of $2$.
 
@@
 \end{equation} 
-Here, $\vh$ is a $d$-dimensional generating vector of positive integers, $\vDelta$ is some point in $[0,1)^d$, often chosen at random, and $\{\phi(i)\}_{i=0}^n$ is the van der Corput sequence, defined by reflecting the binary digits of the integer about the decimal point, i.e.,
+Here, $\vh$ is a $d$-dimensional generating vector of positive integers, $\vDelta$ is some point in $[0,1)^d$, often chosen at random, and $\{\phi(i)\}_{i=0}^\infty$ is the van der Corput sequence, defined by reflecting the binary digits of the integer about the decimal point, i.e.,
 \begin{align} \label{vdCDef}
@@
 \begin{multline} \label{phiprop}
-\phi:\{0, \ldots, n-1 \} \to \{0, 1/n, \ldots, (n-1)/n\} \\
+n\phi:\{0, \ldots, n-1 \} \to \{0, \ldots, n-1\} \\
 \text{is one-to-one},
@@
 An example of $64$ nodes is given in \figref{latticefig}.
-The even coverage of the unit cube is ensured by a well chosen generating vector.
+The even coverage of the unit cube is ensured by a well chosen generating vector, $\vh$.
 The choice of generating vector is typically done offline by computer search.
@@
 The covariance functions $C_\vtheta$ that match integration lattice node sets have the form
+\begin{subequations} \label{eqn:ourkernel}
 \begin{align} \label{eq:shInv}
@@
 This is called a \emph{shift-invariant kernel} because shifting both arguments of the covariance function by the same amount leaves the value unchanged.
-Of course, $K_\vtheta$ must also be of the form that ensures that $C_\vtheta$ is symmetric and positive definite, as assumed in \eqref{FJH:eq:CondPosDef}.
+Here, $K_\vtheta$ is periodic and must  be of the form that ensures that $C_\vtheta$ is symmetric and positive definite, as assumed in \eqref{FJH:eq:CondPosDef}.
 
@@
 \label{the_kernel_eqn_bernoulli}
-C_\vtheta(\vt, \vx) =
+K_\vtheta(\vx) =
 \prod_{l=1}^d \biggl[
-1 - (-1)^{r} \eta B_{2r}( |{x_l-t_l}| ) \biggr], \\  
+1 - (-1)^{r} \eta B_{2r}( x_l) \biggr], \\  
 \forall \vt,\vx \in [0,1]^d, \  \vtheta = (r,\eta), \ r \in \naturals, \ \eta > 0.
 \end{multline}
+\end{subequations}
 Symmetric, periodic, positive definite kernels of this form appear in  \cite{DicEtal14a,Hic96a}.  Bernoulli polynomials are described in \cite[Chapter 24]{OlvEtal10a}.
@@
 Larger $\eta$ implies greater fluctuations of the output with respect to the input.
-Plots of $C(\cdot, 0.3)$ are given in \figref{fig:fourierkernel-dim1} for various $r$ and $\eta$ values.
-
-Integration lattice cubature rules are known to have convergence rates that depend on the smoothness of the integrands \cite{DicEtal14a}.
+Plots of $C_\vtheta(\cdot, 0.3)$ are given in \figref{fig:fourierkernel-dim1} for various $\vtheta=(r, \eta)$ values.
+
+Lattice cubature rules are known to have convergence rates that depend on the smoothness of the integrands, but that are rather independent of the choice of the integration lattice \cite{DicEtal14a}.
 Thus, we expect integration lattice node sets to perform well regardless of the smoothness of the covariance kernel.
@@
 \begin{equation} \label{PermMat}
-    \mP = \bigl( \delta_{\phi(i-1), (j-1)/n}  \bigr)_{i,j=1}^n
+    \mP = \bigl( \delta_{n\phi(i-1), j-1}  \bigr)_{i,j=1}^n
 \end{equation}
-is a permutation matrix, where $\delta$ is the Kronecker delta function.  Then,
+is a permutation matrix, where $\delta_{\cdot,\cdot}$ is the Kronecker delta function.  Then,
 \begin{align}
@@
 & \qquad \qquad  \text{by \eqref{eqn:lattice_def} and \eqref{eq:shInv}}  \\
-& = \mP \mK_{\vtheta}  \mP^T,  \label{shInvKernGramMatrix} \\
-\nonumber 
-\text{where } \mK_{\vtheta} &= \bigl ( K_\vtheta \bigl (\vh (i-j)/n \bmod \vone \bigr ) \bigr)_{i, j = 1}^n.
-\end{align}
-\FJHNote{Check this.}
+\nonumber
+& = \biggl( 
+\sum_{i',j'=1}^n \delta_{n\phi(i-1), i'-1}  \,
+K_\vtheta \bigl (\vh (i'-j')/n \bmod \vone \bigr )\\
+\nonumber
+& \qquad \qquad \times \delta_{j'-1,n\phi(j-1)} 
+\biggr)_{i,j=1}^n \\
+& = \mP \mK_{\vtheta}  \mP^T,  \label{shInvKernGramMatrix} 
+\intertext{where } 
+\mK_{\vtheta} &= \bigl ( K_\vtheta \bigl (\vh (i-j)/n \bmod \vone \bigr ) \bigr)_{i, j = 1}^n.
+\end{align}
 
@@
 Assumptions \eqref{fastcompAssumpA} and \eqref{fastcompAssumpB} can be verified by \eqref{PermMat}, \eqref{Keig}, and \eqref{Clateig}.
-Assumption \eqref{fastcompAssumpC} is satisfied because $\mV^H \vb = \mW^H \mP^T \vb$ is just the discrete Fourier transform of a vectors whose rows have been permuted.
+Assumption \eqref{fastcompAssumpC} is satisfied because $\mV^H \vb = \mW^H \mP^T \vb$ is just the discrete Fourier transform of a vector whose rows have been permuted.
 This can be performed in $\Order(n \log(n))$ operations by the FFT algorithm.
@@
 
-Any shift-invariant covariance kernel can be written as $C_\vtheta = 1 + \rC_\vtheta$.
+Any shift-invariant covariance kernel can be written as $C_\vtheta = 1 + \rC_\vtheta$, where $\rC_\vtheta$ is also symmetric and positive definite.
 The associated Gram matrix for $\rC_\vtheta$ is then $\rmC_\vtheta = \mC_\vtheta - \vone \vone^T$, and the eigenvalues of $\rmC_\vtheta$ are $\rlambda_1 = \lambda_1 - n, \lambda_2, \ldots, \lambda_n$, which follows because $\vone$ is the first eigenvector of both $\mC_\vtheta$ and $\rmC_\vtheta$.
@@
 
-We show how to compute $\rC$ without introducing round-off error.  The covariance functions that we use are of product form, namely,
+We show how to compute $\rC_\vtheta$ without introducing round-off error.  The covariance functions that we use are of product form, namely,
 \begin{equation*}
-C_\vtheta(\vt, \vx) = \prod_{\ell=1}^d \left[1 + \rC_{_\vtheta\ell}(t_\ell,x_\ell) \right], \qquad  \rC_\ell:[0,1]^2 \to \reals.
+C_\vtheta(\vt, \vx) = \prod_{\ell=1}^d \left[1 + \rC_{\vtheta,\ell}(t_\ell,x_\ell) \right], \qquad  \rC_{\vtheta,\ell}:[0,1]^2 \to \reals.
 \end{equation*}
-Direct computation of $\rC_\vtheta(\vt,\vx) = C_\vtheta(\vt,\vx) -1$ introduces cancellation error if the $ \rC_{_\vtheta \ell}$ are small.  So, we employ the iteration
-\begin{align*}
-\rC^{(1)}_\vtheta(\vt,\vx) &= \rC_{\vtheta 1}(t_1,x_1),  \\
-\rC^{(\ell)}_\vtheta(\vt,\vx) &  = \rC^{(\ell-1)}_\vtheta[1 + \rC_{_\vtheta\ell}(t_\ell,x_\ell)] + \rC_\ell(t_\ell,x_\ell), \\
+Direct computation of $\rC_\vtheta(\vt,\vx) = C_\vtheta(\vt,\vx) -1$ introduces cancellation error if the $ \rC_{\vtheta, \ell}$ are small.  So, we employ the iteration
+\begin{align*}
+\rC^{(1)}_\vtheta(\vt,\vx) &= \rC_{\vtheta, 1}(t_1,x_1),  \\
+\rC^{(\ell)}_\vtheta(\vt,\vx) &  = \rC^{(\ell-1)}_\vtheta(\vt,\vx) [1 + \rC_{\vtheta,\ell}(t_\ell,x_\ell)] + \rC_{\vtheta,\ell}(t_\ell,x_\ell), \\
 & \hspace{5cm} \ell = 2, \ldots, d, \\
@@
 		$\vx_1, \vx_2, \ldots$; 
-		a shift-invariant periodic kernel, $C_\vtheta$;
+		a shift-invariant  kernel, $C_\vtheta$;
 		a black-box function, $f$; 
 		an absolute error tolerance,
-		$\varepsilon>0$; the positive initial sample size, $n_0$;
+		$\varepsilon>0$; the positive initial sample size, $n_0$, that is a power of $2$;
 		the maximum sample size $n_{\textup{max}}$
@@
 \begin{theorem}
-Any symmetric, positive definite,  shift-\break invariant covariance kernel of the form \eqref{eq:shInv} scaled to satisfy \eqref{addAssump}, when matched with rank-1 lattice data-sites, must satisfy assumptions \eqref{fastcompAssump}.
+Let $C_\vtheta$ be any symmetric, positive definite,  shift-invariant covariance kernel of the form \eqref{eq:shInv}, where $K_\vtheta$ has period one in every variable.
+Furthermore, let $K_\vtheta$ be scaled to satisfy \eqref{addAssump}.
+When matched with rank-1 lattice data-sites, $C_\vtheta$ must satisfy assumptions \eqref{fastcompAssump}.
 The cubature, $\hmu$, is just the sample mean.
@@
 
-We have implemented the fast adaptive Bayesian cubature algorithm in MATLAB as part of the Guaranteed Adaptive Integration Library (GAIL) \cite{ChoEtal17b} as \allowbreak \code{cubBayesLattice\_g}.
-This algorithm uses the covariance kernel defined in  \eqref{the_kernel_eqn_bernoulli} with  $r=1,2$ and the periodizing variable transforms in  \secref{period_var_tx}.
-The rank-1 lattice node generator is taken from \cite{Nuy17a} \break (\code{exod2\_base2\_m20}).
+We have implemented the fast adaptive Bayesian cubature algorithm in MATLAB as part of the Guaranteed Adaptive Integration Library (GAIL) \cite{ChoEtal17b} as \linebreak[4]  \code{cubBayesLattice\_g}.
+This algorithm uses the covariance kernel defined in \eqref{eqn:ourkernel} with  $r=1$ and $2$, and the periodizing variable transforms in  \secref{period_var_tx}.
+The rank-1 lattice node generator is taken from \cite{Nuy17a} \linebreak[4] (\code{exod2\_base2\_m20}).
 
@@
 \end{subequations}
-If $\Psi$ is sufficiently smooth, $\lim_{x \downarrow 0}x^{-r}\Psi'(x) = \lim_{x \uparrow 1} (x-1)^{-r}\Psi'(x) = 0$ for $ r \in \natzero$, and $g \in C^{(r, \ldots, r)}[0,1]^d$, then $f$ has continuous, periodic derivatives up to order $r$ in each direction.
+If for $r \in \natzero$, 
+\begin{itemize}
+	\item $\Psi \in C^{s+1}[0,1]$,
+	\item  $\lim_{x \downarrow 0}x^{-r-1}\Psi'(x) = \lim_{x \uparrow 1} (1-x)^{-r-1}\Psi'(x) = 0$, and 
+	\item $g \in C^{(r, \ldots, r)}[0,1]^d$,
+\end{itemize}
+then $f$ has continuous, periodic mixed partial derivatives of up to order $r$ in each direction.  
 Examples of this kind of transform include \cite{Sid08a}:
@@
 Periodizing variable transforms are used in the numerical examples below.
-In some cases, they can speed the convergence of the Bayesian cubature because they allow one to take advantage of smoother kernels.
+In some cases, they can speed the convergence of the Bayesian cubature because they allow one to take advantage of smoother covariance kernels.
 However, there is a trade-off.  Smoother periodizing transformations tend to give integrands $f$ with larger inferred $s$ values and thus wider credible intervals.
@@
 
-Three integrals were evaluated using the GAIL algorithm \code{cubBayesLattice\_g}:  a multivariate Gaussian probability, the Keister's example, and an option pricing example.  
+Three integrals were evaluated using the GAIL algorithm \code{cubBayesLattice\_g}:  a multivariate Gaussian \linebreak[4] probability, the Keister's example, and an option pricing example.  
 The sequences $\{\vx_i\}_{i=1}^\infty$ are the randomly shifted lattice node sequences supplied by GAIL. 
-For each integral,  each of our stopping criteria---empirical Bayes, full Bayes, and generalized cross-validation---our algorithm was run for $400$ different randomly chosen error tolerances.
+For each integral and each of our stopping criteria---empirical Bayes, full Bayes, and generalized cross-validation---our algorithm was run for $400$ different randomly chosen error tolerances.
 The error tolerances were chosen randomly in an interval depending on the difficulty of the problem.
-In each run, the nodes were also randomly shifted.
+In each run, the nodes were also randomly shifted with $\mathcal{U}[0,1]$ shifts independent of each other and the error tolerances.
 The accuracy of the algorithm depends mildly on the shift; there is no universally optimal shift.
@@
 
-Ideally, we would optimize both $r$ and $\eta$ simultaneously in the definition of our $C_\vtheta$ in \eqref{the_kernel_eqn_bernoulli}.
+Ideally, we would optimize both $r$ and $\eta$ simultaneously in the definition of our $C_\vtheta$ in \eqref{eqn:ourkernel}.
 However, in these examples we fix $r$ and optimize $\eta$ only.
@@
 
-\paragraph{Multivariate Normal Probability.}
+\paragraph{Multivariate Gaussian Probability.}
 
@@
 We used the same setting as before with generic slow Bayesian cubature in \secref{MVN_example} for comparison.
-For error threshold $\varepsilon=10^{-5}$ with the empirical Bayes stopping criterion, our fast algorithm takes just under 0.01 second as shown in \figref{fig:mvn-guaranteed-MLE} whereas the generic algorithm takes over 20 seconds as shown in \figref{fig:MVN_Metern_d2b2}.
+For error tolerance $\varepsilon=10^{-5}$ with the empirical Bayes stopping criterion, our fast algorithm takes just under 0.01 seconds as shown in \figref{fig:mvn-guaranteed-MLE} whereas the generic algorithm takes over 20 seconds as shown in \figref{fig:MVN_Metern_d2b2}.
 
@@
 One can also observe from the figures, the credible intervals are in general much wider than the true error.
-This could be due to the periodized integrand being smoother than the $r=2$ kernel assumes. Perhaps one should consider smoother covariance kernels.
+This could be due to the periodized integrand being smoother than the $r=2$ covariance kernel assumes. Perhaps one should consider smoother covariance kernels.
 
@@
 As we can see, the GCV stopping criterion achieves faster results than the other stopping criteria, similarly to the multivariate Gaussian case.
-The credible intervals are narrower than the multivariate Gaussian case since the kernel is smoother than the periodization transform used.
+The credible intervals are narrower than the multivariate Gaussian case since the covariance kernel is smoother than the periodization transform used.
 
@@
 
-In summary, the Bayesian cubature algorithm computes the integral within the user-specified threshold in nearly all of the test cases.
+In summary, the Bayesian cubature algorithm computes the integral within the user-specified tolerance in nearly all of the test cases.
 The rare exceptions occurred in the option pricing example for $\varepsilon \le 10^{-4}$.
@@
 \ref{fig:optprice-guaranteed-GCV}.
-%Also notice, our algorithm finished within 10 seconds for Keister and multivariate Normal examples while the option pricing took closer to 70 seconds, again due to the complexity of the integrand.
+%Also notice, our algorithm finished within 10 seconds for Keister and multivariate Gaussian examples while the option pricing took closer to 70 seconds, again due to the complexity of the integrand.
 %FH it is difficult to compare apples to orances, and the timing depends on the error tolerances as well
@@
 %\iffalse
-%\subsection{Properties of Multivariate Normal Distributions}
+%\subsection{Properties of Multivariate Gaussian Distributions}
 

### 2019-07-22 BayesianCubaturePaper2018 - Rev1b.tex
polishing

@@
 \usepackage{amssymb}
+\usepackage{cite}
 %
@@
               Illinois Institute of Technology \\
-              10 W. 32nd St., Room 208\\
+              10 W. 32nd St., Room 208,
               Chicago IL 60616\\
@@
            Fred J. Hickernell \at
-           Center for Computational Science and Department of Applied Mathematics, 
+           Center for Interdisciplinary Scientific Computation and \\
+           Department of Applied Mathematics \\
            Illinois Institute of Technology \\
-           PS 106, 3105 S. Dearborn St., 
+           10 W. 32nd St., Room 208, 
            Chicago IL 60616
@@
 For high dimensional problems, it is difficult to adaptively change the sampling pattern, but one can automatically determine the
-sample size, $n$, given a fixed and reasonable sampling pattern.
+sample size, $n$, given a reasonable, fixed sampling pattern.
 We take this approach here using a Bayesian perspective.
 We postulate that the integrand is an instance of a Gaussian stochastic process parameterized by a constant mean and a covariance function defined by a scale parameter times a parameterized function specifying how the integrand values at two different points in the domain are related.
-These hyperparameters are inferred integrated out using integrand values via one of three techniques:  empirical Bayes, full Bayes, or generalized cross-validation.
-The sample size, $n$, is chosen to make the half-width of the credible interval for the Bayesian posterior mean no greater than the error tolerance.
+These hyperparameters are inferred or integrated out using integrand values via one of three techniques:  empirical Bayes, full Bayes, or generalized cross-validation.
+The sample size, $n$, is increased until the half-width of the credible interval for the Bayesian posterior mean is no greater than the error tolerance.
 
 The process outlined above typically requires a computational cost of $O(N_{\text{opt}}n^3)$, where $N_{\text{opt}}$ is the number of optimization steps required to identify the hyperparameters.
-Our innovation is to pair low discrepancy nodes with matching covariance kernels that lower the  computational cost to $O(N_{\text{opt}} n \log n)$.
-This approach is demonstrated using rank-1 lattice sequences and shift-invariant kernels.
+Our innovation is to pair low discrepancy nodes with matching covariance kernels to lower the  computational cost to $O(N_{\text{opt}} n \log n)$.
+This approach is demonstrated explicitly with rank-1 lattice sequences and shift-invariant kernels.
 Our algorithm is  implemented in the Guaranteed Automatic Integration Library (GAIL).
@@
 
-Users of cubature algorithms typically want the error to be no greater than their error tolerance, denoted by $\varepsilon$, i.e., 
+Users of cubature algorithms typically want the error to be no greater than their specified error tolerance, denoted by $\varepsilon$.  That is, they want
 \begin{align}
@@
 \end{align}
-Some stopping criteria used in practice are heuristic.
-Other rigorous algorithms require rather strong assumptions about the integrand, such as an upper bound on its variance (for simple Monte Carlo) or total variation (for quasi-Monte Carlo).
+Some stopping criteria for choosing $n$ are heuristic.
+Other rigorous algorithms satisfying \eqref{eqn:err_crit}  require strong a priori assumptions about the integrand, such as an upper bound on its variance (for simple Monte Carlo) or total variation (for quasi-Monte Carlo).
 We take a Bayesian approach by constructing a stopping criterion that is based on a credible interval.
@@
 
-The primary contribution of this article is to demonstrate how the choice of a family of covariance kernels that match the low discrepancy sampling nodes facilitates fast computation of the cubature and the data-driven stopping criterion.
+Our primary contribution is to demonstrate how the choice of a family of covariance kernels that match the low discrepancy sampling nodes facilitates fast computation of the cubature and the data-driven stopping criterion.
 Our Bayesian cubature requires a computational cost of
@@
 where $\$(f)$ is the cost of one integrand value, $\$(C)$ is the cost of a single covariance kernel value,  $\Order(n \log(n))$ is the cost of a fast Fourier transform, and $N_{\opt}$ is an upper bound on the number of optimization steps required to choose the hyperparameters.
-If function evaluation is expensive, such as the output of a computationally intensive simulation, or $\$(f) = \Order(d)$ for large $d$, then $\$(f)$ might be similar in magnitude to $N_{\opt} \log(n)$ in practice.
+If function evaluation is expensive, e.g., the output of a computationally intensive simulation, or if $\$(f) = \Order(d)$ for large $d$, then $\$(f)$ might be similar in magnitude to $N_{\opt} \log(n)$ in practice.
 Typically, $\$(C) = \Order(d)$.
@@
 which is explained in Section \ref{sec:bayes_cubature_algo}.
-Note that beyond evaluating the integrand, the computational cost in \eqref{eqn:TheiralgoCost} is much larger than that in \eqref{eqn:OuralgoCost}.
+Note that aside from evaluating the integrand, the computational cost in \eqref{eqn:TheiralgoCost} is much larger than that in \eqref{eqn:OuralgoCost}.
 
@@
 
-We assume that the integrand, $f$, is an instance of a Gaussian stochastic process \cite{BriEtal18a}, \cite{Dia88a}, \cite{OHa91a}, \cite{Rit00a}, \cite{RasGha03a}, i.e., $f \sim \mathcal{GP}(m,s^2 C_\vtheta)$.
+We assume that the integrand, $f$, is an instance of a Gaussian stochastic process  i.e., $f \sim \mathcal{GP}(m,s^2 C_\vtheta)$  \cite{BriEtal18a, Dia88a, OHa91a, Rit00a, RasGha03a}.
 Specifically, $f$ is a real-valued random function with constant mean $m$ and covariance function $s^2C_\vtheta$:
@@
 Here, $c_{0\vtheta}$ and $\vc_\vtheta$ depend explicitly on $\vtheta$.
-We assume that the integrals in these definitions can be computed analytically.
+We assume that $C_\vtheta$ is simple enough that the integrals in these definitions can be computed analytically.
 We need the following lemma pertaining to a conditional Gaussian distribution to derive the distribution of the posterior error of our cubature.
@@
 \right] = 99\%, \\
-\err_{\textup{CI}} = 2.58 s \sqrt{c_{0\vtheta} - \vc_\vtheta^T\mCtheta^{-1}\vc_\vtheta}
+\err_{\textup{CI}} = 2.58 s \sqrt{c_{0\vtheta} - \vc_\vtheta^T\mCtheta^{-1}\vc_\vtheta}.
 \end{gather}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Parameter estimation}
+\subsection{Hyperparameter estimation}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 Integrand data is accumulated until the width of the credible interval, $\err_{\textup{CI}}$, is no greater than the error tolerance.
-As $n$ increases, one expects $\sqrt{c_{0\vtheta} - \vc_\vtheta^T\mCtheta^{-1}\vc_\vtheta}$ to decrease for well-chosen nodes, $\{\vx_i\}_{i=1}^n$.
-
-Note that $\err_{\textup{CI}}$ has no explicit dependence on the integrand values, even though one would intuitively expect that larger integrand should imply a  larger $\err_{\textup{CI}}$.
-This is because parameters, $m, s$, and $\vtheta$, have not yet been inferred from integrand data.
-After inferring the parameters, $\err_{\textup{CI}}$ does reflect the size of the integrand values.
-This section describes three approaches to parameter estimation.
-
-\begin{theorem} \label{thm:param} There are at least three approaches to estimating or integrating out the hyperparameters defining the Gaussian process from which the integrand is drawn: empirical Bayes, full Bayes, and generalized cross-validation.
+As $n$ increases, one expects $c_{0\vtheta} - \vc_\vtheta^T\mCtheta^{-1}\vc_\vtheta$ to decrease for well-chosen nodes, $\{\vx_i\}_{i=1}^n$.
+
+Note that $\err_{\textup{CI}}$ has no explicit dependence on the integrand values, even though one would intuitively expect that a larger integrand should imply a  larger $\err_{\textup{CI}}$.
+This is because the hyperparameters, $m, s$, and $\vtheta$, have not yet been inferred from integrand data.
+After inferring the hyperparameters, $\err_{\textup{CI}}$ does reflect the size of the integrand values.
+This section describes three approaches to hyperparameter estimation.
+
+\begin{theorem} \label{thm:param} There are at least three approaches to estimating or integrating out the hyperparameters defining the Gaussian process from which the integrand is drawn: empirical Bayes, full Bayes, and generalized cross-\linebreak[4]validation.
 Under these three approaches, we have the following:
-%\begin{allowdisplaybreaks}
 \begin{align}
@@
 \label{eqn:thetaMLE}
- & \qquad +  \frac{1}{n} \log(\det(\mC_\vtheta))
+ & \qquad \qquad +  \frac{1}{n} \log(\det(\mC_\vtheta))
 \biggr \}, \\
@@
 \label{vthetaGCV}
-& - \log \left ( \trace(\mC^{-2}_\vtheta) \right ) \biggr\}, \\
+& \qquad \qquad - \log \left ( \trace(\mC^{-2}_\vtheta) \right ) \biggr\}, \\
 \label{eqn:cubMLE}
@@
 \err_{\textup{full}} 
-& = t_{n-1,0.995} \hsigma_{\textup{full}} > \err_\MLE, \label{FJH:eq:errFull}
-\end{align}
-%\end{allowdisplaybreaks}
+& = t_{n-1,0.995} \hsigma_{\textup{full}} > \err_\MLE. \label{FJH:eq:errFull}
+\end{align}
+The resulting credible intervals are then
 \begin{multline}
@@
 
-For the results summarized in the theorem above, note that if the original covariance function, $C_\vtheta$, is replaced by $b C_\vtheta$ for some positive constant $b$, the cubature, $\hmu$, the estimates of $\vtheta$, and the credible interval widths, $\err_{\mathsf{x}}$ for $\mathsf{x} \in \{\MLE, \full, \GCV\}$, all remain unchanged.
+In the theorem above, note that if the original covariance function, $C_\vtheta$, is replaced by $b C_\vtheta$ for some positive constant $b$, the cubature, $\hmu$, the estimates of $\vtheta$, and the credible interval widths, $\err_{\mathsf{x}}$ for $\mathsf{x} \in \{\MLE, \full, \GCV\}$, all remain unchanged.
 The estimates of $s^2$ are multiplied by $b^{-1}$, as would be expected.
@@
 The loss function $\textup{GCV}$ depends on $m$ and $\vtheta$, but not on $s$.
-Minimizing the GCV  yields the formulae in Theorem \ref{thm:param} for $\widehat{\mu}_{\textup{GCV}}$ and $\vtheta_{\textup{GCV}}$.
+Minimizing the GCV  yields the formulae in Theorem \ref{thm:param} for $m_{\textup{GCV}}$ and $\vtheta_{\textup{GCV}}$.
 Plugging the value of $m_\GCV$ into \eqref{eqn:BayesCub} yields the formulae in Theorem \ref{thm:param} for $\widehat{\mu}_{\textup{GCV}}$.
@@
 \end{align*}
-Here, $s^2_{\textup{GCV}}$ is given by the formula in Theorem \ref{thm:param}.
+After simplification, $s^2_{\textup{GCV}}$ defined above becomes the formula in Theorem \ref{thm:param}.
 
@@
 
-We recognize that multiple applications of our credible intervals in one run of our algorithm is not strictly justified.
+We recognize that multiple applications of our credible intervals in one run of the algorithm is not strictly justified.
 However, if our integrand comes from the middle of the sample space and not the extremes, we expect our automatic Bayesian cubature to approximate the integral within the desired error tolerance with high probability.
@@
 and so $\hmu$ is simply the sample mean.  Also, under assumption \eqref{addAssump}, the credible interval widths simplify to
+\begin{subequations}
+\label{errSimple}
 \begin{align}
@@
 \frac{2.58}{n}\left\{\sum_{i=2}^n \frac{\abs{\widetilde{y}_i}^2}{\lambda_i^2}  \left [ \frac 1n \sum_{i=1}^n \frac{1}{\lambda_i} \right]^{-1} 
-\right. \\ &\qquad \qquad \left . \times
+\right. \\ &\hspace{3cm} \left . \times
 \left( 1 -  \frac{n}{\lambda_1} \right)  
@@
 \end{align}
+\end{subequations}
 In the formulas for the credible interval widths, $\vlambda$ depends on $\vtheta$, and  $\vtheta$ is assumed to take on the values $\vtheta_{\MLE}$ or $\vtheta_{\GCV}$ as appropriate.
@@
 Computing the eigenvalues of $\rmC$ via the procedure given in \eqref{eqn:fast_transform_to_eigvalues} yields $\rlambda_1 = \lambda_1 - n, \lambda_2, \ldots, \lambda_n$.
-The widths of the credible intervals in \eqref{eq:errMLEAllAsump}, \eqref{FJH:eq:errFullSimple}, and   \eqref{errGCVSimple} become
+The widths of the credible intervals in \eqref{errSimple} become
 \begin{subequations}

### 2019-07-22 BayesianCubaturePaper2018 - Rev1b.tex
fixed fourier kernel figures

@@
 We take this approach here using a Bayesian perspective.
-We postulate that the integrand is an instance of a Gaussian stochastic process parameterized by a constant mean and a covariance function defined by a scale parameter times a parameterized function specifying how the integrand values at two different points in the domain are related.
+We postulate that the integrand is an instance of a Gaussian stochastic process parameterized by a constant mean and a covariance kernel defined by a scale parameter times a parameterized function specifying how the integrand values at two different points in the domain are related.
 These hyperparameters are inferred or integrated out using integrand values via one of three techniques:  empirical Bayes, full Bayes, or generalized cross-validation.
@@
 We assume that the integrand, $f$, is an instance of a Gaussian stochastic process  i.e., $f \sim \mathcal{GP}(m,s^2 C_\vtheta)$  \cite{BriEtal18a, Dia88a, OHa91a, Rit00a, RasGha03a}.
-Specifically, $f$ is a real-valued random function with constant mean $m$ and covariance function $s^2C_\vtheta$:
+Specifically, $f$ is a real-valued random function with constant mean $m$ and covariance kernel $s^2C_\vtheta$:
 \begin{gather*}
@@
 
-In the theorem above, note that if the original covariance function, $C_\vtheta$, is replaced by $b C_\vtheta$ for some positive constant $b$, the cubature, $\hmu$, the estimates of $\vtheta$, and the credible interval widths, $\err_{\mathsf{x}}$ for $\mathsf{x} \in \{\MLE, \full, \GCV\}$, all remain unchanged.
+In the theorem above, note that if the original covariance kernel, $C_\vtheta$, is replaced by $b C_\vtheta$ for some positive constant $b$, the cubature, $\hmu$, the estimates of $\vtheta$, and the credible interval half-widths, $\err_{\mathsf{x}}$ for $\mathsf{x} \in \{\MLE, \full, \GCV\}$, all remain unchanged.
 The estimates of $s^2$ are multiplied by $b^{-1}$, as would be expected.
@@
 
-	\item $\Order\bigl(N_{\opt} n^3 \bigr)$ for the matrix inversions and determinant calculations.
+	\item $\Order\bigl(N_{\opt} n^3 \bigr)$ for the matrix inversions and determinant calculations; this cost is independent of $d$.
 
@@
 Genz \cite{Gen93} introduced a variable transformation to transform \eqref{eqn:GaussDef} into an integral on the unit cube.
-Not only does this variable transformation accommodate domains that are (semi-)infinite, it also tends to smooth out the integrand better than an affine transformation, which expedites the cubature.
+Not only does this variable transformation accommodate domains that are (semi-)infinite, it also tends to smooth out the integrand better, which expedites the cubature.
 Let $\mSigma= \mL \mL^T$ be the Cholesky decomposition where $\mL = (l_{jk})_{j,k=1}^d$ is a lower triangular matrix.
@@
 Then, $\mu = \int_{[0,1]^{d'-1}} f_{\text{Genz}}(\vx) \, \dvx$.
-As we can see, this approach transforms a $d'$ dimensional integral into a $d=d'-1$ dimensional integral.
+This approach transforms a $d'$ dimensional integral into a $d=d'-1$ dimensional integral.
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-We make some assumptions about the relationship between the covariance kernel and the nodes, which will be shown to hold in Section \ref{sec:shift_invariant_kernel} for rank-1 lattices and shift-invariant kernels.
+We make some assumptions about the relationship between the covariance kernel and the nodes.
+In Section \ref{sec:shift_invariant_kernel} these assumptions are shown to hold  for rank-1 lattices and shift-invariant kernels.
 Although the integrands and covariance kernels are real, it is convenient to allow related vectors and matrices to be complex.
@@
 
-We introduce some notation:
+We introduce some further notation:
 \begin{align}
@@
 In this and later sections, we drop the $\vtheta$ dependence of various quantities for simplicity of notation.
-Here, $\mV^H$ is the Hermitian of $\mV$, $\vC_1,\dots,\vC_n$ are columns of $\mC$.
-$\vV_1,\dots,\vV_n$ are columns of $\mV$ and $\vv_1,\dots,\vv_n$ are rows of $\mV$.
+Here, $\mV^H$ is the Hermitian of $\mV$, $\vC_1,\dots,\vC_n$ are columns of $\mC$,  $\vV_1,\dots,\vV_n$ are columns of $\mV$, and $\vv_1,\dots,\vv_n$ are rows of $\mV$.
 The normalization of $\mV$ assumed in \eqref{eqn:ftk_factor} conveniently allows the first eigenvector, $\vV_1$, to be the vector of ones in \eqref{fastcompAssumpB} below.
-The columns of matrix $\mV$ are eigenvectors of $\mC$, and $\mLambda$ is a diagonal matrix of eigenvalues of $\mC$.
+The columns of $\mV$ are eigenvectors of $\mC$, and $\mLambda$ is a diagonal matrix of eigenvalues of $\mC$.
 For any $n \times 1$ vector $\vb$, define the notation  $\widetilde{\vb} := \mV^H \vb$.
@@
 \end{subequations}
-We call the transformation $\vb \mapsto \mV^H \vb$ a \emph{fast transform} and $C$ a \emph{fast transform kernel}.
+We call the transformation $\vb \mapsto \mV^H \vb$ a \emph{fast transform} and $C_\vtheta$ a \emph{fast transform kernel}.
 
@@
 \begin{theorem} \label{thm:fastparam}
-Under assumptions \eqref{fastcompAssump}, the parameters and credible interval widths in Theorem \ref{thm:param} may be expressed in terms of the fast transforms of the function data, the first column of the Gram matrix, and $\vc_\vtheta$ as follows:
+Under assumptions \eqref{fastcompAssump}, the parameters and credible interval half-widths in Theorem \ref{thm:param} may be expressed in terms of the fast transforms of the function data, the first column of the Gram matrix, and $\vc_\vtheta$ as follows:
 \begin{align}
@@
 \end{equation}
-and so $\hmu$ is simply the sample mean.  Also, under assumption \eqref{addAssump}, the credible interval widths simplify to
+and so $\hmu$ is simply the sample mean.  Also, under assumption \eqref{addAssump}, the credible interval half-widths simplify to
 \begin{subequations}
@@
 \end{subequations}
-In the formulas for the credible interval widths, $\vlambda$ depends on $\vtheta$, and  $\vtheta$ is assumed to take on the values $\vtheta_{\MLE}$ or $\vtheta_{\GCV}$ as appropriate.
+In the formulas for the credible interval half-widths, $\vlambda$ depends on $\vtheta$, and  $\vtheta$ is assumed to take on the values $\vtheta_{\MLE}$ or $\vtheta_{\GCV}$ as appropriate.
 \end{theorem}
@@
 
-The set of nodes used is defined by a shifted extensible integration lattice node sequence, which takes the form
+We choose a set of nodes defined by a shifted extensible integration lattice node sequence, which takes the form
 \begin{equation} \label{eqn:lattice_def}
@@
 \subsection{Shift Invariant Kernels}
-The covariance functions $C_\vtheta$ that match integration lattice node sets have the form
+The covariance kernels $C_\vtheta$ that match integration lattice node sets have the form
 \begin{subequations} \label{eqn:ourkernel}
@@
 \end{align}
-This is called a \emph{shift-invariant kernel} because shifting both arguments of the covariance function by the same amount leaves the value unchanged.
+This is called a \emph{shift-invariant kernel} because shifting both arguments of the covariance kernel by the same amount leaves the value unchanged.
 Here, $K_\vtheta$ is periodic and must  be of the form that ensures that $C_\vtheta$ is symmetric and positive definite, as assumed in \eqref{FJH:eq:CondPosDef}.
@@
 \subsection{The Gram Matrix as the Permutation of a Circulant Matrix}
-For general shift-invariant covariance functions, the Gram matrix takes the form of a permutation of the rows and columns of a circulant matrix.
+For general shift-invariant covariance kernels, the Gram matrix takes the form of a permutation of the rows and columns of a circulant matrix.
 By the properties of $\phi$ in \eqref{phiprop}, it follows that
@@
 \end{equation}
-where the eigenvalues of $\mK_{\vtheta}$ and $\mC_{\vtheta}$ are identical.
+where the eigenvalues of  $\mC_{\vtheta}$ and $\mK_{\vtheta}$ are identical.
 
@@
 Assumption \eqref{fastcompAssumpC} is satisfied because $\mV^H \vb = \mW^H \mP^T \vb$ is just the discrete Fourier transform of a vector whose rows have been permuted.
-This can be performed in $\Order(n \log(n))$ operations by the FFT algorithm.
-A proper scaling of the kernel $K_\vtheta$ ensures that assumption \eqref{addAssump} is satisfied.
+This can be performed in $\Order(n \log(n))$ operations by the FFT.
+A proper scaling of the kernel $K_\vtheta$, such as the one given by \eqref{the_kernel_eqn_bernoulli},  ensures that assumption \eqref{addAssump} is satisfied.
 
@@
 For the covariance kernels used in our computation, it may happen that $n/\lambda_1$ is close to $1$.
-Thus, the term $1-n/\lambda_1$, which appears in the credible interval widths, $\err_{\MLE}$, $\err_{\textup{full}}$, and $\err_{\textup{GCV}}$, may suffer from cancellation error and even become negative.
+Thus, the term $1-n/\lambda_1$, which appears in the credible interval half-widths, $\err_{\MLE}$, $\err_{\textup{full}}$, and $\err_{\textup{GCV}}$, may suffer from cancellation error and even become negative.
 We have observed this phenomenon.
@@
 
-Any shift-invariant covariance kernel can be written as $C_\vtheta = 1 + \rC_\vtheta$, where $\rC_\vtheta$ is also symmetric and positive definite.
+Any shift-invariant covariance kernel satisfying \eqref{addAssump} can be written as $C_\vtheta = 1 + \rC_\vtheta$, where $\rC_\vtheta$ is also symmetric and positive definite.
 The associated Gram matrix for $\rC_\vtheta$ is then $\rmC_\vtheta = \mC_\vtheta - \vone \vone^T$, and the eigenvalues of $\rmC_\vtheta$ are $\rlambda_1 = \lambda_1 - n, \lambda_2, \ldots, \lambda_n$, which follows because $\vone$ is the first eigenvector of both $\mC_\vtheta$ and $\rmC_\vtheta$.
@@
 
-We show how to compute $\rC_\vtheta$ without introducing round-off error.  The covariance functions that we use are of product form, namely,
+The covariance kernels that we use are of product form, namely,
 \begin{equation*}
@@
 \end{align*}
-In this way, the Gram matrix $\rmC_\vtheta$, whose $i,j$-element is $\rC_\vtheta(\vx_i,\vx_j)$ can be constructed with minimal round-off error.
+In this way, the Gram matrix $\rmC_\vtheta$, whose $i,j$-element is $\rC_\vtheta(\vx_i,\vx_j)$ can be constructed in a way that avoids significant cancellation error.
 
@@
 Furthermore, let $K_\vtheta$ be scaled to satisfy \eqref{addAssump}.
-When matched with rank-1 lattice data-sites, $C_\vtheta$ must satisfy assumptions \eqref{fastcompAssump}.
+When matched with rank-1 lattice data sites, $C_\vtheta$ must satisfy assumptions \eqref{fastcompAssump}.
 The cubature, $\hmu$, is just the sample mean.
-The \emph{fast Fourier transform} (FFT) can be used to expedite the estimates of $\vtheta$ in \eqref{fastTheta} and the credible interval widths \eqref{fastStoppingCriterions} so that Algorithm \ref{algorithm2} has a computational cost which is the sum of the following:
+The \emph{fast Fourier transform} (FFT) can be used to expedite the estimates of $\vtheta$ in \eqref{fastTheta} and the credible interval half-widths \eqref{fastStoppingCriterions} so that Algorithm \ref{algorithm2} has a computational cost which is the sum of the following:
 \begin{itemize}
@@
 \begin{equation*}
-\mu := \int_{[0,1]^d} g(\vt) \, \dif \vt
+\mu := \int_{[0,1]^d} g(\vt) \, \dif \vt,
 \end{equation*}
@@
 
-A family of variable transforms that can also preserve continuity of the derivatives that exists in the original integrand $g$ takes the form
+A family of variable transforms that can also preserve continuity of the derivatives from the original integrand $g$ takes the form
 \begin{subequations} %\label{eq:varTrans}
@@
 \end{subequations}
-If for $r \in \natzero$, 
+For $r \in \natzero$, if the following hold:
 \begin{itemize}
-	\item $\Psi \in C^{s+1}[0,1]$,
+	\item $\Psi \in C^{r+1}[0,1]$,
 	\item  $\lim_{x \downarrow 0}x^{-r-1}\Psi'(x) = \lim_{x \uparrow 1} (1-x)^{-r-1}\Psi'(x) = 0$, and 
@@
 This example was already introduced in Section \ref{MVN_example}, where we used the Mat\'ern covariance kernel.
-Here we apply Sidi's $C^2$  periodization to $ f_{\textup{Genz}}$ \eqref{fGenzdef}, choose $d=2$ and $r=2$.
-The simulation results for this example function are summarized in Figures \ref{fig:mvn-guaranteed-MLE}, \ref{fig:mvn-guaranteed-FB}, and \ref{fig:mvn-guaranteed-GCV}.
+Here we apply Sidi's $C^2$  periodization to $ f_{\textup{Genz}}$ \eqref{fGenzdef} and choose $d'=3$, $d=2$, and $r=2$.
+The simulation results for this example are summarized in Figures \ref{fig:mvn-guaranteed-MLE}, \ref{fig:mvn-guaranteed-FB}, and \ref{fig:mvn-guaranteed-GCV}.
 In all cases, the Bayesian cubature returns an approximation within the prescribed error tolerance.
@@
 Since we allow a nonzero mean, this assumption is somewhat more palatable.
-Bayesian algorithms assuming non-Gaussian processes are more difficult, but this is an area for further research.
-
-A noticeable observation from the plots in all three examples is how much the credible interval widths differ from the true error.
-The credible interval widths are not much smaller than $\varepsilon$.
+Bayesian algorithms assuming non-Gaussian processes are more difficult to execute, but this is an area for further research.
+
+A noticeable observation from the plots in all three examples is how much the credible interval half-widths differ from the true error.
+The credible interval half-widths are not much smaller than $\varepsilon$.
 The ratio of the true error to $\varepsilon$ ranges from around one to as small as $10^{-7}$.
-In the latter case, the credible interval widths are quite conservative.
+In the latter case, the credible interval half-widths are quite conservative.
 For option pricing example, this is less serious of an issue than for the multivariate Gaussian and Keister examples.
@@
 The computational cost of the automatic Bayesian cubature can be dramatically reduced if the covariance kernel matches the nodes.
-One such match in practice is rank-1 lattice nodes and shift-invariant kernels.
+One such match in practice is rank-1 lattice nodes and shift-\linebreak[4]invariant kernels.
 The matrix-vector multiplications can be accomplished using the fast Fourier Transform.
@@
 \begin{equation*}
-f = \mathcal{GP} \left( \beta_0 + \beta_1 g_1 + \cdots + \beta_p g_p, s^2 C \right),
+f = \mathcal{GP} \left( \beta_0 + \beta_1 g_1 + \cdots + \beta_p g_p, s^2 C_\vtheta \right),
 \end{equation*}
-for some choice of $g_1, \ldots, g_p$ whose integrals are known, and some parameters $\beta_0, \ldots, \beta_p$ in addition to $s$ and $C$.  The efficacy of this approach has not yet been explored.
+for some choice of $g_1, \ldots, g_p$ whose integrals are known, and some parameters $\beta_0, \ldots, \beta_p$ in addition to $s$ and $C_\vtheta$.
+The efficacy of this approach has not yet been explored.
 

### 2019-07-22 programs/plot_fourier_kernel.m

@@ -1,11 +1,13 @@
 % plots the shift invariant fourier kernel for demo purposes
 function plot_fourier_kernel()
+gail.InitializeDisplay
 
 n = 512;
 shape_param = [0.2 0.8];
 order = [1 2];
 bvec = [0.2 0.8];
 dim = 1;
+yVal = 0.3;
 
 % using uniform points
 l = linspace(0,1,n);
@@ -20,7 +22,7 @@ if dim==1
   leg_text = cell(4,1);
   for r = order
     for sh = shape_param
-      Z(:,i) = kernel(xpts, 2*r, sh);
+      Z(:,i) = kernel(xpts, 2*r, sh, yVal);
       leg_text{i} = sprintf('$r=%d,\\gamma=%1.1f$', r, sh);
       i=i+1;
     end
@@ -28,12 +30,12 @@ if dim==1
 
   plot(xpts,Z)
   xlabel('\(x\)')
-  ylabel('\(C_{\theta}(x,0.3)\)')
+  ylabel(['\(C_{\theta}(x,' num2str(yVal) ')\)'])
   legend(leg_text, 'Interpreter','latex','location','best')
   legend boxoff
   axis tight
 
-  figSavePathName = sprintf('fourier_kernel dim_1.png');
+  figSavePathName = sprintf('fourier_kernel_dim_1.png');
   saveas(hFig, figSavePathName)
 end
 
@@ -44,7 +46,7 @@ if dim==2
     for r = order
       hFig = figure('visible','on');
       set(hFig, 'units', 'inches', 'Position', [4 4 6.5 5.5])
-      Z = kernel([X(:) Y(:)], 2*r, sh);
+      Z = kernel([X(:) Y(:)], 2*r, sh, yVal);
       meshc(X, Y, reshape(Z, [n, n]));
       
       title(sprintf('$r=%d, \\theta$=%0.2f', r, sh), 'Interpreter','latex')
@@ -76,7 +78,7 @@ end
 
 
 % bernoulli polynomial based kernel
-function [K] = kernel(xun,order,a)
+function [K] = kernel(xun,order,a, shift)
 
 constMult = -(-1)^(order/2)*((2*pi)^order)/factorial(order);
 if order == 2
@@ -87,7 +89,7 @@ else
   error('Bernoulli order not implemented !');
 end
 
-xun = mod(xun+0.3, 1);
+xun = mod(xun - shift, 1);
 K = prod(1 + (a)*constMult*bernPloy(xun),2);
 
 end

### 2019-07-22 ResponseToReferees.tex
polishing response

@@
 We have revised our manuscript substantially in response.
-\Response{Specific concerns are addressed point-by-point below in blue.}.
-We hope that all will find the revision satisfactory.
+\Response{Specific concerns are addressed point-by-point below in blue.} We hope that all will find the revision satisfactory.
 
@@
 \Response{We have added some clarification.
-If function evaluation from an expensive simulation takes an 5 minutes for one value, then performing the FFT calculations is going to take less time for practical $n$, say up to a million.}
+If function evaluation from an expensive simulation takes 5 minutes for one value, then performing the FFT calculations is going to take less time for practical $n$, say up to a million.}
 \end{itemize}
@@
 $C$. E.g. in (11) the $\vec{\theta}$ is not visible at all in the expression to be
-minimized for it. The $C$ without subscript also clashes that of lemma 1. \Response{$\vec{\theta}$ has been added as much as possible, and particularly into the equations where there is optimization.}
+minimized for it.
+The $C$ without subscript also clashes that of lemma 1.
+\Response{$\vec{\theta}$ has been added as much as possible, and particularly into the equations where there is optimization.
+However, $\vec{\theta}$ has been omitted in places where it would clutter the derivation.}
 \item  The lead in to lemma 1 makes it feel like this is a field specific lemma but
@@
 
-\item Section 3.3. Elaborate on what is meant with the second sentence.  \Response{This section re-written and eliminaets this sentence.}
+\item Section 3.3. Elaborate on what is meant with the second sentence.  \Response{This section re-written and eliminates this sentence.}
 
@@
 We do not see how we are introducing significantly more numerical error elsewhere.
-We are basically pulling a large constant matrix one out of the Gram matrix.
+We are basically pulling the constant matrix one out of the Gram matrix.
 Then the FFT of the first column is not essentially $n$.
@@
 \item Sec.\ 2.2.1, 2.2.2 I suggest to include some references for the results that are presented in Sections 2.2.1 and 2.2.2.
-\Response{Our knowledge of the literature is limited, but much of what we read assumes a zero mean for the Gaussian process.
+\Response{Our knowledge of the literature is limited, but much of what we read assumes a zero mean for the Gaussian process, which simplifies the derivations and leads to somewhat different results.
 We would welcome sources to cite that consider our setting.}
@@
 \item Sec.\ 5.1 Is there some kind of a universal periodization that ‘works’ for every value of $r$?
-\Response{One could choose an infinitely smooth periodization, but this would change the integrand to potentially make its covariance $s$ large.
+\Response{One could choose an infinitely smooth periodization, but this would change the integrand to potentially make its implied covariance scaling, $s$, large.
 This is mentioned at the end of Section 5.1.}
@@
 \renewcommand{\labelenumi}{\arabic{enumi}.}
-    \item The results in Section 2.2.2 were confusing. \ldots \Response{This has been re-written}
+    \item The results in Section 2.2.2 were confusing. \ldots \Response{This has been re-written.}
 

### 2019-07-22 BayesianCubaturePaper2018 - Rev1b.tex
fixing typos

@@
 \end{align*}
-A credible interval for the integral is given given by 
+A credible interval for the integral is given by 
 \begin{subequations} \label{eqn_prob_confidence_interval}
@@
 
-Because $\mK_\vtheta$ is circulant, we know the form of it's eigevector-eigenvalue decomposition:
+Because $\mK_\vtheta$ is circulant, we know the form of it's eigenvector-eigenvalue decomposition:
 \begin{equation} \label{Keig}
@@
 \end{equation}
-By \eqref{shInvKernGramMatrix} we then have the eigevector-eigenvalue decomposition for $\mC_{\vtheta}$ assumed in \eqref{eqn:ftk_factor}, namely
+By \eqref{shInvKernGramMatrix} we then have the eigenvector-eigenvalue decomposition for $\mC_{\vtheta}$ assumed in \eqref{eqn:ftk_factor}, namely
 \begin{equation} \label{Clateig}

### 2019-07-23 BayesianCubaturePaper2018 - Rev1b.tex
fixing more typos

@@
 We used the Sidi's $C^1$ periodization, dimension $d=4$, and $r=2$.
-As we can see, the GCV stopping criterion achieves faster results than the other stopping criteria, similarly to the multivariate Gaussian case.
+As we can see, the GCV stopping criterion achieves results faster than the other stopping criteria, similar to the multivariate Gaussian case.
 The credible intervals are narrower than the multivariate Gaussian case since the covariance kernel is smoother than the periodization transform used.
@@
 \begin{equation*}
-\mu = \int_{\reals^d} \text{payoff}(\vz) \frac{\exp(\frac 12 \vz^T\mSigma^{-1}\vz)}{\sqrt{(2\pi)^d \det(\mSigma)}} \, \dvz = \int_{[0,1]^d} f(\vx) \, \dvx,
+\mu = \int_{\reals^d} \code{payoff}(\vz) \frac{\exp(\frac 12 \vz^T\mSigma^{-1}\vz)}{\sqrt{(2\pi)^d \det(\mSigma)}} \, \dvz = \int_{[0,1]^d} f(\vx) \, \dvx,
 \end{equation*} 
-where {payoff($\cdot$)} defines the discounted payoff of the option,
+where \code{payoff($\cdot$)} defines the discounted payoff of the option,
 \begin{align*}

### 2019-07-23 BayesianCubaturePaper2018 - Rev1b.tex
final(?)

--- 2019-07-22 BayesianCubaturePaper2018 - Rev1b.tex
@@
 \usepackage{amssymb}
-\usepackage{cite}
+%\usepackage{cite}
 %
@@
 \begin{abstract}
-Automatic cubatures approximate multidimensional integrals to user-specified error tolerances.
+Automatic cubatures approximate integrals to user-specified error tolerances.
 For high dimensional problems, it is difficult to adaptively change the sampling pattern, but one can automatically determine the
@@
 Some stopping criteria for choosing $n$ are heuristic.
-Other rigorous algorithms satisfying \eqref{eqn:err_crit}  require strong a priori assumptions about the integrand, such as an upper bound on its variance (for simple Monte Carlo) or total variation (for quasi-Monte Carlo).
+Rigorous algorithms satisfying \eqref{eqn:err_crit}  typically require strong a priori assumptions about the integrand, such as an upper bound on its variance (for simple Monte Carlo) or total variation (for quasi-Monte Carlo).
 We take a Bayesian approach by constructing a stopping criterion that is based on a credible interval.
@@
 
-We assume that the integrand, $f$, is an instance of a Gaussian stochastic process  i.e., $f \sim \mathcal{GP}(m,s^2 C_\vtheta)$  \cite{BriEtal18a, Dia88a, OHa91a, Rit00a, RasGha03a}.
+We assume that the integrand, $f$, is an instance of a Gaussian stochastic process  i.e., $f \sim \mathcal{GP}(m,s^2 C_\vtheta)$  \cite{BriEtal18a,Dia88a,OHa91a,Rit00a,RasGha03a}.
 Specifically, $f$ is a real-valued random function with constant mean $m$ and covariance kernel $s^2C_\vtheta$:
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-The empirical Bayes approach estimates the parameters, $m$, $s$, and $\vtheta$ via maximum likelihood estimation.  The log-likelihood function of the parameters given the function data $\vy$ is:
+The empirical Bayes approach estimates the parameters, $m$, $s$, and $\vtheta$ via maximum likelihood estimation.  The log-likelihood function of the parameters given the integrand data $\vy$ is:
 \begin{multline*}
@@
 \end{multline*}
-where $\rho_{m, s^2 | \vf}$ is the posterior density of the hyperparameters given the function data. Bayes Theorem tells us that $\rho_{m, s^2 | \vf} \propto \rho_{\vf | m, s^2} \, \vrho_{m,s^2}$, so 
+where $\rho_{m, s^2 | \vf}$ is the posterior density of the hyperparameters given the integrand data.
+Bayes Theorem tells us that $\rho_{m, s^2 | \vf} \propto \rho_{\vf | m, s^2} \, \vrho_{m,s^2}$, so
 \begin{align}
@@
 \begin{itemize}
-	\item $\Order\bigl(n\$(f) \bigr)$ for the function data, where $\$(f)$ is the computational cost of a single $f(\vx)$; $\$(f)$ may be large if it is the result of an expensive simulation; $\$(f)$ is typically proportional to $d$;
+	\item $\Order\bigl(n\$(f) \bigr)$ for the integrand data, where $\$(f)$ is the computational cost of a single $f(\vx)$; $\$(f)$ may be large if it is the result of an expensive simulation; $\$(f)$ is typically proportional to $d$;
 
@@
 \begin{theorem} \label{thm:fastparam}
-Under assumptions \eqref{fastcompAssump}, the parameters and credible interval half-widths in Theorem \ref{thm:param} may be expressed in terms of the fast transforms of the function data, the first column of the Gram matrix, and $\vc_\vtheta$ as follows:
+Under assumptions \eqref{fastcompAssump}, the parameters and credible interval half-widths in Theorem \ref{thm:param} may be expressed in terms of the fast transforms of the integrand data, the first column of the Gram matrix, and $\vc_\vtheta$ as follows:
 \begin{align}
@@
 \begin{itemize}
-	\item $\Order\bigl(n\$(f) \bigr)$ for the function data, where $\$(f)$ is the computational cost of a single $f(\vx)$;
+	\item $\Order\bigl(n\$(f) \bigr)$ for the integrand data, where $\$(f)$ is the computational cost of a single $f(\vx)$;
 
@@
 
-A noticeable observation from the plots in all three examples is how much the credible interval half-widths differ from the true error.
-The credible interval half-widths are not much smaller than $\varepsilon$.
-The ratio of the true error to $\varepsilon$ ranges from around one to as small as $10^{-7}$.
-In the latter case, the credible interval half-widths are quite conservative.
-For option pricing example, this is less serious of an issue than for the multivariate Gaussian and Keister examples.
-A possible reason is that the latter integrands are significantly smoother than the covariance kernel assumed.
+A noticeable observation from the plots in all three examples is how the ratio of the true error to the error tolerance varies from nearly one all the way down to $10^{-7}$.
+Since the credible interval half-widths are not much smaller than $\varepsilon$, this means that the credible intervals are quite conservative in many cases.
+For option pricing example, this is less of an issue than for the multivariate Gaussian and Keister examples.
+The reason that the credible intervals wildy overestimate the true error for the multivariate Gaussian and Keister examples may be that these integrands are significantly smoother than the assumed covariance kernel.
 This is a matter for further investigation.

### 2019-07-23 BayesianCubaturePaper2018 - Rev1b.tex
rephrase the caption

@@
 		\includegraphics[width=0.95\linewidth]{MVN_rapid_n_vs_time_Matern_d2_2019-Jun-29}
-	\caption{Multivariate Gaussian probability estimated using Mat\'ern kernel with $d=2$ using the empirical Bayes stopping criterion.
-Top: Ratio of the integration error to the error tolerance versus execution time.
+	\caption{Multivariate Gaussian probability in $d=2$ estimated using Mat\'ern kernel and empirical Bayes stopping criterion.
+Top: Ratio of the integration error to the error-tolerance versus execution time.
 Bottom: Execution time rapidly increases with increasing $n$.

### 2019-07-29 BayesianCubaturePaper2018 - Rev1b.tex
Editor's comments except the one-column format

@@
 	%\end{subfigure}
-	\caption{The $d'=3$ multivariate Gaussian probability transformed to an integral of $f_{\text{Genz}}$ of $d=2$. This plot can be reproduced using \code{IntegrandPlots.m} in GAIL}
+	\caption{The $d'=3$ multivariate Gaussian probability transformed to an integral of $f_{\text{Genz}}$ of $d=2$. This plot can be reproduced using \code{IntegrandPlots.m} in GAIL.}
 	\label{fig:MVN_Genz}
@@
 Now we explain how to speed up the calculations.
-A key is to choose covariance kernels that match the nodes, $\{\vx_i\}_{i=1}^n$, so that the vector-matrix operations required by Bayesian cubature can be accomplished using fast transforms at a computational cost of $\Order\bigl(n \$(f) + N_{\opt} [n \$(C_\vtheta)  + n \log(n)] \bigr)$.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Fast Transform Kernel}
+A key is to choose covariance kernels that match the nodes, $\{\vx_i\}_{i=1}^n$, so that the vector-matrix operations required by Bayesian cubature can be accomplished using fast Bayesian transforms at a computational cost of $\Order\bigl(n \$(f) + N_{\opt} [n \$(C_\vtheta)  + n \log(n)] \bigr)$.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Fast Bayesian Transform Kernel}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \end{subequations}
-We call the transformation $\vb \mapsto \mV^H \vb$ a \emph{fast transform} and $C_\vtheta$ a \emph{fast transform kernel}.
-
-Under assumptions \eqref{fastcompAssump} the eigenvalues may be identified as the fast transform of the first column of $\mC$:
+We call the transformation $\vb \mapsto \mV^H \vb$ a \emph{fast Bayesian transform} and $C_\vtheta$ a \emph{fast Bayesian transform kernel}.
+
+Under assumptions \eqref{fastcompAssump} the eigenvalues may be identified as the fast Bayesian transform of the first column of $\mC$:
 \begin{align}
@@
 where $\mathsf{I}$ is the identity matrix and $\vv_1^*$ is the complex conjugate of the first row of $\mV$.
-Also note that the fast transform of $\vone$ has a simple form
+Also note that the fast Bayesian transform of $\vone$ has a simple form
 \begin{align*} 
@@
 \begin{theorem} \label{thm:fastparam}
-Under assumptions \eqref{fastcompAssump}, the parameters and credible interval half-widths in Theorem \ref{thm:param} may be expressed in terms of the fast transforms of the integrand data, the first column of the Gram matrix, and $\vc_\vtheta$ as follows:
+Under assumptions \eqref{fastcompAssump}, the parameters and credible interval half-widths in Theorem \ref{thm:param} may be expressed in terms of the fast Bayesian transforms of the integrand data, the first column of the Gram matrix, and $\vc_\vtheta$ as follows:
 \begin{align}
@@
 We  also want to satisfy assumption \eqref{addAssump}.
-To conveniently facilitate the fast transform, it is assumed in this section and the next that $n$ is power of $2$.  
-%To facilitate the fast transform, $n$ must be power of $2$.
+To conveniently facilitate the fast Bayesian transform, it is assumed in this section and the next that $n$ is power of $2$.  
+%To facilitate the fast Bayesian transform, $n$ must be power of $2$.
 
@@
 
-Assumptions \eqref{fastcompAssumpA} and \eqref{fastcompAssumpB} can be verified by \eqref{PermMat}, \eqref{Keig}, and \eqref{Clateig}.
+Fast Bayesian transform assumptions \eqref{fastcompAssumpA} and \eqref{fastcompAssumpB} can be verified by \eqref{PermMat}, \eqref{Keig}, and \eqref{Clateig}.
 Assumption \eqref{fastcompAssumpC} is satisfied because $\mV^H \vb = \mW^H \mP^T \vb$ is just the discrete Fourier transform of a vector whose rows have been permuted.
@@
 Furthermore, let $K_\vtheta$ be scaled to satisfy \eqref{addAssump}.
-When matched with rank-1 lattice data sites, $C_\vtheta$ must satisfy assumptions \eqref{fastcompAssump}.
+When matched with rank-1 lattice data sites, $C_\vtheta$ must satisfy fast Bayesian transform assumptions \eqref{fastcompAssump}.
 The cubature, $\hmu$, is just the sample mean.
@@
 
-The Baker's transform, also called tent transform,
+The baker's transform, also called tent transform,
 \begin{multline} \label{eq:bakerTrans}
@@
 
-Three integrals were evaluated using the GAIL algorithm \code{cubBayesLattice\_g}:  a multivariate Gaussian \linebreak[4] probability, the Keister's example, and an option pricing example.  
+Three integrals were evaluated using the GAIL algorithm \code{cubBayesLattice\_g}:  a multivariate Gaussian \linebreak[4] probability, Keister's example, and an option pricing example. 
+These three integrands are defined below.
 The sequences $\{\vx_i\}_{i=1}^\infty$ are the randomly shifted lattice node sequences supplied by GAIL. 
@@
 Figures \ref{fig:keister-guaranteed-MLE}, \ref{fig:keister-guaranteed-FB}, and \ref{fig:keister-guaranteed-GCV} summarize the numerical tests for this integral.
-We used the Sidi's $C^1$ periodization, dimension $d=4$, and $r=2$.
+We used Sidi's $C^1$ periodization, dimension $d=4$, and $r=2$.
 As we can see, the GCV stopping criterion achieves results faster than the other stopping criteria, similar to the multivariate Gaussian case.
@@
 Moreover, $\mL$ is chosen to be the matrix of eigenvectors of $\mSigma$ times the square root of the diagonal matrix of eigenvalues of $\mSigma$. 
-Because the integrand has a kink caused by the $\max$ function, it does not help to use a periodizing transform that is very smooth.  We choose the Baker's transform \eqref{eq:bakerTrans} and $r = 1$.
+Because the integrand has a kink caused by the $\max$ function, it does not help to use a periodizing transform that is very smooth.  We choose the baker's transform \eqref{eq:bakerTrans} and $r = 1$.
 
@@
 Digital sequences and digital shift and/or scramble invariant kernels have the potential of being another match that satisfies the conditions in Section \ref{sec:fast_BC}.
-The fast transform would correspond to a fast Walsh transform.
+The fast Bayesian transform would correspond to a fast Walsh transform.
 

### 2019-07-29 BayesianCubaturePaper2018 - Rev1b.tex

@@
 %
-%\documentclass{svjour3}                     % onecolumn (standard format)
+\documentclass{svjour3}                     % onecolumn (standard format)
 %\documentclass[smallcondensed]{svjour3}     % onecolumn (ditto)
 %\documentclass[smallextended]{svjour3}       % onecolumn (second format)
-\documentclass[twocolumn]{svjour3}          % twocolumn
+%\documentclass[twocolumn]{svjour3}          % twocolumn
 %
@@
 	then 
-	\begin{multline*}
-	\vY_1 \vert \vY_2 \; \sim \; \calN \bigl(\vm_1 + \mSigma_{21}^T \mSigma_{22}^{-1}(\vY_2 - \vm_2), \\ \mSigma_{11} - \mSigma_{21}^T \mSigma_{22}^{-1} \mSigma_{21} \bigr).
-	\end{multline*}
+	\begin{align*}
+	\vY_1 \vert \vY_2 \; \sim \; \calN \bigl(\vm_1 + \mSigma_{21}^T \mSigma_{22}^{-1}(\vY_2 - \vm_2),  \; \mSigma_{11} - \mSigma_{21}^T \mSigma_{22}^{-1} \mSigma_{21} \bigr).
+	\end{align*}
 Moreover, the inverse of the matrix $\mSigma$ may be partitioned as
@@
 It follows from Lemma \ref{thrm:condDist} that the \emph{conditional} distribution of the integral given observed function values, $\vf = \vy$ is also Gaussian:
-\begin{multline} \label{eqn:condInteg}
+\begin{align} \label{eqn:condInteg}
 \mu | (\vf = \vy) \sim \calN \bigl(m (1 - \vc_\vtheta^T \mCtheta^{-1} \vone)  + \vc_\vtheta^T \mCtheta^{-1} \vy, 
-\\
+\;
 s^2(c_{0\vtheta}  -\vc_\vtheta ^T \mCtheta^{-1} \vc_\vtheta) \bigr).
-\end{multline}
+\end{align}
 The natural choice for  the cubature is the posterior mean of the integral, namely, 
@@
  s^2_{\textup{GCV}} & = \vy^T \left[\mC_\vtheta^{-2} - \frac{\mC_\vtheta^{-2} \vone \vone^T \mC_\vtheta^{-2}}{\vone^T \mC_\vtheta^{-2} \vone}  \right] \vy  \left[ \trace(\mC_\vtheta^{-1}) \right]^{-1}, \\
-\nonumber
+\label{eqn:thetaMLE}
 \vtheta_\MLE
@@
 \right] \vy 
-\right)  \\
-\label{eqn:thetaMLE}
- & \qquad \qquad +  \frac{1}{n} \log(\det(\mC_\vtheta))
+\right)  
+ +  \frac{1}{n} \log(\det(\mC_\vtheta))
 \biggr \}, \\
-\nonumber
-\vtheta_{\GCV} &= \argmin_\vtheta \biggl\{\log \left(  \vy^T \left[\mC^{-2}_\vtheta - \frac{\mC^{-2}_\vtheta \vone \vone^T \mC^{-2}_\vtheta}{\vone^T \mC^{-2}_\vtheta \vone}  \right] \vy \right)  \\
 \label{vthetaGCV}
-& \qquad \qquad - \log \left ( \trace(\mC^{-2}_\vtheta) \right ) \biggr\}, \\
+\vtheta_{\GCV} &= \argmin_\vtheta \biggl\{\log \left(  \vy^T \left[\mC^{-2}_\vtheta - \frac{\mC^{-2}_\vtheta \vone \vone^T \mC^{-2}_\vtheta}{\vone^T \mC^{-2}_\vtheta \vone}  \right] \vy \right)  
+ - \log \left ( \trace(\mC^{-2}_\vtheta) \right ) \biggr\}, \\
 \label{eqn:cubMLE}
@@
 \intertext{The credible intervals widths, $\err_{\textup{CI}}$, are given by}
-\nonumber
-\err_{\mathsf{x}} & = 2.58 s_{\mathsf{x}} \sqrt{c_{0\vtheta} - \vc_{\vtheta}^T\mC_\vtheta^{-1}\vc_{\vtheta} }, \\
-& \hspace{3.5cm} \mathsf{x} \in \{\MLE, \GCV\},  \label{eqn:err_MLEGCV}\\ 
+\label{eqn:err_MLEGCV}
+\err_{\mathsf{x}} & = 2.58 s_{\mathsf{x}} \sqrt{c_{0\vtheta} - \vc_{\vtheta}^T\mC_\vtheta^{-1}\vc_{\vtheta} }, \qquad \mathsf{x} \in \{\MLE, \GCV\},  \\ 
 \err_{\textup{full}} 
@@
 The resulting credible intervals are then
-\begin{multline}
+\begin{align}
 \label{eqn_prob_CI}
 \mathbb{P}_f \left[
-|\mu-\hmu_{\mathsf{x}}| \leq \err_{\mathsf{x}} \right]  = 99\%, \\ \mathsf{x} \in \{\MLE, \full, \GCV\}.
-\end{multline}
+|\mu-\hmu_{\mathsf{x}}| \leq \err_{\mathsf{x}} \right]  = 99\%, \qquad \mathsf{x} \in \{\MLE, \full, \GCV\}.
+\end{align}
 Here $t_{n-1,0.995}$ denotes the $99.5$ percentile of a standard Student's $t$-distribution with $n-1$ degrees of freedom.
@@
 This may be expressed as
-\begin{multline*}
+\begin{align*}
     \rho_{\mu|\vf}(z | \vy) 
 = \int_{0}^\infty \int_{-\infty}^\infty 
-\rho_{\mu | m, s^2, \vf}(z | \xi, \lambda , \vy) \\
-\times  \rho_{m, s^2 | \vf}(\xi, \lambda | \vy)  \, \D \xi \D \lambda, 
-\end{multline*}
+\rho_{\mu | m, s^2, \vf}(z | \xi, \lambda , \vy)  
+\rho_{m, s^2 | \vf}(\xi, \lambda | \vy)  \, \D \xi \D \lambda, 
+\end{align*}
 where $\rho_{m, s^2 | \vf}$ is the posterior density of the hyperparameters given the integrand data.
 Bayes Theorem tells us that $\rho_{m, s^2 | \vf} \propto \rho_{\vf | m, s^2} \, \vrho_{m,s^2}$, so
-\begin{align}
+\begin{align*}
 \nonumber 
@@
 & = \int_{0}^\infty \int_{-\infty}^\infty 
-\rho_{\mu | m, s^2, \vf}(z | \xi, \lambda , \vy) \\
-\nonumber
-& \qquad \times  \rho_{\vf | m, s^2} (\vy | \xi, \lambda) \, \vrho_{m,s^2}(\xi,\lambda)  \, \D \xi \D \lambda \\
+\rho_{\mu | m, s^2, \vf}(z | \xi, \lambda , \vy) 
+\rho_{\vf | m, s^2} (\vy | \xi, \lambda) \, \vrho_{m,s^2}(\xi,\lambda)  \, \D \xi \D \lambda \\
 \nonumber
 & \propto \left( 1 +  \frac{(z - \hmu_{\MLE})^2}{(n-1) \hsigma_{\textup{full}}^2} \right)^{-n/2},
-\end{align}
+\end{align*}
 where $\hsigma_{\textup{full}}^2$ is given in Theorem \ref{thm:param}, and the result above is derived in Appendix \ref{appendix:full_bayes}.
@@
 \begin{align}
-\nonumber
+\label{eqn_MLE_loss_func_optimized_2}
 \vtheta_\MLE
@@
 \sum_{i=2}^n \frac{\abs{\widetilde{y}_i}^2}{\lambda_{\vtheta, i}}
-\right) \right .\\ 
-\label{eqn_MLE_loss_func_optimized_2} %
-& \hspace{3cm} \left .
+\right) 
  + \frac{1}{n}\sum_{i=1}^n \log(\lambda_{\vtheta,i})
 \right],\\
-\nonumber 
+\label{thetaGCV} 
 \vtheta_{\GCV} 
 &= \argmin_\vtheta \left[ \log \left ( \sum_{i=2}^n \frac{\abs{\widetilde{y}_i}^2}{\lambda_{\vtheta, i}^2} 
-\right) \right .\\
-\label{thetaGCV}
-& \qquad \qquad \qquad \qquad  \left . -2\log\left( \sum_{i=1}^n \frac{1}{\lambda_{\vtheta, i}} \right)
+\right)  
+-2\log\left( \sum_{i=1}^n \frac{1}{\lambda_{\vtheta, i}} \right)
 \right], 
@@
 \err_{\textup{GCV}} & =
-\frac{2.58}{n}\left\{\sum_{i=2}^n \frac{\abs{\widetilde{y}_i}^2}{\lambda_i^2}  \left [ \frac 1n \sum_{i=1}^n \frac{1}{\lambda_i} \right]^{-1} \right.
-\\ 
-\nonumber
-&\qquad \qquad \left . \times
+\frac{2.58}{n}\left\{\sum_{i=2}^n \frac{\abs{\widetilde{y}_i}^2}{\lambda_i^2}  \left [ \frac 1n \sum_{i=1}^n \frac{1}{\lambda_i} \right]^{-1} 
 \left( c_0 - \frac 1n \sum_{i=1}^n \frac{\abs{\widetilde{c}_i}^2}{\lambda_i} \right) 
@@
 \frac{2.58}{n}\left\{\sum_{i=2}^n \frac{\abs{\widetilde{y}_i}^2}{\lambda_i^2}  \left [ \frac 1n \sum_{i=1}^n \frac{1}{\lambda_i} \right]^{-1} 
-\right. \\ &\hspace{3cm} \left . \times
 \left( 1 -  \frac{n}{\lambda_1} \right)  
@@
 Note that 
-\begin{multline} \label{phiprop}
-n\phi:\{0, \ldots, n-1 \} \to \{0, \ldots, n-1\} \\
+\begin{align} \label{phiprop}
+n\phi:\{0, \ldots, n-1 \} \to \{0, \ldots, n-1\} \quad
 \text{is one-to-one},
-\end{multline}
+\end{align}
 assuming $n$ is a power of $2$.
@@
 \nonumber
-& = \Bigl ( K_\vtheta \bigl(\vh(\phi(i-1) - \phi(j-1) \bigr) \bmod \vone ) \Bigr)_{i, j = 1}^n \\
-\nonumber
-& \qquad \qquad  \text{by \eqref{eqn:lattice_def} and \eqref{eq:shInv}}  \\
+& = \Bigl ( K_\vtheta \bigl(\vh(\phi(i-1) - \phi(j-1) \bigr) \bmod \vone ) \Bigr)_{i, j = 1}^n 
+\qquad  \text{by \eqref{eqn:lattice_def} and \eqref{eq:shInv}}  \\
 \nonumber
@@
 \sum_{i',j'=1}^n \delta_{n\phi(i-1), i'-1}  \,
-K_\vtheta \bigl (\vh (i'-j')/n \bmod \vone \bigr )\\
-\nonumber
-& \qquad \qquad \times \delta_{j'-1,n\phi(j-1)} 
+K_\vtheta \bigl (\vh (i'-j')/n \bmod \vone \bigr )
+\delta_{j'-1,n\phi(j-1)} 
 \biggr)_{i,j=1}^n \\
@@
 The baker's transform, also called tent transform,
-\begin{multline} \label{eq:bakerTrans}
-\vPsi: \vx \mapsto (\Psi(x_1),  \ldots, \Psi(x_d)), \\ \Psi(x)  =1 - 2 \abs{x - 1/2},
-\end{multline}
+\begin{align} \label{eq:bakerTrans}
+\vPsi: \vx \mapsto (\Psi(x_1),  \ldots, \Psi(x_d)),  \Psi(x)  =1 - 2 \abs{x - 1/2},
+\end{align}
 allows us to write $\mu$ in the form of \eqref{eqn:defn_mu}, where $f(\vx) = g(\vPsi(\vx))$.  Since  $\Psi'(x)$ is not continuous, $f$ does not have continuous derivatives.
@@
 
-Three integrals were evaluated using the GAIL algorithm \code{cubBayesLattice\_g}:  a multivariate Gaussian \linebreak[4] probability, Keister's example, and an option pricing example. 
+Three integrals were evaluated using the GAIL algorithm \code{cubBayesLattice\_g}:  a multivariate Gaussian  probability, Keister's example, and an option pricing example. 
 These three integrands are defined below.
@@
 
-Figures \ref{fig:mvn-guaranteed-MLE} to \ref{fig:optprice-guaranteed-GCV} can be reproduced using the script \code{cubBayesLattice\_guaranteed\_plots.m} in GAIL.
+Figures \ref{fig:mvn-guaranteed-MLE} to \ref{fig:optprice-guaranteed-GCV} can be reproduced using the script \break \code{cubBayesLattice\_guaranteed\_plots.m} in GAIL.
 
@@
 & = \int_{[0,1]^d} f_{\textup{Keister}}(\vx) \, \dvx,\\
-\intertext{where }
+\text{where } \qquad \qquad & \\
 f_\textup{Keister}(\vx) &= \pi^{d/2} \cos\left(\norm{ \Phi^{-1}(\vx)/2}\right)  ,
@@
 I_s(1) &= \int_{x=0}^\infty \exp(-\vx^T\vx)\sin(\vx) \, \dvx 
-\\
-& =  0.4244363835020225,
+\; = \;  0.4244363835020225,
 \\
@@
 & \propto \int_{0}^\infty \int_{-\infty}^\infty 
-\rho_{\mu | m, s^2, \vf}(z | \xi, \lambda , \vy) \\
-& \qquad \times  \rho_{\vf | m, s^2} (\vy | \xi, \lambda) \, \vrho_{m,s^2}(\xi,\lambda)  \, \D \xi \D \lambda \\
-& \propto \displaystyle \int_{0}^\infty  \frac{1}{\lambda^{(n+3)/2}} \cdots \\
-& \cdots \int_{-\infty}^\infty  \exp \biggl( -\frac{1}{2\lambda}\biggl\{
+\rho_{\mu | m, s^2, \vf}(z | \xi, \lambda , \vy) 
+  \rho_{\vf | m, s^2} (\vy | \xi, \lambda) \, \vrho_{m,s^2}(\xi,\lambda)  \, \D \xi \D \lambda \\
+& \propto \displaystyle \int_{0}^\infty  \frac{1}{\lambda^{(n+3)/2}} 
+ \int_{-\infty}^\infty  \exp \biggl( -\frac{1}{2\lambda}\biggl\{
 \frac{
@@
 \text{by \eqref{eqn:fGaussDist}, \eqref{eqn:condInteg}} \; \text{and} \; \rho_{m,s^2}(\xi,\lambda) \propto 1/\lambda \\
-& \propto \displaystyle \int_{0}^\infty  \frac{1}{\lambda^{(n+3)/2}}  \cdots  \\ 
-& \qquad  \cdots  \int_{-\infty}^\infty  \exp\left( -\frac{\alpha \xi^2 -2 \beta \xi + \gamma}{2\lambda(c_0  -\vc ^T \mC^{-1} \vc)} \right) \, \D \xi \D \lambda,
+& \propto \displaystyle \int_{0}^\infty  \frac{1}{\lambda^{(n+3)/2}} 
+\int_{-\infty}^\infty  \exp\left( -\frac{\alpha \xi^2 -2 \beta \xi + \gamma}{2\lambda(c_0  -\vc ^T \mC^{-1} \vc)} \right) \, \D \xi \D \lambda,
 \end{align*}
@@
 \alpha & = (1 - \vc^T \mC^{-1} \vone)^2 + \vone^T \mC^{-1} \vone (c_0  -\vc ^T \mC^{-1} \vc),\\
-\beta & =(1 - \vc^T \mC^{-1} \vone)(z - \vc^T \mC^{-1} \vy ) \\
-& \qquad \qquad  + \vone^T \mC^{-1} \vy (c_0  -\vc ^T \mC^{-1} \vc),\\
+\beta & =(1 - \vc^T \mC^{-1} \vone)(z - \vc^T \mC^{-1} \vy )  
++ \vone^T \mC^{-1} \vy (c_0  -\vc ^T \mC^{-1} \vc),\\
 \gamma &  = (z - \vc^T \mC^{-1} \vy )^2  + \vy^T \mC^{-1} \vy (c_0  -\vc ^T \mC^{-1} \vc).
@@
 \MoveEqLeft{\rho_{\mu|\vf}(z | \vy)} \\
-& \propto \displaystyle \int_{0}^\infty  \frac{1}{\lambda^{(n+3)/2}}  \exp\left( -\frac{  \gamma - \beta^2/\alpha}{2\lambda(c_0  -\vc ^T \mC^{-1} \vc)} \right)  \cdots \\
-& \qquad \qquad \cdots \int_{-\infty}^\infty  \exp\left( -\frac{\alpha (\xi -\beta/\alpha)^2}{2\lambda(c_0  -\vc ^T \mC^{-1} \vc)} \right) \, \D \xi \D \lambda \\
+& \propto \displaystyle \int_{0}^\infty  \frac{1}{\lambda^{(n+3)/2}}  \exp\left( -\frac{  \gamma - \beta^2/\alpha}{2\lambda(c_0  -\vc ^T \mC^{-1} \vc)} \right)  
+\int_{-\infty}^\infty  \exp\left( -\frac{\alpha (\xi -\beta/\alpha)^2}{2\lambda(c_0  -\vc ^T \mC^{-1} \vc)} \right) \, \D \xi \D \lambda \\
 & \propto \displaystyle \int_{0}^\infty  \frac{1}{\lambda^{(n+2)/2}}  \exp\left( -\frac{  \gamma - \beta^2/\alpha}{2\lambda(c_0  -\vc ^T \mC^{-1} \vc)} \right) \D \lambda \\
-& \propto \left(\gamma - \frac{\beta^2}{\alpha}\right)^{-n/2} \propto \left(\alpha \gamma - \beta^2\right)^{-n/2}.
+& \propto \left(\gamma - \frac{\beta^2}{\alpha}\right)^{-n/2} \\
+& \propto \left(\alpha \gamma - \beta^2\right)^{-n/2}.
 \end{align*}
@@
 - \frac{ \mC^{-1} \vone\vone^T \mC^{-1}}{\vone^T \mC^{-1} \vone}  \right]\vy
-\\ 
-\times  \left[\frac{(1 - \vc^T \mC^{-1} \vone)^2}{\vone^T \mC^{-1} \vone} + (c_0  -\vc ^T \mC^{-1} \vc) \right].
+\left[\frac{(1 - \vc^T \mC^{-1} \vone)^2}{\vone^T \mC^{-1} \vone} + (c_0  -\vc ^T \mC^{-1} \vc) \right].
 \end{multline*}

### 2019-07-29 BayesianCubaturePaper2018 - Rev1c.tex
single column edits

--- 2019-07-29 BayesianCubaturePaper2018 - Rev1b.tex
@@
 \begin{align}
-\vf  & \sim \calN(m \vone, s^2 \mCtheta), \\
-\nonumber & \qquad \qquad \text{where $\vone$ is a vector of all ones,}\\
+\vf  & \sim \calN(m \vone, s^2 \mCtheta),  \qquad \text{where $\vone$ is a vector of all ones,}\\
 \mu & \sim \calN(m, s^2 c_{0\vtheta}), 
@@
 	\begin{pmatrix}
-	\var(\vY_{1}) & \cov(\vY_{1}, \vY_2) \\ 	\cov(\vY_2,\vY_{1}) & \var(\vY_{2})
+	\var(\vY_{1}) & \cov(\vY_{1}, \vY_2) \\ 	\cov(\vY_2,\vY_{1}) & \var(\vY_{2}),
 	\end{pmatrix} 
@@
 
-\begin{theorem} \label{thm:param} There are at least three approaches to estimating or integrating out the hyperparameters defining the Gaussian process from which the integrand is drawn: empirical Bayes, full Bayes, and generalized cross-\linebreak[4]validation.
+\begin{theorem} \label{thm:param} There are at least three approaches to estimating or integrating out the hyperparameters defining the Gaussian process from which the integrand is drawn: empirical Bayes, full Bayes, and generalized cross-validation.
 Under these three approaches, we have the following:
@@
 \label{eqn:sigma2_full}
-& \times  \left[\frac{(1 - \vc_{\vtheta}^T \mC_\vtheta^{-1} \vone)^2}{\vone^T \mC_\vtheta^{-1} \vone} + (c_{0\vtheta}  -\vc_{\vtheta} ^T \mC_\vtheta^{-1} \vc_{\vtheta}) \right], \\
+& \qquad \qquad \times  \left[\frac{(1 - \vc_{\vtheta}^T \mC_\vtheta^{-1} \vone)^2}{\vone^T \mC_\vtheta^{-1} \vone} + (c_{0\vtheta}  -\vc_{\vtheta} ^T \mC_\vtheta^{-1} \vc_{\vtheta}) \right], \\
 \nonumber
@@
 Let $\mA = \mC^{-1}_\vtheta$, let $\vzeta = \mA (\vy - m \vone)$, and partition $\mC_\vtheta$, $\mA$, and $\vzeta$ as
-\begin{gather*}
+\begin{equation*}
 \mC_\vtheta = \begin{pmatrix} c_{ii}  & \vC_{-i,i}^T \\  \vC_{-i,i} & \mC_{-i,-i}\end{pmatrix}, \qquad
-\mA = \begin{pmatrix} a_{ii}  & \vA_{-i,i}^T \\  \vA_{-i,i} & \mA_{-i,-i}\end{pmatrix}, \\ \vzeta = \begin{pmatrix} \zeta_i   \\  \vzeta_{-i} \end{pmatrix},
-\end{gather*}
+\mA = \begin{pmatrix} a_{ii}  & \vA_{-i,i}^T \\  \vA_{-i,i} & \mA_{-i,-i}\end{pmatrix}, \qquad \vzeta = \begin{pmatrix} \zeta_i   \\  \vzeta_{-i} \end{pmatrix},
+\end{equation*}
 where the subscript $i$ denotes the $i^{\text{th}}$ row or column, and the subscript $-i$ denotes all rows or columns except the $i^{\text{th}}$.
@@
 
-The generic automatic Bayesian cubature algorithm described in the previous section requires $\Order\bigl(n \$(f) + \linebreak[4] N_{\opt} [n^2 \$(C_\vtheta) + n^3]\bigr)$ operations to compute the cubature.
+The generic automatic Bayesian cubature algorithm described in the previous section requires $\Order\bigl(n \$(f) +  N_{\opt} [n^2 \$(C_\vtheta) + n^3]\bigr)$ operations to compute the cubature.
 Now we explain how to speed up the calculations.
@@
 
-We have implemented the fast adaptive Bayesian cubature algorithm in MATLAB as part of the Guaranteed Adaptive Integration Library (GAIL) \cite{ChoEtal17b} as \linebreak[4]  \code{cubBayesLattice\_g}.
+We have implemented the fast adaptive Bayesian cubature algorithm in MATLAB as part of the Guaranteed Adaptive Integration Library (GAIL) \cite{ChoEtal17b} as  \code{cubBayesLattice\_g}.
 This algorithm uses the covariance kernel defined in \eqref{eqn:ourkernel} with  $r=1$ and $2$, and the periodizing variable transforms in  \secref{period_var_tx}.
-The rank-1 lattice node generator is taken from \cite{Nuy17a} \linebreak[4] (\code{exod2\_base2\_m20}).
+The rank-1 lattice node generator is taken from \cite{Nuy17a}  (\code{exod2\_base2\_m20}).
 
@@
 The computational cost of the automatic Bayesian cubature can be dramatically reduced if the covariance kernel matches the nodes.
-One such match in practice is rank-1 lattice nodes and shift-\linebreak[4]invariant kernels.
+One such match in practice is rank-1 lattice nodes and shift-invariant kernels.
 The matrix-vector multiplications can be accomplished using the fast Fourier Transform.

### 2019-07-30 BayesianCubaturePaper2018 - Rev1c.tex
polished

@@
 The \emph{generalized cross-validation} criterion (GCV) replaces the $i^{\text{th}}$ diagonal element of $\mA$ in the denominator by the average diagonal element of $\mA$ \cite{CraWah79a,GolHeaWah79a,Wah90}:
-\begin{align*} 
-\textup{GCV} &
-= \frac{\sum_{i=1}^n\zeta_i^2}{\left(\frac 1n \sum_{i=1}^n a_{ii} \right)^2} \\
-& = \frac{(\vy - m\vone)^T \mC^{-2}_\vtheta (\vy - m \vone)}{\left(\frac 1n \trace(\mC_\vtheta^{-1}) \right)^2}.
-\end{align*}
+\begin{equation*} 
+\textup{GCV}
+= \frac{\sum_{i=1}^n\zeta_i^2}{\left(\frac 1n \sum_{i=1}^n a_{ii} \right)^2} 
+= \frac{(\vy - m\vone)^T \mC^{-2}_\vtheta (\vy - m \vone)}{\left(\frac 1n \trace(\mC_\vtheta^{-1}) \right)^2}.
+\end{equation*}
 
@@
 \allowdisplaybreaks
-\begin{align*}
-\alpha_1& = \Phi(a_1), \qquad \beta_1 = \Phi(b_1),
+\begin{gather*}
+\alpha_1 = \Phi(a_1), \qquad \beta_1 = \Phi(b_1),
 \\
-\alpha_j&(x_1,\dots,x_{j-1}) = 
-\\
-&\; \Phi
+\alpha_j(x_1,\dots,x_{j-1}) = 
+\Phi
 \left(
@@
 \\
-&\hspace{5cm} j=2,\dots,d,
+\hspace{8cm} j=2,\dots,d,
 \\
-\beta_j&(x_1,\dots,x_{j-1}) = 
-\\
-&\; \Phi
+\beta_j(x_1,\dots,x_{j-1}) = 
+\Phi
 \left(
@@
 \\
-&\hspace{5cm} j=2,\dots,d,
-\end{align*}
-\begin{align}
+\hspace{8cm} j=2,\dots,d,
+\end{gather*}
+\begin{equation}
 \label{fGenzdef}
-f_{\text{Genz}}(\vx) = \prod_{j=1}^d [\beta_j(\vx) - \alpha_j(\vx)].
-\end{align}
+f_{\text{Genz}}(\vx) = \prod_{j=1}^d [\beta_j(\vx) - \alpha_j(\vx)],
+\end{equation}
 where $\Phi$ is the univariate cumulative standard Gaussian distribution function.
@@
 \begin{align}
-\nonumber
 \mC = \mC_\vtheta &= \Big(C_\vtheta(\vx_i,\vx_j)\Big)_{i,j=1}^n  = (\vC_1,\dots,\vC_n) 
-\\
 \label{eqn:ftk_factor}
-&= \frac 1n \mV \mLambda \mV^H , 
+= \frac 1n \mV \mLambda \mV^H , 
 \quad \quad \mV^H = n \mV^{-1}, \\
 \nonumber
-\mV &= (\vv_1,\ldots,\vv_n)^T = (\vV_1,\ldots,\vV_n), \\
-\nonumber
-\mC^p  &= \frac 1n \mV \mLambda^{p} \mV^H, \qquad \forall p \in \integers.
+\mV &= (\vv_1,\ldots,\vv_n)^T = (\vV_1,\ldots,\vV_n),
+\qquad
+\mC^p  = \frac 1n \mV \mLambda^{p} \mV^H, \qquad \forall p \in \integers.
 \end{align}
@@
 Under assumptions \eqref{fastcompAssump} the eigenvalues may be identified as the fast Bayesian transform of the first column of $\mC$:
-\begin{align}
-\nonumber
+\begin{equation}
 \vlambda 
-& = \begin{pmatrix}
+= \begin{pmatrix}
 \lambda_1 \\ \vdots \\ \lambda_n
 \end{pmatrix} = \mLambda \vone = \mLambda \vv_1^* 
-= \underbrace{\left( \frac 1n \mV^H  \mV \right) }_{\mathsf{I}} \mLambda \vv_1^* \\
-&= \mV^H \left( \frac 1n \mV \mLambda \vv_1^* \right)
+= \underbrace{\left( \frac 1n \mV^H  \mV \right) }_{\mathsf{I}} \mLambda \vv_1^* 
+= \mV^H \left( \frac 1n \mV \mLambda \vv_1^* \right)
 = \mV^H \vC_1 =  \widetilde{\vC}_1,
 \label{eqn:fast_transform_to_eigvalues}
-\end{align}
+\end{equation}
 where $\mathsf{I}$ is the identity matrix and $\vv_1^*$ is the complex conjugate of the first row of $\mV$.
@@
 \frac{1}{n(n-1)} \sum_{i=2}^n \frac{\abs{\widetilde{y}_i}^2}{\lambda_i}
-\\
-\nonumber
-& \qquad \times
+\times
 \left[\frac{\lambda_1}{n}{\left(1 - \frac{\widetilde{c}_1}{\lambda_1}\right)^2} + \left(c_0  - \frac 1n \sum_{i=1}^n \frac{\abs{\widetilde{c}_i}^2}{\lambda_i}\right) \right], \\
@@
 
-We have implemented the fast adaptive Bayesian cubature algorithm in MATLAB as part of the Guaranteed Adaptive Integration Library (GAIL) \cite{ChoEtal17b} as  \code{cubBayesLattice\_g}.
+We have implemented the fast adaptive Bayesian cubature algorithm in MATLAB as part of the Guaranteed Adaptive Integration Library (GAIL) \cite{ChoEtal17b} as \linebreak[4]  \code{cubBayesLattice\_g}.
 This algorithm uses the covariance kernel defined in \eqref{eqn:ourkernel} with  $r=1$ and $2$, and the periodizing variable transforms in  \secref{period_var_tx}.
@@
 %&\qquad \qquad \qquad   \Psi'(x) = 30x^2(1-x)^2 \\
-\text{Sidi's } C^1 & : \Psi(x) = x - \frac{\sin(2\pi x)}{2 \pi}, \\
-&\qquad \qquad \qquad   \Psi'(x) = 1 - \cos(2\pi x), \\
-\text{Sidi's } C^2 & : \Psi(x) = \frac {8 - 9 \cos(\pi x) + \cos(3 \pi x)}{16} ,  \\
-&\qquad \qquad \Psi'(x) = \frac {3 \pi[3 \sin(\pi x) - \sin(3 \pi x)]}{16}.
+\text{Sidi's } C^1 & : \Psi(x) = x - \frac{\sin(2\pi x)}{2 \pi},  \qquad   \Psi'(x) = 1 - \cos(2\pi x), \\
+\text{Sidi's } C^2 & : \Psi(x) = \frac {8 - 9 \cos(\pi x) + \cos(3 \pi x)}{16} ,  
+ \quad \Psi'(x) = \frac {3 \pi[3 \sin(\pi x) - \sin(3 \pi x)]}{16}.
 \end{align*}
@@
 \begin{align*}
-\mu & =  \int_{\reals^d} \cos(\norm{ \vt}) \exp(-\norm{ \vt }^2) \, \dvt \\
-\nonumber
-%&  = 
-%\int_{\reals^d} \cos(a\norm{ \vt}) \exp(-a^2\norm{ \vt }^2)  a^d \, \dvt \\
-& = \int_{[0,1]^d} f_{\textup{Keister}}(\vx) \, \dvx,\\
-\text{where } \qquad \qquad & \\
+\mu & =  \int_{\reals^d} \cos(\norm{ \vt}) \exp(-\norm{ \vt }^2) \, \dvt 
+ = \int_{[0,1]^d} f_{\textup{Keister}}(\vx) \, \dvx,\\
+\text{where } 
 f_\textup{Keister}(\vx) &= \pi^{d/2} \cos\left(\norm{ \Phi^{-1}(\vx)/2}\right)  ,
@@
 \MoveEqLeft{\rho_{\mu|\vf}(z | \vy)} \\
-& \propto \displaystyle \int_{0}^\infty  \frac{1}{\lambda^{(n+3)/2}}  \exp\left( -\frac{  \gamma - \beta^2/\alpha}{2\lambda(c_0  -\vc ^T \mC^{-1} \vc)} \right)  
+& \propto \displaystyle \int_{0}^\infty  \frac{1}{\lambda^{(n+3)/2}}  \exp\left( -\frac{  \gamma - \beta^2/\alpha}{2\lambda(c_0  -\vc ^T \mC^{-1} \vc)} \right)  \\
+&\qquad \qquad \times
 \int_{-\infty}^\infty  \exp\left( -\frac{\alpha (\xi -\beta/\alpha)^2}{2\lambda(c_0  -\vc ^T \mC^{-1} \vc)} \right) \, \D \xi \D \lambda \\

### 2019-07-30 BayesianCubaturePaper2018 - Rev1c.tex
oops, a bit more
Auto stash before merge of "master" and "origin/master"
a few more typos

@@
 
-The baker's transform, also called tent transform,
+The baker's transform, also called the tent transform,
 \begin{align} \label{eq:bakerTrans}
@@
 	\includegraphics[width=0.95\linewidth]{"Lattice_Keister_guaranteed_time_MLE_C1sin_d4_r2_2019-Jun-27"}
-	\caption[Keister guaranteed:MLE]{Keister example using the empirical Bayes stopping criterion.}
+	\caption[Keister guaranteed:MLE]{Keister's example using the empirical Bayes stopping criterion.}
 	\label{fig:keister-guaranteed-MLE}
@@
 	\includegraphics[width=0.95\linewidth]{"Lattice_Keister_guaranteed_time_full_C1sin_d4_r2_2019-Jun-27"}
-	\caption[Keister guaranteed:FB]{Keister example using the full Bayes stopping criterion.}
+	\caption[Keister guaranteed:FB]{Keister's example using the full Bayes stopping criterion.}
 	\label{fig:keister-guaranteed-FB}
@@
 	\includegraphics[width=0.95\linewidth]{"Lattice_Keister_guaranteed_time_GCV_C1sin_d4_r2_2019-Jun-27"}
-	\caption[Keister guaranteed:GCV]{Keister example using the GCV stopping criterion.}
+	\caption[Keister guaranteed:GCV]{Keister's example using the GCV stopping criterion.}
 	\label{fig:keister-guaranteed-GCV}
@@
 Since the credible interval half-widths are not much smaller than $\varepsilon$, this means that the credible intervals are quite conservative in many cases.
-For option pricing example, this is less of an issue than for the multivariate Gaussian and Keister examples.
-The reason that the credible intervals wildy overestimate the true error for the multivariate Gaussian and Keister examples may be that these integrands are significantly smoother than the assumed covariance kernel.
+For option pricing example, this is less of an issue than for the multivariate Gaussian and Keister's examples.
+The reason that the credible intervals wildy overestimate the true error for the multivariate Gaussian and Keister's examples may be that these integrands are significantly smoother than the assumed covariance kernel.
 This is a matter for further investigation.
@@
 \begin{align*}
-\MoveEqLeft[1]{\rho_{\mu|\vf}(z | \vy)}\\
+\rho_{\mu|\vf}(z | \vy)
 & \propto \int_{0}^\infty \int_{-\infty}^\infty 
@@
 \begin{align*}
-\MoveEqLeft{\rho_{\mu|\vf}(z | \vy)} \\
+\rho_{\mu|\vf}(z | \vy)
 & \propto \displaystyle \int_{0}^\infty  \frac{1}{\lambda^{(n+3)/2}}  \exp\left( -\frac{  \gamma - \beta^2/\alpha}{2\lambda(c_0  -\vc ^T \mC^{-1} \vc)} \right)  \\

### 2019-08-17 BayesianCubaturePaper2018-Rev1eRefs.tex
Updates from Overleaf

--- 2019-07-30 BayesianCubaturePaper2018 - Rev1c.tex
@@
 \usepackage{graphicx}
+\usepackage{natbib}
+\usepackage{xspace}
 \usepackage{amssymb}
@@
 \newtheorem{prop}{Proposition}
-\providecommand{\HickernellFJ}{Hickernell}
+\providecommand{\HickernellFJ}{Hickernell\xspace}
 \newcommand{\bm}[1]{\boldsymbol{#1}}
@@
 where the weights, $w_0$, and  $\vw = (w_i)_{i=1}^n \in \reals^n$, and the nodes, $\{\vx_i\}_{i=1}^n \subset [0,1]^d$, are chosen to make the error, $\abs{\mu - \hmu}$, small.
-The integration domain $[0,1]^d$ is convenient for the low discrepancy node sets \cite{DicEtal14a,SloJoe94} that we use.
+The integration domain $[0,1]^d$ is convenient for the low discrepancy node sets \citep{DicEtal14a,SloJoe94} that we use.
 The nodes are assumed to be deterministic.
@@
 We take a Bayesian approach by constructing a stopping criterion that is based on a credible interval.
-We build upon the work of Briol et al.~\cite{BriEtal18a}, Diaconis~\cite{Dia88a}, O'Hagan~\cite{OHa91a}, Ritter~\cite{Rit00a}, Rasmussen and Ghahramani~\cite{RasGha03a}, and others.
+We build upon the work of \cite{Dia88a}, \cite{OHa91a}, \cite{Rit00a}, \cite{RasGha03a}, \cite{BriEtal18a}, and others.
 Our algorithm is an example of \emph{probabilistic numerics}.
@@
 
-Hickernell~\cite{Hic17a} compares different approaches to cubature error analysis depending on whether the rule is deterministic or random and whether the integrand is assumed to be deterministic or random.
+\cite{Hic17a} compares different approaches to cubature error analysis depending on whether the rule is deterministic or random and whether the integrand is assumed to be deterministic or random.
 Error analysis that assumes a deterministic integrand lying in a Banach space leads to an error bound that is typically impractical for deciding how large $n$ must be to satisfy \eqref{eqn:err_crit}.
@@
 
-Hickernell and Jim\'enez-Rugama~\cite{HicJim16a,JimHic16a} have developed stopping criteria for cubature rules based on low discrepancy nodes by tracking the decay of the discrete Fourier coefficients of the integrand.
+\cite{HicJim16a} and \cite{JimHic16a} have developed stopping criteria for cubature rules based on low discrepancy nodes by tracking the decay of the discrete Fourier coefficients of the integrand.
 The algorithm proposed here also relies on discrete Fourier coefficients, but in a different way.
@@
 
-We assume that the integrand, $f$, is an instance of a Gaussian stochastic process  i.e., $f \sim \mathcal{GP}(m,s^2 C_\vtheta)$  \cite{BriEtal18a,Dia88a,OHa91a,Rit00a,RasGha03a}.
+We assume that the integrand, $f$, is an instance of a Gaussian stochastic process  i.e., $f \sim \mathcal{GP}(m,s^2 C_\vtheta)$  \citep{Dia88a,OHa91a,Rit00a,RasGha03a,BriEtal18a}.
 Specifically, $f$ is a real-valued random function with constant mean $m$ and covariance kernel $s^2C_\vtheta$:
@@
 
-\begin{lemma} \cite[(A.6), (A.11--13)]{RasWil06a} \label{thrm:condDist} If $\vY = (\vY_1, \vY_2)^T \sim \calN (\vm,\mSigma)$, where $\vY_1$ and $\vY_2$ are random vectors of arbitrary length, and 
+\begin{lemma} \citep[(A.6), (A.11--13)]{RasWil06a} \label{thrm:condDist} If $\vY = (\vY_1, \vY_2)^T \sim \calN (\vm,\mSigma)$, where $\vY_1$ and $\vY_2$ are random vectors of arbitrary length, and 
 	\begin{gather*}
@@
 \end{align*}
-The \emph{generalized cross-validation} criterion (GCV) replaces the $i^{\text{th}}$ diagonal element of $\mA$ in the denominator by the average diagonal element of $\mA$ \cite{CraWah79a,GolHeaWah79a,Wah90}:
+The \emph{generalized cross-validation} criterion (GCV) replaces the $i^{\text{th}}$ diagonal element of $\mA$ in the denominator by the average diagonal element of $\mA$ \citep{CraWah79a,GolHeaWah79a,Wah90}:
 \begin{equation*} 
@@
 
-Genz \cite{Gen93} introduced a variable transformation to transform \eqref{eqn:GaussDef} into an integral on the unit cube.
+\cite{Gen93} introduced a variable transformation to transform \eqref{eqn:GaussDef} into an integral on the unit cube.
 Not only does this variable transformation accommodate domains that are (semi-)infinite, it also tends to smooth out the integrand better, which expedites the cubature.
@@
 \end{align*}
-The node sets are randomly scrambled Sobol' points \cite{DicEtal14a,DicPil10a}.
+The node sets are randomly scrambled Sobol' points \citep{DicEtal14a,DicPil10a}.
 The results are for 400 randomly chosen $\varepsilon$ in the interval $[10^{-5}, 10^{-2}]$ as shown in \figref{fig:MVN_Metern_d2b2}.
@@
 The choice of generating vector is typically done offline by computer search.
-See \cite{DicEtal14a,HicNie03a} for more on extensible integration lattices.
+See \cite{HicNie03a}  and \cite{DicEtal14a} for more on extensible integration lattices.
 \begin{figure}[htp]
@@
 \end{subequations}
-Symmetric, periodic, positive definite kernels of this form appear in  \cite{DicEtal14a,Hic96a}.  Bernoulli polynomials are described in \cite[Chapter 24]{OlvEtal10a}.
+Symmetric, periodic, positive definite kernels of this form appear in  \cite{Hic96a} and  \cite{DicEtal14a}.  Bernoulli polynomials are described in \cite[Chapter 24]{OlvEtal10a}.
 
@@
 
-Lattice cubature rules are known to have convergence rates that depend on the smoothness of the integrands, but that are rather independent of the choice of the integration lattice \cite{DicEtal14a}.
+Lattice cubature rules are known to have convergence rates that depend on the smoothness of the integrands, but that are rather independent of the choice of the integration lattice \citep{DicEtal14a}.
 Thus, we expect integration lattice node sets to perform well regardless of the smoothness of the covariance kernel.
@@
 
-We have implemented the fast adaptive Bayesian cubature algorithm in MATLAB as part of the Guaranteed Adaptive Integration Library (GAIL) \cite{ChoEtal17b} as \linebreak[4]  \code{cubBayesLattice\_g}.
+We have implemented the fast adaptive Bayesian cubature algorithm in MATLAB as part of the Guaranteed Adaptive Integration Library (GAIL) \citep{ChoEtal19a} as  \code{cubBayesLattice\_g}.
 This algorithm uses the covariance kernel defined in \eqref{eqn:ourkernel} with  $r=1$ and $2$, and the periodizing variable transforms in  \secref{period_var_tx}.
@@
 then $f$ has continuous, periodic mixed partial derivatives of up to order $r$ in each direction.  
-Examples of this kind of transform include \cite{Sid08a}:
+Examples of this kind of transform include \citep{Sid08a}:
 \begin{align*}
@@
 We expect $\abs{\mu - \hmu}/\varepsilon$ to be no greater than one, but hopefully not too much smaller than one, which would indicate a stopping criterion that is too conservative.
+Figures \ref{fig:mvn-guaranteed-MLE} to \ref{fig:optprice-guaranteed-GCV} can be reproduced using the script \break \code{cubBayesLattice\_guaranteed\_plots.m} in GAIL.
 
@@
 This is a technical challenge, not a limitation of our theory.
-
-Figures \ref{fig:mvn-guaranteed-MLE} to \ref{fig:optprice-guaranteed-GCV} can be reproduced using the script \break \code{cubBayesLattice\_guaranteed\_plots.m} in GAIL.
 
@@
 %\bibliography{}   % name your BibTeX data base
+\bibliographystyle{abbrvnat}
 \bibliography{FJHown23,FJH23}
-\bibliographystyle{spmpsci}
 

### 2019-08-17 Submission_Jul29/BayesianCubaturePaper_Jul29_Fred_Jagadees - Rev1c - submission.tex
fix typos

--- 2019-07-30 BayesianCubaturePaper2018 - Rev1c.tex
@@
 %\usepackage{refcheck}  % points out unused labels, refs ...
+% \usepackage[htt]{hyphenat}
 
@@
 
-        \State\label{LoopStart}Generate $\{ \vx_i\}_{i=n' + 1}^{n}$ and sample $\{f(\vx_i)\}_{i=n'+1}^{n}$
+        \State Generate $\{ \vx_i\}_{i=n' + 1}^{n}$ and sample $\{f(\vx_i)\}_{i=n'+1}^{n}$
         \State Compute $\vtheta$ by \eqref{eqn:thetaMLE} or \eqref{vthetaGCV}
@@
 \sqrt{\frac{1}{n(n-1)} \sum_{i=2}^n \frac{\abs{\widetilde{y}_i}^2}{\lambda_i}  \left(\frac{\lambda_1}{n}  - 1  \right)}, \\
-\nonumber
+\label{errGCVSimple}
 \err_{\textup{GCV}} & =
@@
 \left( 1 -  \frac{n}{\lambda_1} \right)  
-\right\}^{1/2}. \label{errGCVSimple}
+\right\}^{1/2}. 
 \end{align}
 \end{subequations}
-In the formulas for the credible interval half-widths, $\vlambda$ depends on $\vtheta$, and  $\vtheta$ is assumed to take on the values $\vtheta_{\MLE}$ or $\vtheta_{\GCV}$ as appropriate.
+In the formulas for the credible interval half-widths and $\vlambda$ depends on $\vtheta$, and  $\vtheta$ is assumed to take on the values $\vtheta_{\MLE}$ or $\vtheta_{\GCV}$ as appropriate.
 \end{theorem}
@@
 
-		\State\label{LoopStart}Generate $\{ \vx_i\}_{i=n' + 1}^{n}$ and sample $\{f(\vx_i)\}_{i=n'+1}^{n}$
+		\State Generate $\{ \vx_i\}_{i=n' + 1}^{n}$ and sample $\{f(\vx_i)\}_{i=n'+1}^{n}$
 		\State Compute $\vtheta$ by \eqref{eqn_MLE_loss_func_optimized_2} or \eqref{thetaGCV}

### 2019-08-17 BayesianCubaturePaper2018-Rev1dRefs.tex

--- 2019-08-17 BayesianCubaturePaper2018-Rev1eRefs.tex
@@
 %
-\usepackage{graphicx}
 \usepackage{natbib}
 \usepackage{xspace}
+\usepackage{graphicx}
 \usepackage{amssymb}
@@
 The algorithm proposed here also relies on discrete Fourier coefficients, but in a different way.
-Although we only explore automatic Bayesian cubature for absolute error tolerances, the recent work by Hickernell, Jim\'enez-Rugama, and Li~\cite{HicEtal17a} suggests how one might accommodate more general error criteria, such as relative error tolerances.
+Although we only explore automatic Bayesian cubature for absolute error tolerances, the recent work by \cite{HicEtal17a} suggests how one might accommodate more general error criteria, such as relative error tolerances.
 
@@
 We expect $\abs{\mu - \hmu}/\varepsilon$ to be no greater than one, but hopefully not too much smaller than one, which would indicate a stopping criterion that is too conservative.
-Figures \ref{fig:mvn-guaranteed-MLE} to \ref{fig:optprice-guaranteed-GCV} can be reproduced using the script \break \code{cubBayesLattice\_guaranteed\_plots.m} in GAIL.
+Figures \ref{fig:mvn-guaranteed-MLE} to \ref{fig:optprice-guaranteed-GCV} can be reproduced using the script \code{cubBayesLattice\_guaranteed\_plots.m} in GAIL.
 

### 2019-11-13 BayesianCubaturePaper2018-Rev1eRefs.tex
final changes sent to Springer for publication

@@
 
-\graphicspath{{.}{./figures/}{D:/Mega/MyWriteupBackup/Sep_2ndweek_1/}}
+\graphicspath{{.}{./figures/grey/}{D:/Mega/MyWriteupBackup/Sep_2ndweek_1/}}
 %\graphicspath{{./figures/}}
@@
 \begin{equation} \label{Clateig}
-    \mC_{\vtheta} = \frac 1n \mV \mLambda_\vtheta \mV^H , \qquad \mV = \mP \mW,
+    \mC_{\vtheta} = \frac 1n \mV \mLambda_\vtheta \mV^H , \qquad \mV = \mP \mW \mP^T,
 \end{equation}
+
 where the eigenvalues of  $\mC_{\vtheta}$ and $\mK_{\vtheta}$ are identical.
@@
 This algorithm uses the covariance kernel defined in \eqref{eqn:ourkernel} with  $r=1$ and $2$, and the periodizing variable transforms in  \secref{period_var_tx}.
-The rank-1 lattice node generator is taken from \cite{Nuy17a}  (\code{exod2\_base2\_m20}).
+The rank-1 lattice node generator is taken from \cite{Nuy17a} \\ (\code{exod2\_base2\_m20}).
 

### 2019-11-13 conv_figures_to_gray.m

@@ -1,0 +1,13 @@
+img_list = dir('D:/Dropbox/BayesianCubatureLatticePaper2018/figures/*.png');
+
+for indx=1:length(img_list)%img_file=img_list(3:1:end)
+  img_file = img_list(indx);
+  % [img_file.folder, '\', img_file.name]
+  img_file.name
+  X = imread([img_file.folder, '\', img_file.name]);
+  newX = rgb2gray(X);
+  imwrite(newX, [img_file.folder, '\grey\', img_file.name],'png')
+end
+
+fprintf('')
+%for testFunArg=testFunArgs(end:-1:1)

### 2019-11-13 programs/plot_fourier_kernel.m

@@ -23,7 +23,7 @@ if dim==1
   for r = order
     for sh = shape_param
       Z(:,i) = kernel(xpts, 2*r, sh, yVal);
-      leg_text{i} = sprintf('$r=%d,\\gamma=%1.1f$', r, sh);
+      leg_text{i} = sprintf('$r=%d,\\eta=%1.1f$', r, sh);
       i=i+1;
     end
   end
